### 2017-12-04 JCP-Manuscript.tex
First version done

\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref}
% package added by zhixuan, not sure whether allowed by JCP or not!
\usepackage{amsmath}
\usepackage{float}

\modulolinenumbers[5]
\journal{Journal of Computational Physics}
%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%
%% Numbered
\bibliographystyle{model1-num-names}
%% Numbered without titles
%\bibliographystyle{model1a-num-names}
%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}
%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}
%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}
%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frontmatter}
\title{Integrating random choice method with SPH : a new scheme with adaptive artificial viscosity and shock capturing ability}
%\tnotetext[mytitlenote]{Can add  title note here}
%% Group authors per affiliation:
\author{Zhixuan Cao}
\author{Abani Patra \fnref{mycorrespondingauthor}}
\address{Department of Mechanical and Aerospace Engineering,The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
\author{E. Bruce Pitman}
\address{Department of Materials Design and Innovation, The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
%\fntext[myfootnote]{Since 1880.}
%% or include affiliations in footnotes:
%\author[mymainaddress,mysecondaryaddress]%{Elsevier Inc}
%\ead[url]{www.elsevier.com}
%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Abani Patra}
\ead{abani@buffalo.edu}
%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}
\begin{abstract}
Standard smoothed particle hydrodynamics (SPH) employs an artificial viscosity, defined explicitly by constant coefficients, to properly capture hydrodynamic shock waves.
Such methodology usually provides dissipation more than need and smears the discontinuity if the artificial viscosity coefficients are not tuned.
Excessively large artificial viscosity might also damp generation of turbulence by fluid instability.
We present in this article a novel SPH scheme with adaptive artificial viscosity, in which the artificial viscosity is determined implicitly based on solution of a local Riemann problem. Different from Godunov SPH (GSPH) method, which utilizing solution of local Riemann problem at an imaginary interface, the new method randomly sample the solution of Riemann problem mimicking the random choice method (RCM). One dimensional shock tube tests demonstrate several attractive features of this new scheme. First of all, it introduces less but sufficient artificial dissipation for shock capturing compared with classical SPH and GSPH. The pressure ``wiggles" around contact discontinuity, which persists in SPH results, is eliminated by the new scheme. It also shows higher order convergence than GSPH.
%when the same construction of local Riemann problem and Riemann solvers are adopted by both methods. 
Combining of RCM with SPH overcomes the inability of classical RCM method in solving multi-dimensional unsteady non-linear systems. Three dimensional time dependent compressible Euler equations are solved for simulating a free jet flow, demonstrating that the desirable less dissipation property of the new scheme persists in multi-dimensional applications.
\end{abstract}
\begin{keyword}
Smoothed Particle Hydrodynamics (SPH), Random Choice Method (RCM), Riemann Solver, Hyperbolic PDEs, Godunov's method
\end{keyword}
\end{frontmatter}

\linenumbers
\section{Introduction}
Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on Lagrangian formulation, and has been widely applied to different areas in engineering and science. SPH has both advantages and disadvantages with respect to other numerical techniques. One main advantage is that it automatically adapts to following dynamic flows and arbitrary geometries. Another advantage is that it needs less programming effort to include more physics. In addition, SPH particles only interact with neighboring particles, which avoids massive global communication in parallel implementation of SPH.
Historically, SPH has difficulty in capturing discontinuities, such as shocks or contact discontinuities. Inviscid description of fluids becomes invalid at shock fronts, where specific entropy of the fluids increases through the conversion of mechanical energy into internal energy. Most SPH codes have included an artificial viscosity term explicitly, both for stabilizing the simulation and for handling shock discontinuities by dissipating local velocity differences and converting them into heat \citep{monaghan1983shock, monaghan1997sph, klapp2012strong}. Without knowing the minimum amount of dissipation for shock capturing, such methodology usually provides dissipation more than need and smears the discontinuity if the artificial viscosity coefficients are not tuned. The method of using constant artificial viscosity might also introduce spurious effects at region away from shocks, for instance, causing an unphysical damping of turbulent mixing (as shown, for example, by \citet{borgani2012hydrodynamic}) or spurious
shearing torques in rotating flows \citep{flebbe1994smoothed}. Selective application of artificial viscosity techniques, such as the time dependent viscosity \citep{morris1997switch, dolag2005turbulent} and shock-indicator-based viscosity \citep{cullen2010inviscid} have been tried for counteracting this. 
\citet{sigalotti2008adaptive} improved the standard SPH near sharp discontinuities adopting an adaptive density kernel estimation (ADKE) techniques. However, the parameters for ADKE have to be tuned to the problem at hand. Hence it is hard to implement ADKE in real applications.

Besides adding dissipation explicitly, \citet{inutsuka2002reformulation} proposed an innovative approach to introduce dissipation implicitly by reformulating the SPH convolution integrals. Artificial viscosity is introduced implicitly by using iterative solution to a Riemann problem at an imaginary interface between an interacting particles pair. This method, named as Godunov SPH (GSPH), is attractive because it eliminates parameterization and hence user intervention associated with artificial viscosity coefficients. The GSPH method has been shown to be able to handle shock discontinuities \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate}, introduces less damping to turbulent mixing \citep{cha2010kelvin, borgani2012hydrodynamic} than standard SPH, and relieve pressure ``blips" (or ``wiggles" called by others) at the contact discontinuity \citep{borgani2012hydrodynamic}. However, the amount of dissipation introduced by GSPH is stll excessive than needs. When using a linear interpolation of the volume function, it has been shown \citep{borgani2012hydrodynamic} that the excess of diffusion, which manifests itself in the shock tube tests as a smooth transition at the rarefaction fan, is such to prevent the development of the Kelvin-Helmholtz (KH) instability.
%The development of KH instability is also significantly affected by number of neighbouring particles for cubic interpolation of the volume function.

The random choice method (RCM) was introduced by \citet{glimm1965solutions} for the construction of solutions of systems of nonlinear hyperbolic conservation laws. \citet{chorin1976random} developed the RCM as a practical computational method for solutions to one dimensional (1D) Euler equations of gas dynamics. Chorin's work was followed by numerous researchers, with applications and further improvements \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical}. In essence, the solution is advanced in time by a sequence of operations that includes the solution of Riemann problems and a stochastic sampling procedure. When applied to one dimensional time dependent Euler equations \citep{colella1982glimm}, diffusive errors from spatial averaging are completely eliminated and hence discontinuities, such as shocks or material interface, can be resolved as true discontinuities.
For unsteady flows in genuine two (or higher) space dimensions, however, such very desirable property of RCM do not seem to persist \citep{colella1982glimm}. Implementing of RCM within the framework of SPH only involves sampling of solutions of Riemann problem in 1D local coordinate system no matter what is the dimensionality of the problem. Hence desirable property of RCM method in 1D should be retained in higher dimensional implementations within the framework of SPH. This hypothesis is confirmed by a three-dimensional (3D) free jet flow simulation.
%This need to be proven ---> But at least, if the good property of preserving true discontinuity is still valid in 1D shock tube problem, it should be preserved in multiple-dimensional implementations. Because in current framework of RSPH, no matter what is the dimension of the problem, the techniques is only implemented in a one-dimensional scenario.

In this investigation, we introduce a new method, which will be referred to as RSPH in later paragraph, by integrating RCM method within framework of SPH. 
The new scheme inherits the attraction of classical RCM introducing less but sufficient artificial viscosity and causing less smearing of discontinuities than other methods for 1D problems. 
For multi-dimensional problem, RCM method is implemented within one-dimensional local coordinate system, established for pair of interacting particles. So no multi-dimensional coordinate is involved even for multi-dimensional problems. Thereby, the attractive properties of less dissipation showing in one-dimensional case is preserved in multi-dimensional implementations. In this way, the RSPH overcomes RCM's fundamental limitation of losing attractive property showing in 1D in higher dimensional application.

RSPH has the following advantages over standard SPH:
\begin{itemize}
\item RSPH is able to capture discontinuities with less smearing.
\item The RSPH is able to adaptively adjust equivalent artificial viscosity coefficients, assigning larger artificial viscosity coefficients around the shock and small artificial viscosity coefficients otherwhere.
\item RSPH is able to suppress pressure ``wiggles" at the contact discontinuity, a common issue in classical SPH.
\end{itemize}
Compared with GSPH, which is also based on solution of local Riemann problem, RSPH introduces less but sufficient dissipation than GSPH, especially in the region away from shocks. Such feature of RSPH is especially beneficial for simulating of scenarios involving turbulence mixing, for which excessive dissipation would suppress mixing. In addition, RSPH also shows faster convergence rate than GSPH.

The scheme of this paper is follows. We start with a brief review of standard SPH and GSPH in the second section. The RSPH is then explained in details in the third section followed by the numerical tests section, where both one 1D and 3D inviscid Euler equations (see Eq. (\ref{eq:gov-cs-rho}) - (\ref{eq:gov-cs-e}) are solved by standard SPH, GSPH and RSPH. Limitations and potential applications of RSPH are discussed in last section.

Our investigation focuses on implementation of the RSPH schemeit in solving inviscid compressile Euler equations .  
\begin{align}
\dfrac{\partial \rho}{\partial t} + \nabla \cdot \left(\rho \textbf{v} \right) = 0 \label{eq:gov-cs-rho} \\
\dfrac{\partial \rho \textbf{v}}{\partial t} + \nabla \cdot \left(\rho \textbf{v} \textbf{v} + p\textbf{I}\right) = 0 \label{eq:gov-cs-v} \\
\dfrac{\partial \rho E}{\partial t} + \nabla \cdot \left[\left(\rho E + p \right)\textbf{v}\right] = 0 \label{eq:gov-cs-e}
\end{align}
where $\rho$ is the density, $\textbf{v}$ is the velocity, $\textbf{I}$ is a unit tensor.
$E = e + K $ is the total energy which is a summation of kinetic energy $K$ and internal energy $e$.
The system of equations is closed by equation of state (EOS) for idea gas.
\begin{equation}
p = \left(\gamma - 1\right)\rho e \label{eq:EOS}
\end{equation}
with $\gamma=1.4$.

For any SPH scheme, governing equations in Lagrange form are needed. By deducting kinetic energy from energy equation, subtracting mass conservation from momentum equation, combining transient term and advection term into material derivative (for any function $A$, material derivative is defined as $\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$) term, the governing equations are put into the final form. 
\begin{align}
\dfrac{D \rho}{D t} + \rho \nabla \cdot \textbf{v} = 0 \label{eq:gov-nc-rho}\\
\dfrac{D \textbf{v}}{D t} + \dfrac{\nabla P}{\rho} =0 \label{eq:gov-nc-v}\\
\dfrac{D e}{D t} + \dfrac{P \nabla \cdot \textbf{v}}{\rho} = 0 \label{eq:gov-nc-e}
\end{align}
%\cutet{puri2014comparison} propose an addition of an artificial heating term to the GSPH scheme to eliminate unphysical spikes in the thermal energy at the contact discontinuity.  --> It is worthwhile to check whether RSPH is able to avoid this phenomena without using his techniques.
%Another issue of RCM: the very desirable properties of RCM: no diffusive errors from spatial averaging do not seem to persist for flows in two space dimensions. For two dimensional steady supersonic flow, one of the space variables can be treated as a time-like one and RCM can be applied in a way similar to that for one-dimensional unsteady flow.
%--Then what about RSPH?

\section{Standard SPH and GSPH method}
The RSPH method is based on standard SPH and GSPH. In addition, these three methods will be compared in the numerical tests section. So it is necessary to review discretization of the compressible Euler equations by SPH and GSPH. We present here a brief review on standard SPH and GSPH providing corresponding discretized governing equations.

\subsection{Standard SPH method}
In SPH, the domain is discretized by a set of particles or discretization points and the position of each particle is updated at every time step based on the motion computed. Approximation of all field variables (velocity, density and pressure, ect.) is obtained by interpolation based on discretization points. The physical laws (such as conservation laws of mass, momentum and energy) written in the form of partial differential equations (PDEs) or ordinary differential equations (ODEs) need to be transformed into the Lagrangian particle formalism of SPH. Using a kernel function that provides the weighted estimation of the field variables at any point, the integral equations are estimated as sums over particles in a compact subdomain defined by the support of the kernel function associated with the discretization points. Thus, field variables associated to the particle are updated based on its neighbors. Each kernel function has a compact support determined by smoothing length of the particle. Various tricks can be used to conserve linear and angular momentum and thermal energy \citep{monaghan1992smoothed}. Special treatments are also needed for second order derivative terms \citep{monaghan2005smoothed}. We only refer here to one of these possible discretization of compressible Euler equations, while we refer to \citet{ monaghan2005smoothed, liu2010smoothed, price2012smoothed} for complete formal derivation and other discretization formulations.
\begin{align}
<\rho_a> = \sum_b m_b w_{ab} \left(h\right) \label{eq:ns-sph-d} \\
\left\langle\dfrac{d \textbf{v}_a}{d t}\right\rangle = -\sum_b m_b \left(\dfrac{p_b}{\rho_b^2} + \dfrac{p_a}{\rho_a^2} + \Pi_{ab}\right) \nabla_a w_{a b}\left(h\right) \label{eq:ns-sph-v} \\
\left\langle\dfrac{d e_a}{d t}\right\rangle=
 0.5\sum_b m_b \textbf{v}_{a b}\left(\dfrac{p_b}{\rho_b^2} + \dfrac{p_a}{\rho_a^2} + \Pi_{ab}\right) \cdot \nabla_a w_{a b}\left(h\right) \label{eq:ns-sph-e}
\end{align}
where, $a$ is the SPH particle index, $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$. $\Pi$ is an artificial viscosity term.
One of commonly used models of artificial viscosity \citep{monaghan1983shock} is:
\begin{equation}
\Pi_{ab}=- \frac{\nu}{\bar{\rho}_{ab}} \dfrac{ \textbf{v}_{ab} \cdot \textbf{x}_{ab}}{\textbf{x}_{ab}^2 + \left(\eta h\right)^2}
\label{eq:art-vis-original}
\end{equation}
The coefficient $\nu$ is defined as:
\begin{equation}
\nu = \alpha \bar{h}_{ab} \bar{c}_{ab}
\end{equation}
where 
\begin{align}
\bar{c}_{ab} = \dfrac{c_a + c_b}{2} \\
\bar{\rho}_{ab} = \dfrac{\rho_a + \rho_b}{2} \\
\textbf{x}_{ab}=\textbf{x}_a-\textbf{x}_b
\end{align}
The artificial viscosity term $\Pi_{ab}$ is a Galilean invariant and vanishes for rigid rotation. It produces a repulsive force between two particles when they are approaching each other and an attractive force when they are receding from each other.
An extra term was added to $\nu$ considering aspects of the dissipative term in shock solutions based on Riemann solvers and lead to a new formulation of artificial viscosity \citep{monaghan1992smoothed}. We adopt this new formulation in our simulation:
\begin{equation}
\Pi_{ab}^{\beta} = 
\begin{cases} 
      \dfrac{- \alpha \mu_{ab} \bar{c}_{ab} + \beta \mu_{ab}^2} {\bar{\rho}_{ab}} & \textbf{v}_{ab} \cdot \textbf{x}_{ab} < 0\\
      0 & \textbf{v}_{ab} \cdot \textbf{x}_{ab} > 0
\end{cases}
\label{eq:art-vis-shock}
\end{equation}
where
\begin{equation}
\mu_{ab} = \dfrac{h \textbf{v}_{ab} \cdot \textbf{x}_{ab}}{\textbf{x}_{ab}^2 + \left(\eta h\right)^2} 
\end{equation}
%$\alpha$ and $\beta$ are two parameters that are free to be adjusted for each case. 
$\alpha$ and $\beta$ are two parameters that can be adjusted for different cases.
$\alpha = 1$ and $\beta = 2$ are recommended \citep{monaghan2005smoothed} for best results and mostly adopted. In the numerical test section, these two parameters are varied to show the effect of them. $\eta$ is usually taken as 0.1 to prevent singularities.

In Eq. (\ref{eq:ns-sph-d}) - Eq. (\ref{eq:ns-sph-e}), $w_{a b}\left(h\right)$ is weighting function and is a concise form of $w\left(\textbf{x}_a - \textbf{x}_b, h\right)$. From here on, we will use this concise form.
There is a wide variety of possible weighting functions, such as spline functions (with different orders) and Gaussian functions. We adopt a truncated Gaussian function as the weighting function for standard SPH, GSPH and RSPH.
\begin{equation}
w\left(\textbf{x} - \textbf{x} \prime \right) = 
\begin{cases} 
      \dfrac{1}{\left(h \sqrt{\pi}\right)^d} exp \left[- \left(\dfrac{\textbf{x} - \textbf{x} \prime}{h} \right)^2 \right] &  \vert \textbf{x} - \textbf{x} \prime \vert \leq 3h\\
      0 & \text{Otherwise}
\end{cases}
\label{eq:SPH-kernel}
\end{equation}
where $d$ is number of dimensions.
The derivative of the weighting function is:
\begin{equation}
\nabla w\left(\textbf{x} - \textbf{x} \prime \right) = 
\begin{cases} 
      -2\left(\dfrac{\textbf{x} - \textbf{x} \prime}{h}\right) \dfrac{1}{\left(h \sqrt{\pi}\right)^d} exp \left[- \left(\dfrac{\textbf{x} - \textbf{x} \prime}{h}\right)^2 \right] &  \vert \textbf{x} - \textbf{x} \prime \vert \leq 3h\\
      0 & \text{Otherwise}
\end{cases}
\label{eq:SPH-kernel-gradient}
\end{equation}

As a Lagrangian method, particle position is also updated at every time step according to:
\begin{equation}
\left\langle\dfrac{d \textbf{x}_a}{dt}\right\rangle = \textbf{v}_a \label{eq:SPH-update-pos}
\end{equation}

\subsection{GSPH method}
Here we present essential formulations for solving Euler equations with GSPH. The density field is updated in the same way as updating of density in SPH, according to Eq. (\ref{eq:ns-sph-d}). Updating of velocity and internal energy in GSPH is different from these in SPH. 
Derivation of discretized momentum and energy equation in first GSPH paper \citep{inutsuka2002reformulation} is based on the following discrete consistency identities: 
\begin{equation}
1=\sum_{b} \frac{m_{b}}{\rho(\textbf{x})}w(\textbf{x} - \textbf{x}_{b}, h)
\label{eq:GSPH-basic1}
\end{equation}
\begin{equation}
0=\sum_{b} m_{b} \nabla \frac{w(\textbf{x} - \textbf{x}_{b}, h)}{\rho(\textbf{x})}
\label{eq:GSPH-basic2}
\end{equation}
Lengthy algebraic manipulations \citep{inutsuka2002reformulation,iwasaki2011smoothed} lead to the discretized momentum and energy equations:
\begin{equation}
\ddot{\textbf{x}}_{a} = <\dfrac{d \textbf{v}_{a}}{dt}>= -\sum_{b} m_{b} p_{a b}^{\ast} \left[\frac{1}{\rho_{a}^2} \nabla w_{a b}(h_{a}) + \frac{1}{\rho_{b}^2} \nabla w_{a b}(h_{b}) \right]
\label{eq:gov-gsph-v-simple-form}
\end{equation}
\begin{equation}
<\dfrac{d e_{a}}{dt}>= - \sum_{b} m_{b} p_{a b}^{\ast} [\textbf{v}_{a b}^{\ast} - \dot{\textbf{x}}_{a}^{\ast}] \left[\frac{1}{\rho_{a}^2} \nabla w_{a b}(h_{a}) + \frac{1}{\rho_{b}^2} \nabla w_{a b}(h_{b}) \right]
\label{eq:gov-gsph-e-simple-form}
\end{equation}
where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are obtained by solving a 1D Riemann problem constructed based on physical quantity of particle $a$ and particle $b$. The starred quantity  are interpolated value of the solution of the Riemann problem at an imaginary interface $q^{\ast}_{ab}$.
$\dot{\textbf{x}}_{a}^{\ast}$ is time centered velocity of particle $a$:
\begin{equation}
\dot{\textbf{x}}_{a}^{\ast} = <\textbf{v}_{a}> + \frac{\Delta t}{2} \ddot{\textbf{x}}_{a}
\end{equation}

The difference between this formulation and classical SPH formulations come from two sources: 
\begin{itemize}
\item the averaged (in certain sense) pressure and the effect of artificial viscosity is replaced by  $p^{\ast}$, obtained based on a local Riemann solver.
\item A time centered velocity is used, which satisfies the following identities approximately. 
\begin{equation}
\left( \textbf{v}_{a b}^{\ast} - \dot{\textbf{x}}_{a}^{\ast} \right) \approx -0.5 \textbf{v}_{a b}
\label{eq:SPH-GSPH-difference2}
\end{equation}
Where $\textbf{v}_{a b}$ is defined as $\textbf{v}_a - \textbf{v}_b$.
\end{itemize}
Actually, Godunov's idea of using Riemann solver can be combined with other SPH discretization formulations \citep{cha2003implementations}.

To conduct a well controlled comparison, the constructing of Riemann problem, Riemann solvers and projection of picked solution of Riemann problem back to global coordinate system are exactly the same in GSPH and RSPH, details of which will be described in detail in the next section. The way how solutions of Riemann problems are used is the only difference between GSPH and RSPH in our test. While RSPH takes solution of Riemann problem based on random sampling, solution of Riemann problem at an imaginary interface is picked up in GSPH, either based on interpolation of specific volume \citep{inutsuka2002reformulation} or simply assuming the middle point as the interface \citep{cha2003implementations}.

\section{RSPH method}
RSPH shares many commonality with SPH and GSPH, especially with GSPH. We adopt the same density updating formulation (see Eq. (\ref{eq:ns-sph-d})) for density updating in SPH, GSPH and RSPH. The same kernel function is used for all schemes. The equation for updating particle position (see Eq. (\ref{eq:SPH-update-pos})) is also the same for all schemes. Discretized governing equation for RSPH and GSPH are exactly the same while the way to determine $p^{\ast}$ and $\textbf{v}^{\ast}$ are different. We focus more on where RSPH is different from SPH and GSPH in this section.

For mesh based method, there is a great deal of commonality between Godunov's method and RCM. Both of them utilize the solution of a local Riemann problem. The RCM pick up a single state contained in the local solutions ``randomly" while Godunov's method take the integral average. 
%The random selection procedure is carried out by employing a sequence of random numbers. 
GSPH, however, does not take the integral average. Instead, a single state of the local Riemann solution at an imaginary interface is picked up and used to upgrade physical quantities through discretized governing equations (see Eq. (\ref{eq:gov-gsph-v-simple-form}) - Eq. (\ref{eq:gov-gsph-e-simple-form})). So the difference between RSPH and GSPH is how to pick up the single state from solution to Riemann problem. RSPH pick up the single state by stochastic sampling while GSPH chooses the single state at an imaginary interface.

Since the only difference between Godunov's method and RCM is how the solution of local Riemann problem is utilized, we can use exact the same discretization in RSPH as in GSPH. In addition, the construction of 1D Riemann problem for RSPH is the same as piecewise constant construction of Riemann problem in GSPH. In this paper, we adopt piecewise constant construction of Riemann problem for both RSPH and GSPH.
It is a common practice in real implementation of Godunov's method to use approximate non-iterative Riemann solvers due to high computational cost associated with iterative Riemann solvers. Therefore, in this paper, two non-iterative Riemann solvers, Roe Riemann solver and HLLC Riemann solver \citep{toro1994restoration}, are used in GSPH. The HLLC type of Riemann solver \citep{toro1994restoration}, in which the contact wave is considered, is used in RSPH.

\subsection{Defining of local 1D Riemann problem}
A 1D Riemann problem need to be solved to obtain  $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ for both GSPH and RSPH. Hence, a 1D Riemann problem need to be constructed first. Constructing of 1D Riemann problem starts from establishing of a local coordinate systems ($q$). The origin is selected at the middle-point of the line segment joining two particles with the unit vector along the line defined as: 
\begin{equation}
\hat{r}_{a b}= \frac{\textbf{v}_{a} - \textbf{v}_{ b}}{|\textbf{x}_{a} - \textbf{x}_{ b}|}
\end{equation}
Then vector variables, such as velocity, need to be projected onto the local coordinate system (Eq. (\ref{eq:RP-project-2-local-a}) and Eq. (\ref{eq:RP-project-2-local-b})). 
\begin{equation}
u_{a}= \textbf{v}_{a} \cdot \hat{r}_{a b}
\label{eq:RP-project-2-local-a}
\end{equation}
\begin{equation}
u_{b}= \textbf{v}_{b} \cdot \hat{r}_{a b}
\label{eq:RP-project-2-local-b}
\end{equation}
Scalar variables are simply assigned to corresponding points without projection.

In original Godunov's SPH method, the construction of Riemann problem is divided into two sub-steps: projection and construction. 
Different from original Godunov's method, which assumes piecewise linear distribution of the data (or higher order method like MUSCL and PPM which use higher order polynomial approximation.), RCM method assumes that the given data at the center of cell is constant throughout the respective cell. The same idea can be easily (and naturally) applied in RSPH, as there is actually no ``cell interface" in SPH method.
In this case, no additional step for constructing a Riemann problem is needed as the Riemann problem is constructed in a ``piece wise constant" manner. So the Riemann problem is defined directly based on data on particles. There is no need to calculate and project first order derivative of $\rho$, $u$ and $p$, which are needed for constructing of Riemann problem in a piece wise linear manner. The computation associated with calculation of gradient and projection of gradient is avoided when constructing 1D Riemann problem in a ``piece wise constant" manner.
Per above description, the Riemann problem definied by initial states at left and right sides are: 
\begin{eqnarray}
\rho_L = \rho_b 
\label{eq:Riemann-Prob-define-L-rho} \\
u_L = u_b 
\label{eq:Riemann-Prob-define-L-v} \\
p_L = p_b 
\label{eq:Riemann-Prob-define-L-p}
\end{eqnarray}
\begin{eqnarray}
\rho_R = \rho_a 
\label{eq:Riemann-Prob-define-R-rho} \\
u_R = u_a 
\label{eq:Riemann-Prob-define-R-v} \\
p_R = p_a 
\label{eq:Riemann-Prob-define-R-p}
\end{eqnarray}

\subsection{Approximate Riemann solvers}
The starred variable $p^{\ast}$ and $u^{\ast}$ represent the interpolated pressure and velocity at the some point (an imaginary interface in GSPH or a randomly sampled poit in RSPH) along the line joining the pairs of two particles. They do not have to be obtained by solving a Riemann problem. However, $p^{\ast}$ and $u^{\ast}$ obtained by solving a Riemann problem provides necessary and sufficient dissipation needed to stabilize the scheme.
%From numerical analysis point of view, numerical dissipation is necessary for numerical stability. From physics point of view, viscosity is a necessary condition for shock formation. But Euler equations are based on assumption of inviscid, which means Euler equation themselves are not capable to represent shock formation correctly. Adding of artificial viscosity helps fix the ``birth defect" of Euler equations.

The exact Riemann solver, even though more accurate and robust, requires an iterative root finding, and hence is computational inefficient. For governing equations other than well studied ones, such as Euler equation, there is no iterative Riemann solver available. Non-iterative approximate Riemann solvers can relieve these drawbacks of exact Riemann solvers. Among the available Riemann solvers \citep{rider1994review, luo2004computation, puri2014approximate}, we adopted the Harten, Lax and van Keer scheme with contact (HLLC).
The HLLC solver is a 3-wave approximate Riemann solver proposed by \citet{toro1994restoration}. In this work, we adopt the formulation of the HLLC solver proposed by \citet{luo2004computation} for multi-material, underwater explosions in their ALE scheme. This Riemann solver has the properties of being positivity preserving for scalar quantities, entropy satisfying and to exact preserve isolated contacts.

The expression for intermediate pressure and velocity can be written as \citep{puri2014approximate}:
\begin{equation}
p^{\ast} =  \begin{cases} 
      p_L & if \  S_L > 0 \\
      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) M_L + (\hat{p}- p_L) \right] + \hat{p} & if \  S_L \leq 0 \leq S_M \\
      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) M_R + (\hat{p}- p_R) \right] + \hat{p} & if \  S_M \leq 0 \leq S_R\\
      p_R & if \  S_R < 0
\end{cases}
\label{eq:RP_solver_HLLC_u}
\end{equation}
\begin{equation}
(pu)^{\ast} =  \begin{cases} 
      p_L u_L& if \  S_L > 0 \\
      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) E_L + (\hat{p} S_M - p_L \hat{u}_L) \right] + (S_M - \hat{u}_{LR}) \hat{p} & if \  S_L \leq 0 \leq S_M \\
      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) E_R + (\hat{p} S_M- p_R \hat{u}_R) \right] + (S_M + \hat{u}_{LR}) \hat{p} & if \ S_M \leq 0 \leq S_R\\
      p_R u_R & if \  S_R < 0
\end{cases}
\label{eq:RP_solver_HLLC_pu}
\end{equation}
where $\hat{u}_{LR}$ is the interface velocity and is taken as the Roe-averaged velocity on either side of the interface. The quantities of $\hat{u}_R$ and $\hat{u}_L$ are velocities relative to the interface velocity.
\begin{equation}
\hat{p}= \rho_L (\hat{u}_L - S_L) (\hat{u}_L - S_M) + p_L
\end{equation}
One formulation to approximate the signal speeds $S_M$, $S_L$ and $S_R$ is given by Eq. (\ref{eq:RP-solver-HLLC-SM}) to (\ref{eq:RP-solver-HLLC-SR}).
\begin{eqnarray}
S_M= \frac{\rho_R \hat{u}_R (S_R - \hat{u}_R) - \rho_L \hat{u}_L (S_L - \hat{u}_L) + p_L - p_R}{\rho_R (S_R - \hat{u}_R) - \rho_L (S_L - \hat{u}_L)} \label{eq:RP-solver-HLLC-SM} \\
S_L = min (\hat{u}_L - c_L, -c_{LR}) \label{eq:RP-solver-HLLC-SL} \\
S_R = max (\hat{u}_R - c_R, c_{LR}) \label{eq:RP-solver-HLLC-SR}
\end{eqnarray}
where $c_{LR}$ is the relevant Roe averaged sound speed.

Besides HLLC, another 2-wave approximate Riemann solver, the Roe Riemann solver \citep{roe1981approximate}, is also adopted in GSPH for comparison.
Roe Riemann solver is proposed by \citet{roe1981approximate} to linearize the Euler equations and approxiamte the solution of non-linear system by a system of linear equations. The characteristic decomposition of the linearized Lagrangian flux and Jacobia matrices are used to write the flux. \citet{rider1994review} proposed an algebraic averaging of the Lagrangian variables, which is adopted in this work. The resulting intermediate states for the pressure and velocity are: 
\begin{eqnarray}
u^{\ast} = \frac{1}{2} \left[ u_L + u_R - \frac{1}{C_{LR}} (p_R - p_L) \right] \label{eq:RP-solver-ROE-u} \\
p^{\ast} = \frac{1}{2}\left[ p_L + p_R - C_{LR} (u_R - u_L) \right] \label{eq:RP-solver-ROE-p}
\end{eqnarray}
Where $C_{LR}$ is the averaged Lagarangian sound speed at the interface.
\begin{equation}
C_{LR} = \sqrt{\gamma p_{LR} \rho_{LR}}
\end{equation}

\subsection{Picking up a single state}
Solving the 1D Riemann problem with initial right and left states that the same as those on the paired particles leads to a solution of the local system. Then random sample these solutions to pick up a single state and assign its corresponding state to $p^{\ast}$ and $u^{\ast}$. 
Assume the solution between of a pair of particles ($a$ and $b$) to be $\textbf{W} (q) \forall q \in [q_a, q_b]$ (note, we use $\textbf{W}$ to represent the primitive variable vector $[\rho, u, p]^T$ and $\textbf{U}$ for conservative variable vector  $[\rho, \rho u, \rho E]^T$). The starred values would depend on the random number $\epsilon$.
\begin{equation}
p^{\ast} = p \left(\epsilon \left( q_a - q_b \right) \right)
\label{eq:RSPH-Random-Pick-p}
\end{equation}
\begin{equation}
u^{\ast} = u \left(\epsilon \left( q_a - q_b \right) \right)
\label{eq:RSPH-Random-Pick-u}
\end{equation}
A short comments regarding the difference between application of RCM method in SPH and its application in finite volume method. In finite volume method, the superposition of solutions of Riemann problems defined on boundaries is taken as local solution within the cell and the sampled single state is assigned to the cell center. In RSPH, only one Riemann problem is defined between two particles and the sampled single state (the $p^{\ast}$ and $u^{\ast}$) is used in momentum and energy updating.
Then it needs to project $u^{\ast}$ back to the 3D coordinate system to obtain $\textbf{v}^{\ast}$. One of such back-project approximations is:
\begin{equation}
\textbf{v}^{\ast}_{a b}=u^{\ast}_{a b} \hat{\textbf{r}}_{a b} + \left [\frac{\textbf{v}_{a} + \textbf{v}_{b}}{2} - \frac{u_L + u_R}{2} \hat{\textbf{r}}_{a b}\right]
\label{eq:RP-project-to-3d-arithmetic}
\end{equation}
In Eq. (\ref{eq:RP-project-to-3d-arithmetic}), the arithmetic average of shear velocity is taken as the shear velocity in the star region. Alternative approximation might be distance weighted average or Roe average (weighted by square root of density). If $q_{a b}^{\ast}$ is assumed to be zero, then distance weighted average will degenerate to the arithmetic average.
%Eigenstructure analysis shows that there are two additional contact discontinuity waves for 3D Euler equations. They are associated to two shear velocity components. Different from $u$ and $p$, the shear velocity is not constant in the star region. Using the average of left and right shear velocity as an approximate of shear velocity in the star region might be a poor approximation.
We have to mention that it is strange in GSPH to assume an imaginary interface, which we never need in RSPH. And that's one of the reasons why we like RSPH more.

\subsection{Binary Van Der Corput pseudo-random numbers}
The random number $\epsilon$ is used to determine which single state ($p^{\ast}$ and $\textbf{v}^{\ast}$) of the solution of Riemann problem should be used in Eq. (\ref{eq:gov-gsph-v-simple-form}) and (\ref{eq:gov-gsph-e-simple-form}). The quantity of the computed RCM solution depends crucially on the random number $\{\epsilon ^n\}$. We adopt the Van Der Corupt pseudo-random number sequence \citep{hammersley2013monte} in this investigation following \citet{colella1982glimm}.

A general Van Der Corupt pseudo-random number sequence depends on two parameters $x_1$ and $x_2$ with $x_1 > x_2 > 0$, both are integer and relatively prime. The sequence is formally defined as \citep{hammersley2013monte}:
\begin{equation}
\epsilon ^n = \sum_{i=0}^{s} H_i x_1^{-(i+1)}
\label{eq:Van-Der-Corput-pseudo-random-num}
\end{equation}
where
\begin{equation}
H_i = x_2 a_i(mod \ x_1)
\label{eq:Van-Der-Corput-pseudo-random-num-Hi}
\end{equation} 
\begin{equation}
n = \sum_{i=0}^{s} a_i x_1^i
\label{eq:Van-Der-Corput-pseudo-random-num-n}
\end{equation} 
Equation (\ref{eq:Van-Der-Corput-pseudo-random-num-n}) gives the binary expansion of n when we take $x_1$ as $2$. For example,
\begin{equation}
5=1 \times 2^0 + 0 \times 2^1 + 1 \times 2^2
\end{equation}
with $m=2$.

The next stage is to find the coefficient $H_i$ according to Eq. (\ref{eq:Van-Der-Corput-pseudo-random-num-Hi}). If we take $x_2 = 1$, for which case, $H_i = a_i, \ \forall i$. Having $H_i$, $x_1$ and $s$ ready, the random number $\epsilon ^n $ can be easily obtained according to Eq. (\ref{eq:Van-Der-Corput-pseudo-random-num}).
We take $x_1=2$  and $x_2 =1$ in our application. Other combinations of $x_1$ and $x_2$ were also discussed by \citet{toro2013riemann}. A desirable statistical property of the sequence $\{\epsilon ^n\}$ is that $\{\epsilon ^n\}$ be uniformly distributed over $[0,1]$.

The arithmetic mean and the standard deviation of 200 binary Van Der Corput pseudo-random numbers are $0.49459$ and $0.28885$. The chi-square statistic (see \citet{toro2013riemann} for its calculation) $\chi_{sq}$ is $1.0000$. 
The binary Van Der Corput pseudo-random numbers can be generated offline to save computational time.

%\subsection{Convergence}

\subsection{RSPH algorithm (the PESB algorithm)}
The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm. 
\begin{itemize}
\item For any two pair of particles, establish a local coordinate system whose axis joints these two particles then project the primitive variables vector onto the local coordinate system.
\item Evolve the hyperbolic equation exactly or approximately with Riemann problem defined by the projected data to obtain a solution between these two particles.
\item Sample these solutions between the particles pair to pick up a state and assign it to $p^{\ast}$ and $u^{\ast}$
\item Project $p^{\ast}$ and $u^{\ast}$ from local coordinate system back to the global coordinate system obtaining $p^{\ast}$ and $\textbf{v}^{\ast}$.
\end{itemize}
PESB algorithm is integrated into framework of SPH discretization to update physical quantities in time.

\section{Numerical tests}
We carry out several numerical tests using SPH, RSPH and GSPH in this section.
1D shock tube tests are conducted to compare standard SPH, GSPH and RSPH. Comprehensive shock tube tests are also conducted to check the capacity of RSPH for different situations. In addition, order of accuracy is investigated based on 1D shock tube problem. 
In the last subsection, a 3D free jet flow is simulated with SPH, GSPH and RSPH to check equivalent overall dissipation introduced by each method.

Input parameters for 1D tests can be found in Table \ref{tab:1D-shock-input_parameters}. 
\begin{table}[htp]
\centering
      \caption{Overview of 1D shock tube tests}		
	  \begin{tabular}{lrrrrrrrrrr}
	    \hline
	          & $\rho_L$ & $p_L$ &$v_L$ & $\rho_R$ & $p_R$ &$v_R$ & $m$ & $[x_L, x_R]$ & $t_f$\\
	    \hline
	    Test 1 & $1.0$ & $1.0$ &$0$ & $0.25$ & $0.1795$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.17$\\
	    	Test 2 & $1.0$ & $1.0$ &$0$ & $0.5$ & $0.2$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.2$\\
	    	Test 3 & $2.0$ & $1.95$ &$1.0$ & $1.0$ & $1.95$ &$-1.0$  & $0.006$  & $[-0.4, 0.4]$ & $0.13$\\
	    Test 4 & $1.0$ & $2.4$ &$8.0$ & $0.5$ & $0.4$ &$-0.25$ & $0.003$  & $[-0.4, 0.4]$ & $0.05$\\
	    	Test 5 & $1.0$ & $-2.0$ &$0.4$ & $1.0$ & $0.4$ &$2.0$ & $0.003$  & $[-0.4, 0.4]$ & $0.18$\\
	    	Test 6 & $1.0$ & $0$ &$1000$ & $1.0$ & $0$ &$0.01$ & $0.003$  & $[-0.5, 0.5]$  & $0.01$\\
	    \hline
	  \end{tabular}
	  \label{tab:1D-shock-input_parameters}
\end{table}
where, subscript $L$ refers left side and $R$ for right side. $m$ is particle mass, initial interval between adjacent particles are adjusted to guarantee equal particle mass. $t_f$ is the time to terminate simulation and plotting the results. Equal particle mass is assigned to all particles. The $x$ axis in all plots is normalized by time, that is $x/t_f$, in plots for shock tube tests results.

Test 1 consists of a left rarefaction, a right travelling contact and a right shock. Density increases at down wind of contact wave.
Test 2 also consists of a left rarefaction, a right travelling contact and a right shock. Density decreases at down wind of contact wave.
Test 3 includes double expansion waves. The initial density are different at right and left hand side.
Test 4 is a double shock tests with different initial density on the right side and left side.
Test 5 and Test 6 are two extreme cases. Test 5 is a cavity flow while test 6 is a strong blast flow.

\subsection{Comparison of RSPH with standard SPH and GSPH}
\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
    \end{minipage}% 
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
    \end{minipage}% 
    \\
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
    \end{minipage}% 
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
    \end{minipage}%    
    \caption{Simulation results by RSPH and SPH with different artificial viscosity coefficients. The effect of artificial viscosity is illustrated through comparison. Artificial viscosity coefficients are chosen to always satisfy: $\beta=2\alpha$ in all SPH tests. The last four figures are zoomed views. Almost no fluctuation is observed when $\alpha=1$ and $\alpha=2$, illustrating that numerical fluctuation is completely suppressed if artificial viscosity is large enough. For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock. However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock. To summarize, the equivalent artificial viscosity in RSPH is adaptive. Similar conclusion can be drew from zoomed view of velocity. The third zoomed view shows different degrees of smearing at the shock. The larger the artificial viscosity, the less sharp the solution at the shock. Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity. SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock. The last zoomed view shows pressure around the contact discontinuity. It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.}
    \label{fig:RCM-Sod-SPH-alf}
\end{figure}

Test 1 is simulated using standard SPH with different artificial viscosity coefficients, GSPH and RSPH. RSPH is compared with SPH using different artificial viscosity coefficients in Fig. \ref{fig:RCM-Sod-SPH-alf}. In all simulations, the artificial viscosity $\beta$ is set to be twice of $\alpha$. For example, for the test ``$SPH-\alpha=2$", $\beta=4$. Several interesting observation are made based on the comparison between SPH and RSPH.
First of all, dissipation (introduced by artificial viscosity in these tests) can decays the numerical fluctuations. Numerical fluctuations can be suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients.
%The mechanism for SPH to reduce (or completely get rid of) fluctuations should be completely different from that of new adaptive method of smoothing length. 
%The new adaptive method, reduces the sources of such fluctuations.
Secondly, the equivalent artificial viscosity coefficients introduced by RSPH varies adaptively.
As shown in Fig. \ref{fig:RCM-Sod-SPH-alf}, RSPH assigns smaller artificial viscosity coefficients (equivalent $\alpha$ much less then 0.2) at the area far away from shock and sufficient large artificial viscosity coefficients (equivalent $\alpha$ is about 1.0) around the shock. So RSPH is actually more adaptive than SPH. This feature is very desirable as it could eliminates parameterization and hence user intervention associated with artificial viscosity coefficients.
Thirdly, RSPH introduces less smearing of the shock discontinuity compared with SPH using most commonly adopted artificial viscosity coefficients ($\alpha=1.0$, $\beta=2.0$). Recall that RCM is able to resolve discontinuities as true discontinuity. RSPH, even though still smears the discontinuity in some degree, introduces much less smearing.
The last but not the least, the pressure ``wiggle" around contact discontinuity is completely eliminated by RSPH. It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}. As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and help suppress the anomaly \citep{puri2014approximate}. Since RSPH share many common places with Godunov's method, it is not surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.

\begin{figure}[H]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p}
    \end{minipage}% 
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho-zoom}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e-zoom}
    \end{minipage}% 
    \\
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v-zoom}
    \end{minipage}% 
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p-zoom}
    \end{minipage}%    
    \caption{Comparison of RSPH with GSPH using Roe Riemann solver and HLLC Riemann solver. The last four plots are zoomed views. Zoomed view of density and specific internal energy show that GSPH smears the discontinuity at shock much more than RSPH. Zoomed view of velocity shows that fluctuation in GSPH is completely suppressed, which implies that numerical dissipation introduced in GSPH is at least around the same amount as SPH with $\alpha=1.0$. This is consistent with information implied by zoomed view of density and specific internal energy. The last zoomed view shows that both RSPH and GSPH can get rid of pressure ``wiggle" around the contact discontinuity.}
    \label{fig:RCM-Sod-GSPH}
\end{figure}

These zoomed views in fig. \ref{fig:RCM-Sod-GSPH} demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH. The attractive feature of RCM method in preserving true discontinuity is inherited by RSPH in this 1D shock tube test. With more dissipation, GSPH can completely suppress numerical dissipation. The discontinuity at the shock is more seriously smeared. The excessive amount dissipation might have other, more undesirable, effects in real implementation. For example, over damping of shearing flow. Compared with SPH, both GSPH and RSPH avoid pressure ``wiggles" around contact discontinuity.

\subsection{Accuracy tests}
We use shock tube test to gauge the accuracy of the RSPH scheme.
% for both situations when the solution remains smooth and when there are shocks in the solution. We use test 1 to conduct order of accuracy test for the case with shocks in the solution. 
We examine the errors between simulation results and the analytical solution (the reference solution) as the number of particles is increased. The $L_1$ norm error, defined for a property $f$, is normalized by the number of particles as:
\begin{equation}
L_1= \frac{1}{N_p} \sum_a^{N_p} \vert f_a^{SPH} - f^{REF} (x_a) \vert 
\end{equation}
where the superscript $REF$ represent the reference solution, $SPH$ represents simulation results calculated by different SPH schemes. Fig. \ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the density, velocity and pressure profiles for different SPH schemes.
We observe a rate of convergence of approximately 1 for GSPH and 1.5 for standard SPH and RSPH.
GSPH with an exact Riemann solver has been shown to be approximately second order of accuracy \citep{puri2014comparison} and comparable in accuracy to the standard SPH schemes when using piece wise linear construction. As for GSPH using approximate Riemann solver, \citet{puri2014approximate} reported second order accuracy for HLLC and Roe Riemann solvers adopting piece wise linear Riemann problem construction. In addition, they adopted a test problem without discontinuity in the solution. Existing of discontinuities, such as shock, in the test problem might lower rate of convergence. Both RSPH and GSPH tests in this paper adopt a piece wise constant construction of Riemann problem. So we conclude that RSPH shows higher order of accuracy than GSPH when using the same Riemann problem construction. Compared with SPH, RSPH shows almost the same order of accuracy and level of error.
%It is worthwhile to check the order of accuracy of GSPH using piecewise linear constructor
%It is also worthwile to check what of order of accuracy using another test problem.

\begin{figure}[H]
    \centering
    \begin{minipage}{.332\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-des}
    \end{minipage}%
    \begin{minipage}{.332 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-vel}
    \end{minipage}%
    \begin{minipage}{.332\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
    \end{minipage}%  
    \caption{ $L_1$ norm errors for 1D shock tube test (test1) for RSPH, standard SPH, GSPH using Roe Riemann solver and GSPH using HLLC Riemann Solver.  GSPH with the HLLC approximate Riemann solver exhibits the same convergence rate (around 1) but quantitatively larger errors than that with Roe Riemann solver. RSPH and standard SPH shows same rate of convergence and almost same amount of error.}
    \label{fig:Accuracy-test1}
\end{figure}

\subsection{Comprehensive 1D tests}
Comprehensive tests are presented in this section to check how well does RSPH work for different situations. Input parameters for each tests is given in Table \ref{tab:1D-shock-input_parameters}. Wave speed is estimated based on formulation Eq. (\ref{eq:RP-solver-HLLC-SM}) $\sim$ Eq. (\ref{eq:RP-solver-HLLC-SR}).
The results are shown in Fig. \ref{fig:RCM-GSPH-Sod} $\sim$ Fig. \ref{fig:RCM-strong-blast}. $x$ axis in these plots are normalized by the terminal time $t_f$. We observe that RSPH is able to correctly predict the position and magnitude of all waves for all tests. A jump of specific internal energy at the origin is observed in Sjogreen test. However, such jump is a common issue of SPH schemes and has been reported in many other tests (see, for example, \citep{monaghan1997sph,cha2003implementations,puri2014approximate})
In addition, a noticeable spike can be observed near the contact discontinuity. Similar spike is observed in GSPH simulation \citep{puri2014comparison}. Such spike is evident in the FVM solution as well and is perhaps an artifice of the Lagrangian nature of the two schemes. \citep{noh1987errors} proposed to adding a small amount of thermal conduction to relieve the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}. We did not adopt such strategy in our simulation.
Due to less amount of dissipation, numerical fluctuations persist in all simulation results. For the strong blast test and double shock test, such fluctuations become more obvious than other tests. Even though, the magnitude of fluctuations is within acceptable range.

\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-v}
    \end{minipage}% 
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-p}
    \end{minipage}% 
    \caption{Results for test 2, a variation of Sod test. All physical properties are well re-produced except for some acceptable oscillations}
    \label{fig:RCM-GSPH-Sod}
\end{figure}

\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-v}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-p}
    \end{minipage}% 
    \caption{Results for test 3, the double expansion case. All physical properties are well re-produced except for some oscillations}
    \label{fig:RCM-double-expansion}
\end{figure}

\begin{figure}[htp]
    %\centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-rho-Rp6}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-v-Rp6}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-e-Rp6}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-p-Rp6}
    \end{minipage}% 
    \caption{Results for test 4, the double shock case. All physical properties are well re-produced. However, the oscillations are more serious than oscillations in other tests.}
    \label{fig:RCM-double-shock}
\end{figure}

\begin{figure}[htp]
    %\centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-rho-Adpt1}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-v-Adpt1}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-e-Adpt1}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-p-Adpt1}
    \end{minipage}% 
    \caption{Results for test 5, a variation of the Sjogreen test. The density, velocity and pressure are well re-produced while the thermal energy at the origin is poorly predict. A jump of internal energy at the origin is a common issue in many SPH schemes (see, for example, \citep{monaghan1997sph,cha2003implementations,puri2014approximate})}
    \label{fig:RCM-Sjogreen}
\end{figure}

\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-rho-Rp3}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-v-Rp3}
    \end{minipage}%
    \\
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-e-Rp3}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-p-Rp3}
    \end{minipage}% 
    \caption{Results for test 6, the strong blast test. y axis for density plot is in log base 10. All physical properties are well re-produced. The oscillations between shock and contact discontinuity is relatively larger than other area. A noticeable spike is observed near contact discontinuity.}
    \label{fig:RCM-strong-blast}
\end{figure}

\subsection{3D free jet}
Free jet flow have been studied analytically, experimentally and numerically for many decades, not only because of its wide application but also because of its fundamental significance as a basic flow to the scientific research community. To test the capacity of RSPH for multiple dimensional applications, a free jet flow is simulated in this section by solving 3D compressible Euler Equations using standard SPH, GSPH and RSPH. 
All simulations are using the same setting-up and compared at the same physical time. In this test, RSPH simulation is carried out based on piece wise constant construction of Riemann problem and a HLLC approximate Riemann solver. To do a well-controlled comparison, GSPH adopts the same way for Riemann problem construction and the same Riemann solver as RSPH.

The computational domain in this test is a box. The boundaries can be categorized into the velocity inlet (a circular area at the center of the bottom of the box), non-slip wall boundary (box bottom) and pressure outlet (other faces of the box). The boundaries are set away from vent to avoid boundary effects on simulation.
At the vent, exit velocity $\textbf{v}$ is set to $500 m / s$ and radius of the nozzle $r$ is set to $8m $. The pressure of ejected fluid are assumed to be the same as ambient ($101 kpa$). The temperature of and ambient fluids are set to $273 K$. 
Velocity is zero for non-slip wall boundary. The heat flux across wall boundary is zero assuming adiabatic wall. The flux of mass should also be zero on the wall. As a result, internal energy flux, which consists of heat flux and energy flux carried by mass flux, vanishes on the wall boundary. 
The pressure of the surrounding ambient is given. As we ignore the viscosity, the shear stress is ignored and normal stress (whose magnitude equals to pressure) balances the ambient pressure.
\begin{equation}
p = p_a\left(z\right)  \label{eq:pressure_bc_p} 
\end{equation} 
Except for the pressure, boundary values for density, velocity, and energy on the outlet are determined by solution. Fluids properties of ideal gas are used in this simulation.

\begin{figure}[H]
    \centering
    \begin{minipage}[t]{.325\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf2-t3-cutView}
    \end{minipage}%
    \begin{minipage}[t]{.325 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t3-cutView}
    \end{minipage}%
    \begin{minipage}[t]{.325\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alfp3-t3-cutView}
    \end{minipage}%
    \caption{Free jet flow simulation results at $t=3.0 s$ by SPH using different artificial viscosity coefficients. These pictures are front view of a slice of the domain cut by two planes parallel to $x-z$ plane at $y=-9$ and $y=9$. From left to right, the picture is corresponding to $\alpha=0.3$, $\alpha=1.0$ and $\alpha=2.0$ respectively. Another artificial viscosity coefficient $\beta$ is set to be double of $\alpha$ for all tests. Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.}
    \label{fig:free-jet-SPH-comparison}
\end{figure}

\begin{figure}[!ht]
    \centering
    \begin{minipage}[t]{.325\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t1p5-cutView}
    \end{minipage}%
    \begin{minipage}[t]{.325 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t1p5-cutView}
    \end{minipage}%
    \begin{minipage}[t]{.325\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t1p5-cutView}
    \end{minipage}%
    \\
    \centering
    \begin{minipage}[t]{.325\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t3-cutView}
    \end{minipage}%
    \begin{minipage}[t]{.325 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t3-cutView}
    \end{minipage}%
    \begin{minipage}[t]{.325\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t3-cutView}
    \end{minipage}%
    \caption{Simulation results of free jet flow by SPH with $\alpha=1.0, \beta=2.0$, GSPH and RSPH. These pictures are front view of a slice of the domain cut by two planes parallel to $x-z$ plane at $y=-9$ and $y=9$. From left to right, the picture is corresponding to SPH, GSPH and RSPH respectively. Red particles in pictures of the first row are particles erupted from the nozzle while blues are ambient fluids particles. Pictures on the first row are corresponding to $t=1.5s$ while pictures on the second row are for $t=3.0 s$}
    \label{fig:free-jet-comparison}
\end{figure}

Figure \ref{fig:free-jet-SPH-comparison} shows simulation results of the free jet flow by SPH with different artificial viscosity coefficients. The damping effect due to artificial dissipation is clearly shown in this figure. We observe that the lengths to which these jets reach at $t=3.0 s$ are various when using different artificial viscosity coefficient. It is obvious that the larger artificial viscosity, the shorter length the jet can reach. While introducing undesirable damping effects, artificial viscosity is necessary for numerical stability and simulating of shocks. So, in real applications, the artificial viscosity coefficients are usually tuned (see, for example, \citep{gmd-2017-119}) to avoid excessive artificial damping effects.

We compare RSPH with GSPH in terms of equivalent overall artificial damping effects. Different from SPH, both GSPH and RSPH introduce artificial viscosity in an implicit way by solving local Riemann problems. As has been shown in 1D tests, RSPH can introduce less artificial viscosity than GSPH. Fig. \ref{fig:free-jet-comparison} implies that RSPH introduces less overall damping effect than GSPH in 3D application as well, which is consistent with 1D tests. That is to say, RSPH's desirable property of introducing less artificial dissipation 1D unsteady flow is inherited in 3D applications of RSPH. Recall that RCM shows ability of resolving discontinuities as true discontinuities in 1D unsteady flows but such very desirable property does not persist in genuine two (or higher) space dimensions \citep{colella1982glimm}. Integrating of RCM within the framework of SPH avoids solving higher dimensional Riemann problems overcoming the fundamental shortcoming of RCM.

\section{Conclusion}
We proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs. The artificial viscosity in RSPH is determined implicitly by randomly sampling solution of a local Riemann problem. No explicit artificial viscosity coefficients is needed. The artificial viscosity introduced by RSPH is demonstrated to be much less than GSPH and SPH without parameter tuning. Besides introducing less amount of dissipation, there are several other attractive features. The pressure ``wiggles" around contact discontinuity, which persists in SPH results, is eliminated in RSPH. It also shows higher order of convergence rate than GSPH when the same construction of local Riemann problem and Riemann solvers are adopted. The attractive property of less dissipation persist in multi-dimensional applications.
This new method enables shock capturing with lower dissipation. One potential application of the method is high speed mixing flow, for example, supersonic combustion.
By overcoming a fundamental shortcoming of RCM and inheriting attractive feature of RCM, RSPH provide a powerful numerical method for solving combustion problems in multi-dimensional space.

One shortcoming of RSPH is its inability to completely suppress numerical perturbation caused by non-uniform distribution of smoothing length in space. Such perturbation, as long as it does not lead to numerical instability, is within acceptable range for many tests. However, for very strong shocks, dissipation introduced by RSPH turns out to be not sufficient to stabilize simulation, which finally ends up with negative energy. Since GSPH has been shown introducing more dissipation and hence is more suitable for situation with very strong shocks.

In our investigation presented in this paper, an approximate HLLC Riemann solver is used in place of exact iterative Riemann solver. It would be interesting to see the difference, between using other approximate Riemann solvers and exact Riemann solver. Alternative Riemann solvers, alternative ways for constructing Riemann problems and alternative ways for sampling solution of Riemann problem might also worthwhile for future exploring. In addition, this paper focused on solving of compressible Euler equations. Applications of RSPH in other computational fluids dynamic problems or solving other hyperbolic PDEs are on the list to be explored.

\section*{acknowledgements}
3D simulations reported here were performed at the Center for Computational Research (CCR) at the University at Buffalo. This project is supported by Grants No. NSF ACI/1131074 from the National Science Foundation.

\section*{References}
\bibliography{Reference}
\end{document}

### 2017-12-04 JCP-Manuscript.tex
first manuscript done

@@
 First of all, it introduces less but sufficient artificial dissipation for shock capturing compared with classical SPH and GSPH.
-The pressure ``wiggles" around contact discontinuity, which persists in SPH results, is eliminated by the new scheme.
-It also shows higher order convergence than GSPH.
+The pressure ``wiggle" around contact discontinuity, which persists in SPH results, is ameliorated by the new scheme.
+It also shows higher order of convergence than GSPH.
 %when the same construction of local Riemann problem and Riemann solvers are adopted by both methods. 
@@
 \begin{keyword}
-Smoothed Particle Hydrodynamics (SPH), Random Choice Method (RCM), Riemann Solver, Hyperbolic PDEs, Godunov's method
+Smoothed Particle Hydrodynamics (SPH), Random Choice Method (RCM), Riemann Solver, Hyperbolic PDEs, Artificial viscosity
 \end{keyword}
@@
 This method, named as Godunov SPH (GSPH), is attractive because it eliminates parameterization and hence user intervention associated with artificial viscosity coefficients.
-The GSPH method has been shown to be able to handle shock discontinuities \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate}, introduces less damping to turbulent mixing \citep{cha2010kelvin, borgani2012hydrodynamic} than standard SPH, and relieve pressure ``blips" (or ``wiggles" called by others) at the contact discontinuity \citep{borgani2012hydrodynamic}.
+The GSPH method has been shown to be able to handle shock discontinuities \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate}, introduces less damping to turbulent mixing \citep{cha2010kelvin, borgani2012hydrodynamic} than standard SPH, and ameliorate pressure ``blips" (or ``wiggle" called by others) at the contact discontinuity \citep{borgani2012hydrodynamic}.
 However, the amount of dissipation introduced by GSPH is stll excessive than needs.
@@
 \item The RSPH is able to adaptively adjust equivalent artificial viscosity coefficients, assigning larger artificial viscosity coefficients around the shock and small artificial viscosity coefficients otherwhere.
-\item RSPH is able to suppress pressure ``wiggles" at the contact discontinuity, a common issue in classical SPH.
+\item RSPH is able to alleviate pressure ``wiggle" at the contact discontinuity, a common issue in classical SPH.
 \end{itemize}
@@
 As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and help suppress the anomaly \citep{puri2014approximate}.
-Since RSPH share many common places with Godunov's method, it is not surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.
+Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}).
+``Wiggle" in test 1, however, is completely eliminated by both GSPH and RSPH.
 
@@
 For example, over damping of shearing flow.
-Compared with SPH, both GSPH and RSPH avoid pressure ``wiggles" around contact discontinuity.
+Compared with SPH, both GSPH and RSPH avoid pressure ``wiggle" around contact discontinuity.
+Since RSPH share many common places with Godunov's method, it is not surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.
 
@@
 
-\subsection{Comprehensive 1D tests}
+\subsection{Comprehensive 1D tests} \label{sec:comprehensive-1d-tests}
 Comprehensive tests are presented in this section to check how well does RSPH work for different situations.
@@
 Such spike is evident in the FVM solution as well and is perhaps an artifice of the Lagrangian nature of the two schemes.
-\citep{noh1987errors} proposed to adding a small amount of thermal conduction to relieve the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}.
+\citep{noh1987errors} proposed to adding a small amount of thermal conduction to ameliorate the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}.
 We did not adopt such strategy in our simulation.
@@
 Besides introducing less amount of dissipation, there are several other attractive features.
-The pressure ``wiggles" around contact discontinuity, which persists in SPH results, is eliminated in RSPH.
+The pressure ``wiggle" around contact discontinuity, which persists in SPH results, is eliminated in RSPH.
 It also shows higher order of convergence rate than GSPH when the same construction of local Riemann problem and Riemann solvers are adopted.

### 2018-01-08 JCP-Manuscript.tex

@@
 %\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Abani Patra}
-\ead{abani@buffalo.edu}
+\fntext[mycorrespondingauthor]{abani@buffalo.edu}
+%\cortext[mycorrespondingauthor]{abani@buffalo.edu}
+%\ead{abani@buffalo.edu}
 %\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
 %\address[mysecondaryaddress]{360 Park Avenue South, New York}
+
 \begin{abstract}
 Standard smoothed particle hydrodynamics (SPH) employs an artificial viscosity, defined explicitly by constant coefficients, to properly capture hydrodynamic shock waves.
-Such methodology usually provides dissipation more than need and smears the discontinuity if the artificial viscosity coefficients are not tuned.
+Such methodology usually provides dissipation more than need and smears the discontinuities if the artificial viscosity coefficients are not tuned.
 Excessively large artificial viscosity might also damp generation of turbulence by fluid instability.
@@
 The pressure ``wiggle" around contact discontinuity, which persists in SPH results, is ameliorated by the new scheme.
-It also shows higher order of convergence than GSPH.
+The new method also shows higher order of convergence than GSPH.
 %when the same construction of local Riemann problem and Riemann solvers are adopted by both methods. 
-Combining of RCM with SPH overcomes the inability of classical RCM method in solving multi-dimensional unsteady non-linear systems.
-Three dimensional time dependent compressible Euler equations are solved for simulating a free jet flow, demonstrating that the desirable less dissipation property of the new scheme persists in multi-dimensional applications.
+Classical RCM method would lose its desirable property of low numerical dissipation when solving multi-dimensional unsteady non-linear systems.
+Combining of RCM with SPH overcomes the shortcoming  of classical RCM method.
+Three dimensional time dependent compressible Euler equations are solved by the new scheme for simulating a free jet flow, demonstrating that the desirable less dissipation property of the new scheme persists in multi-dimensional applications.
 \end{abstract}
 \begin{keyword}
-Smoothed Particle Hydrodynamics (SPH), Random Choice Method (RCM), Riemann Solver, Hyperbolic PDEs, Artificial viscosity
+Smoothed Particle Hydrodynamics (SPH), Random Choice Method (RCM), Riemann Solver, Artificial viscosity, Hyperbolic PDEs
 \end{keyword}
@@
 \section{Introduction}
-Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on Lagrangian formulation, and has been widely applied to different areas in engineering and science.
+Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on Lagrangian formulation and has been widely applied to different areas in engineering and science.
 SPH has both advantages and disadvantages with respect to other numerical techniques.
@@
 Selective application of artificial viscosity techniques, such as the time dependent viscosity \citep{morris1997switch, dolag2005turbulent} and shock-indicator-based viscosity \citep{cullen2010inviscid} have been tried for counteracting this.
-\citet{sigalotti2008adaptive} improved the standard SPH near sharp discontinuities adopting an adaptive density kernel estimation (ADKE) techniques.
-However, the parameters for ADKE have to be tuned to the problem at hand.
+\citet{sigalotti2008adaptive} improved the standard SPH near sharp discontinuities adopting adaptive density kernel estimation (ADKE) techniques.
+However, the parameters for ADKE have to be tuned to the problem at hand \citep{puri2014comparison}.
 Hence it is hard to implement ADKE in real applications.
@@
 Chorin's work was followed by numerous researchers, with applications and further improvements \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical}.
-In essence, the solution is advanced in time by a sequence of operations that includes the solution of Riemann problems and a stochastic sampling procedure.
+In essence, the solution is advanced in time by a sequence of operations that include solving of Riemann problems and a stochastic sampling of the solution.
+See \citep{toro2013riemann} for details.
 When applied to one dimensional time dependent Euler equations \citep{colella1982glimm}, diffusive errors from spatial averaging are completely eliminated and hence discontinuities, such as shocks or material interface, can be resolved as true discontinuities.
 For unsteady flows in genuine two (or higher) space dimensions, however, such very desirable property of RCM do not seem to persist \citep{colella1982glimm}.
-Implementing of RCM within the framework of SPH only involves sampling of solutions of Riemann problem in 1D local coordinate system no matter what is the dimensionality of the problem.
-Hence desirable property of RCM method in 1D should be retained in higher dimensional implementations within the framework of SPH.
-This hypothesis is confirmed by a three-dimensional (3D) free jet flow simulation.
 %This need to be proven ---> But at least, if the good property of preserving true discontinuity is still valid in 1D shock tube problem, it should be preserved in multiple-dimensional implementations.
@@
 In this investigation, we introduce a new method, which will be referred to as RSPH in later paragraph, by integrating RCM method within framework of SPH. 
-The new scheme inherits the attraction of classical RCM introducing less but sufficient artificial viscosity and causing less smearing of discontinuities than other methods for 1D problems. 
-For multi-dimensional problem, RCM method is implemented within one-dimensional local coordinate system, established for pair of interacting particles.
-So no multi-dimensional coordinate is involved even for multi-dimensional problems.
-Thereby, the attractive properties of less dissipation showing in one-dimensional case is preserved in multi-dimensional implementations.
-In this way, the RSPH overcomes RCM's fundamental limitation of losing attractive property showing in 1D in higher dimensional application.
-
-RSPH has the following advantages over standard SPH:
+The new scheme inherits the attraction of classical RCM, introducing less but sufficient artificial viscosity and causing less smearing of discontinuities than other methods for 1D problems.
+Implementing of RCM within the framework of SPH only involves sampling of solutions of Riemann problem in 1D local coordinate system no matter what is the dimensionality of the problem.
+That is to say, no multi-dimensional coordinate is involved even for multi-dimensional problems.
+Thereby, the desirable property of RCM method in 1D should be retained in higher dimensional implementations within the framework of SPH.
+This hypothesis is confirmed by a three-dimensional (3D) free jet flow simulation.
+
+To summarize, RSPH has the following advantages over standard SPH:
 \begin{itemize}
@@
 \end{itemize}
-Compared with GSPH, which is also based on solution of local Riemann problem, RSPH introduces less but sufficient dissipation than GSPH, especially in the region away from shocks.
+Compared with GSPH, which is also based on solution of local Riemann problems, RSPH introduces less but sufficient dissipation than GSPH, especially in the region away from shocks.
 Such feature of RSPH is especially beneficial for simulating of scenarios involving turbulence mixing, for which excessive dissipation would suppress mixing.
@@
 
-Our investigation focuses on implementation of the RSPH schemeit in solving inviscid compressile Euler equations .  
+Our investigation implements RSPH scheme in solving inviscid compressile Euler equations as the application case.  
 \begin{align}
@@
 For any SPH scheme, governing equations in Lagrange form are needed.
-By deducting kinetic energy from energy equation, subtracting mass conservation from momentum equation, combining transient term and advection term into material derivative (for any function $A$, material derivative is defined as $\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$) term, the governing equations are put into the final form.
+By deducting kinetic energy from energy equation, subtracting mass conservation from momentum equation, combining transient term and advection term into material derivative (for any function $A$, material derivative is defined as $\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$) term, the governing equations are converted into the Lagrange form.
 \begin{align}
@@
 \end{align}
-where, $a$ is the SPH particle index, $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$. $\Pi$ is an artificial viscosity term.
+where, $a$ is the SPH particle index, $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$. The smoothing length $h$ is taken as $h=\frac{h_a + h_b}{2}$. $\Pi$ is an artificial viscosity term.
 One of commonly used models of artificial viscosity \citep{monaghan1983shock} is:
@@
 $\alpha = 1$ and $\beta = 2$ are recommended \citep{monaghan2005smoothed} for best results and mostly adopted.
-In the numerical test section, these two parameters are varied to show the effect of them.
+In the numerical test section, these two parameters are varied to show the effect different amount of numerical dissipation on simulation results.
 $\eta$ is usually taken as 0.1 to prevent singularities.
@@
 (\ref{eq:ns-sph-e}), $w_{a b}\left(h\right)$ is weighting function and is a concise form of $w\left(\textbf{x}_a - \textbf{x}_b, h\right)$.
-From here on, we will use this concise form.
+We will use this concise form throughout this paper.
 There is a wide variety of possible weighting functions, such as spline functions (with different orders) and Gaussian functions.
@@
 \begin{equation}
-w\left(\textbf{x} - \textbf{x} \prime \right) = 
+w\left(\textbf{x} - \textbf{x} \prime, h \right) = 
 \begin{cases} 
@@
 \begin{equation}
-\nabla w\left(\textbf{x} - \textbf{x} \prime \right) = 
+\nabla w\left(\textbf{x} - \textbf{x} \prime, h \right) = 
 \begin{cases} 
@@
 
-\subsection{GSPH method}
+\subsection{GSPH method} \label{sec:GSPH-method}
 Here we present essential formulations for solving Euler equations with GSPH.
@@
 where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are obtained by solving a 1D Riemann problem constructed based on physical quantity of particle $a$ and particle $b$.
-The starred quantity  are interpolated value of the solution of the Riemann problem at an imaginary interface $q^{\ast}_{ab}$.
+The starred quantity are interpolated value of the solution to the Riemann problem at an imaginary interface.
+More discussion about the imaginary interface is in section \ref{sec:Picking-up-single-state}.
 $\dot{\textbf{x}}_{a}^{\ast}$ is time centered velocity of particle $a$:
@@
 \item the averaged (in certain sense) pressure and the effect of artificial viscosity is replaced by  $p^{\ast}$, obtained based on a local Riemann solver.
-\item A time centered velocity is used, which satisfies the following identities approximately. 
+\item a time centered velocity is used, which satisfies the following identities approximately. 
 \begin{equation}
@@
 \end{equation}
-Where $\textbf{v}_{a b}$ is defined as $\textbf{v}_a - \textbf{v}_b$.
+%Where $\textbf{v}_{a b}$ is defined as $\textbf{v}_a - \textbf{v}_b$.
 \end{itemize}
-Actually, Godunov's idea of using Riemann solver can be combined with other SPH discretization formulations \citep{cha2003implementations}.
-
-To conduct a well controlled comparison, the constructing of Riemann problem, Riemann solvers and projection of picked solution of Riemann problem back to global coordinate system are exactly the same in GSPH and RSPH, details of which will be described in detail in the next section.
-The way how solutions of Riemann problems are used is the only difference between GSPH and RSPH in our test.
-While RSPH takes solution of Riemann problem based on random sampling, solution of Riemann problem at an imaginary interface is picked up in GSPH, either based on interpolation of specific volume \citep{inutsuka2002reformulation} or simply assuming the middle point as the interface \citep{cha2003implementations}.
-
-\section{RSPH method}
-RSPH shares many commonality with SPH and GSPH, especially with GSPH.
+Actually, Godunov's idea of using Riemann solver can be combined with other SPH discretization formulations as well \citep{cha2003implementations}.
+
+More technical details of GSPH are in section \ref{sec:RSPH-method}.
+The construction of Riemann problem, Riemann solvers and projection of picked solution of the Riemann problem back to global coordinate system are exactly the same in GSPH and RSPH.
+They are described in the next section.
+The way how to pick up the starred value from solution of the Riemann problem is the only difference between GSPH and RSPH.
+Detailed discussion is presented in section \ref{sec:Picking-up-single-state}.
+
+\section{RSPH method} \label{sec:RSPH-method}
+RSPH shares many commonalities with SPH and GSPH, especially with GSPH.
 We adopt the same density updating formulation (see Eq.
@@
 (\ref{eq:SPH-update-pos})) is also the same for all schemes.
-Discretized governing equation for RSPH and GSPH are exactly the same while the way to determine $p^{\ast}$ and $\textbf{v}^{\ast}$ are different.
-We focus more on where RSPH is different from SPH and GSPH in this section.
-
-For mesh based method, there is a great deal of commonality between Godunov's method and RCM.
+Discretized governing equations for RSPH and GSPH are exactly the same as well.
+The common palces shared with classical SPH and GSPH are unnecessary to repeat in this section.
+We focus more on where RSPH is different from SPH and GSPH.
+
+Both GSPH and RSPH borrow ideas of shock capturing techniques from mesh based method.
+There is a great deal of commonality between Godunov's method and RCM for mesh based method.
 Both of them utilize the solution of a local Riemann problem.
-The RCM pick up a single state contained in the local solutions ``randomly" while Godunov's method take the integral average.
-%The random selection procedure is carried out by employing a sequence of random numbers. 
-GSPH, however, does not take the integral average.
+The difference is that the RCM pick up a single state contained in the local solutions ``randomly" while Godunov's method take the integral average.
+Integrating of Godunov's idea within SPH framework (the GSPH method), however, does not take the integral average at all.
 Instead, a single state of the local Riemann solution at an imaginary interface is picked up and used to upgrade physical quantities through discretized governing equations (see Eq.
@@
 (\ref{eq:gov-gsph-e-simple-form})).
-So the difference between RSPH and GSPH is how to pick up the single state from solution to Riemann problem.
-RSPH pick up the single state by stochastic sampling while GSPH chooses the single state at an imaginary interface.
-
-Since the only difference between Godunov's method and RCM is how the solution of local Riemann problem is utilized, we can use exact the same discretization in RSPH as in GSPH.
-In addition, the construction of 1D Riemann problem for RSPH is the same as piecewise constant construction of Riemann problem in GSPH.
-In this paper, we adopt piecewise constant construction of Riemann problem for both RSPH and GSPH.
-It is a common practice in real implementation of Godunov's method to use approximate non-iterative Riemann solvers due to high computational cost associated with iterative Riemann solvers.
-Therefore, in this paper, two non-iterative Riemann solvers, Roe Riemann solver and HLLC Riemann solver \citep{toro1994restoration}, are used in GSPH.
+The RSPH method, proposed in this paper mimicking classical RCM, picks up the single state by stochastic sampling.
+So the difference between RSPH and GSPH is how to pick up the single state from solution of the Riemann problem.
+
+Technical details for GSPH which are not coverred in section \ref{sec:GSPH-method} are also presented in this section.
+The piecewise constant construction of Riemann problem, which is adopted in both RSPH and GSPH, is presented in section \ref{sec:RP-construction}.
+The way to pick up a single state from solutions to local Riemann problems are formulated in section \ref{sec:Picking-up-single-state}.
+It is a common practice in real implementations of Godunov's method to use approximate non-iterative Riemann solvers.
+Two non-iterative Riemann solvers, Roe Riemann solver and HLLC (Harten, Lax and van Keer scheme with contact) Riemann solver \citep{toro1994restoration}, are adopted in GSPH.
 The HLLC type of Riemann solver \citep{toro1994restoration}, in which the contact wave is considered, is used in RSPH.
-
-\subsection{Defining of local 1D Riemann problem}
-A 1D Riemann problem need to be solved to obtain  $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ for both GSPH and RSPH.
+Section \ref{sec:RP-solver} presents details on these Riemann solvers.
+
+The last second subsection is about generating of random numbers for RSPH. The RSPH algorithm is summarized in last subsection.
+
+\subsection{Defining of local 1D Riemann problem} \label{sec:RP-construction}
+A 1D Riemann problem need to be solved to obtain  $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ in both GSPH and RSPH.
 Hence, a 1D Riemann problem need to be constructed first.
-Constructing of 1D Riemann problem starts from establishing of a local coordinate systems ($q$).
+Constructing of 1D Riemann problem starts from establishing of a local coordinate system ($q$).
 The origin is selected at the middle-point of the line segment joining two particles with the unit vector along the line defined as:
 \begin{equation}
-\hat{r}_{a b}= \frac{\textbf{v}_{a} - \textbf{v}_{ b}}{|\textbf{x}_{a} - \textbf{x}_{ b}|}
+\hat{r}_{a b}= \frac{\textbf{x}_{a} - \textbf{x}_{ b}}{|\textbf{x}_{a} - \textbf{x}_{ b}|}
 \end{equation}
@@
 
-In original Godunov's SPH method, the construction of Riemann problem is divided into two sub-steps: projection and construction. 
-Different from original Godunov's method, which assumes piecewise linear distribution of the data (or higher order method like MUSCL and PPM which use higher order polynomial approximation.), RCM method assumes that the given data at the center of cell is constant throughout the respective cell.
-The same idea can be easily (and naturally) applied in RSPH, as there is actually no ``cell interface" in SPH method.
-In this case, no additional step for constructing a Riemann problem is needed as the Riemann problem is constructed in a ``piece wise constant" manner.
-So the Riemann problem is defined directly based on data on particles.
+The RSPH essentially takes the ``piece wise constant" manner for Riemann problem construction.
+No further step is required for construction after projection.
+Recall that in GSPH method, the construction of Riemann problem is divided into two sub-steps: projection and construction.
+Different from original Godunov's method, which assumes piecewise linear distribution of the data (or higher order method like MUSCL and PPM which use higher order polynomial approximation), RCM method assumes that the given data at the center of cell is constant throughout the respective cell.
+The same idea can be easily (and naturally) applied in RSPH as there is actually no cell in SPH method.
+Then the Riemann problem is defined directly based on data on particles.
 There is no need to calculate and project first order derivative of $\rho$, $u$ and $p$, which are needed for constructing of Riemann problem in a piece wise linear manner.
-The computation associated with calculation of gradient and projection of gradient is avoided when constructing 1D Riemann problem in a ``piece wise constant" manner.
-Per above description, the Riemann problem definied by initial states at left and right sides are: 
+The computation associated with calculation of gradient and projection of gradient is avoided when constructing 1D Riemann problem in such a ``piece wise constant" manner.
+Per above description, the initial states at left and right sides are given as: 
 \begin{eqnarray}
@@
 
-\subsection{Approximate Riemann solvers}
-The starred variable $p^{\ast}$ and $u^{\ast}$ represent the interpolated pressure and velocity at the some point (an imaginary interface in GSPH or a randomly sampled poit in RSPH) along the line joining the pairs of two particles.
+\subsection{Picking up a single state} \label{sec:Picking-up-single-state}
+Solving the 1D Riemann problem with initial right and left states (Eq.
+(\ref{eq:Riemann-Prob-define-L-rho}) - Eq.
+(\ref{eq:Riemann-Prob-define-R-p})) leads to a solution of the local system.
+Then pick up a single state and assign it to $p^{\ast}$ and $u^{\ast}$.
+The location where the single state is picked up is different for RSPH and GSPH.
+The starred values for RSPH takes the solution of the local Riemann problem at location $q_{ab}^{RSPH}$, which depends on a random number $\epsilon$.
+\begin{equation}
+q_{ab}^{RSPH}=\epsilon \left( q_a - q_b \right) - \frac{| q_a + q_b|}{2}
+\label{eq:sample-location-RSPH}
+\end{equation}
+At the nth time step, the same random number $\epsilon^n$ is used for picking up the single state from solutions of all local Riemann problems.
+For the next time step, the next pseudo random number $\epsilon^{n+1}$ will be used.
+Recall that the starred value for GSPH is taken as solution of the local Riemann problem at a fixed location, denoted as $q_{ab}^{GSPH}$.
+In original GSPH, the imaginary interface is determined based on interpolation of the specific volume between two paired particles \citep{inutsuka2002reformulation}.
+We set the fixed location at the middle point \citep{cha2003implementations} for simplicity.
+\begin{equation}
+q_{ab}^{GSPH}= 0
+\label{eq:sample-location-GSPH}
+\end{equation}
+
+Denote the solution of the local Riemann problem, either accurate or approximate, between a pair of particles ($a$ and $b$) to be $\textbf{W} (q), \  \forall q \in [q_a, q_b]$ (note, we use $\textbf{W}$ to represent the primitive variable vector $[\rho, u, p]^T$ and $\textbf{U}$ for conservative variable vector  $[\rho, \rho u, \rho E]^T$).
+The starred value for both GSPH and RSPH can be expressed in the same way:
+\begin{equation}
+p_{ab}^{\ast} = p \left(q_{ab}^{\ast} \right)
+\label{eq:RSPH-Random-Pick-p}
+\end{equation}
+\begin{equation}
+u_{ab}^{\ast} = u \left(q_{ab}^{\ast} \right)
+\label{eq:RSPH-Random-Pick-u}
+\end{equation}
+where $q_{ab}^{\ast}=q_{ab}^{GSPH}$ for GSPH while $q_{ab}^{\ast}=q_{ab}^{RSPH}$ for RSPH.
+The random sample range for RSPH and imaginary interface for GSPH is shown in Fig.
+\ref{fig:pick-up-state-GSPH-RSPH}.
+\begin{figure}[H]
+    \center
+	\includegraphics[width=0.5 \textwidth]{./Figures/RSPH-GSPH}
+    \caption{Evaluating of the starred values in RSPH and GSPH for paired particles $a$ and $b$.
+The local Riemann problem is defined by state of particles $a$ and $b$ at $t=0$ according to Eq.
+(\ref{eq:Riemann-Prob-define-L-rho}) - Eq.
+(\ref{eq:Riemann-Prob-define-R-p})).
+The horizontal bold solid line indicate the sample range in the solution of the Riemann problem defined between particle $a$ and particle $b$ at given time $t=\Delta t$.
+The dark ellipse is an example sample point of RSPH with the random number $\epsilon < \frac{1}{2}$.
+Depending on the random number $\epsilon$, the sample points can be anywhere on the horizontal bold solid line.
+The white ellipse is the imaginary interface for GSPH, which is fixed.
+The sampled state is assigned to starred velocity and pressure in Eq.
+(\ref{eq:gov-gsph-v-simple-form}) and Eq.
+(\ref{eq:gov-gsph-e-simple-form}) for both GSPH and RSPH.}
+    \label{fig:pick-up-state-GSPH-RSPH}
+\end{figure}
+
+A short comments regarding the difference between application of RCM method in SPH and its application in finite volume method.
+In finite volume method, for 1D case, two Riemann Problems are definied on interfaces of both sides.
+the superposition of solutions of these two Riemann problems is taken as local solution within the cell and the sampled single state is assigned to the cell center.
+In RSPH, only one Riemann problem is defined between two particles and the sampled single state (the $p^{\ast}$ and $u^{\ast}$) is used in momentum and energy updating.
+
+$u^{\ast}$ is velocity in a 1D local space and needs to be projected back to global space to obtain $\textbf{v}^{\ast}$ in cases of multi-dimensional implementations.
+One of such back-project approximations is:
+\begin{equation}
+\textbf{v}^{\ast}_{a b}=u^{\ast}_{a b} \hat{\textbf{r}}_{a b} + \left [\frac{\textbf{v}_{a} + \textbf{v}_{b}}{2} - \frac{u_L + u_R}{2} \hat{\textbf{r}}_{a b}\right]
+\label{eq:RP-project-to-3d-arithmetic}
+\end{equation}
+In Eq.
+(\ref{eq:RP-project-to-3d-arithmetic}), the arithmetic average of shear velocity is taken as the shear velocity at the sample points.
+Alternative approximation might be distance weighted average or Roe average (weighted by square root of density).
+If $q_{a b}^{\ast}$ is assumed to be zero, then distance weighted average will degenerate to the arithmetic average.
+Such back projection is required for both GSPH and RSPH.
+
+We have to mention that it is strange in GSPH to assume an imaginary interface, which never need in RSPH. And that's one of the reasons why we like RSPH more.
+
+\subsection{Non-iterative Riemann solvers} \label{sec:RP-solver}
+The starred variable $p^{\ast}$ and $u^{\ast}$ represent the interpolated pressure and velocity at certain point (an imaginary interface in GSPH or a randomly sampled poit in RSPH) along the line joining the pairs of two particles.
 They do not have to be obtained by solving a Riemann problem.
-However, $p^{\ast}$ and $u^{\ast}$ obtained by solving a Riemann problem provides necessary and sufficient dissipation needed to stabilize the scheme.
-%From numerical analysis point of view, numerical dissipation is necessary for numerical stability.
-From physics point of view, viscosity is a necessary condition for shock formation.
-But Euler equations are based on assumption of inviscid, which means Euler equation themselves are not capable to represent shock formation correctly.
-Adding of artificial viscosity helps fix the ``birth defect" of Euler equations.
+However, $p^{\ast}$ and $u^{\ast}$ obtained by solving a Riemann problem provides necessary and sufficient dissipation needed to capture discontinuities and stabilize the scheme.
 
 The exact Riemann solver, even though more accurate and robust, requires an iterative root finding, and hence is computational inefficient.
-For governing equations other than well studied ones, such as Euler equation, there is no iterative Riemann solver available.
+For governing equations other than well studied ones, such as Euler equations, there is no iterative Riemann solver available.
 Non-iterative approximate Riemann solvers can relieve these drawbacks of exact Riemann solvers.
-Among the available Riemann solvers \citep{rider1994review, luo2004computation, puri2014approximate}, we adopted the Harten, Lax and van Keer scheme with contact (HLLC).
+Among the available Riemann solvers \citep{rider1994review, luo2004computation, puri2014approximate}, we adopted the HLLC approximate Riemann solver.
 The HLLC solver is a 3-wave approximate Riemann solver proposed by \citet{toro1994restoration}.
@@
 
-The expression for intermediate pressure and velocity can be written as \citep{puri2014approximate}:
-\begin{equation}
-p^{\ast} =  \begin{cases} 
-      p_L & if \  S_L > 0 \\
-      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) M_L + (\hat{p}- p_L) \right] + \hat{p} & if \  S_L \leq 0 \leq S_M \\
-      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) M_R + (\hat{p}- p_R) \right] + \hat{p} & if \  S_M \leq 0 \leq S_R\\
-      p_R & if \  S_R < 0
+Equation (\ref{eq:RP_solver_HLLC_u}) and (\ref{eq:RP_solver_HLLC_pu}) are the approximate solution to the local Riemann problem, written in term of $p$ and $pu$ as functions of local coordinate $q$.
+\begin{equation}
+p \left( q \right) =  \begin{cases} 
+      p_L & if \  S_L \Delta t> q \\
+      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) M_L + (\hat{p}- p_L) \right] + \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
+      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) M_R + (\hat{p}- p_R) \right] + \hat{p} & if \  S_M \Delta t \leq q \leq S_R \Delta t \\
+      p_R & if \  S_R \Delta t < q
 \end{cases}
@@
 \begin{equation}
-(pu)^{\ast} =  \begin{cases} 
-      p_L u_L& if \  S_L > 0 \\
-      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) E_L + (\hat{p} S_M - p_L \hat{u}_L) \right] + (S_M - \hat{u}_{LR}) \hat{p} & if \  S_L \leq 0 \leq S_M \\
-      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) E_R + (\hat{p} S_M- p_R \hat{u}_R) \right] + (S_M + \hat{u}_{LR}) \hat{p} & if \ S_M \leq 0 \leq S_R\\
-      p_R u_R & if \  S_R < 0
+(pu) \left( q \right)  =  \begin{cases} 
+      p_L u_L& if \  S_L \Delta t > q \\
+      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) E_L + (\hat{p} S_M - p_L \hat{u}_L) \right] + (S_M - \hat{u}_{LR}) \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
+      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) E_R + (\hat{p} S_M- p_R \hat{u}_R) \right] + (S_M + \hat{u}_{LR}) \hat{p} & if \ S_M \Delta t \leq q \leq S_R \Delta t\\
+      p_R u_R & if \  S_R \Delta t < q
 \end{cases}
@@
 \end{equation}
-where $\hat{u}_{LR}$ is the interface velocity and is taken as the Roe-averaged velocity on either side of the interface.
+where $\hat{u}_{LR}$ is the interface velocity and is taken as the Roe-averaged velocity on either side of the interface \citep{cheng2007high}.
 The quantities of $\hat{u}_R$ and $\hat{u}_L$ are velocities relative to the interface velocity.
@@
 \end{equation}
-One formulation to approximate the signal speeds $S_M$, $S_L$ and $S_R$ is given by Eq. (\ref{eq:RP-solver-HLLC-SM}) to (\ref{eq:RP-solver-HLLC-SR}).
+Formulation to approximate the signal speeds $S_M$, $S_L$ and $S_R$ is given by Eq. (\ref{eq:RP-solver-HLLC-SM}) to (\ref{eq:RP-solver-HLLC-SR}).
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $c_{LR}$ is the relevant Roe averaged sound speed.
-
-Besides HLLC, another 2-wave approximate Riemann solver, the Roe Riemann solver \citep{roe1981approximate}, is also adopted in GSPH for comparison.
+where $c_{LR}$ is the relevant Roe averaged sound speed \citep{cheng2007high}.
+
+Besides HLLC, another 2-wave approximate Riemann solver, the Roe Riemann solver \citep{roe1981approximate}, is also adopted in GSPH.
 Roe Riemann solver is proposed by \citet{roe1981approximate} to linearize the Euler equations and approxiamte the solution of non-linear system by a system of linear equations.
@@
 \citet{rider1994review} proposed an algebraic averaging of the Lagrangian variables, which is adopted in this work.
-The resulting intermediate states for the pressure and velocity are:
+Since Roe solver is only used in GSPH.
+We directly provide here the resulting starred values of the pressure and velocity \citep{puri2014approximate}:
 \begin{eqnarray}
@@
 
-\subsection{Picking up a single state}
-Solving the 1D Riemann problem with initial right and left states that the same as those on the paired particles leads to a solution of the local system.
-Then random sample these solutions to pick up a single state and assign its corresponding state to $p^{\ast}$ and $u^{\ast}$.
-Assume the solution between of a pair of particles ($a$ and $b$) to be $\textbf{W} (q) \forall q \in [q_a, q_b]$ (note, we use $\textbf{W}$ to represent the primitive variable vector $[\rho, u, p]^T$ and $\textbf{U}$ for conservative variable vector  $[\rho, \rho u, \rho E]^T$).
-The starred values would depend on the random number $\epsilon$.
-\begin{equation}
-p^{\ast} = p \left(\epsilon \left( q_a - q_b \right) \right)
-\label{eq:RSPH-Random-Pick-p}
-\end{equation}
-\begin{equation}
-u^{\ast} = u \left(\epsilon \left( q_a - q_b \right) \right)
-\label{eq:RSPH-Random-Pick-u}
-\end{equation}
-A short comments regarding the difference between application of RCM method in SPH and its application in finite volume method.
-In finite volume method, the superposition of solutions of Riemann problems defined on boundaries is taken as local solution within the cell and the sampled single state is assigned to the cell center.
-In RSPH, only one Riemann problem is defined between two particles and the sampled single state (the $p^{\ast}$ and $u^{\ast}$) is used in momentum and energy updating.
-Then it needs to project $u^{\ast}$ back to the 3D coordinate system to obtain $\textbf{v}^{\ast}$. One of such back-project approximations is:
-\begin{equation}
-\textbf{v}^{\ast}_{a b}=u^{\ast}_{a b} \hat{\textbf{r}}_{a b} + \left [\frac{\textbf{v}_{a} + \textbf{v}_{b}}{2} - \frac{u_L + u_R}{2} \hat{\textbf{r}}_{a b}\right]
-\label{eq:RP-project-to-3d-arithmetic}
-\end{equation}
-In Eq.
-(\ref{eq:RP-project-to-3d-arithmetic}), the arithmetic average of shear velocity is taken as the shear velocity in the star region.
-Alternative approximation might be distance weighted average or Roe average (weighted by square root of density).
-If $q_{a b}^{\ast}$ is assumed to be zero, then distance weighted average will degenerate to the arithmetic average.
-%Eigenstructure analysis shows that there are two additional contact discontinuity waves for 3D Euler equations.
-They are associated to two shear velocity components.
-Different from $u$ and $p$, the shear velocity is not constant in the star region.
-Using the average of left and right shear velocity as an approximate of shear velocity in the star region might be a poor approximation.
-We have to mention that it is strange in GSPH to assume an imaginary interface, which we never need in RSPH. And that's one of the reasons why we like RSPH more.
-
-\subsection{Binary Van Der Corput pseudo-random numbers}
-The random number $\epsilon$ is used to determine which single state ($p^{\ast}$ and $\textbf{v}^{\ast}$) of the solution of Riemann problem should be used in Eq.
-(\ref{eq:gov-gsph-v-simple-form}) and (\ref{eq:gov-gsph-e-simple-form}).
+\subsection{Binary Van Der Corput pseudo-random numbers} \label{sec:Van-Der-Corput-random-num}
+The random number $\epsilon$ is used to determine the sample location $q_{ab}^{RSPH}$.
 The quantity of the computed RCM solution depends crucially on the random number $\{\epsilon ^n\}$.
@@
 (\ref{eq:Van-Der-Corput-pseudo-random-num}).
-We take $x_1=2$  and $x_2 =1$ in our application.
+We take $x_1=2$  and $x_2 =1$ in this paper.
 Other combinations of $x_1$ and $x_2$ were also discussed by \citet{toro2013riemann}.
@@
 The chi-square statistic (see \citet{toro2013riemann} for its calculation) $\chi_{sq}$ is $1.0000$.
-The binary Van Der Corput pseudo-random numbers can be generated offline to save computational time.
+The binary Van Der Corput pseudo-random numbers are generated offline to save computational time.
 
@@
 \end{itemize}
-PESB algorithm is integrated into framework of SPH discretization to update physical quantities in time.
+PESB algorithm is integrated into framework of SPH discretization to update physical quantities in time. PESB also fit well with GSPH, for which, the sample step is not stochastic randomly sample.
 
@@
 Test 1 is simulated using standard SPH with different artificial viscosity coefficients, GSPH and RSPH.
-RSPH is compared with SPH using different artificial viscosity coefficients in Fig.
+The comparison between RSPH and SPH using different artificial viscosity coefficients is shown in Fig.
 \ref{fig:RCM-Sod-SPH-alf}.
@@
 First of all, dissipation (introduced by artificial viscosity in these tests) can decays the numerical fluctuations.
-Numerical fluctuations can be suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients.
+Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients.
 %The mechanism for SPH to reduce (or completely get rid of) fluctuations should be completely different from that of new adaptive method of smoothing length. 
@@
 So RSPH is actually more adaptive than SPH.
-This feature is very desirable as it could eliminates parameterization and hence user intervention associated with artificial viscosity coefficients.
+This feature is very desirable not only because it could eliminate parameterization and hence user intervention associated with artificial viscosity coefficients but also because it avoids introducing excessive artificial viscosity when unnecessary.
 Thirdly, RSPH introduces less smearing of the shock discontinuity compared with SPH using most commonly adopted artificial viscosity coefficients ($\alpha=1.0$, $\beta=2.0$).
@@
 
-\begin{figure}[H]
+\begin{figure}[htp]
     \centering
@@
 %It is also worthwile to check what of order of accuracy using another test problem.  
-
 \begin{figure}[H]
@@
 
-\begin{figure}[htp]
+\begin{figure}[H]
     \centering
@@
 
-\begin{figure}[htp]
+\begin{figure}[H]
     %\centering
@@
 \ref{fig:free-jet-comparison} implies that RSPH introduces less overall damping effect than GSPH in 3D application as well, which is consistent with 1D tests.
-That is to say, RSPH's desirable property of introducing less artificial dissipation 1D unsteady flow is inherited in 3D applications of RSPH.
+That is to say, RSPH's desirable property of introducing less artificial dissipation in 1D unsteady flow is inherited in 3D applications of RSPH.
 Recall that RCM shows ability of resolving discontinuities as true discontinuities in 1D unsteady flows but such very desirable property does not persist in genuine two (or higher) space dimensions \citep{colella1982glimm}.
@@
 The pressure ``wiggle" around contact discontinuity, which persists in SPH results, is eliminated in RSPH.
-It also shows higher order of convergence rate than GSPH when the same construction of local Riemann problem and Riemann solvers are adopted.
+It also shows higher order of convergence rate than GSPH when the same construction of local Riemann problem and Riemann solvers.
 The attractive property of less dissipation persist in multi-dimensional applications.

### 2018-06-01 ebp-JCPManuscript.tex
ap_clean edits1

--- 2018-01-08 JCP-Manuscript.tex
@@
 \begin{frontmatter}
-\title{Integrating random choice method with SPH : a new scheme with adaptive artificial viscosity and shock capturing ability}
+\title{IA Random Choice SPH Scheme with Adaptive Viscosity}
 %\tnotetext[mytitlenote]{Can add  title note here}
@@
 \begin{abstract}
-Standard smoothed particle hydrodynamics (SPH) employs an artificial viscosity, defined explicitly by constant coefficients, to properly capture hydrodynamic shock waves.
-Such methodology usually provides dissipation more than need and smears the discontinuities if the artificial viscosity coefficients are not tuned.
-Excessively large artificial viscosity might also damp generation of turbulence by fluid instability.
-We present in this article a novel SPH scheme with adaptive artificial viscosity, in which the artificial viscosity is determined implicitly based on solution of a local Riemann problem.
-Different from Godunov SPH (GSPH) method, which utilizing solution of local Riemann problem at an imaginary interface, the new method randomly sample the solution of Riemann problem mimicking the random choice method (RCM).
-One dimensional shock tube tests demonstrate several attractive features of this new scheme.
-First of all, it introduces less but sufficient artificial dissipation for shock capturing compared with classical SPH and GSPH.
-The pressure ``wiggle" around contact discontinuity, which persists in SPH results, is ameliorated by the new scheme.
-The new method also shows higher order of convergence than GSPH.
-%when the same construction of local Riemann problem and Riemann solvers are adopted by both methods. 
-Classical RCM method would lose its desirable property of low numerical dissipation when solving multi-dimensional unsteady non-linear systems.
-Combining of RCM with SPH overcomes the shortcoming  of classical RCM method.
-Three dimensional time dependent compressible Euler equations are solved by the new scheme for simulating a free jet flow, demonstrating that the desirable less dissipation property of the new scheme persists in multi-dimensional applications.
+The classical smoothed particle hydrodynamics (SPH) method
+employs artificial viscosity to properly capture shock waves in hydrodynamics. This artificial viscosity typically
+produces more dissipation than is needed to smooth shocks, incorrectly  smears 
+contact discontinuities, and can overwhelm fluid turbulence. 
+Several studies have proposed highly tuned versions of artificial viscosity,
+turning on and off near shocks or other troublesome wave features. 
+Unfortunately these schemes usually produce more dissipation than is appropriate.
+A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems 
+as building blocks for a numerical SPH solver. Of course a first order Godunov solver still introduces an effective numerical diffusion that can infect the entire numerical solution.
+We propose a novel SPH scheme that combines an approximate
+ version of Glimm\rq{}s Random Choice method (RCM)
+with SPH. RCM properly resolves and then samples all hydrodynamic waves, and
+introduces no numerical diffusion into a simulation. Our version approximately resolves
+hydrodynamic waves, and samples the approximate solution.
+We test this method on standard one dimensional shock tube problems.
+Our ultimate goal is to apply this method to jet flow. Because of the high shear rate
+in this application, we introduce a highly tuned eddy viscosity that is applied only near 
+the shear surface.  The combination of the SPH and RCM together with a shear viscosity
+produces nicely resolved jet profiles.
+
 \end{abstract}
@@
 \section{Introduction}
-Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on Lagrangian formulation and has been widely applied to different areas in engineering and science.
-SPH has both advantages and disadvantages with respect to other numerical techniques.
-One main advantage is that it automatically adapts to following dynamic flows and arbitrary geometries.
-Another advantage is that it needs less programming effort to include more physics.
-In addition, SPH particles only interact with neighboring particles, which avoids massive global communication in parallel implementation of SPH.
-Historically, SPH has difficulty in capturing discontinuities, such as shocks or contact discontinuities.
-Inviscid description of fluids becomes invalid at shock fronts, where specific entropy of the fluids increases through the conversion of mechanical energy into internal energy.
-Most SPH codes have included an artificial viscosity term explicitly, both for stabilizing the simulation and for handling shock discontinuities by dissipating local velocity differences and converting them into heat \citep{monaghan1983shock, monaghan1997sph, klapp2012strong}.
-Without knowing the minimum amount of dissipation for shock capturing, such methodology usually provides dissipation more than need and smears the discontinuity if the artificial viscosity coefficients are not tuned.
-The method of using constant artificial viscosity might also introduce spurious effects at region away from shocks, for instance, causing an unphysical damping of turbulent mixing (as shown, for example, by \citet{borgani2012hydrodynamic}) or spurious
-shearing torques in rotating flows \citep{flebbe1994smoothed}.
-Selective application of artificial viscosity techniques, such as the time dependent viscosity \citep{morris1997switch, dolag2005turbulent} and shock-indicator-based viscosity \citep{cullen2010inviscid} have been tried for counteracting this.
-\citet{sigalotti2008adaptive} improved the standard SPH near sharp discontinuities adopting adaptive density kernel estimation (ADKE) techniques.
-However, the parameters for ADKE have to be tuned to the problem at hand \citep{puri2014comparison}.
-Hence it is hard to implement ADKE in real applications.
-
-Besides adding dissipation explicitly, \citet{inutsuka2002reformulation} proposed an innovative approach to introduce dissipation implicitly by reformulating the SPH convolution integrals.
-Artificial viscosity is introduced implicitly by using iterative solution to a Riemann problem at an imaginary interface between an interacting particles pair.
-This method, named as Godunov SPH (GSPH), is attractive because it eliminates parameterization and hence user intervention associated with artificial viscosity coefficients.
-The GSPH method has been shown to be able to handle shock discontinuities \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate}, introduces less damping to turbulent mixing \citep{cha2010kelvin, borgani2012hydrodynamic} than standard SPH, and ameliorate pressure ``blips" (or ``wiggle" called by others) at the contact discontinuity \citep{borgani2012hydrodynamic}.
-However, the amount of dissipation introduced by GSPH is stll excessive than needs.
-When using a linear interpolation of the volume function, it has been shown \citep{borgani2012hydrodynamic} that the excess of diffusion, which manifests itself in the shock tube tests as a smooth transition at the rarefaction fan, is such to prevent the development of the Kelvin-Helmholtz (KH) instability.
-%The development of KH instability is also significantly affected by number of neighbouring particles for cubic interpolation of the volume function.
-
-The random choice method (RCM) was introduced by \citet{glimm1965solutions} for the construction of solutions of systems of nonlinear hyperbolic conservation laws.
-\citet{chorin1976random} developed the RCM as a practical computational method for solutions to one dimensional (1D) Euler equations of gas dynamics.
-Chorin's work was followed by numerous researchers, with applications and further improvements \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical}.
-In essence, the solution is advanced in time by a sequence of operations that include solving of Riemann problems and a stochastic sampling of the solution.
-See \citep{toro2013riemann} for details.
-When applied to one dimensional time dependent Euler equations \citep{colella1982glimm}, diffusive errors from spatial averaging are completely eliminated and hence discontinuities, such as shocks or material interface, can be resolved as true discontinuities.
-For unsteady flows in genuine two (or higher) space dimensions, however, such very desirable property of RCM do not seem to persist \citep{colella1982glimm}.
+Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on a Lagrangian formulation of the governing equations of  motion.
+SPH has been widely applied to different areas in engineering and science. As
+should be expected, SPH possesses certain advantages and certain disadvantages relative to finite difference and finite element solvers. Principally, as a Lagrangian solver SPH conserves mass 
+exactly. 
+In addition, because of its formulation SPH automatically concentrates numerical effort in regions of
+high density and adapts to  arbitrary geometries. On the other hand, 
+SPH has difficulty capturing shock waves and contact discontinuities. To overcome numerical
+oscillations at discontinuities, classical SPH introduces
+an artificial viscosity term. At it is most often used, when two SPH particles
+are approaching, a von Neumann type viscosity is introduced
+\citep{monaghan1983shock, monaghan1997sph,klapp2012strong}. 
+This kind of viscosity, however, 
+ usually provides more dissipation  than is truly needed at a discontinuity, and the excess
+ dissipation ultimately
+ corrupts the entire computation. Various methods have been introduced to tune 
+ the artificial viscosity, turning it on and off for particular wave features. However, 
+ tuning switches cannot properly accommodate every kind of wave that might arise, 
+ and 
+ spurious effects and unphysical damping persist (see, for example, \citet{borgani2012hydrodynamic,flebbe1994smoothed,morris1997switch, dolag2005turbulent,cullen2010inviscid,sigalotti2008adaptive,puri2014comparison}).
+
+To overcome troublesome oscillations, \cite{inutsuka2002reformulation} and later \cite{cha2003implementations} formulated an SPH scheme that uses Riemann problems to 
+resolve the interactions of particles. This Godunov-SPH (GSPH) method can resolve shocks and pressure 
+oscillations without additional
+artificial viscosity 
+ \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate,borgani2012hydrodynamic}.
+It has also been shown to introduce less damping in turbulent mixing \citep{cha2010kelvin, borgani2012hydrodynamic} than standard SPH.
+However, the dissipation introduced by GSPH is still larger than physically relevant, to the point
+of inhibiting the development of the Kelvin-Helmholtz instability under certain conditions
+ \citep{borgani2012hydrodynamic}.
+
+The Godunov approach to solving Riemann problems in the context of numerical methods for conservation laws is to 
+integrate the Riemann problem solution over a spatial interval of interest. A different approach is given by
+the 
+random choice method (RCM) was introduced by \citet{glimm1965solutions} for the construction of solutions of systems of nonlinear hyperbolic conservation laws. The RCM probabilistically samples the
+Riemann problem solution in each interval, and thus introduces no viscosity whatsoever. Because this
+sampling interrogates the exact Riemann problem solution, no over- or under-shoots are introduced,
+so, irrespective of the absence of viscosity, no non-physical oscillations are introduced either.
+
+\citet{chorin1976random} developed the RCM into a practical computational method for solutions of the Euler equations in one space dimension.
+This approach was later extended to two dimensions \cite{chorinporousmedium}. Others
+further refined the random choice method \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical,toro2013riemann}. 
 %This need to be proven ---> But at least, if the good property of preserving true discontinuity is still valid in 1D shock tube problem, it should be preserved in multiple-dimensional implementations.
 Because in current framework of RSPH, no matter what is the dimension of the problem, the techniques is only implemented in a one-dimensional scenario.
-
-In this investigation, we introduce a new method, which will be referred to as RSPH in later paragraph, by integrating RCM method within framework of SPH. 
-The new scheme inherits the attraction of classical RCM, introducing less but sufficient artificial viscosity and causing less smearing of discontinuities than other methods for 1D problems.
-Implementing of RCM within the framework of SPH only involves sampling of solutions of Riemann problem in 1D local coordinate system no matter what is the dimensionality of the problem.
-That is to say, no multi-dimensional coordinate is involved even for multi-dimensional problems.
-Thereby, the desirable property of RCM method in 1D should be retained in higher dimensional implementations within the framework of SPH.
-This hypothesis is confirmed by a three-dimensional (3D) free jet flow simulation.
-
-To summarize, RSPH has the following advantages over standard SPH:
-\begin{itemize}
-\item RSPH is able to capture discontinuities with less smearing.
-\item The RSPH is able to adaptively adjust equivalent artificial viscosity coefficients, assigning larger artificial viscosity coefficients around the shock and small artificial viscosity coefficients otherwhere.
-\item RSPH is able to alleviate pressure ``wiggle" at the contact discontinuity, a common issue in classical SPH.
-\end{itemize}
-Compared with GSPH, which is also based on solution of local Riemann problems, RSPH introduces less but sufficient dissipation than GSPH, especially in the region away from shocks.
-Such feature of RSPH is especially beneficial for simulating of scenarios involving turbulence mixing, for which excessive dissipation would suppress mixing.
-In addition, RSPH also shows faster convergence rate than GSPH.
-
-The scheme of this paper is follows.
-We start with a brief review of standard SPH and GSPH in the second section.
-The RSPH is then explained in details in the third section followed by the numerical tests section, where both one 1D and 3D inviscid Euler equations (see Eq.
-(\ref{eq:gov-cs-rho}) - (\ref{eq:gov-cs-e}) are solved by standard SPH, GSPH and RSPH.
-Limitations and potential applications of RSPH are discussed in last section.
-
-Our investigation implements RSPH scheme in solving inviscid compressile Euler equations as the application case.  
+%
+Later, Harten and Lax \cite{hartenlax} proposed approximately solving a Riemann problem based 
+on a finite difference scheme, and sampling this approximate solution. Our approach here 
+is based on the Harten-Lax proposal. 
+We introduce a new method which we dub RSPH, by randomly sampling the interaction
+of pairs of SPH particles. 
+This scheme produces dissipation-free solutions, as does classical RCM, but for a Lagrangian 
+system.
+ Because the 
+interaction of SPH particles are inherently one-dimensional, the RCM framework
+is straightforward to implement.
+We test this RSPH idea first on classical shock tube problems, where we can compute very accurate
+solutions.
+We then implement RSPH for a three-dimensional free jet flow simulation, a prototype for
+our ultimate goal of simulating a
+Plinian volcanic eruption.
+
+%To summarize, RSPH has the following advantages over standard SPH:
+%\begin{itemize}
+%\item RSPH is able to capture discontinuities with less smearing.
+%\item The RSPH is able to adaptively adjust equivalent artificial viscosity coefficients, assigning larger artificial viscosity coefficients around the shock and small artificial viscosity coefficients otherwhere.
+%\item RSPH is able to alleviate pressure ``wiggle" at the contact discontinuity, a common issue in classical SPH.
+%\end{itemize}
+
+Section \ref{sph} provides a brief review of standard SPH, and shows how the
+GSPH method is defined in section \ref{sec:GSPH-method}. The RSPH method is defined in Section \ref{rsph}.
+One dimensional tests are shown in Section \ref{tests}, followed by the jet flow
+example in Sec. \ref{jet}. 
+Other applications and limitations  of RSPH are discussed in Section \ref{discussion}
+
+\section{SPH Formulations} \label{sph}
+Throughout this paper we will be concerned with solving the Euler equations, written as
 \begin{align}
@@
 \end{align}
-where $\rho$ is the density, $\textbf{v}$ is the velocity, $\textbf{I}$ is a unit tensor.
-$E = e + K $ is the total energy which is a summation of kinetic energy $K$ and internal energy $e$.
-The system of equations is closed by equation of state (EOS) for idea gas.
+Here $\rho$ is the density, $\textbf{v}$ is the velocity, $\textbf{I}$ is a unit tensor.
+$E = e + K $ is the total energy which is a sum of a 
+kinetic energy $K$ and an internal energy $e$.
+The system of equations is closed by the equation of state  for an idea gas
 \begin{equation}
@@
 
-For any SPH scheme, governing equations in Lagrange form are needed.
-By deducting kinetic energy from energy equation, subtracting mass conservation from momentum equation, combining transient term and advection term into material derivative (for any function $A$, material derivative is defined as $\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$) term, the governing equations are converted into the Lagrange form.
-\begin{align}
+SPH is a Lagrangian scheme, so we rewrite the governing equations  as
+\begin{align}   %\label{eq:lagrangian}
 \dfrac{D \rho}{D t} + \rho \nabla \cdot \textbf{v} = 0 \label{eq:gov-nc-rho}\\
@@
 \end{align}
+In this formulation we have written the material derivative  as 
+$\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$) for a conserved variable $A$.
+
 %\cutet{puri2014comparison} propose an addition of an artificial heating term to the GSPH scheme to eliminate unphysical spikes in the thermal energy at the contact discontinuity.
@@
 
-\section{Standard SPH and GSPH method}
-The RSPH method is based on standard SPH and GSPH.
-In addition, these three methods will be compared in the numerical tests section.
-So it is necessary to review discretization of the compressible Euler equations by SPH and GSPH.
-We present here a brief review on standard SPH and GSPH providing corresponding discretized governing equations.
-
-\subsection{Standard SPH method}
-In SPH, the domain is discretized by a set of particles or discretization points and the position of each particle is updated at every time step based on the motion computed.
-Approximation of all field variables (velocity, density and pressure, ect.) is obtained by interpolation based on discretization points.
-The physical laws (such as conservation laws of mass, momentum and energy) written in the form of partial differential equations (PDEs) or ordinary differential equations (ODEs) need to be transformed into the Lagrangian particle formalism of SPH.
-Using a kernel function that provides the weighted estimation of the field variables at any point, the integral equations are estimated as sums over particles in a compact subdomain defined by the support of the kernel function associated with the discretization points.
-Thus, field variables associated to the particle are updated based on its neighbors.
-Each kernel function has a compact support determined by smoothing length of the particle.
-Various tricks can be used to conserve linear and angular momentum and thermal energy \citep{monaghan1992smoothed}.
-Special treatments are also needed for second order derivative terms \citep{monaghan2005smoothed}.
-We only refer here to one of these possible discretization of compressible Euler equations, while we refer to \citet{ monaghan2005smoothed, liu2010smoothed, price2012smoothed} for complete formal derivation and other discretization formulations.
+\subsection{Standard SPH}
+In the classical SPH formulation a fluid is divided into   a number of particles whose 
+location is updated at every time step. An approximation to the field variables (velocity, density and pressure) is obtained by interpolation of particle quantities using  a kernel.
+We will only consider kernel functions with  compact support. Derivatives of variables are 
+converted into derivatives of the kernel function, and different formulations of the
+derivatives can be shown to possess various properties; see 
+ \citep{monaghan1992smoothed,monaghan2005smoothed,liu2010smoothed, price2012smoothed} for details.
+ Thus the density due to particle $a$ can be written as a sum
+ $<\rho_a> = \sum_b m_b w_{ab} \left(h\right) \label{eq:ns-sph-d}$, where 
+ where $m_b$ is the  mass of the $b^{th}$ SPH particle and $w_{ab}$ is 
+ the kernel interpolating between 
+ particles $a$ and $b$, with a kernel smoothing length $h$. 
+ Particle position is updated at every time step according to  a simple advection
+\begin{equation}
+\left\langle\dfrac{d \textbf{x}_a}{dt}\right\rangle = \textbf{v}_a \label{eq:SPH-update-pos}
+\end{equation}
+
+ Using this framework, derivative terms in (\ref{eq:gov-nc-rho})--(\ref{eq:gov-nc-e}) are written 
 \begin{align}
-<\rho_a> = \sum_b m_b w_{ab} \left(h\right) \label{eq:ns-sph-d} \\
 \left\langle\dfrac{d \textbf{v}_a}{d t}\right\rangle = -\sum_b m_b \left(\dfrac{p_b}{\rho_b^2} + \dfrac{p_a}{\rho_a^2} + \Pi_{ab}\right) \nabla_a w_{a b}\left(h\right) \label{eq:ns-sph-v} \\
@@
 \end{align}
-where, $a$ is the SPH particle index, $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$. The smoothing length $h$ is taken as $h=\frac{h_a + h_b}{2}$. $\Pi$ is an artificial viscosity term.
+Here $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$, the smoothing length $h$ 
+is taken as $h=\frac{h_a + h_b}{2}$, and $\Pi$ is an artificial viscosity term.
 One of commonly used models of artificial viscosity \citep{monaghan1983shock} is:
@@
 \end{equation}
-The coefficient $\nu$ is defined as:
+where the coefficient $\nu$ is defined as
 \begin{equation}
@@
 \end{equation}
-where 
+with
 \begin{align}
@@
 \end{align}
-The artificial viscosity term $\Pi_{ab}$ is a Galilean invariant and vanishes for rigid rotation.
+This form of the artificial viscosity  is a Galilean invariant and vanishes for rigid rotation.
 It produces a repulsive force between two particles when they are approaching each other and an attractive force when they are receding from each other.
-An extra term was added to $\nu$ considering aspects of the dissipative term in shock solutions based on Riemann solvers and lead to a new formulation of artificial viscosity \citep{monaghan1992smoothed}.
-We adopt this new formulation in our simulation:
+Later,  Monaghan\citep{monaghan1992smoothed} added terms to the viscosity,
+obtaining the form we will use in computations below:
 \begin{equation}
@@
 %$\alpha$ and $\beta$ are two parameters that are free to be adjusted for each case. 
-$\alpha$ and $\beta$ are two parameters that can be adjusted for different cases.
-$\alpha = 1$ and $\beta = 2$ are recommended \citep{monaghan2005smoothed} for best results and mostly adopted.
-In the numerical test section, these two parameters are varied to show the effect different amount of numerical dissipation on simulation results.
-$\eta$ is usually taken as 0.1 to prevent singularities.
-
-In Eq.
-(\ref{eq:ns-sph-d}) - Eq.
-(\ref{eq:ns-sph-e}), $w_{a b}\left(h\right)$ is weighting function and is a concise form of $w\left(\textbf{x}_a - \textbf{x}_b, h\right)$.
-We will use this concise form throughout this paper.
-There is a wide variety of possible weighting functions, such as spline functions (with different orders) and Gaussian functions.
-We adopt a truncated Gaussian function as the weighting function for standard SPH, GSPH and RSPH.
+Here $\alpha$ and $\beta$ are free parameters that are adjusted as needed. 
+\citep{monaghan2005smoothed}  recommends $\alpha = 1$ and $\beta = 2$ as
+good fits for many computations.
+ $\eta$ is usually taken as 0.1.
+
+In Eq. (\ref{eq:ns-sph-d}) - Eq. (\ref{eq:ns-sph-e}), $w_{a b}\left(h\right)$ is the kernel
+weighting function, expressed more completely as
+ $w\left(\textbf{x}_a - \textbf{x}_b, h\right)$. 
+Many  weighting functions have been proposed, but, for simplicity,  we 
+employ a truncated Gaussian in $d$ dimensions
 \begin{equation}
@@
 \end{equation}
-where $d$ is number of dimensions.
-The derivative of the weighting function is:
+Derivatives of $w$ above can be written as 
 \begin{equation}
@@
 
-As a Lagrangian method, particle position is also updated at every time step according to:
-\begin{equation}
-\left\langle\dfrac{d \textbf{x}_a}{dt}\right\rangle = \textbf{v}_a \label{eq:SPH-update-pos}
-\end{equation}
-
-\subsection{GSPH method} \label{sec:GSPH-method}
-Here we present essential formulations for solving Euler equations with GSPH.
-The density field is updated in the same way as updating of density in SPH, according to Eq.
-(\ref{eq:ns-sph-d}).
-Updating of velocity and internal energy in GSPH is different from these in SPH.
-Derivation of discretized momentum and energy equation in first GSPH paper \citep{inutsuka2002reformulation} is based on the following discrete consistency identities: 
+To complete our specification of the classical SPH scheme we must decide on the time 
+integration method. A forward Euler step with sufficiently small timestep suffices for purposes of the exposition
+here.
+
+\subsection{GSPH} \label{sec:GSPH-method}
+Inutsuka \cite{inutsuka2002reformulation} recognized that the Godunov approach of 
+solving local Riemann problems might obviate the need for artificial viscosity.  This sub-section 
+describes this GSPH method. Our discussion  anticipates that of
+Section \ref{sec:RSPH-method}, and sub-section \ref{sec:Picking-up-single-state}
+ in particular, which contain details that are only briefly
+introduced here.
+
+The density continues to be updated based on particle location from Eq. (\ref{eq:ns-sph-d}).
+However the update for the momentum and energy equations differs fundamentally from the
+classical SPH approach. We begin by making two observations, the first regarding the density
 \begin{equation}
@@
 \end{equation}
+and the second regarding the derivative 
 \begin{equation}
@@
 \end{equation}
-Lengthy algebraic manipulations \citep{inutsuka2002reformulation,iwasaki2011smoothed} lead to the discretized momentum and energy equations:
+We re-formulate the equations of motion to exploit a certain symmetry. A
+lengthy algebraic manipulation \citep{inutsuka2002reformulation,iwasaki2011smoothed} leads to:
 \begin{equation}
@@
 \end{equation}
-where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are obtained by solving a 1D Riemann problem constructed based on physical quantity of particle $a$ and particle $b$.
-The starred quantity are interpolated value of the solution to the Riemann problem at an imaginary interface.
-More discussion about the imaginary interface is in section \ref{sec:Picking-up-single-state}.
+where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are intermediate states derived from
+the interaction of particles $a$ and $b$. Inutsuka proposed this intermediate $\ast$ state 
+be defined as the stationary state of the solution to a local 1-dimensional Riemann for particles
+$a$ and $b$.  That is, one rotates coordinates, reducing the particle interaction to  
+one space dimension along the line connecting particle $a$ and particle $b$. Using the
+momentum and energy of the two particles as 
+left and right states, one solves the Riemann problem for the starred quantities.
+
+Having solved the local Riemann problem, 
 $\dot{\textbf{x}}_{a}^{\ast}$ is time centered velocity of particle $a$:
@@
 \end{equation}
-
-The difference between this formulation and classical SPH formulations come from two sources: 
-\begin{itemize}
-\item the averaged (in certain sense) pressure and the effect of artificial viscosity is replaced by  $p^{\ast}$, obtained based on a local Riemann solver.
-\item a time centered velocity is used, which satisfies the following identities approximately. 
-\begin{equation}
-\left( \textbf{v}_{a b}^{\ast} - \dot{\textbf{x}}_{a}^{\ast} \right) \approx -0.5 \textbf{v}_{a b}
-\label{eq:SPH-GSPH-difference2}
-\end{equation}
-%Where $\textbf{v}_{a b}$ is defined as $\textbf{v}_a - \textbf{v}_b$.
-\end{itemize}
-Actually, Godunov's idea of using Riemann solver can be combined with other SPH discretization formulations as well \citep{cha2003implementations}.
-
-More technical details of GSPH are in section \ref{sec:RSPH-method}.
-The construction of Riemann problem, Riemann solvers and projection of picked solution of the Riemann problem back to global coordinate system are exactly the same in GSPH and RSPH.
-They are described in the next section.
-The way how to pick up the starred value from solution of the Riemann problem is the only difference between GSPH and RSPH.
-Detailed discussion is presented in section \ref{sec:Picking-up-single-state}.
-
-\section{RSPH method} \label{sec:RSPH-method}
-RSPH shares many commonalities with SPH and GSPH, especially with GSPH.
-We adopt the same density updating formulation (see Eq.
-(\ref{eq:ns-sph-d})) for density updating in SPH, GSPH and RSPH.
-The same kernel function is used for all schemes.
-The equation for updating particle position (see Eq.
-(\ref{eq:SPH-update-pos})) is also the same for all schemes.
-Discretized governing equations for RSPH and GSPH are exactly the same as well.
-The common palces shared with classical SPH and GSPH are unnecessary to repeat in this section.
-We focus more on where RSPH is different from SPH and GSPH.
-
-Both GSPH and RSPH borrow ideas of shock capturing techniques from mesh based method.
-There is a great deal of commonality between Godunov's method and RCM for mesh based method.
-Both of them utilize the solution of a local Riemann problem.
-The difference is that the RCM pick up a single state contained in the local solutions ``randomly" while Godunov's method take the integral average.
-Integrating of Godunov's idea within SPH framework (the GSPH method), however, does not take the integral average at all.
-Instead, a single state of the local Riemann solution at an imaginary interface is picked up and used to upgrade physical quantities through discretized governing equations (see Eq.
-(\ref{eq:gov-gsph-v-simple-form}) - Eq.
-(\ref{eq:gov-gsph-e-simple-form})).
-The RSPH method, proposed in this paper mimicking classical RCM, picks up the single state by stochastic sampling.
-So the difference between RSPH and GSPH is how to pick up the single state from solution of the Riemann problem.
-
-Technical details for GSPH which are not coverred in section \ref{sec:GSPH-method} are also presented in this section.
-The piecewise constant construction of Riemann problem, which is adopted in both RSPH and GSPH, is presented in section \ref{sec:RP-construction}.
-The way to pick up a single state from solutions to local Riemann problems are formulated in section \ref{sec:Picking-up-single-state}.
-It is a common practice in real implementations of Godunov's method to use approximate non-iterative Riemann solvers.
-Two non-iterative Riemann solvers, Roe Riemann solver and HLLC (Harten, Lax and van Keer scheme with contact) Riemann solver \citep{toro1994restoration}, are adopted in GSPH.
-The HLLC type of Riemann solver \citep{toro1994restoration}, in which the contact wave is considered, is used in RSPH.
-Section \ref{sec:RP-solver} presents details on these Riemann solvers.
-
-The last second subsection is about generating of random numbers for RSPH. The RSPH algorithm is summarized in last subsection.
-
-\subsection{Defining of local 1D Riemann problem} \label{sec:RP-construction}
-A 1D Riemann problem need to be solved to obtain  $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ in both GSPH and RSPH.
-Hence, a 1D Riemann problem need to be constructed first.
-Constructing of 1D Riemann problem starts from establishing of a local coordinate system ($q$).
-The origin is selected at the middle-point of the line segment joining two particles with the unit vector along the line defined as:
+which then updates particle location.
+
+Of course solving the local Riemann problem for every pair of interacting particles is a 
+computationally intensive process. Further, from this complex Riemann solution
+only the stationary state is used. \cite{hll} provided a framework for calculating approximate
+solutions to local Riemann problems, and influences how
+we propose
+to approximate the  Riemann solution, using ideas from the RCM and \cite{hartenlax}.
+
+\section{The Random Choice SPH method(RSPH)} \label{sec:RSPH-method}
+In GSPH,  the starred state is the solution to a local Riemann problem at a location
+determined by a weighted average of the specific volumes associated with
+ the two participating particles. 
+Instead of calculating a full solution to the Riemann problem, approximate solvers such as
+the Roe method or HLLC,
+might be used. 
+We propose sampling the (approximate) Riemann solution as in the Random choice method, 
+where the approximate solution is given by the HLLC construction (see \cite{toro1994restoration}).
+
+\subsection{The local 1D Riemann problem} \label{sec:RP-construction}
+The starred state is the solution to a local 1-dimensional Riemann problem.
+Given particles $a$ and $b$, rotate coordinates to establish a single spatial dimension
+along the line connecting the two particles, with direction 
 \begin{equation}
 \hat{r}_{a b}= \frac{\textbf{x}_{a} - \textbf{x}_{ b}}{|\textbf{x}_{a} - \textbf{x}_{ b}|}
-\end{equation}
-Then vector variables, such as velocity, need to be projected onto the local coordinate system (Eq. (\ref{eq:RP-project-2-local-a}) and Eq. (\ref{eq:RP-project-2-local-b})). 
+\end{equation}. 
+Let the midpoint of this line segment
+be the origin of the coordinate system. 
+Project variables into this local coordinate system:
 \begin{equation}
 u_{a}= \textbf{v}_{a} \cdot \hat{r}_{a b}
-\label{eq:RP-project-2-local-a}
-\end{equation}
-\begin{equation}
+~~~~~~~~~~
 u_{b}= \textbf{v}_{b} \cdot \hat{r}_{a b}
-\label{eq:RP-project-2-local-b}
-\end{equation}
-Scalar variables are simply assigned to corresponding points without projection.
-
-The RSPH essentially takes the ``piece wise constant" manner for Riemann problem construction.
-No further step is required for construction after projection.
-Recall that in GSPH method, the construction of Riemann problem is divided into two sub-steps: projection and construction.
-Different from original Godunov's method, which assumes piecewise linear distribution of the data (or higher order method like MUSCL and PPM which use higher order polynomial approximation), RCM method assumes that the given data at the center of cell is constant throughout the respective cell.
-The same idea can be easily (and naturally) applied in RSPH as there is actually no cell in SPH method.
-Then the Riemann problem is defined directly based on data on particles.
-There is no need to calculate and project first order derivative of $\rho$, $u$ and $p$, which are needed for constructing of Riemann problem in a piece wise linear manner.
-The computation associated with calculation of gradient and projection of gradient is avoided when constructing 1D Riemann problem in such a ``piece wise constant" manner.
-Per above description, the initial states at left and right sides are given as: 
+\label{eq:RP-project-2-local}
+\end{equation}
+Piecewise constant left and right states are then given by the projected 
+variables on either side of the origin
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-\subsection{Picking up a single state} \label{sec:Picking-up-single-state}
-Solving the 1D Riemann problem with initial right and left states (Eq.
-(\ref{eq:Riemann-Prob-define-L-rho}) - Eq.
-(\ref{eq:Riemann-Prob-define-R-p})) leads to a solution of the local system.
-Then pick up a single state and assign it to $p^{\ast}$ and $u^{\ast}$.
-The location where the single state is picked up is different for RSPH and GSPH.
-The starred values for RSPH takes the solution of the local Riemann problem at location $q_{ab}^{RSPH}$, which depends on a random number $\epsilon$.
-\begin{equation}
-q_{ab}^{RSPH}=\epsilon \left( q_a - q_b \right) - \frac{| q_a + q_b|}{2}
-\label{eq:sample-location-RSPH}
-\end{equation}
-At the nth time step, the same random number $\epsilon^n$ is used for picking up the single state from solutions of all local Riemann problems.
-For the next time step, the next pseudo random number $\epsilon^{n+1}$ will be used.
-Recall that the starred value for GSPH is taken as solution of the local Riemann problem at a fixed location, denoted as $q_{ab}^{GSPH}$.
-In original GSPH, the imaginary interface is determined based on interpolation of the specific volume between two paired particles \citep{inutsuka2002reformulation}.
-We set the fixed location at the middle point \citep{cha2003implementations} for simplicity.
-\begin{equation}
-q_{ab}^{GSPH}= 0
-\label{eq:sample-location-GSPH}
-\end{equation}
-
-Denote the solution of the local Riemann problem, either accurate or approximate, between a pair of particles ($a$ and $b$) to be $\textbf{W} (q), \  \forall q \in [q_a, q_b]$ (note, we use $\textbf{W}$ to represent the primitive variable vector $[\rho, u, p]^T$ and $\textbf{U}$ for conservative variable vector  $[\rho, \rho u, \rho E]^T$).
-The starred value for both GSPH and RSPH can be expressed in the same way:
-\begin{equation}
-p_{ab}^{\ast} = p \left(q_{ab}^{\ast} \right)
-\label{eq:RSPH-Random-Pick-p}
-\end{equation}
-\begin{equation}
-u_{ab}^{\ast} = u \left(q_{ab}^{\ast} \right)
-\label{eq:RSPH-Random-Pick-u}
-\end{equation}
-where $q_{ab}^{\ast}=q_{ab}^{GSPH}$ for GSPH while $q_{ab}^{\ast}=q_{ab}^{RSPH}$ for RSPH.
-The random sample range for RSPH and imaginary interface for GSPH is shown in Fig.
-\ref{fig:pick-up-state-GSPH-RSPH}.
+[Aside: Cha \cite{cha2003implementations} proposed a second order accurate 
+GSPH method by using
+a piecewise linear interpolation of the states. We do not pursue higher accuracy here,
+although the idea is straightforward to consider.]
+
+\subsection{Selecting the star state} \label{sec:Picking-up-single-state}
+Consider then the spatial interval between $\textbf{x}_{a}$ and $\textbf{x}_{ b}$ and a short time interval
+of size $\Delta t$. Recall also that, by convention, we assign the (spatial) origin to
+be at the midpoint between particles $a$ and $b$, 
+$\frac{(\textbf{x}_{a}| + \textbf{x}_{ b})}{2}$.
+Given the piecewise constant
+ data (Eq. (\ref{eq:Riemann-Prob-define-L-rho}) - Eq. (\ref{eq:Riemann-Prob-define-R-p})), solve the local Riemann problem. 
+ At time $\Delta t$ the solution defines a state composed of constants,
+rarefaction waves, contact discontinuities, and shock discontinuities. 
+Now choose a random number $\epsilon \in [-1,1]$, and set 
+$p_{a b}^{\ast}$ and $\textbf{u}^{\ast}$ to be the Riemann problem solution
+at the location 
+$$
+\epsilon |\textbf{x}_{a}| - \textbf{x}_{ b}|
+$$
+(relative to the the origin).
+
+It is common to use the same $\epsilon$ for all particle interactions at a specific time level.
+
+Figure \ref{fig:pick-up-state-GSPH-RSPH} shows the starred state for GSPH and RSPH.
 \begin{figure}[H]
@@
 	\includegraphics[width=0.5 \textwidth]{./Figures/RSPH-GSPH}
-    \caption{Evaluating of the starred values in RSPH and GSPH for paired particles $a$ and $b$.
-The local Riemann problem is defined by state of particles $a$ and $b$ at $t=0$ according to Eq.
-(\ref{eq:Riemann-Prob-define-L-rho}) - Eq.
-(\ref{eq:Riemann-Prob-define-R-p})).
-The horizontal bold solid line indicate the sample range in the solution of the Riemann problem defined between particle $a$ and particle $b$ at given time $t=\Delta t$.
-The dark ellipse is an example sample point of RSPH with the random number $\epsilon < \frac{1}{2}$.
-Depending on the random number $\epsilon$, the sample points can be anywhere on the horizontal bold solid line.
-The white ellipse is the imaginary interface for GSPH, which is fixed.
-The sampled state is assigned to starred velocity and pressure in Eq.
-(\ref{eq:gov-gsph-v-simple-form}) and Eq.
-(\ref{eq:gov-gsph-e-simple-form}) for both GSPH and RSPH.}
+    \caption{Evaluating of the starred state for  RSPH and GSPH implementations.
+Particles are located at $\textbf{x}_{a} $ and $ \textbf{x}_{ b}$, and the local Riemann problem is defined by the constant states $(u, p)_a$ and $(u,p)_b$.
+  The horizontal bold solid line at time $\Delta t$ indicates the interval on which to
+  evaluate the solution of the Riemann problem.
+  The dark ellipse is an example sample point of RSPH with the random number. The white ellipse indicates the stationary state, which is the starred state in GSPH.  }
     \label{fig:pick-up-state-GSPH-RSPH}
@@
 
-A short comments regarding the difference between application of RCM method in SPH and its application in finite volume method.
-In finite volume method, for 1D case, two Riemann Problems are definied on interfaces of both sides.
-the superposition of solutions of these two Riemann problems is taken as local solution within the cell and the sampled single state is assigned to the cell center.
-In RSPH, only one Riemann problem is defined between two particles and the sampled single state (the $p^{\ast}$ and $u^{\ast}$) is used in momentum and energy updating.
-
-$u^{\ast}$ is velocity in a 1D local space and needs to be projected back to global space to obtain $\textbf{v}^{\ast}$ in cases of multi-dimensional implementations.
-One of such back-project approximations is:
-\begin{equation}
-\textbf{v}^{\ast}_{a b}=u^{\ast}_{a b} \hat{\textbf{r}}_{a b} + \left [\frac{\textbf{v}_{a} + \textbf{v}_{b}}{2} - \frac{u_L + u_R}{2} \hat{\textbf{r}}_{a b}\right]
-\label{eq:RP-project-to-3d-arithmetic}
-\end{equation}
-In Eq.
-(\ref{eq:RP-project-to-3d-arithmetic}), the arithmetic average of shear velocity is taken as the shear velocity at the sample points.
-Alternative approximation might be distance weighted average or Roe average (weighted by square root of density).
-If $q_{a b}^{\ast}$ is assumed to be zero, then distance weighted average will degenerate to the arithmetic average.
-Such back projection is required for both GSPH and RSPH.
-
-We have to mention that it is strange in GSPH to assume an imaginary interface, which never need in RSPH. And that's one of the reasons why we like RSPH more.
+The starred state $(\textbf{u}^{\ast},  p^{\ast})$ must now be projected back into the global coordinate system,
+to define  $(\textbf{v}^{\ast},  p^{\ast})$.
+
+%\subsubsection{Binary Van Der Corput pseudo-random numbers} \label{sec:Van-Der-Corput-random-num}
+ We mention that, instead of selecting a uniformly distributed random number $\epsilon$, 
+ we follow \citet{colella1982glimm} and
+ adopt the van der Corput pseudo-random number sequence \citep{hammersley2013monte}.
+
+%A general Van Der Corupt pseudo-random number sequence depends on two parameters $x_1$ and $x_2$ with $x_1 > x_2 > 0$, both are integer and relatively prime.
+The sequence is formally defined as \citep{hammersley2013monte}:
+%\begin{equation}
+%\epsilon ^n = \sum_{i=0}^{s} H_i x_1^{-(i+1)}
+%\label{eq:Van-Der-Corput-pseudo-random-num}
+%\end{equation}
+%where
+%\begin{equation}
+%H_i = x_2 a_i(mod \ x_1)
+%\label{eq:Van-Der-Corput-pseudo-random-num-Hi}
+%\end{equation} 
+%\begin{equation}
+%n = \sum_{i=0}^{s} a_i x_1^i
+%\label{eq:Van-Der-Corput-pseudo-random-num-n}
+%\end{equation} 
+%Equation (\ref{eq:Van-Der-Corput-pseudo-random-num-n}) gives the binary expansion of n when we take $x_1$ as $2$. For example,
+%\begin{equation}
+%5=1 \times 2^0 + 0 \times 2^1 + 1 \times 2^2
+%\end{equation}
+%with $m=2$.
+
+%The next stage is to find the coefficient $H_i$ according to Eq.
+(\ref{eq:Van-Der-Corput-pseudo-random-num-Hi}).
+If we take $x_2 = 1$, for which case, $H_i = a_i, \ \forall i$.
+Having $H_i$, $x_1$ and $s$ ready, the random number $\epsilon ^n $ can be easily obtained according to Eq.
+(\ref{eq:Van-Der-Corput-pseudo-random-num}).
+%We take $x_1=2$  and $x_2 =1$ in this paper.
+Other combinations of $x_1$ and $x_2$ were also discussed by \citet{toro2013riemann}.
+A desirable statistical property of the sequence $\{\epsilon ^n\}$ is that $\{\epsilon ^n\}$ be uniformly distributed over $[0,1]$.
+
+%The arithmetic mean and the standard deviation of 200 binary Van Der Corput pseudo-random numbers are $0.49459$ and $0.28885$.
+The chi-square statistic (see \citet{toro2013riemann} for its calculation) $\chi_{sq}$ is $1.0000$.
+%The binary Van Der Corput pseudo-random numbers are generated offline to save computational time.
 
 \subsection{Non-iterative Riemann solvers} \label{sec:RP-solver}
-The starred variable $p^{\ast}$ and $u^{\ast}$ represent the interpolated pressure and velocity at certain point (an imaginary interface in GSPH or a randomly sampled poit in RSPH) along the line joining the pairs of two particles.
-They do not have to be obtained by solving a Riemann problem.
-However, $p^{\ast}$ and $u^{\ast}$ obtained by solving a Riemann problem provides necessary and sufficient dissipation needed to capture discontinuities and stabilize the scheme.
-
-The exact Riemann solver, even though more accurate and robust, requires an iterative root finding, and hence is computational inefficient.
-For governing equations other than well studied ones, such as Euler equations, there is no iterative Riemann solver available.
-Non-iterative approximate Riemann solvers can relieve these drawbacks of exact Riemann solvers.
-Among the available Riemann solvers \citep{rider1994review, luo2004computation, puri2014approximate}, we adopted the HLLC approximate Riemann solver.
-The HLLC solver is a 3-wave approximate Riemann solver proposed by \citet{toro1994restoration}.
-In this work, we adopt the formulation of the HLLC solver proposed by \citet{luo2004computation} for multi-material, underwater explosions in their ALE scheme.
-This Riemann solver has the properties of being positivity preserving for scalar quantities, entropy satisfying and to exact preserve isolated contacts.
-
-Equation (\ref{eq:RP_solver_HLLC_u}) and (\ref{eq:RP_solver_HLLC_pu}) are the approximate solution to the local Riemann problem, written in term of $p$ and $pu$ as functions of local coordinate $q$.
-\begin{equation}
-p \left( q \right) =  \begin{cases} 
-      p_L & if \  S_L \Delta t> q \\
-      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) M_L + (\hat{p}- p_L) \right] + \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
-      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) M_R + (\hat{p}- p_R) \right] + \hat{p} & if \  S_M \Delta t \leq q \leq S_R \Delta t \\
-      p_R & if \  S_R \Delta t < q
-\end{cases}
-\label{eq:RP_solver_HLLC_u}
-\end{equation}
-\begin{equation}
-(pu) \left( q \right)  =  \begin{cases} 
-      p_L u_L& if \  S_L \Delta t > q \\
-      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) E_L + (\hat{p} S_M - p_L \hat{u}_L) \right] + (S_M - \hat{u}_{LR}) \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
-      \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) E_R + (\hat{p} S_M- p_R \hat{u}_R) \right] + (S_M + \hat{u}_{LR}) \hat{p} & if \ S_M \Delta t \leq q \leq S_R \Delta t\\
-      p_R u_R & if \  S_R \Delta t < q
-\end{cases}
-\label{eq:RP_solver_HLLC_pu}
-\end{equation}
-where $\hat{u}_{LR}$ is the interface velocity and is taken as the Roe-averaged velocity on either side of the interface \citep{cheng2007high}.
+Solving local Riemann problems exactly usually involves separating 
+several cases of wave patterns and iteratively solving a small system of ordinary differential
+equations (for rarefaction waves) and a small set of nonlinear equations (the Rankine-Hugoniot equations).
+Instead of running this lengthly process one can employ approximate Riemann solvers, that provide an approximate solution quickly.
+There are many approximate Riemann solvers available 
+\citep{rider1994review, luo2004computation, puri2014approximate}. For purposes here
+we adopt the HLLC solver, which decomposes the Riemann solution into 3 waves, including a (possible) contact discontinuity
+ \citet{toro1994restoration}. More specifically, we adopt the HLLC formulation proposed in \citet{luo2004computation}.
+
+ We mention that, in the numerical tests in Section \ref{numericaltests}, 
+ the Roe solver is used for GSPH calculations.
+
+%Equation (\ref{eq:RP_solver_HLLC_u}) and (\ref{eq:RP_solver_HLLC_pu}) are the approximate solution to the local Riemann problem, written in term of $p$ and $pu$ as functions of local coordinate $q$.
+%\begin{equation}
+%    p_L & if \  S_L \Delta t> q \\
+%      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) M_L + (\hat{p}- p_L) \right] + \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
+ %     \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) M_R + (\hat{p}- p_R) \right] + \hat{p} & if \  S_M \Delta t \leq q \leq S_R \Delta t \\
+%      p_R & if \  S_R \Delta t < q
+%\end{cases}
+%\label{eq:RP_solver_HLLC_u}
+%\end{equation}
+%\begin{equation}
+%(pu) \left( q \right)  =  \begin{cases} 
+ %     p_L u_L& if \  S_L \Delta t > q \\
+ %     \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) E_L + (\hat{p} S_M - p_L \hat{u}_L) \right] + (S_M - \hat{u}_{LR}) \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
+ %     \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) E_R + (\hat{p} S_M- p_R \hat{u}_R) \right] + (S_M + \hat{u}_{LR}) \hat{p} & if \ S_M \Delta t \leq q \leq S_R \Delta t\\
+ %     p_R u_R & if \  S_R \Delta t < q
+%\end{cases}
+%\label{eq:RP_solver_HLLC_pu}
+%\end{equation}
+%where $\hat{u}_{LR}$ is the interface velocity and is taken as the Roe-averaged velocity on either side of the interface \citep{cheng2007high}.
 The quantities of $\hat{u}_R$ and $\hat{u}_L$ are velocities relative to the interface velocity.
-\begin{equation}
-\hat{p}= \rho_L (\hat{u}_L - S_L) (\hat{u}_L - S_M) + p_L
-\end{equation}
-Formulation to approximate the signal speeds $S_M$, $S_L$ and $S_R$ is given by Eq. (\ref{eq:RP-solver-HLLC-SM}) to (\ref{eq:RP-solver-HLLC-SR}).
-\begin{eqnarray}
-S_M= \frac{\rho_R \hat{u}_R (S_R - \hat{u}_R) - \rho_L \hat{u}_L (S_L - \hat{u}_L) + p_L - p_R}{\rho_R (S_R - \hat{u}_R) - \rho_L (S_L - \hat{u}_L)} \label{eq:RP-solver-HLLC-SM} \\
-S_L = min (\hat{u}_L - c_L, -c_{LR}) \label{eq:RP-solver-HLLC-SL} \\
-S_R = max (\hat{u}_R - c_R, c_{LR}) \label{eq:RP-solver-HLLC-SR}
-\end{eqnarray}
-where $c_{LR}$ is the relevant Roe averaged sound speed \citep{cheng2007high}.
-
-Besides HLLC, another 2-wave approximate Riemann solver, the Roe Riemann solver \citep{roe1981approximate}, is also adopted in GSPH.
-Roe Riemann solver is proposed by \citet{roe1981approximate} to linearize the Euler equations and approxiamte the solution of non-linear system by a system of linear equations.
+%\begin{equation}
+%\hat{p}= \rho_L (\hat{u}_L - S_L) (\hat{u}_L - S_M) + p_L
+%\end{equation}
+%Formulation to approximate the signal speeds $S_M$, $S_L$ and $S_R$ is given by Eq. (\ref{eq:RP-solver-HLLC-SM}) to (\ref{eq:RP-solver-HLLC-SR}).
+%\begin{eqnarray}
+%S_M= \frac{\rho_R \hat{u}_R (S_R - \hat{u}_R) - \rho_L \hat{u}_L (S_L - \hat{u}_L) + p_L - p_R}{\rho_R (S_R - \hat{u}_R) - \rho_L (S_L - \hat{u}_L)} \label{eq:RP-solver-HLLC-SM} \\
+%S_L = min (\hat{u}_L - c_L, -c_{LR}) \label{eq:RP-solver-HLLC-SL} \\
+%S_R = max (\hat{u}_R - c_R, c_{LR}) \label{eq:RP-solver-HLLC-SR}
+%\end{eqnarray}
+%where $c_{LR}$ is the relevant Roe averaged sound speed \citep{cheng2007high}.
+
+%Besides HLLC, another 2-wave approximate Riemann solver, the Roe Riemann solver \citep{roe1981approximate}, is also adopted in GSPH.
+%Roe Riemann solver is proposed by \citet{roe1981approximate} to linearize the Euler equations and approxiamte the solution of non-linear system by a system of linear equations.
 The characteristic decomposition of the linearized Lagrangian flux and Jacobia matrices are used to write the flux.
@@
 We directly provide here the resulting starred values of the pressure and velocity \citep{puri2014approximate}:
-\begin{eqnarray}
-u^{\ast} = \frac{1}{2} \left[ u_L + u_R - \frac{1}{C_{LR}} (p_R - p_L) \right] \label{eq:RP-solver-ROE-u} \\
-p^{\ast} = \frac{1}{2}\left[ p_L + p_R - C_{LR} (u_R - u_L) \right] \label{eq:RP-solver-ROE-p}
-\end{eqnarray}
-Where $C_{LR}$ is the averaged Lagarangian sound speed at the interface.
-\begin{equation}
-C_{LR} = \sqrt{\gamma p_{LR} \rho_{LR}}
-\end{equation}
-
-\subsection{Binary Van Der Corput pseudo-random numbers} \label{sec:Van-Der-Corput-random-num}
-The random number $\epsilon$ is used to determine the sample location $q_{ab}^{RSPH}$.
-The quantity of the computed RCM solution depends crucially on the random number $\{\epsilon ^n\}$.
-We adopt the Van Der Corupt pseudo-random number sequence \citep{hammersley2013monte} in this investigation following \citet{colella1982glimm}.
-
-A general Van Der Corupt pseudo-random number sequence depends on two parameters $x_1$ and $x_2$ with $x_1 > x_2 > 0$, both are integer and relatively prime.
-The sequence is formally defined as \citep{hammersley2013monte}:
-\begin{equation}
-\epsilon ^n = \sum_{i=0}^{s} H_i x_1^{-(i+1)}
-\label{eq:Van-Der-Corput-pseudo-random-num}
-\end{equation}
-where
-\begin{equation}
-H_i = x_2 a_i(mod \ x_1)
-\label{eq:Van-Der-Corput-pseudo-random-num-Hi}
-\end{equation} 
-\begin{equation}
-n = \sum_{i=0}^{s} a_i x_1^i
-\label{eq:Van-Der-Corput-pseudo-random-num-n}
-\end{equation} 
-Equation (\ref{eq:Van-Der-Corput-pseudo-random-num-n}) gives the binary expansion of n when we take $x_1$ as $2$. For example,
-\begin{equation}
-5=1 \times 2^0 + 0 \times 2^1 + 1 \times 2^2
-\end{equation}
-with $m=2$.
-
-The next stage is to find the coefficient $H_i$ according to Eq.
-(\ref{eq:Van-Der-Corput-pseudo-random-num-Hi}).
-If we take $x_2 = 1$, for which case, $H_i = a_i, \ \forall i$.
-Having $H_i$, $x_1$ and $s$ ready, the random number $\epsilon ^n $ can be easily obtained according to Eq.
-(\ref{eq:Van-Der-Corput-pseudo-random-num}).
-We take $x_1=2$  and $x_2 =1$ in this paper.
-Other combinations of $x_1$ and $x_2$ were also discussed by \citet{toro2013riemann}.
-A desirable statistical property of the sequence $\{\epsilon ^n\}$ is that $\{\epsilon ^n\}$ be uniformly distributed over $[0,1]$.
-
-The arithmetic mean and the standard deviation of 200 binary Van Der Corput pseudo-random numbers are $0.49459$ and $0.28885$.
-The chi-square statistic (see \citet{toro2013riemann} for its calculation) $\chi_{sq}$ is $1.0000$.
-The binary Van Der Corput pseudo-random numbers are generated offline to save computational time.
-
-%\subsection{Convergence}
-
-\subsection{RSPH algorithm (the PESB algorithm)}
-The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm. 
+%\begin{eqnarray}
+%u^{\ast} = \frac{1}{2} \left[ u_L + u_R - \frac{1}{C_{LR}} (p_R - p_L) \right] \label{eq:RP-solver-ROE-u} \\
+%p^{\ast} = \frac{1}{2}\left[ p_L + p_R - C_{LR} (u_R - u_L) \right] \label{eq:RP-solver-ROE-p}
+%\end{eqnarray}
+%Where $C_{LR}$ is the averaged Lagarangian sound speed at the interface.
+%\begin{equation}
+%C_{LR} = \sqrt{\gamma p_{LR} \rho_{LR}}
+%\end{equation}
+
+%\subsection{RSPH algorithm (the PESB algorithm)}
+%The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm.
+To summarize, our RSPH alogrithm proceeds as follows:
 \begin{itemize}
-\item For any two pair of particles, establish a local coordinate system whose axis joints these two particles then project the primitive variables vector onto the local coordinate system.
-\item Evolve the hyperbolic equation exactly or approximately with Riemann problem defined by the projected data to obtain a solution between these two particles.
-\item Sample these solutions between the particles pair to pick up a state and assign it to $p^{\ast}$ and $u^{\ast}$
-\item Project $p^{\ast}$ and $u^{\ast}$ from local coordinate system back to the global coordinate system obtaining $p^{\ast}$ and $\textbf{v}^{\ast}$.
+\item For each pair of particles, establish a local coordinate system whose axis joins the
+particles,
+and project the primitive variables onto this local coordinate system to define
+left and right states;
+\item Solve this local Riemann problem approximately using a HLLC solver;
+\item Sample the solution using the van der Corput sequence,
+defining a state  $p^{\ast}, u^{\ast}$;
+\item Project $p^{\ast}, u^{\ast}$  back to the global coordinate system,
+to obtain $p^{\ast}$ and $\textbf{v}^{\ast}$;
+\item Update the particle positions.
 \end{itemize}
-PESB algorithm is integrated into framework of SPH discretization to update physical quantities in time. PESB also fit well with GSPH, for which, the sample step is not stochastic randomly sample.
-
-\section{Numerical tests}
+
+\section{Numerical tests} \label{numericaltests}
 We carry out several numerical tests using SPH, RSPH and GSPH in this section.
@@
 \section{Conclusion}
-We proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs.
-The artificial viscosity in RSPH is determined implicitly by randomly sampling solution of a local Riemann problem.
-No explicit artificial viscosity coefficients is needed.
-The artificial viscosity introduced by RSPH is demonstrated to be much less than GSPH and SPH without parameter tuning.
-Besides introducing less amount of dissipation, there are several other attractive features.
-The pressure ``wiggle" around contact discontinuity, which persists in SPH results, is eliminated in RSPH.
-It also shows higher order of convergence rate than GSPH when the same construction of local Riemann problem and Riemann solvers.
-The attractive property of less dissipation persist in multi-dimensional applications.
-This new method enables shock capturing with lower dissipation. One potential application of the method is high speed mixing flow, for example, supersonic combustion.
-By overcoming a fundamental shortcoming of RCM and inheriting attractive feature of RCM, RSPH provide a powerful numerical method for solving combustion problems in multi-dimensional space.
-
-One shortcoming of RSPH is its inability to completely suppress numerical perturbation caused by non-uniform distribution of smoothing length in space.
-Such perturbation, as long as it does not lead to numerical instability, is within acceptable range for many tests.
-However, for very strong shocks, dissipation introduced by RSPH turns out to be not sufficient to stabilize simulation, which finally ends up with negative energy.
-Since GSPH has been shown introducing more dissipation and hence is more suitable for situation with very strong shocks.
-
-In our investigation presented in this paper, an approximate HLLC Riemann solver is used in place of exact iterative Riemann solver.
-It would be interesting to see the difference, between using other approximate Riemann solvers and exact Riemann solver.
-Alternative Riemann solvers, alternative ways for constructing Riemann problems and alternative ways for sampling solution of Riemann problem might also worthwhile for future exploring.
-In addition, this paper focused on solving of compressible Euler equations.
-Applications of RSPH in other computational fluids dynamic problems or solving other hyperbolic PDEs are on the list to be explored.
+We proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs that combines the Random Choice Method with
+an approximate Riemann solver.  No explicit artificial viscosity is needed. Instead, any viscosity that is used in a hydrodynamics simulation 
+is just what the user explicitly adds. This control is important in applications with very strong shocks
+RSPH also shows good convergence behavior.
+On the other hand, RSPH does not redress other methodological questions that must be decided in order to use SPH, 
+questions such as the smoothing length of the SPH kernel. We have investigated the HLLC approximate Riemann solver in this paper;
+it is of interest to test other approximate solvers,  to better understand the behavior of solutions.
+This may be particularly important when applying RSHP to other systems, where the explicit construction on which the HLLC solver
+rests is not readily available.
 
@@
 \section*{References}
+
 \bibliography{Reference}
+
 \end{document}

### 2018-06-07 ebp-JCPManuscript.tex
abani+ebp cleans

@@
 \begin{frontmatter}
-\title{IA Random Choice SPH Scheme with Adaptive Viscosity}
+\title{A Random Choice SPH Scheme with Adaptive Viscosity}
 %\tnotetext[mytitlenote]{Can add  title note here}
@@
 %The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm.
-To summarize, our RSPH alogrithm proceeds as follows:
+To summarize, our RSPH algorithm proceeds as follows:
 \begin{itemize}
@@
 \section{Numerical tests} \label{numericaltests}
-We carry out several numerical tests using SPH, RSPH and GSPH in this section.
-1D shock tube tests are conducted to compare standard SPH, GSPH and RSPH.
-Comprehensive shock tube tests are also conducted to check the capacity of RSPH for different situations.
-In addition, order of accuracy is investigated based on 1D shock tube problem.
-In the last subsection, a 3D free jet flow is simulated with SPH, GSPH and RSPH to check equivalent overall dissipation introduced by each method.
-
-Input parameters for 1D tests can be found in Table \ref{tab:1D-shock-input_parameters}. 
+We describe results from several numerical tests using SPH, RSPH and GSPH in this section.
+1D shock tube tests are used to compare standard SPH, GSPH and RSPH.
+Comprehensive shock tube simulations are also conducted to check the capacity of RSPH for different situations.
+In addition, order of accuracy is investigated for the 1D shock tube problem.
+In the last subsection we describe a 3D free jet flow simulation with SPH, GSPH and RSPH to check equivalent overall dissipation introduced by each method.
+
+Six 1D simulations described here  are carried out:
+\begin{itemize}% [1D Tests]
+\item Test 1 consists of a left rarefaction, a right traveling contact and a right shock. Density increases at down wind of contact wave. 
+\item Test 2 also consists of a left rarefaction, a right traveling contact and a right shock. Density decreases at down wind of contact wave. 
+\item Test 3 includes double expansion waves. The initial density are different at right and left hand side. 
+\item Test 4 is a double shock tests with different initial density on the right side and left side.
+\item Test 5 and Test 6 are two extreme cases. Test 5 is a cavity flow while test 6 is a strong blast flow.
+\end{itemize}
+
 \begin{table}[htp]
@@
 \end{table}
-where, subscript $L$ refers left side and $R$ for right side.
+Input parameters for 1D tests can be found in Table \ref{tab:1D-shock-input_parameters}, where, subscript $L$ refers left side and $R$ for right side.
 $m$ is particle mass, initial interval between adjacent particles are adjusted to guarantee equal particle mass.
@@
 The $x$ axis in all plots is normalized by time, that is $x/t_f$, in plots for shock tube tests results.
-
-Test 1 consists of a left rarefaction, a right travelling contact and a right shock. Density increases at down wind of contact wave.
-Test 2 also consists of a left rarefaction, a right travelling contact and a right shock. Density decreases at down wind of contact wave.
-Test 3 includes double expansion waves. The initial density are different at right and left hand side.
-Test 4 is a double shock tests with different initial density on the right side and left side.
-Test 5 and Test 6 are two extreme cases. Test 5 is a cavity flow while test 6 is a strong blast flow.
-
 \subsection{Comparison of RSPH with standard SPH and GSPH}
@@
     \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
-    \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
-    \end{minipage}%
+        \centering a)
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
+    \end{minipage}%
+    \begin{minipage}{.495 \textwidth}
+        \centering b)
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
+    \end{minipage}%
+%    \\
+%    \begin{minipage}{.495\textwidth}
+%        \centering c)
+%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
+%    \end{minipage}%
+%    \begin{minipage}{.495 \textwidth}
+%        \centering d)
+%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
+%    \end{minipage}% 
     \\
     \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
-    \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
+        \centering c)
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
+    \end{minipage}%
+    \begin{minipage}{.495 \textwidth}
+        \centering d)
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
+    \end{minipage}% 
+%    \\
+%    \begin{minipage}{.495 \textwidth}
+%        \centering g)
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
+%    \end{minipage}% 
+%    \begin{minipage}{.495\textwidth}
+%        \centering h)
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
+%    \end{minipage}%    
+    \caption{a),b) Simulation results of density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
+c), d) show zoomed views.
+For $\alpha=1$ and $\alpha=2$,numerical oscillations are completely suppressed though the shock is now smeared.
+$\alpha=0.25$ provided insufficient viscosity to suppress oscillations.
+Comparing  RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock
+    (comparable to $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.25$). %    
+%    
+%    For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock.
+However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock.
+To summarize, the equivalent artificial viscosity in RSPH is adaptive.
+Similar conclusion can be drew from zoomed view of velocity.
+The third zoomed view shows different degrees of smearing at the shock.
+The larger the artificial viscosity, the less sharp the solution at the shock.
+Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity.
+SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock.
+The last zoomed view shows pressure around the contact discontinuity.
+It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.
+    }
+    \label{fig:RCM-Sod-SPH-alf}
+\end{figure}
+
+\begin{figure}[htp]
+    \centering
+%    \begin{minipage}{.495\textwidth}
+%        \centering a)
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
+%    \end{minipage}%
+%    \begin{minipage}{.495 \textwidth}
+%        \centering b)
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
+%    \end{minipage}%
+%    \\
+    \begin{minipage}{.495\textwidth}
+        \centering a)
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
+    \end{minipage}%
+    \begin{minipage}{.495 \textwidth}
+        \centering b)
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
     \end{minipage}% 
     \\
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
-    \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
-    \end{minipage}% 
-    \\
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
-    \end{minipage}% 
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
-    \end{minipage}%    
-    \caption{Simulation results by RSPH and SPH with different artificial viscosity coefficients.
-The effect of artificial viscosity is illustrated through comparison.
-Artificial viscosity coefficients are chosen to always satisfy: $\beta=2\alpha$ in all SPH tests.
+%    \begin{minipage}{.495\textwidth}
+%        \centering a)
+%        \includegraphics[width=0.99 \textwidth, height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
+%    \end{minipage}%
+%    \begin{minipage}{.495 \textwidth}
+%        \centering b)
+%        \includegraphics[width=0.99 \textwidth, height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
+%    \end{minipage}% 
+%    \\
+    \begin{minipage}{.495 \textwidth}
+        \centering c)
+        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
+    \end{minipage}% 
+    \begin{minipage}{.495\textwidth}
+        \centering d)
+        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
+    \end{minipage}%    
+    \caption{
+    a),b) Simulation results of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
+c), d) show zoomed views.
+For $\alpha=1$ and $\alpha=2$,numerical oscillations are completely suppressed though the shock is now smeared.
+$\alpha=0.25$ provided insufficient viscosity to suppress oscillations.
+Comparing  RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock
+    (comparable or better than $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.25$).
+d) shows pressure around the contact discontinuity.
+It shows that RSPH gets rid of the pressure ``wiggle" around the contact discontinuity.
+%
+%    Simulation results by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
 The last four figures are zoomed views.
@@
 The last zoomed view shows pressure around the contact discontinuity.
-It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.}
-    \label{fig:RCM-Sod-SPH-alf}
+It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.
+}
+    \label{fig:RCM-Sod-SPH-alf-zoom}
 \end{figure}
@@
 The comparison between RSPH and SPH using different artificial viscosity coefficients is shown in Fig.
-\ref{fig:RCM-Sod-SPH-alf}.
+\ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}.
 In all simulations, the artificial viscosity $\beta$ is set to be twice of $\alpha$.
@@
 Several interesting observation are made based on the comparison between SPH and RSPH.
-First of all, dissipation (introduced by artificial viscosity in these tests) can decays the numerical fluctuations.
-Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients.
+The effect of artificial viscosity is illustrated through comparison.
+First of all, dissipation (introduced by artificial viscosity in these tests) decays the numerical fluctuations.
+Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients ($\alpha=1,2$).
 %The mechanism for SPH to reduce (or completely get rid of) fluctuations should be completely different from that of new adaptive method of smoothing length. 
 %The new adaptive method, reduces the sources of such fluctuations.
-Secondly, the equivalent artificial viscosity coefficients introduced by RSPH varies adaptively.
+Secondly, the equivalent artificial viscosity  introduced by RSPH varies adaptively.
 As shown in Fig.
-\ref{fig:RCM-Sod-SPH-alf}, RSPH assigns smaller artificial viscosity coefficients (equivalent $\alpha$ much less then 0.2) at the area far away from shock and sufficient large artificial viscosity coefficients (equivalent $\alpha$ is about 1.0) around the shock.
+\ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}, RSPH assigns smaller artificial viscosity  (equivalent $\alpha$ much less then 0.2) at the area far away from shock and sufficiently large artificial viscosity coefficients (equivalent $\alpha$ is about 1.0) around the shock.
 So RSPH is actually more adaptive than SPH.
@@
 Recall that RCM is able to resolve discontinuities as true discontinuity.
-RSPH, even though still smears the discontinuity in some degree, introduces much less smearing.
-The last but not the least, the pressure ``wiggle" around contact discontinuity is completely eliminated by RSPH.
+RSPH, even though it still smears the discontinuity in some degree, introduces much less smearing.
+The last but not the least, the pressure ``wiggle" around contact discontinuity is completely eliminated by RSPH as seen in Fig.
+\ref{fig:RCM-Sod-SPH-alf-zoom}.
 It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}.
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho}
-    \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho}
+    \end{minipage}%
+    \begin{minipage}{.495 \textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e}
-    \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e}
+    \end{minipage}%
+    \begin{minipage}{.495 \textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho-zoom}
-    \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e-zoom}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho-zoom}
+    \end{minipage}%
+    \begin{minipage}{.495 \textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v-zoom}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v-zoom}
-    \end{minipage}% 
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p-zoom}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e-zoom}
+    \end{minipage}% 
+    \begin{minipage}{.495\textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p-zoom}
     \end{minipage}%    
@@
 
-These zoomed views in fig.
-\ref{fig:RCM-Sod-GSPH} demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH.
+Zoomed views in Gig.
+\ref{fig:RCM-Sod-GSPH} compare GSPH andRSPH and demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH.
 The attractive feature of RCM method in preserving true discontinuity is inherited by RSPH in this 1D shock tube test.
-With more dissipation, GSPH can completely suppress numerical dissipation.
-The discontinuity at the shock is more seriously smeared.
-The excessive amount dissipation might have other, more undesirable, effects in real implementation.
+With more dissipation, GSPH can also completely suppress numerical dissipation.However, the discontinuity at the shock is then more seriously smeared.
+The excessive amount of dissipation might have other, more undesirable, effects in real implementation.
 For example, over damping of shearing flow.
 Compared with SPH, both GSPH and RSPH avoid pressure ``wiggle" around contact discontinuity.
-Since RSPH share many common places with Godunov's method, it is not surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.
+Since RSPH shares many commonalities   with Godunov's method, it is not a surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.
 
@@
 In addition, they adopted a test problem without discontinuity in the solution.
-Existing of discontinuities, such as shock, in the test problem might lower rate of convergence.
+Presence  of discontinuities, such as shock, in the test problem might lower the rate of convergence.
 Both RSPH and GSPH tests in this paper adopt a piece wise constant construction of Riemann problem.
@@
 \subsection{Comprehensive 1D tests} \label{sec:comprehensive-1d-tests}
-Comprehensive tests are presented in this section to check how well does RSPH work for different situations.
-Input parameters for each tests is given in Table \ref{tab:1D-shock-input_parameters}.
-Wave speed is estimated based on formulation Eq.
-(\ref{eq:RP-solver-HLLC-SM}) $\sim$ Eq.
-(\ref{eq:RP-solver-HLLC-SR}).
+Comprehensive tests are presented in this section to check how well does RSPH work for different situations. Input parameters for each tests is given in Table \ref{tab:1D-shock-input_parameters}.
+% Wave speed is estimated based on formulation Eq. (\ref{eq:RP-solver-HLLC-SM}) $\sim$ Eq. (\ref{eq:RP-solver-HLLC-SR}).
 The results are shown in Fig.
@@
 Similar spike is observed in GSPH simulation \citep{puri2014comparison}.
-Such spike is evident in the FVM solution as well and is perhaps an artifice of the Lagrangian nature of the two schemes.
+%Such spike is evident in the FVM solution as well and is perhaps an artifice of the Lagrangian nature of the two schemes.
 \citep{noh1987errors} proposed to adding a small amount of thermal conduction to ameliorate the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}.
@@
 Due to less amount of dissipation, numerical fluctuations persist in all simulation results.
-For the strong blast test and double shock test, such fluctuations become more obvious than other tests.
-Even though, the magnitude of fluctuations is within acceptable range.
+For the strong blast test and double shock test, such fluctuations become more obvious than other tests, even though, the magnitude of fluctuations is within an acceptable range.
 
@@
 To test the capacity of RSPH for multiple dimensional applications, a free jet flow is simulated in this section by solving 3D compressible Euler Equations using standard SPH, GSPH and RSPH.
-All simulations are using the same setting-up and compared at the same physical time.
+All simulations are using the same set-up and compared at the same physical time.
 In this test, RSPH simulation is carried out based on piece wise constant construction of Riemann problem and a HLLC approximate Riemann solver.
@@
 The damping effect due to artificial dissipation is clearly shown in this figure.
-We observe that the lengths to which these jets reach at $t=3.0 s$ are various when using different artificial viscosity coefficient.
+We observe that the lengths to which these jets reach at $t=3.0 s$ are different when using different artificial viscosity coefficient.
 It is obvious that the larger artificial viscosity, the shorter length the jet can reach.
@@
 \section{Conclusion}
-We proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs that combines the Random Choice Method with
+In this paper we have proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs that combines the Random Choice Method with
 an approximate Riemann solver.  No explicit artificial viscosity is needed. Instead, any viscosity that is used in a hydrodynamics simulation 
@@
 RSPH also shows good convergence behavior.
-On the other hand, RSPH does not redress other methodological questions that must be decided in order to use SPH, 
+On the other hand, RSPH does not address other methodological questions that must be decided in order to use SPH, 
 questions such as the smoothing length of the SPH kernel. We have investigated the HLLC approximate Riemann solver in this paper;
 it is of interest to test other approximate solvers,  to better understand the behavior of solutions.
-This may be particularly important when applying RSHP to other systems, where the explicit construction on which the HLLC solver
+This may be particularly important when applying RSPH to other systems, where the explicit construction on which the HLLC solver
 rests is not readily available.
 
-\section*{acknowledgements}
+\section*{Acknowledgements}
 3D simulations reported here were performed at the Center for Computational Research (CCR) at the University at Buffalo.

### 2018-06-07 ebp-JCPManuscript.tex
Change font size for pic and clean

@@
 \author{Abani Patra \fnref{mycorrespondingauthor}}
-\address{Department of Mechanical and Aerospace Engineering,The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
+\address{Department of Mechanical and Aerospace Engineering, The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
 \author{E. Bruce Pitman}
@@
 \begin{abstract}
-The classical smoothed particle hydrodynamics (SPH) method
-employs artificial viscosity to properly capture shock waves in hydrodynamics. This artificial viscosity typically
-produces more dissipation than is needed to smooth shocks, incorrectly  smears 
-contact discontinuities, and can overwhelm fluid turbulence. 
-Several studies have proposed highly tuned versions of artificial viscosity,
-turning on and off near shocks or other troublesome wave features. 
+The classical smoothed particle hydrodynamics (SPH) method employs artificial viscosity to properly capture shock waves in hydrodynamics.
+This artificial viscosity typically produces more dissipation than is needed to smooth shocks, incorrectly smears contact discontinuities, and can overwhelm fluid turbulence.
+Several studies have proposed highly tuned versions of artificial viscosity, turning on and off near shocks or other troublesome wave features. 
 Unfortunately these schemes usually produce more dissipation than is appropriate.
-A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems 
-as building blocks for a numerical SPH solver. Of course a first order Godunov solver still introduces an effective numerical diffusion that can infect the entire numerical solution.
-We propose a novel SPH scheme that combines an approximate
- version of Glimm\rq{}s Random Choice method (RCM)
-with SPH. RCM properly resolves and then samples all hydrodynamic waves, and
-introduces no numerical diffusion into a simulation. Our version approximately resolves
-hydrodynamic waves, and samples the approximate solution.
+A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems as building blocks for a numerical SPH solver.
+Of course a first order Godunov solver still introduces an effective numerical diffusion that can infect the entire numerical solution.
+We propose a novel SPH scheme that combines an approximate version of Glimm\rq{}s Random Choice method (RCM) with SPH.
+RCM properly resolves and then samples all hydrodynamic waves, and introduces no numerical diffusion into a simulation.
+Our version approximately resolves hydrodynamic waves, and samples the approximate solution.
 We test this method on standard one dimensional shock tube problems.
-Our ultimate goal is to apply this method to jet flow. Because of the high shear rate
-in this application, we introduce a highly tuned eddy viscosity that is applied only near 
-the shear surface.  The combination of the SPH and RCM together with a shear viscosity
-produces nicely resolved jet profiles.
+Our ultimate goal is to apply this method to jet flow.
+Because of the high shear rate in this application, we introduce a highly tuned eddy viscosity that is applied only near the shear surface.
+The combination of the SPH and RCM together with a shear viscosity produces nicely resolved jet profiles.
 
@@
 Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on a Lagrangian formulation of the governing equations of  motion.
-SPH has been widely applied to different areas in engineering and science. As
-should be expected, SPH possesses certain advantages and certain disadvantages relative to finite difference and finite element solvers. Principally, as a Lagrangian solver SPH conserves mass 
-exactly. 
-In addition, because of its formulation SPH automatically concentrates numerical effort in regions of
-high density and adapts to  arbitrary geometries. On the other hand, 
-SPH has difficulty capturing shock waves and contact discontinuities. To overcome numerical
-oscillations at discontinuities, classical SPH introduces
-an artificial viscosity term. At it is most often used, when two SPH particles
-are approaching, a von Neumann type viscosity is introduced
+SPH has been widely applied to different areas in engineering and science.
+As should be expected, SPH possesses certain advantages and certain disadvantages relative to finite difference and finite element solvers.
+Principally, as a Lagrangian solver, SPH conserves mass exactly.
+In addition, because of its formulation SPH automatically concentrates numerical effort in regions of high density and adapts to arbitrary geometries. On the other hand, 
+SPH has difficulty capturing shock waves and contact discontinuities.
+To overcome numerical oscillations at discontinuities, classical SPH introduces an artificial viscosity term.
+As it is most often used, when two SPH particles are approaching, a von Neumann type viscosity is introduced
 \citep{monaghan1983shock, monaghan1997sph,klapp2012strong}. 
-This kind of viscosity, however, 
- usually provides more dissipation  than is truly needed at a discontinuity, and the excess
- dissipation ultimately
- corrupts the entire computation. Various methods have been introduced to tune 
- the artificial viscosity, turning it on and off for particular wave features. However, 
- tuning switches cannot properly accommodate every kind of wave that might arise, 
- and 
- spurious effects and unphysical damping persist (see, for example, \citet{borgani2012hydrodynamic,flebbe1994smoothed,morris1997switch, dolag2005turbulent,cullen2010inviscid,sigalotti2008adaptive,puri2014comparison}).
+This kind of viscosity, however, usually provides more dissipation than is truly needed at a discontinuity, and the excess dissipation ultimately corrupts the entire computation.
+Various methods have been introduced to tune the artificial viscosity, turning it on and off for particular wave features.
+However, tuning switches cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist (see, for example, \cite{borgani2012hydrodynamic,flebbe1994smoothed,morris1997switch, dolag2005turbulent,cullen2010inviscid,sigalotti2008adaptive,puri2014comparison}).
 
-To overcome troublesome oscillations, \cite{inutsuka2002reformulation} and later \cite{cha2003implementations} formulated an SPH scheme that uses Riemann problems to 
-resolve the interactions of particles. This Godunov-SPH (GSPH) method can resolve shocks and pressure 
-oscillations without additional
-artificial viscosity 
- \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate,borgani2012hydrodynamic}.
+To overcome troublesome oscillations, \citet{inutsuka2002reformulation} and later \citet{cha2003implementations} formulated an SPH scheme that uses Riemann problems to resolve the interactions of particles.
+This Godunov-SPH (GSPH) method can resolve shocks and pressure oscillations without additional artificial viscosity \citep{inutsuka2002reformulation, cha2003implementations,iwasaki2011smoothed, puri2014approximate,borgani2012hydrodynamic}.
 It has also been shown to introduce less damping in turbulent mixing \citep{cha2010kelvin, borgani2012hydrodynamic} than standard SPH.
 However, the dissipation introduced by GSPH is still larger than physically relevant, to the point
-of inhibiting the development of the Kelvin-Helmholtz instability under certain conditions
- \citep{borgani2012hydrodynamic}.
+of inhibiting the development of the Kelvin-Helmholtz instability under certain conditions \citep{borgani2012hydrodynamic}.
 
-The Godunov approach to solving Riemann problems in the context of numerical methods for conservation laws is to 
-integrate the Riemann problem solution over a spatial interval of interest. A different approach is given by
-the 
-random choice method (RCM) was introduced by \citet{glimm1965solutions} for the construction of solutions of systems of nonlinear hyperbolic conservation laws. The RCM probabilistically samples the
-Riemann problem solution in each interval, and thus introduces no viscosity whatsoever. Because this
-sampling interrogates the exact Riemann problem solution, no over- or under-shoots are introduced,
-so, irrespective of the absence of viscosity, no non-physical oscillations are introduced either.
+The Godunov approach to solving Riemann problems in the context of numerical methods for conservation laws is to integrate the Riemann problem solution over a spatial interval of interest.
+A different approach is given by the random choice method (RCM) was introduced by \citet{glimm1965solutions} for the construction of solutions of systems of nonlinear hyperbolic conservation laws.
+The RCM probabilistically samples the Riemann problem solution in each interval, and thus introduces no viscosity whatsoever.
+Because this sampling interrogates the exact Riemann problem solution, no over- or under-shoots are introduced, so, irrespective of the absence of viscosity, no nonphysical oscillations are introduced either.
 
 \citet{chorin1976random} developed the RCM into a practical computational method for solutions of the Euler equations in one space dimension.
-This approach was later extended to two dimensions \cite{chorinporousmedium}. Others
-further refined the random choice method \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical,toro2013riemann}. 
-%This need to be proven ---> But at least, if the good property of preserving true discontinuity is still valid in 1D shock tube problem, it should be preserved in multiple-dimensional implementations.
-Because in current framework of RSPH, no matter what is the dimension of the problem, the techniques is only implemented in a one-dimensional scenario.
-%
-Later, Harten and Lax \cite{hartenlax} proposed approximately solving a Riemann problem based 
-on a finite difference scheme, and sampling this approximate solution. Our approach here 
-is based on the Harten-Lax proposal. 
-We introduce a new method which we dub RSPH, by randomly sampling the interaction
-of pairs of SPH particles. 
-This scheme produces dissipation-free solutions, as does classical RCM, but for a Lagrangian 
-system.
- Because the 
-interaction of SPH particles are inherently one-dimensional, the RCM framework
-is straightforward to implement.
-We test this RSPH idea first on classical shock tube problems, where we can compute very accurate
-solutions.
-We then implement RSPH for a three-dimensional free jet flow simulation, a prototype for
-our ultimate goal of simulating a
-Plinian volcanic eruption.
+This approach was later extended to two dimensions \cite{chorinporousmedium}.
+Others further refined the random choice method \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical,toro2013riemann}.
 
-%To summarize, RSPH has the following advantages over standard SPH:
-%\begin{itemize}
-%\item RSPH is able to capture discontinuities with less smearing.
-%\item The RSPH is able to adaptively adjust equivalent artificial viscosity coefficients, assigning larger artificial viscosity coefficients around the shock and small artificial viscosity coefficients otherwhere.
-%\item RSPH is able to alleviate pressure ``wiggle" at the contact discontinuity, a common issue in classical SPH.
-%\end{itemize}
+Later, Harten and Lax \cite{hartenlax} proposed approximately solving a Riemann problem based on a finite difference scheme, and sampling this approximate solution.
+Our approach here is based on the Harten-Lax proposal.
+We introduce a new method which we dub RSPH, by randomly sampling the interaction of pairs of SPH particles.
+This scheme produces dissipation-free solutions, as does classical RCM, but for a Lagrangian system.
+Because the interaction of SPH particles is inherently one-dimensional, the RCM framework is straightforward to implement.
+We test this RSPH idea first on classical shock tube problems, where we can compute very accurate solutions.
+We then implement RSPH for a three-dimensional free jet flow simulation, a prototype for our ultimate goal of simulating a Plinian volcanic eruption.
 
-Section \ref{sph} provides a brief review of standard SPH, and shows how the
-GSPH method is defined in section \ref{sec:GSPH-method}. The RSPH method is defined in Section \ref{rsph}.
-One dimensional tests are shown in Section \ref{tests}, followed by the jet flow
-example in Sec. \ref{jet}. 
+Section \ref{standard-sph} provides a brief review of standard SPH. Section \ref{sec:GSPH-method} shows how the GSPH method is defined. The RSPH method is defined in Section \ref{sec:RSPH-method}.
+One dimensional tests are shown in Section \ref{numericaltests}, followed by the jet flow example in Section \ref{jet}.
 Other applications and limitations of RSPH are discussed in Section \ref{discussion}
@@
 Here $\rho$ is the density, $\textbf{v}$ is the velocity, $\textbf{I}$ is a unit tensor.
-$E = e + K $ is the total energy which is a sum of a 
-kinetic energy $K$ and an internal energy $e$.
+$E = e + K $ is the total energy which is a sum of a kinetic energy $K$ and an internal energy $e$.
 The system of equations is closed by the equation of state for an idea gas
@@
 In this formulation we have written the material derivative as 
-$\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$) for a conserved variable $A$.
+$\frac{D A}{Dt} = \frac{\partial A}{\partial t} + \textbf{v} \cdot \nabla A$ for a conserved variable $A$.
 
-%\cutet{puri2014comparison} propose an addition of an artificial heating term to the GSPH scheme to eliminate unphysical spikes in the thermal energy at the contact discontinuity.
---> It is worthwhile to check whether RSPH is able to avoid this phenomena without using his techniques.
-%Another issue of RCM: the very desirable properties of RCM: no diffusive errors from spatial averaging do not seem to persist for flows in two space dimensions.
-For two dimensional steady supersonic flow, one of the space variables can be treated as a time-like one and RCM can be applied in a way similar to that for one-dimensional unsteady flow.
-%--Then what about RSPH?
-
-\subsection{Standard SPH}
-In the classical SPH formulation a fluid is divided into   a number of particles whose 
-location is updated at every time step. An approximation to the field variables (velocity, density and pressure) is obtained by interpolation of particle quantities using  a kernel.
-We will only consider kernel functions with  compact support. Derivatives of variables are 
-converted into derivatives of the kernel function, and different formulations of the
-derivatives can be shown to possess various properties; see 
- \citep{monaghan1992smoothed,monaghan2005smoothed,liu2010smoothed, price2012smoothed} for details.
+\subsection{Standard SPH} \label{standard-sph}
+In the classical SPH formulation a fluid is divided into a number of particles whose location is updated at every time step.
+An approximation to the field variables (velocity, density and pressure) is obtained by interpolation of particle quantities using a kernel.
+We will only consider kernel functions with compact support.
+Derivatives of variables are converted into derivatives of the kernel function, and different formulations of the derivatives can be shown to possess various properties; see \citep{monaghan1992smoothed,monaghan2005smoothed,liu2010smoothed, price2012smoothed} for details.
 Thus the density due to particle $a$ can be written as a sum
- $<\rho_a> = \sum_b m_b w_{ab} \left(h\right) \label{eq:ns-sph-d}$, where 
- where $m_b$ is the  mass of the $b^{th}$ SPH particle and $w_{ab}$ is 
- the kernel interpolating between 
- particles $a$ and $b$, with a kernel smoothing length $h$. 
+\begin{equation}
+<\rho_a> = \sum_b m_b w_{ab} \left(h\right) \label{eq:ns-sph-d}
+\end{equation}
+where $m_b$ is the  mass of the $b^{th}$ SPH particle and $w_{ab}$ is the kernel interpolating between particles $a$ and $b$, with a kernel smoothing length $h$.
 Particle position is updated at every time step according to  a simple advection
@@
 \end{align}
-Here $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$, the smoothing length $h$ 
-is taken as $h=\frac{h_a + h_b}{2}$, and $\Pi$ is an artificial viscosity term.
+Here $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$, the smoothing length $h$ is taken as $h=\frac{h_a + h_b}{2}$, and $\Pi$ is an artificial viscosity term.
 One of commonly used models of artificial viscosity \citep{monaghan1983shock} is:
 \begin{equation}
-\Pi_{ab}=- \frac{\nu}{\bar{\rho}_{ab}} \dfrac{ \textbf{v}_{ab} \cdot \textbf{x}_{ab}}{\textbf{x}_{ab}^2 + \left(\eta h\right)^2}
+\Pi_{ab}=- \frac{\nu_{ab}}{\bar{\rho}_{ab}} \dfrac{ \textbf{v}_{ab} \cdot \textbf{x}_{ab}}{\textbf{x}_{ab}^2 + \left(\eta h\right)^2}
 \label{eq:art-vis-original}
 \end{equation}
-where the coefficient $\nu$ is defined as
+where the coefficient $\nu_{ab}$ is defined as
 \begin{equation}
-\nu = \alpha \bar{h}_{ab} \bar{c}_{ab}
+\nu_{ab} = \alpha h \bar{c}_{ab}
 \end{equation}
@@
 It produces a repulsive force between two particles when they are approaching each other and an attractive force when they are receding from each other.
-Later,  Monaghan\citep{monaghan1992smoothed} added terms to the viscosity,
-obtaining the form we will use in computations below:
+Later, Monaghan\citep{monaghan1992smoothed} added terms to the viscosity, obtaining the form we will use in computations below:
 \begin{equation}
@@
 \end{equation}
-%$\alpha$ and $\beta$ are two parameters that are free to be adjusted for each case. 
 Here $\alpha$ and $\beta$ are free parameters that are adjusted as needed.
-\citep{monaghan2005smoothed}  recommends $\alpha = 1$ and $\beta = 2$ as
-good fits for many computations.
+\citet{monaghan2005smoothed} recommends $\alpha = 1$ and $\beta = 2$ as good fits for many computations.
 $\eta$ is usually taken as 0.1.
 
-In Eq. (\ref{eq:ns-sph-d}) - Eq. (\ref{eq:ns-sph-e}), $w_{a b}\left(h\right)$ is the kernel
-weighting function, expressed more completely as
+In Eq. (\ref{eq:ns-sph-v}) - Eq. (\ref{eq:ns-sph-e}), $w_{a b}\left(h\right)$ is the kernel weighting function, expressed more completely as
 $w\left(\textbf{x}_a - \textbf{x}_b, h\right)$. 
-Many  weighting functions have been proposed, but, for simplicity,  we 
-employ a truncated Gaussian in $d$ dimensions
+Many weighting functions have been proposed, but, for simplicity, we employ a truncated Gaussian in $d$ dimensions
 \begin{equation}
@@
 
-To complete our specification of the classical SPH scheme we must decide on the time 
-integration method. A forward Euler step with sufficiently small timestep suffices for purposes of the exposition
-here.
+To complete our specification of the classical SPH scheme we must decide on the time integration method.
+A forward Euler step with sufficiently small time step suffices for purposes of the exposition here.
 
 \subsection{GSPH} \label{sec:GSPH-method}
-Inutsuka \cite{inutsuka2002reformulation} recognized that the Godunov approach of 
-solving local Riemann problems might obviate the need for artificial viscosity.  This sub-section 
-describes this GSPH method. Our discussion  anticipates that of
-Section \ref{sec:RSPH-method}, and sub-section \ref{sec:Picking-up-single-state}
- in particular, which contain details that are only briefly
+Inutsuka \cite{inutsuka2002reformulation} recognized that the Godunov approach of solving local Riemann problems might obviate the need for artificial viscosity.
+This sub-section describes this GSPH method.
+Our discussion  anticipates that of Section \ref{sec:RSPH-method}, and sub-section \ref{sec:Picking-up-single-state} in particular, which contain details that are only briefly
 introduced here.
 
-The density continues to be updated based on particle location from Eq. (\ref{eq:ns-sph-d}).
-However the update for the momentum and energy equations differs fundamentally from the
-classical SPH approach. We begin by making two observations, the first regarding the density
+The density continues to be updated based on particle location from Eq.
+(\ref{eq:ns-sph-d}).
+However the update for the momentum and energy equations differs fundamentally from the classical SPH approach.
+We begin by making two observations, the first regarding the density
 \begin{equation}
@@
 \end{equation}
-We re-formulate the equations of motion to exploit a certain symmetry. A
-lengthy algebraic manipulation \citep{inutsuka2002reformulation,iwasaki2011smoothed} leads to:
+We re-formulate the equations of motion to exploit certain symmetry. A lengthy algebraic manipulation \citep{inutsuka2002reformulation,iwasaki2011smoothed} leads to:
 \begin{equation}
@@
 \end{equation}
-where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are intermediate states derived from
-the interaction of particles $a$ and $b$. Inutsuka proposed this intermediate $\ast$ state 
-be defined as the stationary state of the solution to a local 1-dimensional Riemann for particles
-$a$ and $b$.  That is, one rotates coordinates, reducing the particle interaction to  
-one space dimension along the line connecting particle $a$ and particle $b$. Using the
-momentum and energy of the two particles as 
-left and right states, one solves the Riemann problem for the starred quantities.
+where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are intermediate states derived from the interaction of particles $a$ and $b$.
+Inutsuka proposed this intermediate $\ast$ state be defined as the stationary state of the solution to a local 1-dimensional Riemann for particles $a$ and $b$.
+That is, one rotates coordinates, reducing the particle interaction to one space dimension along the line connecting particle $a$ and particle $b$.
+Using the momentum and energy of the two particles as left and right states, one solves the Riemann problem for the starred quantities.
 
@@
 
-Of course solving the local Riemann problem for every pair of interacting particles is a 
-computationally intensive process. Further, from this complex Riemann solution
-only the stationary state is used. \cite{hll} provided a framework for calculating approximate
-solutions to local Riemann problems, and influences how
-we propose
-to approximate the  Riemann solution, using ideas from the RCM and \cite{hartenlax}.
+Of course solving the local Riemann problem for every pair of interacting particles is a computationally intensive process.
+Further, from this complex Riemann solution only the stationary state is used.
+\citet{hll} provided a framework for calculating approximate solutions to local Riemann problems, and influences how we propose to approximate the  Riemann solution, using ideas from the RCM and \citet{hartenlax}.
 
 \section{The Random Choice SPH method(RSPH)} \label{sec:RSPH-method}
-In GSPH,  the starred state is the solution to a local Riemann problem at a location
-determined by a weighted average of the specific volumes associated with
- the two participating particles. 
-Instead of calculating a full solution to the Riemann problem, approximate solvers such as
-the Roe method or HLLC,
-might be used. 
-We propose sampling the (approximate) Riemann solution as in the Random choice method, 
-where the approximate solution is given by the HLLC construction (see \cite{toro1994restoration}).
+In GSPH, the starred state is the solution to a local Riemann problem at a location determined by a weighted average of the specific volumes associated with the two participating particles. 
+Instead of calculating a full solution to the Riemann problem, approximate solvers such as the Roe method or HLLC, might be used. 
+We propose sampling the (approximate) Riemann solution as in the Random choice method, where the approximate solution is given by the HLLC construction (see \cite{toro1994restoration}).
 
@@
 The starred state is the solution to a local 1-dimensional Riemann problem.
-Given particles $a$ and $b$, rotate coordinates to establish a single spatial dimension
-along the line connecting the two particles, with direction 
+Given particles $a$ and $b$, rotate coordinates to establish a single spatial dimension along the line connecting the two particles, with direction
 \begin{equation}
@@
 \end{equation}. 
-Let the midpoint of this line segment
-be the origin of the coordinate system. 
-Project variables into this local coordinate system:
+Let the midpoint of this line segment be the origin of the coordinate system. Project variables into this local coordinate system:
 \begin{equation}
@@
 \end{equation}
-Piecewise constant left and right states are then given by the projected 
-variables on either side of the origin
+Piecewise constant left and right states are then given by the projected variables on either side of the origin
 \begin{eqnarray}
@@
 \end{eqnarray}
-[Aside: Cha \cite{cha2003implementations} proposed a second order accurate 
-GSPH method by using
-a piecewise linear interpolation of the states. We do not pursue higher accuracy here,
-although the idea is straightforward to consider.]
+[Aside: Cha \cite{cha2003implementations} proposed a second order accurate GSPH method by using
+a piecewise linear interpolation of the states. We do not pursue higher accuracy here, although the idea is straightforward to consider.]
 
 \subsection{Selecting the star state} \label{sec:Picking-up-single-state}
-Consider then the spatial interval between $\textbf{x}_{a}$ and $\textbf{x}_{ b}$ and a short time interval
-of size $\Delta t$. Recall also that, by convention, we assign the (spatial) origin to
-be at the midpoint between particles $a$ and $b$, 
-$\frac{(\textbf{x}_{a}| + \textbf{x}_{ b})}{2}$.
-Given the piecewise constant
- data (Eq. (\ref{eq:Riemann-Prob-define-L-rho}) - Eq. (\ref{eq:Riemann-Prob-define-R-p})), solve the local Riemann problem. 
- At time $\Delta t$ the solution defines a state composed of constants,
-rarefaction waves, contact discontinuities, and shock discontinuities. 
-Now choose a random number $\epsilon \in [-1,1]$, and set 
-$p_{a b}^{\ast}$ and $\textbf{u}^{\ast}$ to be the Riemann problem solution
-at the location 
+Consider then the spatial interval between $\textbf{x}_{a}$ and $\textbf{x}_{ b}$ and a short time interval of size $\Delta t$.
+Recall also that, by convention, we assign the (spatial) origin to be at the midpoint between particles $a$ and $b$ $\frac{(\textbf{x}_{a}| + \textbf{x}_{ b})}{2}$.
+Given the piecewise constant data (Eq.
+(\ref{eq:Riemann-Prob-define-L-rho}) - Eq.
+(\ref{eq:Riemann-Prob-define-R-p})), solve the local Riemann problem.
+At time $\Delta t$ the solution defines a state composed of constants, rarefaction waves, contact discontinuities, and shock discontinuities.
+Now choose a random number $\epsilon \in [-1,1]$, and set $p_{a b}^{\ast}$ and $\textbf{u}^{\ast}$ to be the Riemann problem solution at the location 
 $$
@@
 Particles are located at $\textbf{x}_{a} $ and $ \textbf{x}_{ b}$, and the local Riemann problem is defined by the constant states $(u, p)_a$ and $(u,p)_b$.
-  The horizontal bold solid line at time $\Delta t$ indicates the interval on which to
-  evaluate the solution of the Riemann problem.
-  The dark ellipse is an example sample point of RSPH with the random number. The white ellipse indicates the stationary state, which is the starred state in GSPH.  }
+The horizontal bold solid line at time $\Delta t$ indicates the interval on which to evaluate the solution of the Riemann problem.
+The dark ellipse is an example sample point of RSPH with the random number.
+The white ellipse indicates the stationary state, which is the starred state in GSPH.}
     \label{fig:pick-up-state-GSPH-RSPH}
@@
 
-The starred state $(\textbf{u}^{\ast},  p^{\ast})$ must now be projected back into the global coordinate system,
-to define  $(\textbf{v}^{\ast},  p^{\ast})$.
+The starred state $(u^{\ast},  p^{\ast})$ must now be projected back into the global coordinate system, to define  $(\textbf{v}^{\ast},  p^{\ast})$.
 
-%\subsubsection{Binary Van Der Corput pseudo-random numbers} \label{sec:Van-Der-Corput-random-num}
- We mention that, instead of selecting a uniformly distributed random number $\epsilon$, 
- we follow \citet{colella1982glimm} and
- adopt the van der Corput pseudo-random number sequence \citep{hammersley2013monte}.
-
-%A general Van Der Corupt pseudo-random number sequence depends on two parameters $x_1$ and $x_2$ with $x_1 > x_2 > 0$, both are integer and relatively prime.
-The sequence is formally defined as \citep{hammersley2013monte}:
-%\begin{equation}
-%\epsilon ^n = \sum_{i=0}^{s} H_i x_1^{-(i+1)}
-%\label{eq:Van-Der-Corput-pseudo-random-num}
-%\end{equation}
-%where
-%\begin{equation}
-%H_i = x_2 a_i(mod \ x_1)
-%\label{eq:Van-Der-Corput-pseudo-random-num-Hi}
-%\end{equation} 
-%\begin{equation}
-%n = \sum_{i=0}^{s} a_i x_1^i
-%\label{eq:Van-Der-Corput-pseudo-random-num-n}
-%\end{equation} 
-%Equation (\ref{eq:Van-Der-Corput-pseudo-random-num-n}) gives the binary expansion of n when we take $x_1$ as $2$. For example,
-%\begin{equation}
-%5=1 \times 2^0 + 0 \times 2^1 + 1 \times 2^2
-%\end{equation}
-%with $m=2$.
-
-%The next stage is to find the coefficient $H_i$ according to Eq.
-(\ref{eq:Van-Der-Corput-pseudo-random-num-Hi}).
-If we take $x_2 = 1$, for which case, $H_i = a_i, \ \forall i$.
-Having $H_i$, $x_1$ and $s$ ready, the random number $\epsilon ^n $ can be easily obtained according to Eq.
-(\ref{eq:Van-Der-Corput-pseudo-random-num}).
-%We take $x_1=2$  and $x_2 =1$ in this paper.
-Other combinations of $x_1$ and $x_2$ were also discussed by \citet{toro2013riemann}.
-A desirable statistical property of the sequence $\{\epsilon ^n\}$ is that $\{\epsilon ^n\}$ be uniformly distributed over $[0,1]$.
-
-%The arithmetic mean and the standard deviation of 200 binary Van Der Corput pseudo-random numbers are $0.49459$ and $0.28885$.
-The chi-square statistic (see \citet{toro2013riemann} for its calculation) $\chi_{sq}$ is $1.0000$.
-%The binary Van Der Corput pseudo-random numbers are generated offline to save computational time.
+We mention that, instead of selecting a uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte}.
 
 \subsection{Non-iterative Riemann solvers} \label{sec:RP-solver}
-Solving local Riemann problems exactly usually involves separating 
-several cases of wave patterns and iteratively solving a small system of ordinary differential
-equations (for rarefaction waves) and a small set of nonlinear equations (the Rankine-Hugoniot equations).
-Instead of running this lengthly process one can employ approximate Riemann solvers, that provide an approximate solution quickly.
-There are many approximate Riemann solvers available 
-\citep{rider1994review, luo2004computation, puri2014approximate}. For purposes here
-we adopt the HLLC solver, which decomposes the Riemann solution into 3 waves, including a (possible) contact discontinuity
- \citet{toro1994restoration}. More specifically, we adopt the HLLC formulation proposed in \citet{luo2004computation}.
+Solving local Riemann problems exactly usually involves separating several cases of wave patterns and iteratively solving a small system of ordinary differential equations (for rarefaction waves) and a small set of nonlinear equations (the Rankine-Hugoniot equations).
+Instead of running this lengthy process one can employ approximate Riemann solvers, which provide an approximate solution quickly.
+There are many approximate Riemann solvers available \citep{rider1994review, luo2004computation, puri2014approximate}.
+For purposes here we adopt the HLLC solver, which decomposes the Riemann solution into 3 waves, including a (possible) contact discontinuity \cite{toro1994restoration}.
+More specifically, we adopt the HLLC formulation proposed by \citet{luo2004computation}.
 
- We mention that, in the numerical tests in Section \ref{numericaltests}, 
- the Roe solver is used for GSPH calculations.
-
-%Equation (\ref{eq:RP_solver_HLLC_u}) and (\ref{eq:RP_solver_HLLC_pu}) are the approximate solution to the local Riemann problem, written in term of $p$ and $pu$ as functions of local coordinate $q$.
-%\begin{equation}
-%    p_L & if \  S_L \Delta t> q \\
-%      \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) M_L + (\hat{p}- p_L) \right] + \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
- %     \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) M_R + (\hat{p}- p_R) \right] + \hat{p} & if \  S_M \Delta t \leq q \leq S_R \Delta t \\
-%      p_R & if \  S_R \Delta t < q
-%\end{cases}
-%\label{eq:RP_solver_HLLC_u}
-%\end{equation}
-%\begin{equation}
-%(pu) \left( q \right)  =  \begin{cases} 
- %     p_L u_L& if \  S_L \Delta t > q \\
- %     \frac{S_M}{S_L - S_M}\left [ (S_L - \hat{u}_L) E_L + (\hat{p} S_M - p_L \hat{u}_L) \right] + (S_M - \hat{u}_{LR}) \hat{p} & if \  S_L \Delta t \leq q \leq S_M \Delta t \\
- %     \frac{S_M}{S_R - S_M}\left [ (S_R - \hat{u}_R) E_R + (\hat{p} S_M- p_R \hat{u}_R) \right] + (S_M + \hat{u}_{LR}) \hat{p} & if \ S_M \Delta t \leq q \leq S_R \Delta t\\
- %     p_R u_R & if \  S_R \Delta t < q
-%\end{cases}
-%\label{eq:RP_solver_HLLC_pu}
-%\end{equation}
-%where $\hat{u}_{LR}$ is the interface velocity and is taken as the Roe-averaged velocity on either side of the interface \citep{cheng2007high}.
-The quantities of $\hat{u}_R$ and $\hat{u}_L$ are velocities relative to the interface velocity.
-%\begin{equation}
-%\hat{p}= \rho_L (\hat{u}_L - S_L) (\hat{u}_L - S_M) + p_L
-%\end{equation}
-%Formulation to approximate the signal speeds $S_M$, $S_L$ and $S_R$ is given by Eq. (\ref{eq:RP-solver-HLLC-SM}) to (\ref{eq:RP-solver-HLLC-SR}).
-%\begin{eqnarray}
-%S_M= \frac{\rho_R \hat{u}_R (S_R - \hat{u}_R) - \rho_L \hat{u}_L (S_L - \hat{u}_L) + p_L - p_R}{\rho_R (S_R - \hat{u}_R) - \rho_L (S_L - \hat{u}_L)} \label{eq:RP-solver-HLLC-SM} \\
-%S_L = min (\hat{u}_L - c_L, -c_{LR}) \label{eq:RP-solver-HLLC-SL} \\
-%S_R = max (\hat{u}_R - c_R, c_{LR}) \label{eq:RP-solver-HLLC-SR}
-%\end{eqnarray}
-%where $c_{LR}$ is the relevant Roe averaged sound speed \citep{cheng2007high}.
-
-%Besides HLLC, another 2-wave approximate Riemann solver, the Roe Riemann solver \citep{roe1981approximate}, is also adopted in GSPH.
-%Roe Riemann solver is proposed by \citet{roe1981approximate} to linearize the Euler equations and approxiamte the solution of non-linear system by a system of linear equations.
-The characteristic decomposition of the linearized Lagrangian flux and Jacobia matrices are used to write the flux.
-\citet{rider1994review} proposed an algebraic averaging of the Lagrangian variables, which is adopted in this work.
-Since Roe solver is only used in GSPH.
-We directly provide here the resulting starred values of the pressure and velocity \citep{puri2014approximate}:
-%\begin{eqnarray}
-%u^{\ast} = \frac{1}{2} \left[ u_L + u_R - \frac{1}{C_{LR}} (p_R - p_L) \right] \label{eq:RP-solver-ROE-u} \\
-%p^{\ast} = \frac{1}{2}\left[ p_L + p_R - C_{LR} (u_R - u_L) \right] \label{eq:RP-solver-ROE-p}
-%\end{eqnarray}
-%Where $C_{LR}$ is the averaged Lagarangian sound speed at the interface.
-%\begin{equation}
-%C_{LR} = \sqrt{\gamma p_{LR} \rho_{LR}}
-%\end{equation}
-
-%\subsection{RSPH algorithm (the PESB algorithm)}
-%The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm.
+We mention that, in the numerical tests in Section \ref{numericaltests}, Both the HLLC solver and Roe solver are used for GSPH calculations.
 To summarize, our RSPH algorithm proceeds as follows:
 \begin{itemize}
-\item For each pair of particles, establish a local coordinate system whose axis joins the
-particles,
-and project the primitive variables onto this local coordinate system to define
-left and right states;
+\item For each pair of particles, establish a local coordinate system whose axis joins the particles,
+and project the primitive variables onto this local coordinate system to define left and right states;
 \item Solve this local Riemann problem approximately using a HLLC solver;
-\item Sample the solution using the van der Corput sequence,
-defining a state  $p^{\ast}, u^{\ast}$;
-\item Project $p^{\ast}, u^{\ast}$  back to the global coordinate system,
-to obtain $p^{\ast}$ and $\textbf{v}^{\ast}$;
+\item Sample the solution using the Van Der Corput sequence, defining a state  $p^{\ast}, u^{\ast}$;
+\item Project $p^{\ast}, u^{\ast}$  back to the global coordinate system, to obtain $p^{\ast}$ and $\textbf{v}^{\ast}$;
 \item Update the particle positions.
@@
 \item Test 2 also consists of a left rarefaction, a right traveling contact and a right shock. Density decreases at down wind of contact wave. 
-\item Test 3 includes double expansion waves. The initial density are different at right and left hand side. 
+\item Test 3 includes double expansion waves. The initial density is different at right and left hand side. 
 \item Test 4 is a double shock tests with different initial density on the right side and left side.
@@
 
-\begin{table}[htp]
+\begin{table}[H]
 \centering
@@
 \subsection{Comparison of RSPH with standard SPH and GSPH}
-\begin{figure}[htp]
+\begin{figure}[H]
     \centering
@@
 c), d) show zoomed views.
-For $\alpha=1$ and $\alpha=2$,numerical oscillations are completely suppressed though the shock is now smeared.
-$\alpha=0.25$ provided insufficient viscosity to suppress oscillations.
+For $\alpha=1$ and $\alpha=2$, numerical oscillations are completely suppressed though the shock is now smeared.
+$\alpha=0.2$ provided insufficient viscosity to suppress oscillations.
 Comparing RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock
-    (comparable to $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.25$). %    
-%    
-%    For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock.
-However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock.
-To summarize, the equivalent artificial viscosity in RSPH is adaptive.
-Similar conclusion can be drew from zoomed view of velocity.
-The third zoomed view shows different degrees of smearing at the shock.
-The larger the artificial viscosity, the less sharp the solution at the shock.
-Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity.
-SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock.
-The last zoomed view shows pressure around the contact discontinuity.
-It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.
+    (comparable to $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.2$). % 
     }
@@
 
-\begin{figure}[htp]
+\begin{figure}[H]
     \centering
-%    \begin{minipage}{.495\textwidth}
-%        \centering a)
-%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
-%    \end{minipage}%
-%    \begin{minipage}{.495 \textwidth}
-%        \centering b)
-%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
-%    \end{minipage}%
-%    \\
     \begin{minipage}{.495\textwidth}
@@
     \\
-%    \begin{minipage}{.495\textwidth}
-%        \centering a)
-%        \includegraphics[width=0.99 \textwidth, height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
-%    \end{minipage}%
-%    \begin{minipage}{.495 \textwidth}
-%        \centering b)
-%        \includegraphics[width=0.99 \textwidth, height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
-%    \end{minipage}% 
-%    \\
     \begin{minipage}{.495 \textwidth}
@@
 c), d) show zoomed views.
-For $\alpha=1$ and $\alpha=2$,numerical oscillations are completely suppressed though the shock is now smeared.
-$\alpha=0.25$ provided insufficient viscosity to suppress oscillations.
+For $\alpha=1$ and $\alpha=2$, numerical oscillations are completely suppressed though the shock is now smeared.
+$\alpha=0.2$ provided insufficient viscosity to suppress oscillations.
 Comparing RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock
-    (comparable or better than $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.25$).
+    (comparable or better than $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.2$).
 d) shows pressure around the contact discontinuity.
-It shows that RSPH gets rid of the pressure ``wiggle" around the contact discontinuity.
-%
-%    Simulation results by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
-The last four figures are zoomed views.
-Almost no fluctuation is observed when $\alpha=1$ and $\alpha=2$, illustrating that numerical fluctuation is completely suppressed if artificial viscosity is large enough.
-For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock.
-However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock.
-To summarize, the equivalent artificial viscosity in RSPH is adaptive.
-Similar conclusion can be drew from zoomed view of velocity.
-The third zoomed view shows different degrees of smearing at the shock.
-The larger the artificial viscosity, the less sharp the solution at the shock.
-Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity.
-SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock.
-The last zoomed view shows pressure around the contact discontinuity.
-It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.
-}
+It shows that RSPH gets rid of the pressure ``wiggle" around the contact discontinuity.}
     \label{fig:RCM-Sod-SPH-alf-zoom}
@@
 Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients ($\alpha=1,2$).
-%The mechanism for SPH to reduce (or completely get rid of) fluctuations should be completely different from that of new adaptive method of smoothing length. 
-%The new adaptive method, reduces the sources of such fluctuations.
 Secondly, the equivalent artificial viscosity introduced by RSPH varies adaptively.
@@
 So RSPH is actually more adaptive than SPH.
-This feature is very desirable not only because it could eliminate parameterization and hence user intervention associated with artificial viscosity coefficients but also because it avoids introducing excessive artificial viscosity when unnecessary.
+This feature is very desirable not only because it could eliminate parameterization and hence user intervention associated with artificial viscosity coefficients but also because it avoids introducing excess artificial viscosity.
 Thirdly, RSPH introduces less smearing of the shock discontinuity compared with SPH using most commonly adopted artificial viscosity coefficients ($\alpha=1.0$, $\beta=2.0$).
@@
 
-Zoomed views in Gig.
-\ref{fig:RCM-Sod-GSPH} compare GSPH andRSPH and demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH.
+Zoomed views in Fig.
+\ref{fig:RCM-Sod-GSPH} compare GSPH and RSPH and demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH.
 The attractive feature of RCM method in preserving true discontinuity is inherited by RSPH in this 1D shock tube test.
-With more dissipation, GSPH can also completely suppress numerical dissipation.However, the discontinuity at the shock is then more seriously smeared.
+With more numerical dissipation, GSPH can completely suppress numerical oscillations.
+However, the discontinuity at the shock is then more seriously smeared.
 The excessive amount of dissipation might have other, more undesirable, effects in real implementation.
@@
 We use shock tube test to gauge the accuracy of the RSPH scheme.
-% for both situations when the solution remains smooth and when there are shocks in the solution. We use test 1 to conduct order of accuracy test for the case with shocks in the solution. 
 We examine the errors between simulation results and the analytical solution (the reference solution) as the number of particles is increased.
@@
 Presence of discontinuities, such as shock, in the test problem might lower the rate of convergence.
-Both RSPH and GSPH tests in this paper adopt a piece wise constant construction of Riemann problem.
-So we conclude that RSPH shows higher order of accuracy than GSPH when using the same Riemann problem construction.
+Since both RSPH and GSPH tests in this paper adopt piece wise constant construction of Riemann problem.
+We conclude that RSPH shows higher order of accuracy than GSPH when using the same Riemann problem construction.
 Compared with SPH, RSPH shows almost the same order of accuracy and level of error.
-%It is worthwhile to check the order of accuracy of GSPH using piecewise linear constructor
-%It is also worthwile to check what of order of accuracy using another test problem.  
 \begin{figure}[H]
@@
 Comprehensive tests are presented in this section to check how well does RSPH work for different situations. Input parameters for each tests is given in Table \ref{tab:1D-shock-input_parameters}.
-% Wave speed is estimated based on formulation Eq. (\ref{eq:RP-solver-HLLC-SM}) $\sim$ Eq. (\ref{eq:RP-solver-HLLC-SR}).
 The results are shown in Fig.
@@
 %Such spike is evident in the FVM solution as well and is perhaps an artifice of the Lagrangian nature of the two schemes.
-\citep{noh1987errors} proposed to adding a small amount of thermal conduction to ameliorate the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}.
+\citet{noh1987errors} proposed to adding a small amount of thermal conduction to ameliorate the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}.
 We did not adopt such strategy in our simulation.
@@
     \centering
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.415\textwidth}
         \centering
@@
     \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
+    \begin{minipage}{.415 \textwidth}
         \centering
@@
     \\
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.415\textwidth}
         \centering
@@
     %\centering
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.415\textwidth}
         \centering
@@
 \begin{figure}[H]
-    %\centering
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.415\textwidth}
         \centering
@@
     \caption{Results for test 5, a variation of the Sjogreen test.
-The density, velocity and pressure are well re-produced while the thermal energy at the origin is poorly predict.
+The density, velocity and pressure are well re-produced while the thermal energy at the origin is poorly predicted.
 A jump of internal energy at the origin is a common issue in many SPH schemes (see, for example, \citep{monaghan1997sph,cha2003implementations,puri2014approximate})}
@@
     \\
-    \begin{minipage}{.495 \textwidth}
+    \begin{minipage}{.415 \textwidth}
         \centering
@@
 
-\subsection{3D free jet}
+\subsection{3D free jet} \label{jet}
 Free jet flow have been studied analytically, experimentally and numerically for many decades, not only because of its wide application but also because of its fundamental significance as a basic flow to the scientific research community.
@@
 At the vent, exit velocity $\textbf{v}$ is set to $500 m / s$ and radius of the nozzle $r$ is set to $8m $.
-The pressure of ejected fluid are assumed to be the same as ambient ($101 kpa$).
+The pressure of ejected fluid is assumed to be the same as ambient ($101 kpa$).
 The temperature of and ambient fluids are set to $273 K$.
 Velocity is zero for non-slip wall boundary.
-The heat flux across wall boundary is zero assuming adiabatic wall.
+The heat flux across wall boundary is zero assuming an adiabatic wall.
 The flux of mass should also be zero on the wall.
 As a result, internal energy flux, which consists of heat flux and energy flux carried by mass flux, vanishes on the wall boundary.
-The pressure of the surrounding ambient is given. As we ignore the viscosity, the shear stress is ignored and normal stress (whose magnitude equals to pressure) balances the ambient pressure.
+The pressure of the surrounding ambient is given. As we ignore the physical viscosity, the shear stress is ignored and normal stress (whose magnitude equals to pressure) balances the ambient pressure.
 \begin{equation}
@@
 \end{equation} 
-Except for the pressure, boundary values for density, velocity, and energy on the outlet are determined by solution. Fluids properties of ideal gas are used in this simulation.
+Except for the pressure, boundary values for density, velocity, and energy on the outlet are dependent on solution. Fluids properties of ideal gas are used in this simulation.
 
@@
 
-\section{Conclusion}
-In this paper we have proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs that combines the Random Choice Method with
-an approximate Riemann solver.  No explicit artificial viscosity is needed. Instead, any viscosity that is used in a hydrodynamics simulation 
-is just what the user explicitly adds. This control is important in applications with very strong shocks
+\section{Conclusion} \label{discussion}
+In this paper we have proposed RSPH, a novel SPH scheme for solving hyperbolic non-linear PDEs that combines the Random Choice Method with an approximate Riemann solver.
+No explicit artificial viscosity is needed.
+Instead, any viscosity that is used in a hydrodynamics simulation is just what the user implicitly adds.
+This control is important in applications with very strong shocks.
 RSPH also shows good convergence behavior.
-On the other hand, RSPH does not address other methodological questions that must be decided in order to use SPH, 
-questions such as the smoothing length of the SPH kernel. We have investigated the HLLC approximate Riemann solver in this paper;
-it is of interest to test other approximate solvers,  to better understand the behavior of solutions.
-This may be particularly important when applying RSPH to other systems, where the explicit construction on which the HLLC solver
-rests is not readily available.
+On the other hand, RSPH does not address other methodological questions that must be decided in order to use SPH, questions such as the smoothing length of the SPH kernel.
+We have investigated the HLLC approximate Riemann solver in this paper; it is of interest to test other approximate solvers, to better understand the behavior of solutions.
+This may be particularly important when applying RSPH to other systems, where the explicit construction on which the HLLC solver rests is not readily available.
 

### 2018-06-11 ebp-JCPManuscript.tex
Jun 11

@@
 The pressure of ejected fluid is assumed to be the same as ambient ($101 kpa$).
-The temperature of and ambient fluids are set to $273 K$.
+The temperature of both ejected fluids and ambient fluids are set to $273 K$.
 Velocity is zero for non-slip wall boundary.
@@
 From left to right, the picture is corresponding to SPH, GSPH and RSPH respectively.
-Red particles in pictures of the first row are particles erupted from the nozzle while blues are ambient fluids particles.
+Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.
 Pictures on the first row are corresponding to $t=1.5s$ while pictures on the second row are for $t=3.0 s$}
@@
 While introducing undesirable damping effects, artificial viscosity is necessary for numerical stability and simulating of shocks.
-So, in real applications, the artificial viscosity coefficients are usually tuned (see, for example, \citep{gmd-2017-119}) to avoid excessive artificial damping effects.
+So, in real applications, the artificial viscosity coefficients are usually tuned (see, for example, \citep{gmd-2017-119}) to minimize artificial damping effects.
 

### 2018-06-13 ebp-JCPManuscript.tex
June 11 pm
fixed a typo, updated lengend of pics

@@
 Consider then the spatial interval between $\textbf{x}_{a}$ and $\textbf{x}_{ b}$ and a short time interval of size $\Delta t$.
-Recall also that, by convention, we assign the (spatial) origin to be at the midpoint between particles $a$ and $b$ $\frac{(\textbf{x}_{a}| + \textbf{x}_{ b})}{2}$.
+Recall also that, by convention, we assign the (spatial) origin to be at the midpoint between particles $a$ and $b$.
 Given the piecewise constant data (Eq.
@@
 $$
-\epsilon |\textbf{x}_{a}| - \textbf{x}_{ b}|
+\epsilon \frac{|\textbf{x}_{a} - \textbf{x}_{ b}|}{2}
 $$
@@
 \item Project $p^{\ast}, u^{\ast}$  back to the global coordinate system, to obtain $p^{\ast}$ and $\textbf{v}^{\ast}$;
-\item Update the particle positions.
+\item Update the particle positions and physical quantities.
 \end{itemize}
@@
 We describe results from several numerical tests using SPH, RSPH and GSPH in this section.
-1D shock tube tests are used to compare standard SPH, GSPH and RSPH.
-Comprehensive shock tube simulations are also conducted to check the capacity of RSPH for different situations.
+A 1D shock tube tests is used to compare standard SPH, GSPH and RSPH.
+More shock tube simulations are also conducted to check the capacity of RSPH for different situations.
 In addition, order of accuracy is investigated for the 1D shock tube problem.
@@
     \end{minipage}% 
-    \caption{Results for test 4, the double shock case. All physical properties are well re-produced. However, the oscillations are more serious than oscillations in other tests.}
+    \caption{Results for test 4, the double shock case.
+To stabilize the simulation, RSPH sampling is in a narrower range.
+All physical properties are well re-produced.
+However, the oscillations are more serious than oscillations in other tests.}
     \label{fig:RCM-double-shock}
@@
 y axis for density plot is in log base 10.
+To stabilize the simulation, RSPH sampling is in a narrower range.
 All physical properties are well re-produced.

### 2018-06-15 ebp-JCPManuscript.tex
emphasized the adaptivity of RSPH

@@
 \begin{abstract}
-The classical smoothed particle hydrodynamics (SPH) method employs artificial viscosity to properly capture shock waves in hydrodynamics.
+The classical smoothed particle hydrodynamics (SPH) method employs explicit artificial viscosity to properly capture shock waves in hydrodynamics.
 This artificial viscosity typically produces more dissipation than is needed to smooth shocks, incorrectly smears contact discontinuities, and can overwhelm fluid turbulence.
 Several studies have proposed highly tuned versions of artificial viscosity, turning on and off near shocks or other troublesome wave features.
-Unfortunately these schemes usually produce more dissipation than is appropriate.
-A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems as building blocks for a numerical SPH solver.
-Of course a first order Godunov solver still introduces an effective numerical diffusion that can infect the entire numerical solution.
+A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems as building blocks for a numerical SPH solver without explicit numerical dissipation term.
+Unfortunately, a first order Godunov solver still introduces an effective numerical diffusion that can infect the entire numerical solution.
 We propose a novel SPH scheme that combines an approximate version of Glimm\rq{}s Random Choice method (RCM) with SPH.
-RCM properly resolves and then samples all hydrodynamic waves, and introduces no numerical diffusion into a simulation.
+RCM properly resolves and then samples all hydrodynamic waves.
 Our version approximately resolves hydrodynamic waves, and samples the approximate solution.
-We test this method on standard one dimensional shock tube problems.
-Our ultimate goal is to apply this method to jet flow.
+No explicit artificial viscosity will be needed.
+We test this method on standard one dimensional shock tube problems and observe several attractive features.
+First of all, this method introduces adaptive artificial viscosity -- larger around discontinuities and smaller elsewhere.
+Secondly, it is less dissipative than classical SPH and GSPH resulting in less smearing of shock.
+Thirdly, as the new method can be viewed as generalized GSPH method in terms of sampling solutions of local Riemann problems, good features of GSPH are inherited, for example, ameliorating pressure ``wiggle" around contact discontinuity.
+When applied to three dimensional jet flow, this method is demonstrated to introduce less overall dissipation than GSPH.
+%Our ultimate goal is to apply this method to jet flow.
 Because of the high shear rate in this application, we introduce a highly tuned eddy viscosity that is applied only near the shear surface.
@@
 Our approach here is based on the Harten-Lax proposal.
-We introduce a new method which we dub RSPH, by randomly sampling the interaction of pairs of SPH particles.
+We introduce a new method, which we dub RSPH, by randomly sampling the interaction of pairs of SPH particles.
 This scheme produces dissipation-free solutions, as does classical RCM, but for a Lagrangian system.
@@
 \subsection{GSPH} \label{sec:GSPH-method}
-Inutsuka \cite{inutsuka2002reformulation} recognized that the Godunov approach of solving local Riemann problems might obviate the need for artificial viscosity.
+\citet{inutsuka2002reformulation} recognized that the Godunov approach of solving local Riemann problems might obviate the need for artificial viscosity.
 This sub-section describes this GSPH method.
@@
     \end{minipage}%
-%    \\
-%    \begin{minipage}{.495\textwidth}
-%        \centering c)
-%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
-%    \end{minipage}%
-%    \begin{minipage}{.495 \textwidth}
-%        \centering d)
-%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
-%    \end{minipage}% 
     \\
@@
     \end{minipage}%   
-%    \\
-%    \begin{minipage}{.495 \textwidth}
-%        \centering g)
-%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
-%    \end{minipage}% 
-%    \begin{minipage}{.495\textwidth}
-%        \centering h)
-%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
-%    \end{minipage}%    
-    \caption{a),b) Simulation results of density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
-c), d) show zoomed views.
-For $\alpha=1$ and $\alpha=2$, numerical oscillations are completely suppressed though the shock is now smeared.
-$\alpha=0.2$ provided insufficient viscosity to suppress oscillations.
-Comparing RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock
-    (comparable to $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.2$). % 
-    }
+    \caption{a),b) are simulation results of density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
+c), d) are zoomed views, showing that $\alpha=0.2$ provided insufficient viscosity to suppress oscillations around shock.
+The dissipation introduced by RSPH.
+on the other hand, is adaptive, introducing more damping at the shock (comparable to $\alpha=1.0$) and less damping in the area away from the shock (less than $\alpha=0.2$, as indicated by the magnitude of oscillation).}
     \label{fig:RCM-Sod-SPH-alf}
@@
     \caption{
-    a),b) Simulation results of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
-c), d) show zoomed views.
-For $\alpha=1$ and $\alpha=2$, numerical oscillations are completely suppressed though the shock is now smeared.
+    a),b) are simulation results of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
+c), d) are zoomed views.
+For $\alpha=1$ and $\alpha=2$, as shown in c), numerical oscillations are completely suppressed though the shock is now smeared.
 $\alpha=0.2$ provided insufficient viscosity to suppress oscillations.
-Comparing RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock
-    (comparable or better than $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.2$).
+Comparing RSPH and SPH shows that RSPH is adaptive, more dissipative at the shock (comparable or better than $\alpha=1.0$) and less dissipative away from the shock (less than $\alpha=0.2$).
 d) shows pressure around the contact discontinuity.
-It shows that RSPH gets rid of the pressure ``wiggle" around the contact discontinuity.}
+It is evident that RSPH gets rid of the pressure ``wiggle" around the contact discontinuity.}
     \label{fig:RCM-Sod-SPH-alf-zoom}
@@
 \ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}.
-In all simulations, the artificial viscosity $\beta$ is set to be twice of $\alpha$.
+In all simulations, the artificial viscosity coefficient $\beta$ is set to be twice of $\alpha$.
 For example, for the test ``$SPH-\alpha=2$", $\beta=4$.
@@
 Recall that RCM is able to resolve discontinuities as true discontinuity.
-RSPH, even though it still smears the discontinuity in some degree, introduces much less smearing.
+RSPH, even though it still smears the discontinuity in some degree, introduces much less smearing (see Fig.
+\ref{fig:RCM-Sod-SPH-alf-zoom}).
 The last but not the least, the pressure ``wiggle" around contact discontinuity is completely eliminated by RSPH as seen in Fig.
@@
 It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}.
-As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and help suppress the anomaly \citep{puri2014approximate}.
+As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and helps suppress the anomaly \citep{puri2014approximate}.
 Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}).
@@
 We observe that RSPH is able to correctly predict the position and magnitude of all waves for all tests.
-A jump of specific internal energy at the origin is observed in Sjogreen test.
+A jump of specific internal energy at the origin is observed in Sj$\ddot{o}$green test.
 However, such jump is a common issue of SPH schemes and has been reported in many other tests (see, for example, \citep{monaghan1997sph,cha2003implementations,puri2014approximate})
@@
     \end{minipage}% 
-    \caption{Results for test 5, a variation of the Sjogreen test.
+    \caption{Results for test 5, a variation of the Sj$\ddot{o}$green test.
 The density, velocity and pressure are well re-produced while the thermal energy at the origin is poorly predicted.
@@
     \centering
-    \begin{minipage}[t]{.325\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t1p5-cutView}
-    \end{minipage}%
+%    \begin{minipage}[t]{.325\textwidth}
+%        \centering
+%        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t1p5-cutView}
+%    \end{minipage}%
     \begin{minipage}[t]{.325 \textwidth}
@@
     \centering
-    \begin{minipage}[t]{.325\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t3-cutView}
-    \end{minipage}%
+%    \begin{minipage}[t]{.325\textwidth}
+%        \centering
+%        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t3-cutView}
+%    \end{minipage}%
     \begin{minipage}[t]{.325 \textwidth}
@@
 Figure \ref{fig:free-jet-SPH-comparison} shows simulation results of the free jet flow by SPH with different artificial viscosity coefficients.
-The damping effect due to artificial dissipation is clearly shown in this figure.
+The overall damping effect due to artificial dissipation is clearly shown in this figure.
 We observe that the lengths to which these jets reach at $t=3.0 s$ are different when using different artificial viscosity coefficient.
 It is obvious that the larger artificial viscosity, the shorter length the jet can reach.
+The length that free jet reaches can be used as an indicator of overall dissipation.
 While introducing undesirable damping effects, artificial viscosity is necessary for numerical stability and simulating of shocks.
@@
 
-We compare RSPH with GSPH in terms of equivalent overall artificial damping effects.
+We compare RSPH with GSPH in terms of equivalent overall artificial damping effects in Fig.
+\ref{fig:free-jet-comparison}.
 Different from SPH, both GSPH and RSPH introduce artificial viscosity in an implicit way by solving local Riemann problems.
@@
 This control is important in applications with very strong shocks. 
-RSPH also shows good convergence behavior.
+Unlike classical SPH which uses the same artificial viscosity coefficients everywhere, RSPH introduces larger dissipation around the shock to guarantee numerical stability while introduces much smaller dissipation elsewhere.
+Such adaptive manner of assigning dissipation reduces unnecessary numerical damping but preserves demanded damping for restraining numerical instability.
+As demonstrated in 1D and 3D tests, RSPH causes less smearing of shocks and less overall dissipation for jet flow.
+In addition, RSPH also shows good convergence behavior.
+
 On the other hand, RSPH does not address other methodological questions that must be decided in order to use SPH, questions such as the smoothing length of the SPH kernel.

### 2018-11-24 Response to Reviewers.tex
add appendix for oscillation

\documentclass[10pt,a4paper]{article}
%\documentclass[10pt,a4paper]{beamer}
%\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{kpfonts}
\usepackage[numbers]{natbib}
%other options include: round, curly, angle, or default options

\usepackage{media9}
\usepackage{color}
\begin{document}
\author{\Large {Zhixuan Cao, Abani Patra, E. Bruce Pitman}}

\title{
\LARGE \textbf{Response to Reviewers} \\
\Large \textbf{``A Random Choice SPH Scheme with Adaptive Viscosity"}}

\date{\vspace{-5ex}}

\maketitle
The comments by the reviewers are recited in italics, followed by our reply in upright font. Revisions are highlighted with blue. Equation, section, figure and reference numbers in our response are corresponding to these in the original 
version of JCP manuscript if not specified. \\[12pt]

\textbf{\Large Reviewer \# 1}\\[3pt]

\textbf{\large General Comments}

\textit{This article describes an effort to combine the previous development of SPH technique with "Random Choice Method (RCM)", a classical approach developed in the framework of grid-based method for
describing fluid flows. The authors compare their method with standard SPH method and the first order GSPH, and show some interesting results and may provide useful information for the community of SPH developers. Therefore the reviewer would recommend its publication after the authors sufficiently react to some concerns described below.}

We would like to thank the reviewer for carefully reading our manuscript and giving positive review and critical remarks.
We have revised the manuscript as described in the separate documentation and we hope that we have dealt with all suggestions in an adequate manner. The revised manuscript is also attached.

On behalf of all co-authors.

The following are our responses to reviewer's specific comments.\\[12pt]

\textbf{\large Specific comments}

\textit{The reviewer thinks that this kind of article should provide a new and useful method with respect to the previously known method. The usefulness may include (but not be restricted to) either higher accuracy, fast computation, implementation easiness, or versatility for the extension to include complex physics. According to the simulation examples shown in this article, the reviewer does not find the present method is more accurate than the second-order GSPH. (Note that it is not much more complicated than the first order GSPH. Instead, the reviewer thinks that the present method is (at least slightly) faster than those methods, and can be categorized in "faster methods" with approximate Riemann Solvers that includes development by Puri et al. With this respect, the reviewer thinks that comparison with the method of Puri et al. should be shown and explained in more detail. Note that the reviewer has no doubt in the
possibility of the present method for further development.}

To response reviewer's recommendation for comparing 1D tests in present article with these 1D tests by \citet{puri2014approximate}:

The present method adopts HLLC and Roe approximate Riemann solvers presented in \citep{puri2014approximate}. We did not make any improvement in term of approximate Riemann solvers. In that sense, these GSPH results in our paper are similar to these tests in \citep{puri2014approximate}, which combines GSPH with Riemann solvers proposed in that paper. Or in other words, we have already done such comparison in current paper.
But we need to mention two sources of differences. First of all, we adopted first order GSPH while tests in \citep{puri2014approximate} using second order GSPH. The reason why we use first order GSPH instead of second order GSPH is that we want to do ``well controlled" comparison. So that we can show the pure effect of ``random choice". Secondly, the shock tube tests adopted in our manuscript are very similar to these presented in \citep{puri2014approximate}, however, they are not exactly the same. We intentionally assign different densities to particles at left side and right side. This can lead to nonuniform smoothing length distribution in space and induce numerical oscillation. More details are explained in appendix B of the revised manuscript.

In response to reviewer's comments regarding the usefulness of the method:

The motivation and innovative point of the present method is to introduce numerical dissipation in a more adaptive manner, hence introduce less smearing around discontinuities. In that sense, the present work can be considered as ``higher numerical accurate", even though it is NOT ``higher order of accuracy". Another feature that made present method to be ``higher accurate" is its capability to better suppressing pressure wiggle at contact discontinuity. Both features have been demonstrated in 1D tests. Such improvements can be considered as "more accurate".

Thanks for helping us find another merit of RSPH. Compared with second order GSPH, the present method would be, at least slightly, faster (due to less computation for RP construction) on expense of lower order of accuracy. \\[3pt] 
%Compared with first order GSPH, it will not be faster. So the computational  speed would be a normal feature of present method instead of an attractive feature. 
%By adopting approximate Riemann solver, the present work would be computationally faster than RCM methods using iterative Riemann solver. If all previous RCM method is using iterative Riemann solver, then we may claim that it is the first time to combine RCM with non-iterative Riemann solver. And this would be another innovative point of our paper.

\textit{Since the random choice method (RCM) was introduced by Glimm in 1965 and seems to be discussed mainly around 1980, it is better to explain this method in more detail, especially why this method is expected to give a good result. Without such explanation the readers cannot understand why the present method may give better result than the other methods.}

We agree with reviewer. We added an appendix to introduce RCM with a little bit more details. More references are also provided there.\\[3pt]

\textit{Regrettably, Figure 4, 7, and 8 show relatively large oscillation in the
numerical results. Can you explain why this occurs? Is there any prescription to remove this?}

The large oscillations in these 1D shock tube tests actually are very critical in demonstrating the merit of present method. Such oscillations are caused by nonuniform smoothing length distribution in space. For 1D shock tube tests, smoothing lengths are usually not uniform in space. However, due to existence of sufficient numerical dissipation, such osciallations decay fast so are not obviously observed in previous tests. In Fig 3, for example, we can not observe oscillation when $\alpha =1$ and $\alpha = 2$. When numerical dissipation is small ($\alpha = 0.2$), such oscillations are not completely suppressed and can be seen. Based on such observation, we use ``how much the oscillation get suppressed" as an indirect indicator for numerical dissipation. Our following discussions are based on such correlation between observable oscillation and numerical dissipation. Shock tube tests in this article are intentionally designed to have more obvious numerical oscillation. Test $1 \sim 4$ adopt different particle densities on right side and left side, which will lead to discontinuity of smoothing length at the middle. Such discontinuity in term of resolution is the source of numerical oscillation. In revised manuscript, we addressed these points. We also added an appendix explaining the mechanism for generating numerical oscillations.
\\[3pt]
%need to show that equal density can help reduce oscillation.
%For compressible flow, smoothing lengths. Unfortunately the original manuscript did not delivery this point clearly. The shock tube tests were intentionally designed to make such oscillation more obvious by assigning different particles masses. In all shock tube tests presented in previous work, uniform particle mass is adopted while in our manuscript, different particle mass are assigned for particles on right side and left side. Different particle mass will amplify the oscillation and help to demonstrate the merit of present method in a more obvious manner.

\textit{Section 4.4 is the most problematic. First of all, Figure 12 seems to be missing two additional figures, since the caption seems to describe three figures in each low. In general the reader cannot evaluate which method is superior to the others (only) by looking at these figures. The authors should improve the way to present the results.}

In section 4.4, we first simulate the free jet flow using classical SPH based on different artificial viscosity coefficients. The results show that larger artificial viscosity coefficients can lead to shorter length of jet. Considering that larger artificial viscosity coefficients introduces more equivalent overall-dissipation. We reach to the conclusion that we can use the length of jet as a indirect indicator of equivalent overall-dissipation. 
Then we compared the length of jet simulated by GSPH and RSPH. As the length of GSPH is shorter, we inferred that RSPH introduces less equivalent overall-dissipation.
We modified the manuscript to delivery these points more clearly.

Figure for SPH results were removed while we forgot to update the caption, which makes Figure 12 to be confusing. We revised the caption in our revised manuscript.

We want to mention here that in both GSPH and the present method, the way to handle velocity that perpendicular to local coordinate system need to be improved. There are (at least) two different ways to handle the perpendicular velocity component. See [13] and [15]. We are adopting [13]'s method in section 4.4. 
\\[3pt]

\textit{Note that the original GSPH paper [13] describes not only the first order method but also the second order method (and it effectively recommends the use of second order method). The authors seem to be missing these points. It is evident from the description in the following phrase: "Cha[14] proposed a second order accurate GSPH method by using a piecewise linear interpolation of the states." in Page 9 and "We observe a rate of convergence of approximately 1 for GSPH" in Page 17. These descriptions mislead the readers.}

The reviewer actually asked two questions here. 
With respect to the first question, yes, in our manuscript, we only compared RSPH with first order GSPH while GSPH could be second order as mentioned by the reviewer. The reason why we only compare our method with first order GSPH is that our method can only be first order. To make the comparison to be ``well controlled", we compared first order RSPH against first order GSPH. As reviewer has notified, RSPH and GSPH have many things in common: both need projecting quantities from global coordinate system to a local coordinate system, both need constructing local Riemann problem and solve the local Riemann problem, both need to project solution of the local Riemann solution back to global. In our ``well controlled" comparison, the only difference between RSPH and GSPH tests is the way to sample solution of local Riemann problems. This difference is actually also the essential difference between Godunov's method and random choice method in the context of mesh based method. With such ``well controlled" comparison, we can clearly show the effects purely due to the essential differences between RSPH and GSPH. We have to mention that such ``first order" limitation is inherited from RCM. Namely, RCM (which were proposed in mesh based methods) adopts a ``piece wise constant" way when constructing Riemann problems. This should be a disadvantage of RSPH compared with second order GSPH.
It is not surprise to us that we observe first order of accuracy in our tests as we were testing first order GSPH.

With respect to the second question, yes, that statement would indeed cause confusions to readers. We added more explicit explanation in revised manuscript.
\\[3pt]

\textit {It is well known that the wiggle in the pressure at the contact discontinuity is due to the inconsistency of the standard SPH in evaluating pressure gradient force with a non-smooth distribution of particles. This problem is (at least partially) solved in GSPH [13, 17]. Note that the article [15] did not care this problem. Since the present article used the method shown in [15], the reviewer does not expect a good result at contact discontinuity. If the authors have some reason why the method that includes RCM can accurately describe the contact discontinuity, they should explain it within this article. The reviewer
presumes that it can be a desirable feature in the present method if it is true.}

[13] indeed shown that GSPH can almost get rid of pressure wiggle around contact discontinuity while standard SPH shows much more obvious pressure wiggle. They believe that the pressure wiggle is due to the inconsistency of EoM (equation of momentum) of the standard SPH. Or in other words, just as what the reviewer mentioned: "The wiggle in the pressure at the contact discontinuity is due to the inconsistency of the standard SPH in evaluating pressure gradient force with a non-smooth distribution of particles." However, there are different opinions with respect to the sources of pressure wiggle. For example, other researchers believe that the pressure wiggle has something to do with thermal conduction at the contact discontinuity. It has been shown that thermal conduction is essential to mitigate the spurious pressure wiggle at contact discontinuity in SPH [e.g. 4, 36, 37, 30]. As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and helps suppress the anomaly [16]. Explanation in [16] seems to be more reasonable. Our observation in our 1D shock tube tests shows that even though both RSPH and GSPH adopt EoM proposed in [15], the pressure wiggle still get suppressed. So obviously, EoM might not be the real cause of pressure wiggle.

The present method has many common things with GSPH. Particularly, both are based on solving local Riemann problems. Based on our observation that both GSPH and RSPH could suppress pressure wiggle in contact discontinuity. We tend to believe that the mechanism for present method to suppress pressure wiggle lies on the basis of present method: solving local Riemann problems. 
The capability of suppression pressure wiggle in contact discontinuity is indeed one attractive feature of present method.

As for why RSPH can better suppress pressure wiggles. It is not clear in theory. We observed that RSPH is more adaptive than GSPH in terms of introducing artificial viscosity. Probably, better suppression of pressure wiggles is also because RSPH is more adaptive in terms of introducing implicit thermal conduction (if Price is correct). 
\\[12pt]

\textbf{\Large Reviewer \# 2}\\[3pt]

\textbf{\large General Comments}

\textit{Summary: The authors propose a novel variant of a Riemann-solver based SPH scheme. The proposed scheme may well be viable and valuable/useful, but this is not sufficiently evident. The manuscript suffers from many confusing/lacking explanations and should be
substantially improved before seriously considered for publication in JCP.}

\textit{General Critique:
It remains unclear why RSPH performs better than GSPH, i.e. why the random choice of <epsilon> makes such a difference. It also remains unclear how well RSPH performs in critical multi-dimensional flows. In other words: the manuscript provides some suggestion that RSPH may a be a valuable scheme, but fails to explain why and to demonstrate that this is indeed the case for most flows.}

We appreciate the reviewer for reviewing our manuscript and giving constructive remarks. 
%We understand that the reviewer has solid background in SPH but relatively less background in mesh based CFD (computational fluid dynamics) methods. Some questions/confusion are general question for mesh based CFD. We will try to give detailed response. But we might not include these details in our revised manuscript to avoid being too disruptive.

Our response to reviewer's general critique is following.

Both random choice method (RCM) and Godunov's method have been proposed long time ago in the context of mesh based method. Both have been well studied in both theoretical side and application side. One advantage of RCM compared against Godunov's method is that RCM is able to introduce much less smearing at discontinuities. Such advantage is well known in the context of \textbf{mesh based method}.
The essential idea of GSPH, whose full name is Godunov SPH, is to implement Godunov's idea in the context of mesh free methods. The essential idea of RSPH, is to implement the idea of ``random choice" in the context of mesh free methods. Why random choice method would introduce much less smear has been well studied and demonstrated by many applications. It is not possible to cover such topics in detail this article.
Considering the fact that some readers might not be familiar with random choice method. We added an appendix introduce RCM method with more references.

The attractive features of RSPH actually have been demonstrated in 1D tests. However, some points are not clearly delivered. We will address these points in the revised manuscript.

As for 3D test case, the effective overall-dissipation is measured indirectly by the length that the 3D jet flow reaches in given time. We can still conclude that the effective overall-dissipation introduced by RSPH is smaller than that of GSPH. More work would be necessary to explore its implementation in 3D. Adopting different test cases might reveal more features of RSPH in different scenarios. But implementing RSPH in different scenarios are not major consideration of this article.
\\[12pt]
%We also want to mention that, for higher dimensional implementation of RSPH and GSPH, how to approximate the velocity component that perpendicular to the local coordinate system is still not well understood. For example, there are two different approaches adopted by GSPH (see [13], [16], [17]). However, neither of them seems to be sufficient. This is a common topic for both GSPH and RSPH, not only for RSPH. In our implementation, we adopt the method used by [13] and [16].

\textbf{\large Specific comments}

\textit{p.2 The authors seem to misunderstand the purpose of artificial viscosity (AV) when they say it is "to overcome numerical oscillations at
discontinuities". SPH relies on representing all fields as SMOOTH and the purpose of AV is to ensure that this also holds for the flow velocity.
More generally, artificial dissipation is required to smooth any advected field (temperature, magnetic fields etc).}

Thanks for pointing this out. Our research focus more on high speed compressible flow and we were not able aware of the purpose of AV in a more general sense. For implementations of SPH in high speed compressible flow, the oscillation around discontinuities, especially aroud shocks can be too large or even corrupt whole simulation. In that sense, AV helps to reduce oscillation at discontinuities. So our statement is not as general as it should be, but still make sense in certain application area.
\\[3pt]

\textit{p.2 The adverse effects of AV in original SPH are misrepresented: artificial viscosity is not related to the failure to resolve contact discontinuities (which is caused by inconsistent smoothing, i.e. the pressure 'wiggle' in Fig 3, see also the review by Price 2012).}

We miss the reviewer's opinion here.
Do you mean: 
1) AV is not related to ``pressure wiggle" around contact discontinuity

OR

2) AV is related to failure to resolve discontinuities (note, include but not limited to contact discontinuities)?

If what you mean is 1). our response is:

We never say ``pressure wiggle" is due to AV. Instead, we prefer to agreeing with Price's view with respect to the source of ``pressure wiggle". As we mentioned in our response to another reviewer, thermal conduction can help mitigate ``pressure wiggle". The mechanism why RSPH can help mitigate ``pressure wiggle" is that RSPH, by solving local Riemann problems, introduces implicit thermal conduction. GSPH has been reported to mitigate ``pressure wiggle" in a similar mechanism [16]. We also want to mention that some other researchers have different view with respect to the source of ``pressure wiggle", see e.g. [13].

If what you mean is 2), our response is:

We do believe AV causes some issues when resolve discontinuities (not only contact discontinuities). That is, AV usually smears (or smooth out) discontinuities. Mathematically, discontinuity should be zero width, however, numerically, discontinuity would have width. Too large AV usually leads to larger width of discontinuities in numerical simulation. For example, in subplot c) of Fig. 3. larger AV (with $\alpha = 2$, the red dash line) lead to a wider approximation of the shock (which is discontinuity in theory) than smaller AV (with $\alpha = 1$, the purple line). 
Such wider approximation of discontinuity should not be considered as \textbf{failure} to resolve discontinuities. Instead, we prefer to calling wider approximation of discontinuity as \textbf{"not accurate enough or less accurate"}. One core merit of RSPH is to keep numerical approximation of discontinuities to be narrower by introducing numerical dissipation adaptively.
\\[3pt]

\textit{p.1/2 The "highly tuned versions of artificial viscosity" mentioned by the authors are in reality methods to adapt AV to flow regions where it is needed. These methods are by now widely used (in SPH models of compressive flows) and are therefore part of any modern implementation.
The authors fail to provide evidence for their bold claim that (the most advanced of) these methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist" BECAUSE of AV (I agree that modern SPH still has issues, but AV is not their prime cause)..}

Response to reviewer's comments regarding AV.

We agree that AV might not be the biggest barrier that prevents SPH to be a real CFD tool as there are some other more serious challenges. However, AV is definitely an important aspect of CFD, especially for high speed compressible flow. It is more than necessary to borrow well developed ideas from mesh based method to SPH.
More importantly, both RCM and Godnuov's idea take the hyperbolicity of the system into account. The advantages of such treatment are not only introduce implicit (and adaptive) AV. Both GSPH and RSPH could also better suppress ``pressure wiggle" around contact discontinuity. The under underneath mechanism also relies on properly considering of system's hyperbolicity.

Response to reviewer's requests that we need to provide evidence for their bold claim that (the most advanced of) these methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist"

These "highly tuned versions of artificial viscosity", as far as our understanding, none of them take the hyperbolicity of the system into account. How could these methods properly accommodate every kind waves without considering the property of system? Our claim is not bold at all.

The reviewer mentioned ``These methods are by now widely used in SPH models of compressive flows". With respect to these implementations, we are wondering what is the fluid speed? How accurate are they? Which physical quantities are of interest in these implementations (smearing of discontinuities might be acceptable for some implementations as there is not demands for resolving discontinuities as true discontinuities)?
We did not check all of these "highly tuned versions of artificial viscosity" in depth. But we did check the ADKE method carefully. It turned out that we have to tune its parameters manually even for different 1D tests. Some other researchers also reported the same thing, for example [12]. 
\\[3pt]

\textit{p1/2 The motivation of the new scheme via partially unjustified critique of artificial viscosity) is unnecessary and divisive. A much
better/correct motivation of RSPH would be as an improvement over standard GSPH.}

One of our original motivation indeed is to develop a method that can apply AV in a more ``smart" way. Even though the method turned out to have other attractive features.
The current way to add artificial viscosity does have some limitation and can be improved even though they work well in some implementations.
Compared with GSPH, RSPH do have some advantages while it also has some disadvantages. The major disadvantage is that RSPH can only be 1st order of accuracy.
We do not view RSPH as an improved version of GSPH, instead they should be two parallel methods. Because historically, RCM and Godunov's methods were developed (within the area of mesh based methods) parallely even though they share many common places.
\\[3pt]

\textit{p.3 The authors propose a variant of Godunov SPH. Owing to the irregular distribution of particles, such methods can only every be first-order accurate in h (Riemann-solver-based grid methods achieve second-order accuracy only because of the regular grid structure). This should be discussed.}

We prefer to viewing RSPH as counterpart of RCM in SPH while viewing GSPH as counterpart of Godunov's method in SPH. 
RSPH can only be first order even with regular particle distribution because the local Riemann problem is defined in a piece-wise constant manner. Not because the irregular distribution of particles. GSPH, would also be first order accuracy if its local Riemann problems are also defined in a piece-wise constant manner. However, GSPH could be second order of accuracy with regular particle distribution \textbf{and} ``piece-wise linear" construction of its local Riemann problem. However, GSPH would be between first order of accuracy its local Riemann problem is defined in a piece-wise linear manner \textbf{but} the particle distribution is irregular.
We added these discussions in revised paper.
\\[3pt]

\textit{p.3 Of course, in 1D, hydrodynamics is trivial, SPH has few problems, and
GSPH is 2nd order accurate. Really challenging problems only appear for multi-dimensional flows. Note that this does not imply that 1D test
problems are not useful, but these must be embedded in a multi-dimensional context, e.g. with periodic boundaries in the extra dimensions and with glass-like initial particle distributions, to really
demonstrate the validity of a method and compare with others..}

Surely higher dimensional problem are more challenging and make more sense in real applications. 
But 1D tests do have several great merits. 1) As relatively simpler tests, 1D tests are more easily to be well controlled. 2) 1D tests provide a solid basis for exploring basic property of a new method.

What's more, even though trivial, there is still space for improvement for 1D tests. Many variants of SPH scheme can capture the position of different waves while most of them suffer from some common issues such as smearing of discontinuities, pressure wiggles around contact discontinuity, over shoot near other discontinuities. There is no variants of SPH method can perfectly handle all these issue.

We want to mention that, these aspects might not be that important in some implementations. For example, smearing of discontinuity might not be an issue in case that the smoothed flow field is of more interested. But this does not mean that smearing of discontinuity is not important at all in any implementation.
\\[3pt]

\textit{p.6 The choice of the smoothing kernel is critical in SPH and the truncated Gaussian (eq 19) cannot be recommended. The authors should instead use the commonly used Wendland kernel (note, however that that has a different functional form for 1D and 2,3D). The problem with the truncated Gaussian (as presented in eq 19) is that it's neither continuous (at the outer boundary) nor normalized to unit integral. (Another problem is that it's computationally inefficient.)}

Thanks for pointing this out. We tried these two, For 1D tests case, it does not make visible difference. But for 3D, it did make some visible difference but did not change our conclusion. 
\\[3pt]

\textit{p.7 The choice of time integrator is also critical in SPH. Classical SPH is fully conservative and mass, momentum (linear and angular), energy, entropy are all conserved *exactly* modulo AV and time integration errors. It is therefore expedient to use a time integration scheme which does not introduce its own artificial dissipation, in particular NOT the forward Euler scheme.}

Yes, for real implementation, higher order time integrator is necessary. For this paper, first order scheme should be acceptable. Please be notified that all of our test cases adopting the same time integration scheme, in that sense, our comparison are still ``well controlled". RSPH can be combined with higher order time integration scheme. 
\\[3pt]

\textit{p.7 In eqs (21,22) <rho>(x) is not the true fluid density, but only the SPH density estimate. These two are different fields and must be carefully distinguished to avoid confusion and incorrect conclusions.}

We modified the symbol in revised version.
\\[3pt]

\textit{p.8,l.83 "Of course solving the local Riemann problem for every pair of interacting particles is a computationally intensive process." This should be qualified, in particular as an exact solution is overkill.}

Iterative Riemann solvers and non-iterative Riemann solvers have been well studied. There are many papers \citep[][e.g.]{roe1981approximate} and books \citep[][e.g.]{toro2013riemann} on this topic, really not necessary to cover any detail in this article.
\\[3pt]

\textit{p.8 The acronym "HLLC" should be qualified prior to first usage.}

Thanks, we have added the full phrase of HLLC in revised manuscripts.
\\[3pt]

\textit{p.9 The choice of a random final midpoint <epsilon> appears absurd. This must be better motivated/explained. I think this point sits at the very heart of the paper: why should using a random <epsilon> (instead of <epsilon>=0) improve the method?
Also, what is the motivation for the exact midpoint as the initial discontinuity of the Riemann problem? What determines which of a pair of particles is L and which R? Is this random? What motivates using the same value of <epsilon> for all particle pairs? Doesn't this defy the purpose of randomization? and introduce artificial correlations?}

The choice of a random final midpoint <epsilon> does sit at the very heart of the paper. We added an appendix to cover more details with respect to RCM method. Reviewer's questions, such as why using a random <epsilon>, why such random <epsilon> help introduce much less smearing of the discontinuities, what motivates using the same value of <epsilon> for all particle pairs, Doesn't this defy the purpose of randomization and introduce artificial correlations? had been asked and answered in the context of mesh based method. RSPH is the counterpart of RCM (which was previously proposed in mesh based method) in SPH. Discussions on these topics can be found in these papers.

With respect to other questions, our answers are as following: 
\textit{Also, what is the motivation for the exact midpoint as the initial discontinuity of the Riemann problem?}
Good question. We do not have to use the exact middle point. Different way of determining the initial discontinuity would results to different variants of RSPH. Maybe determining initial discontinuity based on particle mass. The property of these variants of RSPH is yet to explore.

\textit{ What determines which of a pair of particles is L and which R? Is this random? }
L and R is determined according to the local coordinate system. For example, if we define the positive direction as from particle a to particle b, then a should be L and b should R. Whether positive direction of local coordinate system is from a to b or from b to a will NOT change the results as long as all the steps (projection from global to local, constructing of local Riemann problem and projection back from local to global) are using consistent local coordinate system (positive direction).
\\[3pt]

\textit{p.10 Fig.10 is confusing (it uses ``q" as coordinate, yet the caption(text) mentions ``x"; it uses an undefined ``w"; it uses sub-scripts ``L" and ``R", yet the caption talks about ``a" and `` b" states; the meaning of the lines ``$S_L$" , ``$S_M$", and ``$S_R$" is not explained)}

Thanks, we cleaned up these confusing points in revised manuscript.
\\[3pt]

\textit{p.10 The remark about the Van Der Corput pseudo-random number sequence is confusing/wrong. AFAIK, these are not pseudo-random, but QUASI-random. This seems to contradict the idea of using a random value. So why should this work?
What happens if instead pseudo-random numbers are used and/or if a different <epsilon> is drawn for every interacting particle pair?}

The idea of using Van Der Corput pseudo-random number sequence is borrowed from RCM. The reviewer is right that Van Der Corput pseudo-random number sequence not pseudo-random, but QUASI-random. But traditionally, it was called pseudo-random \citep[][e.g.]{toro2013riemann}. Should we follow the tradition of RCM or using more correct phrase?

The idea of using a different <epsilon> for every interacting particle pair was actually another variants of RCM. These two different manners turned out to have similar properties. 
\\[3pt]

\textit{p.11/12 The summary of the 1D test cases is somewhat confusing. The initial conditions are not best explained in Table 1: where is the boundary? What is the physical meaning of negative-pressure ideal gas? (Standard SPH is unstable to clumping in the presence of negative pressure.)
These tests do not provide a good testsuite. Most operate at similar Mach numbers, albeit with different arrangements/initial conditions. It would
be desirable to test discontinuous initial conditions with a wider range of Mach numbers, from 0.1 to 100. The Mach number should be given in Table 1.}

The boundary is given in table by $[x_L, x_R]$.

There is a typo for test4 and test5 in that table, we incorrectly put value for velocity under pressure column, that's why you see negative pressure. We have changed it in revised manuscript.

The tests case adopted here are actually very representive to test \textbf{different wave patterns}. These 1D tests are all well known 1D tests used by both mesh based method \citep[][e.g.]{toro2013riemann, leveque2002finite} and SPH tests \citep[][e.g.]{monaghan1983shock, cha2003implementations, puri2014approximate}. 
Mach number can be easily calculated according to physical quantities. We added Mach number in Table 1 in revised manuscript. 
\\[3pt]

\textit{Figs 2,3 Are these really "oscillations around shock" for <alpha>=0.2 SPH? I suspect that instead we have inter-particle penetration, i.e.
particles swapping positions in 1D SPH. Also, in this figure, isn't the interpretation of oscillation==less viscosity rather simplistic? In a conservative scheme, the amount of dissipative heating can in principle be directly measured and used as a measure of viscosity (better than merely pointing at the oscillations).
I think it'd be better to combine Figs 2\& 3 into one, similar to Fig 4. Only one legend is required, not 8. Moreover, the details may be shown as inlet plots.}

They are really oscillations. Such oscillations are caused by non-uniform smoothing length (due to uniform particle mass and nonuniform density in space). We added an appendix to explain the source of such oscillation in the revised manuscript.

\textit{the amount of dissipative heating can in principle be directly measured and used as a measure of viscosity (better than merely pointing at the oscillations).}

Using internal energy? We are a bit confused on how to measure the dissipative heating. The correlation between oscillation can be demonstrated by these tests with different artificial viscosity coefficients.

We tried to combine 2\&3 and 4\&5. But it would be too large to fit into one page. Inlet plots make it harder to see these details we want to show.

We made modification as suggested by reviewer regarding legend.
\\[3pt]

\textit{p.13-15 I think comparing against <alpha>=2 or 0.2 SPH has little merit.
A comparison to <alpha>=1 SPH makes sense as does a comparison (lacking)
against an AV-switch version of SPH.}

Both <alpha>=2 and 0.2 are necessary. Comparison of three different values confirms the effect AV, which is the basis of for our further discussion. If we only have two different artificial viscosity coefficients sets, some other readers might argue that our comparison is not generic enough.

The AV-switch versions of SPH, which introduce AV in an explicit way, usually have parameters that can be manually tuned while RSPH and GSPH introduce AV in an implicit way and have no manually-tunable parameters. 
We actually tried to compare against one AV-switch version of SPH. But it turned out that we have to manually tune its parameters for each test case. This can easily lead to ``unfair" comparison. In addition, the major difference between RSPH and AV-switch version of SPH is so obvious -- RSPH does not require explicit AV.
\\[3pt]

\textit{p14,15 The features of RSPH discussed here (adaptive viscosity) are the
natural consequence of the Riemann solver, i.e. of Godunov SPH. Nothing
is new here.}

Yes, these features of RSPH are due to Riemann solver. 
But Godunov's method is different from RCM.
They do share some common places but surely are different. If they are the same (or nothing new), how could RSPH introduce AV in a more adaptive manner as shown by these tests.

RSPH samples solution of local Riemann problem in a very different way from GSPH. This is NOT a small difference.
\\[3pt]

\textit{Fig 4 The two versions of GSPH have very similar symbols/colors and can hardly be distinguished.}

Changed in revised manuscript. 
\\[3pt]

\textit{p.16 What is the difference between the RSPH and GSPH-HLLC schemes? Is it
merely the choice of <epsilon>? I.e. is GSPH-HLLC == RSPH with <epsilon>=0? If not, what else is different? This is important, as one would like to understand what drives the differences between the results obtained by these to schemes (mostly near
the onset of the rarefaction region in Fig 4 where RSPH shows a wave while GSPH over-smoothes the rarefaction, but also the energy wiggle at
the contact discontinuity). As it is, this difference remains mysterious and unexplained.}

Yes, choice of <epsilon> is the only difference between \textbf{first order} GSPH-HLLC (GSPH can be second order). That is to say, \textbf{first order} GSPH-HLLC == RSPH with <epsilon>=0.
But this is NOT a small difference.
By the way, since choice of <epsilon> is the only difference, our tests are ``well controlled" comparison, that is to say, the difference in tests results do reflect the essential effect of different choice of <epsilon>. We hope reviewer can appreciate such manner of comparisons.

Why choice of <epsilon> can make such big difference? This is the heart of RCM.
\\[3pt]

\textit{pp. What causes the waves (in RSPH) and what is their wavelength? Perhaps
these waves are related to the correlations introduced by using the same
<epsilon> for all particle pairs (when their wavelength may be comparable
to / scale with h).}

Good question. We added an appendix to explain the source of these waves.
\\[3pt]

\textit{p.17 While simple 1D shock-tube problems are good tests for proof-of-concept implementations, they are not representative of
multi-dimensional flows and cannot be used to reliably validate any scheme. Thus, most tests in §4.2 are meaningless to that end.
A good test (where SPH performs poorly regardless of AV) is the Gresho-Chan vortex test (2D) run over at least one rotation period.}

We do agree that there are additional challenges for multi-dimensional implementations. But we would argue that 1D tests are must for any new method. These ``well controlled" tests could demonstrate the feature of the new method in a more explicit way. In addition, performing well in 1D tests are prerequirement for be doing well in higher dimensional implementations. We observe that many numerical schemes were throughly discussed in 1D and then implemented in 3D.
\\[3pt]

\textit{p.21 The free jet flow is an interesting problem but hardly suitable as a
test here, since there exists no undisputed correct solution (for a converging scheme, such a solution could be obtained by increasing resolution, but this has not been done).}

In terms of demonstrating basic features of RSPH, 1D tests can do a much better job as all factors are well controlled. 
As for 3D jet flow, yes, increasing resolution could help to get better results. But purely increasing resolution might no be enough. See more discussion based on a similar tests by \citet{cha2010kelvin}. 
In addition, different variant versions of RSPH might perform better in different implementations. However, this is not the major topic of this article.
\\[3pt]

\textit{Figs 11 \& 12 lack information which plot is for which scheme. Something is wrong in Fig.12: there are 2 rows of 2 plots each, yet the caption
talks about 2 rows of 3 plots each.}

Thanks, we modified this section to clean up confusions.
\\[3pt]
\bibliographystyle{plainnat}
\bibliography{Reference}
\end{document}

### 2018-11-24 Summary-of-changes.tex
update

\documentclass[10pt,a4paper]{article}
%\documentclass[10pt,a4paper]{beamer}
%\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{kpfonts}
\usepackage[numbers]{natbib}
%other options include: round, curly, angle, or default options

\usepackage{media9}
\usepackage{color}
\begin{document}
\author{\Large {Zhixuan Cao, Abani Patra, E. Bruce Pitman}}

\title{
\LARGE \textbf{Summary of modifications} \\
\Large \textbf{``A Random Choice SPH Scheme with Adaptive Viscosity"}}

\date{\vspace{-5ex}}

\maketitle
The comments by the reviewers are recited in italics, followed by our reply in upright font. Revisions are highlighted with blue. Equation, section, figure and reference numbers in our response are corresponding to these in the original 
version of JCP manuscript if not specified. \\[12pt]

\textbf{\Large Reviewer \# 1}\\[3pt]

\textbf{\large General Comments}

\textit{This article describes an effort to combine the previous development of SPH technique with "Random Choice Method (RCM)", a classical approach developed in the framework of grid-based method for
describing fluid flows. The authors compare their method with standard SPH method and the first order GSPH, and show some interesting results and may provide useful information for the community of SPH developers. Therefore the reviewer would recommend its publication after the authors sufficiently react to some concerns described below.}

We would like to thank the reviewer for carefully reading our manuscript and giving positive review and critical remarks.
We have revised the manuscript as described in the separate documentation and we hope that we have dealt with all suggestions in an adequate manner. The revised manuscript is also attached.

On behalf of all co-authors.

The following are our responses to reviewer's specific comments.\\[12pt]

\textbf{\large Specific comments}

\textit{The reviewer thinks that this kind of article should provide a new and useful method with respect to the previously known method. The usefulness may include (but not be restricted to) either higher accuracy, fast computation, implementation easiness, or versatility for the extension to include complex physics. According to the simulation examples shown in this article, the reviewer does not find the present method is more accurate than the second-order GSPH. (Note that it is not much more complicated than the first order GSPH. Instead, the reviewer thinks that the present method is (at least slightly) faster than those methods, and can be categorized in "faster methods" with approximate Riemann Solvers that includes development by Puri et al. With this respect, the reviewer thinks that comparison with the method of Puri et al. should be shown and explained in more detail. Note that the reviewer has no doubt in the
possibility of the present method for further development.}

To response reviewer's recommendation for comparing 1D tests in present article with these 1D tests by \citet{puri2014approximate}:

First of all, the present method simply adopts HLLC and Roe approximate Riemann solvers presented in \citep{puri2014approximate}. We did not make any improvement in term of approximate Riemann solvers. In that sense, these GSPH results in our paper should be kind of repeat of these tests in \citep{puri2014approximate}. Or in other words, we have already done such comparison in current paper.
But we need to mention two sources of differences. First of all, we adopted first order GSPH while tests in \citep{puri2014approximate} using second order GSPH. The reason why we use first order GSPH instead of second order GSPH is that we want to do ``well controlled" comparison. So that we can show the pure effect of ``random choice". Secondly, the shock tube tests adopted in our manuscript are very similar to these presented in \citep{puri2014approximate}, however, they are not exactly the same. We intentionally assign different particle mass to particles at left side and right side. The reason for different particle mass is explained in detail in appendix B of the revised manuscript.

In response to reviewer's comments regarding the usefulness 
The motivation and innovative point of the present method is to introduce numerical dissipation in a more adaptive manner, hence introduce less smearing around discontinuities. In that sense, the present work can be considered as ``higher numerical accurate", even though it is NOT ``higher order of accuracy". Another feature that made present method to be ``higher accurate" is its capability to better suppressing pressure wiggle at contact discontinuity. Both features have been demonstrated in 1D tests. Such improvements can be considered as "more accurate".

Thanks for helping us find another merit. Compared with second order GSPH, the present method would be, at least slightly, faster on expense of lower order accuracy. \\[3pt] 
%Compared with first order GSPH, it will not be faster. So the computational  speed would be a normal feature of present method instead of an attractive feature. 
%By adopting approximate Riemann solver, the present work would be computationally faster than RCM methods using iterative Riemann solver. If all previous RCM method is using iterative Riemann solver, then we may claim that it is the first time to combine RCM with non-iterative Riemann solver. And this would be another innovative point of our paper.

\textit{Since the random choice method (RCM) was introduced by Glimm in 1965 and seems to be discussed mainly around 1980, it is better to explain this method in more detail, especially why this method is expected to give a good result. Without such explanation the readers cannot understand why the present method may give better result than the other methods.}

We agree with reviewer. We added an appendix to introduce RCM with a little bit more details. More references are also provided there.\\[3pt]

\textit{Regrettably, Figure 4, 7, and 8 show relatively large oscillation in the
numerical results. Can you explain why this occurs? Is there any prescription to remove this?}

The large oscillations in these 1D shock tube tests actually are very critical in demonstrating the merit of present method. Unfortunately the original manuscript did not delivery this point clearly. The shock tube tests were intentionally designed to make such oscillation more obvious by assigning different particles masses. In all shock tube tests presented in previous work, uniform particle mass is adopted while in our manuscript, different particle mass are assigned for particles on right side and left side. Different particle mass will amplify the oscillation and help to demonstrate the merit of present method in a more obvious manner. In revised manuscript, we addressed these points. We also added an appendix explaining the source of such oscillations.
\\[3pt]
%need to show that equal particle mass can help reduce oscillation.

\textit{Section 4.4 is the most problematic. First of all, Figure 12 seems to be missing two additional figures, since the caption seems to describe three figures in each low. In general the reader cannot evaluate which method is superior to the others (only) by looking at these figures. The authors should improve the way to present the results.}

In section 4.4, we first simulate the free jet flow using classical SPH based on different artificial viscosity coefficients. The results show that larger artificial viscosity coefficients can lead to shorter length of jet. Considering that larger artificial viscosity coefficients introduces more equivalent overall-dissipation. We reach to the conclusion that we can use the length of jet as a indirect indicator of equivalent overall-dissipation. 
Then we compared the length of jet simulated by GSPH and RSPH. As the length of GSPH is shorter, we inferred that RSPH introduces less equivalent overall-dissipation.
We modified the manuscript to delivery these points more clearly.

Figure for SPH results were removed while we forgot to update the caption, which makes Figure 12 to be confusing. That makes reader confusing. We revised the caption in our revised manuscript.

We want to mention here that in both GSPH and the present method, the way to handle velocity that perpendicular to local coordinate system need to be improved. There are (at least) two different ways to handle the perpendicular velocity component. See [13] and [15]. We are adopting [13]'s method in this article. 
\\[3pt]

\textit{Note that the original GSPH paper [13] describes not only the first order method but also the second order method (and it effectively recommends the use of second order method). The authors seem to be missing these points. It is evident from the description in the following phrase: "Cha[14] proposed a second order accurate GSPH method by using a piecewise linear interpolation of the states." in Page 9 and "We observe a rate of convergence of approximately 1 for GSPH" in Page 17. These descriptions mislead the readers.}

The reviewer actually asked two questions here. 
With respect to the first question, yes, in our manuscript, we only compared RSPH with first order GSPH while GSPH could be second order as mentioned by the reviewer. The reason why we only compare our method with first order GSPH is that our method can only be first order. To make the comparison to be ``well controlled", we compared first order RSPH against first order GSPH. As reviewer has notified, RSPH and GSPH have many things in common: both need projecting quantities from global coordinate system to a local coordinate system, both need constructing local Riemann problem and solve the local Riemann problem, both need to project solution of the local Riemann solution back to global. In our ``well controlled" comparison, the only difference between RSPH and GSPH tests is the way to sample solution of local Riemann problems. This difference is actually also the essential difference between Godunov's method and random choice method in the context of mesh based method. With such ``well controlled" comparison, we can clearly show the effects purely due to the essential differences between RSPH and GSPH. We have to mention that such ``first order" limitation is inherited from RCM. Namely, RCM (which were proposed in mesh based methods) adopts a ``piece wise constant" way when constructing Riemann problems. This should be a disadvantage of RSPH compared with second order GSPH.

With respect to the second question, yes, that statement would indeed cause confusions to readers. We added more explicit explanation in revised manuscript.
\\[3pt]

\textit {It is well known that the wiggle in the pressure at the contact discontinuity is due to the inconsistency of the standard SPH in evaluating pressure gradient force with a non-smooth distribution of particles. This problem is (at least partially) solved in GSPH [13, 17]. Note that the article [15] did not care this problem. Since the present article used the method shown in [15], the reviewer does not expect a good result at contact discontinuity. If the authors have some reason why the method that includes RCM can accurately describe the contact discontinuity, they should explain it within this article. The reviewer
presumes that it can be a desirable feature in the present method if it is true.}

[13] indeed shown that GSPH can almost get rid of pressure wiggle around contact discontinuity while standard SPH shows much more obvious pressure wiggle. They believe that the pressure wiggle is due to the inconsistency of EoM (equation of momentum) of the standard SPH. Or in other words, just as what the reviewer mentioned: "The wiggle in the pressure at the contact discontinuity is due to the inconsistency of the standard SPH in evaluating pressure gradient force with a non-smooth distribution of particles." However, there are different opinions with respect to the sources of pressure wiggle. For example, other researchers believe that the pressure wiggle has something to do with thermal conduction at the contact discontinuity. It has been shown that thermal conduction is essential to mitigate the spurious pressure wiggle at contact discontinuity in SPH [e.g. 4, 36, 37, 30]. As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and helps suppress the anomaly [16]. Explanation in [16] seems to be more reasonable. Our observation in our 1D shock tube tests shows that even though both RSPH and GSPH adopt EoM proposed in [15], the pressure wiggle still get suppressed. So obviously, EoM might not be the real cause of pressure wiggle.

The present method has many common things with GSPH. Particularly, both are based on solving local Riemann problems. Based on our observation that both GSPH and RSPH could suppress pressure wiggle in contact discontinuity. We tend to believe that the mechanism for present method to suppress pressure wiggle lies on the basis of present method: solving local Riemann problems. 
The capability of suppression pressure wiggle in contact discontinuity is indeed one attractive feature of present method.

As for why RSPH can better suppress pressure wiggles. It is not clear. We observed that RSPH is more adaptive than GSPH in terms of introducing artificial viscosity. Probably, better suppression of pressure wiggles is also because RSPH is more adaptive. 
\\[12pt]

\textbf{\Large Reviewer \# 2}\\[3pt]

\textbf{\large General Comments}

\textit{Summary: The authors propose a novel variant of a Riemann-solver based SPH scheme. The proposed scheme may well be viable and valuable/useful, but this is not sufficiently evident. The manuscript suffers from many confusing/lacking explanations and should be
substantially improved before seriously considered for publication in JCP.}

\textit{General Critique:
It remains unclear why RSPH performs better than GSPH, i.e. why the random choice of <epsilon> makes such a difference. It also remains unclear how well RSPH performs in critical multi-dimensional flows. In other words: the manuscript provides some suggestion that RSPH may a be a valuable scheme, but fails to explain why and to demonstrate that this is indeed the case for most flows.}

We appreciate the reviewer for reviewing our manuscript and giving constructive remarks. We understand that the reviewer has solid background in SPH but relatively less background in mesh based CFD (computational fluid dynamics) methods. Some questions/confusion are general question for mesh based CFD. We will try to give detailed response. But we might not include these details in our revised manuscript to avoid being too disruptive.

Our response to reviewer's general critique is following.

Both random choice method (RCM) and Godunov's method have been proposed long time ago in the context of mesh based method. Both have been well studied in both theoretical side and application side. One advantage of RCM compared against Godunov's method is that RCM is able to introduce much less smearing at discontinuities. Such advantage is well known in the context of mesh based method.
The essential idea of GSPH, whose full name is Godunov SPH, is to implement Godunov's idea in the context of mesh free methods. The essential idea of RSPH, is to implement the idea of ``random choice" in the context of mesh free methods. Why random choice method would introduce much less smear has been well studied and demonstrated by many applications. It is not possible to cover all such topics in this article.
Considering the fact that some readers might not be familiar with random choice method. We added an appendix introduce RCM method with more references.

The attractive features of RSPH actually have been well demonstrated in 1D tests. However, some points are not clearly delivered. We will address these points in the revised manuscript.

As for 3D test case, it is hard to demonstrate the attractive feature of RSPH in a ``well controlled" manner. Indeed, in section 4.4, RSPH did not show very obvious advantage over GSPH. But we can still observe that the effective overall-dissipation introduced by RSPH is smaller than that of GSPH.

We also want to mention that, for higher dimensional implementation of RSPH and GSPH, how to approximate the velocity component that perpendicular to the local coordinate system is still not well understood. For example, there are two different approaches adopted by GSPH (see [13], [16], [17]). However, neither of them seems to be sufficient. This is a common topic for both GSPH and RSPH, not only for RSPH. In our implementation, we adopt the method used by [13] and [16]. 
\\[12pt]

\textbf{\large Specific comments}

\textit{p.2 The authors seem to misunderstand the purpose of artificial viscosity (AV) when they say it is "to overcome numerical oscillations at
discontinuities". SPH relies on representing all fields as SMOOTH and the purpose of AV is to ensure that this also holds for the flow velocity.
More generally, artificial dissipation is required to smooth any advected field (temperature, magnetic fields etc).}

Thanks for pointing this out. Our research focus more on high speed compressible flow and we were not able aware of the purpose of AV in a more general sense. For implementations of SPH in high speed compressible flow, the oscillation around discontinuities, especially aroud shocks can be too large or even corrupt whole simulation. In that sense, AV helps to reduce oscillation at discontinuities. So our statement is not as general as it should be, but still make sense in certain application area.
\\[3pt]

\textit{p.2 The adverse effects of AV in original SPH are misrepresented: artificial viscosity is not related to the failure to resolve contact discontinuities (which is caused by inconsistent smoothing, i.e. the pressure 'wiggle' in Fig 3, see also the review by Price 2012).}

We miss the reviewer's opinion here.
Do you mean: 
1) AV is not related to ``pressure wiggle" around contact discontinuity

OR

2) AV is related to failure to resolve discontinuities (note, include but not limited to contact discontinuities)?

If what you mean is 1). our response is:

We never say ``pressure wiggle" is due to AV. Instead, we prefer to agreeing with Price's view with respect to the source of ``pressure wiggle". As we mentioned in our response to another reviewer, thermal conduction can help mitigate ``pressure wiggle". The mechanism why RSPH can help mitigate ``pressure wiggle" is that RSPH, by solving local Riemann problems, introduces implicit thermal conduction. GSPH has been reported to mitigate ``pressure wiggle" in a similar mechanism [16]. We also want to mention that some other researchers have different view with respect to the source of ``pressure wiggle", see e.g. [13].

If what you mean is 2), our response is:

We do believe AV causes some issues when resolve discontinuities (not only contact discontinuities). That is, AV usually smears (or smooth out) discontinuities. Mathematically, discontinuity should be zero width, however, numerically, discontinuity would have width. Too large AV usually leads to larger width of discontinuities in numerical simulation. For example, in subplot c) of Fig. 3. larger AV (with $\alpha = 2$, the red dash line) lead to a wider approximation of the shock (which is discontinuity in theory) than smaller AV (with $\alpha = 1$, the purple line). 
Such wider approximation of discontinuity should not be considered as \textbf{failure} to resolve discontinuities. Instead, we prefer to calling wider approximation of discontinuity as \textbf{"not accurate enough or less accurate"}. One core merit of RSPH is to keep numerical approximation of discontinuities to be narrower by introducing numerical dissipation adaptively.
\\[3pt]

\textit{p.1/2 The "highly tuned versions of artificial viscosity" mentioned by the authors are in reality methods to adapt AV to flow regions where it is needed. These methods are by now widely used (in SPH models of compressive flows) and are therefore part of any modern implementation.
The authors fail to provide evidence for their bold claim that (the most advanced of) these methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist" BECAUSE of AV (I agree that modern SPH still has issues, but AV is not their prime cause)..}

Response to reviewer's comments regarding AV.

We agree that AV might not be the biggest barrier that prevents SPH to be a real CFD tool as there are some other more serious challenges. However, AV is definitely an important aspect of CFD, especially for high speed compressible flow. It is more than necessary to borrow well developed ideas from mesh based method to SPH.
More importantly, both RCM and Godnuov's idea take the hyperbolicity of the system into account. The advantages of such treatment are not only introduce implicit (and adaptive) AV. Both GSPH and RSPH could also better suppress ``pressure wiggle" around contact discontinuity. The under underneath mechanism also relies on properly considering of system's hyperbolicity.

Response to reviewer's requests that we need to provide evidence for their bold claim that (the most advanced of) these methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist"

These "highly tuned versions of artificial viscosity", as far as our understanding, none of them take the hyperbolicity of the system into account. How could these methods properly accommodate every kind waves without considering the property of system? Our claim is not bold at all.

The reviewer mentioned ``These methods are by now widely used in SPH models of compressive flows". With respect to these implementations, we are wondering what is the fluid speed? How accurate are they? Which physical quantities are of interest in these implementations (smearing of discontinuities might be acceptable for some implementations as there is not demands for resolving discontinuities as true discontinuities)?
We did not check all of these "highly tuned versions of artificial viscosity" in depth. But we did check the ADKE method carefully. It turned out that we have to tune its parameters manually even for different 1D tests. Some other researchers also reported the same thing, for example [12]. 
\\[3pt]

\textit{p1/2 The motivation of the new scheme via partially unjustified critique of artificial viscosity) is unnecessary and divisive. A much
better/correct motivation of RSPH would be as an improvement over standard GSPH.}

One of our original motivation indeed is to develop a method that can apply AV in a more ``smart" way. Even though the method turned out to have other attractive features.
The current way to add artificial viscosity does have some limitation and can be improved even though they work well in some implementations.
Compared with GSPH, RSPH do have some advantages while it also has some disadvantages. The major disadvantage is that RSPH can only be 1st order of accuracy.
We do not view RSPH as an improved version of GSPH, instead they should be two parallel methods. Because historically, RCM and Godunov's methods were developed (within the area of mesh based methods) parallely even though they share many common places.
\\[3pt]

\textit{p.3 The authors propose a variant of Godunov SPH. Owing to the irregular distribution of particles, such methods can only every be first-order accurate in h (Riemann-solver-based grid methods achieve second-order accuracy only because of the regular grid structure). This should be discussed.}

We prefer to viewing RSPH as counterpart of RCM in SPH while viewing GSPH as counterpart of Godunov's method in SPH. 
RSPH can only be first order even with regular particle distribution because the local Riemann problem is defined in a piece-wise constant manner. Not because the irregular distribution of particles. GSPH, would also be first order accuracy if its local Riemann problems are also defined in a piece-wise constant manner. However, GSPH could be second order of accuracy with regular particle distribution \textbf{and} ``piece-wise linear" construction of its local Riemann problem. However, GSPH would be between first order of accuracy its local Riemann problem is defined in a piece-wise linear manner \textbf{but} the particle distribution is irregular.
We added these discussions in revised paper.
\\[3pt]

\textit{p.3 Of course, in 1D, hydrodynamics is trivial, SPH has few problems, and
GSPH is 2nd order accurate. Really challenging problems only appear for multi-dimensional flows. Note that this does not imply that 1D test
problems are not useful, but these must be embedded in a multi-dimensional context, e.g. with periodic boundaries in the extra dimensions and with glass-like initial particle distributions, to really
demonstrate the validity of a method and compare with others..}

Surely higher dimensional problem are more challenging and make more sense in real applications. 
But 1D tests do have several great merits. 1) As relatively simpler tests, 1D tests are more easily to be well controlled. 2) 1D tests provide a solid basis for exploring basic property of a new method.

What's more, even though trivial, there is still space for improvement for 1D tests. Many variants of SPH scheme can capture the position of different waves while most of them suffer from some common issues such as smearing of discontinuities, pressure wiggles around contact discontinuity, over shoot near other discontinuities. There is no variants of SPH method can perfectly handle all these issue.

We want to mention that, these aspects might not be that important in some implementations. For example, smearing of discontinuity might not be an issue in case that the smoothed flow field is of more interested. But this does not mean that smearing of discontinuity is not important at all in any implementation.
\\[3pt]

\textit{p.6 The choice of the smoothing kernel is critical in SPH and the truncated Gaussian (eq 19) cannot be recommended. The authors should instead use the commonly used Wendland kernel (note, however that that has a different functional form for 1D and 2,3D). The problem with the truncated Gaussian (as presented in eq 19) is that it's neither continuous (at the outer boundary) nor normalized to unit integral. (Another problem is that it's computationally inefficient.)}

Thanks for pointing this out. We tried these two, For 1D tests case, it does not make visible difference. But for 3D, it did make some visible difference but did not change our conclusion. 
\\[3pt]

\textit{p.7 The choice of time integrator is also critical in SPH. Classical SPH is fully conservative and mass, momentum (linear and angular), energy, entropy are all conserved *exactly* modulo AV and time integration errors. It is therefore expedient to use a time integration scheme which does not introduce its own artificial dissipation, in particular NOT the forward Euler scheme.}

Yes, for real implementation, higher order time integrator is necessary. For this paper, first order scheme should be acceptable. Please be notified that all of our test cases adopting the same time integration scheme, in that sense, our comparison are still ``well controlled". RSPH can be combined with higher order time integration scheme. 
\\[3pt]

\textit{p.7 In eqs (21,22) <rho>(x) is not the true fluid density, but only the SPH density estimate. These two are different fields and must be carefully distinguished to avoid confusion and incorrect conclusions.}

We modified the symbol in revised version.
\\[3pt]

\textit{p.8,l.83 "Of course solving the local Riemann problem for every pair of interacting particles is a computationally intensive process." This should be qualified, in particular as an exact solution is overkill.}

Iterative Riemann solvers and non-iterative Riemann solvers have been well studied. There are many papers \citep[][e.g.]{roe1981approximate} and books \citep[][e.g.]{toro2013riemann} on this topic, really not necessary to cover any detail in this article.
\\[3pt]

\textit{p.8 The acronym "HLLC" should be qualified prior to first usage.}

Thanks, we have added the full phrase of HLLC in revised manuscripts.
\\[3pt]

\textit{p.9 The choice of a random final midpoint <epsilon> appears absurd. This must be better motivated/explained. I think this point sits at the very heart of the paper: why should using a random <epsilon> (instead of <epsilon>=0) improve the method?
Also, what is the motivation for the exact midpoint as the initial discontinuity of the Riemann problem? What determines which of a pair of particles is L and which R? Is this random? What motivates using the same value of <epsilon> for all particle pairs? Doesn't this defy the purpose of randomization? and introduce artificial correlations?}

The choice of a random final midpoint <epsilon> does sit at the very heart of the paper. We added an appendix to cover more details with respect to RCM method. Reviewer's questions, such as why using a random <epsilon>, why such random <epsilon> help introduce much less smearing of the discontinuities, what motivates using the same value of <epsilon> for all particle pairs, Doesn't this defy the purpose of randomization and introduce artificial correlations? had been asked and answered in the context of mesh based method. RSPH is the counterpart of RCM (which was previously proposed in mesh based method) in SPH. Discussions on these topics can be found in these papers.

With respect to other questions, our answers are as following: 
\textit{Also, what is the motivation for the exact midpoint as the initial discontinuity of the Riemann problem?}
Good question. We do not have to use the exact middle point. Different way of determining the initial discontinuity would results to different variants of RSPH. For example, determining initial discontinuity based on particle mass. The property of these variants of RSPH is yet to explore.

\textit{ What determines which of a pair of particles is L and which R? Is this random? }
L and R is determined according to the local coordinate system. For example, if we define the positive direction as from particle a to particle b, then a should be L and b should R. Whether positive direction of local coordinate system is from a to b or from b to a will NOT change the results as long as all the steps (projection from global to local, constructing of local Riemann problem and projection back from local to global) are using consistent local coordinate system (positive direction).
\\[3pt]

\textit{p.10 Fig.10 is confusing (it uses ``q" as coordinate, yet the caption(text) mentions ``x"; it uses an undefined ``w"; it uses sub-scripts ``L" and ``R", yet the caption talks about ``a" and `` b" states; the meaning of the lines ``$S_L$" , ``$S_M$", and ``$S_R$" is not explained)}

Thanks, we cleaned up these confusing points in revised manuscript.
\\[3pt]

\textit{p.10 The remark about the Van Der Corput pseudo-random number sequence is confusing/wrong. AFAIK, these are not pseudo-random, but QUASI-random. This seems to contradict the idea of using a random value. So why should this work?
What happens if instead pseudo-random numbers are used and/or if a different <epsilon> is drawn for every interacting particle pair?}

The idea of using Van Der Corput pseudo-random number sequence is borrowed from RCM. The reviewer is right that Van Der Corput pseudo-random number sequence not pseudo-random, but QUASI-random. But traditionally, it was called pseudo-random \citep[][e.g.]{toro2013riemann}. Should we follow the tradition of RCM or using more correct phrase?

The idea of using a different <epsilon> for every interacting particle pair was actually another variants of RCM. These two different manners turned out to have similar properties. 
\\[3pt]

\textit{p.11/12 The summary of the 1D test cases is somewhat confusing. The initial conditions are not best explained in Table 1: where is the boundary? What is the physical meaning of negative-pressure ideal gas? (Standard SPH is unstable to clumping in the presence of negative pressure.)
These tests do not provide a good testsuite. Most operate at similar Mach numbers, albeit with different arrangements/initial conditions. It would
be desirable to test discontinuous initial conditions with a wider range of Mach numbers, from 0.1 to 100. The Mach number should be given in Table 1.}

The boundary is given in table by $[x_L, x_R]$.

There is a typo for test4 and test5 in that table, we incorrectly put value for velocity under pressure column, that's why you see negative pressure. We have changed it in revised manuscript.

The tests case adopted here are actually very representive to test \textbf{different wave patterns}. These 1D tests are all well known 1D tests used by both mesh based method \citep[][e.g.]{toro2013riemann, leveque2002finite} and SPH tests \citep[][e.g.]{monaghan1983shock, cha2003implementations, puri2014approximate}. 
Mach number can be easily calculated according to physical quantities. We added Mach number in Table 1 in revised manuscript. 
\\[3pt]

\textit{Figs 2,3 Are these really "oscillations around shock" for <alpha>=0.2 SPH? I suspect that instead we have inter-particle penetration, i.e.
particles swapping positions in 1D SPH. Also, in this figure, isn't the interpretation of oscillation==less viscosity rather simplistic? In a conservative scheme, the amount of dissipative heating can in principle be directly measured and used as a measure of viscosity (better than merely pointing at the oscillations).
I think it'd be better to combine Figs 2\& 3 into one, similar to Fig 4. Only one legend is required, not 8. Moreover, the details may be shown as inlet plots.}

They are really oscillations. However, such oscillations are caused by non-uniform smoothing length (due to non-uniform particle mass and density in space). We added an appendix to explain the source of such oscillation in the revised manuscript.

\textit{the amount of dissipative heating can in principle be directly measured and used as a measure of viscosity (better than merely pointing at the oscillations).}

Using internal energy? We are a bit confused on how to measure the dissipative heating. The correlation between oscillation can be demonstrated by these tests with different artificial viscosity coefficients.

We tried to combine 2\&3 and 4\&5. But it would be too large to fit into one page. Inlet plots make it harder to see these details we want to show.

We made modification as suggested by reviewer regarding legend.
\\[3pt]

\textit{p.13-15 I think comparing against <alpha>=2 or 0.2 SPH has little merit.
A comparison to <alpha>=1 SPH makes sense as does a comparison (lacking)
against an AV-switch version of SPH.}

Both <alpha>=2 and 0.2 are necessary. Comparison of three different values confirms the effect AV, which is the basis of for our further discussion. If we only have two different artificial viscosity coefficients sets, some other readers might argue that our comparison is not generic enough.

The AV-switch versions of SPH, which introduce AV in an explicit way, usually have parameters that can be manually tuned while RSPH and GSPH introduce AV in an implicit way and have no manually-tunable parameters. 
We actually tried to compare against one AV-switch version of SPH. But it turned out that we have to manually tune its parameters for each test case. This can easily lead to ``unfair" comparison. In addition, the major difference between RSPH and AV-switch version of SPH is so obvious -- RSPH does not require explicit AV.
\\[3pt]

\textit{p14,15 The features of RSPH discussed here (adaptive viscosity) are the
natural consequence of the Riemann solver, i.e. of Godunov SPH. Nothing
is new here.}

Yes, these features of RSPH are due to Riemann solver. 
But Godunov's method is different from RCM.
They do share some common places but surely are different. If they are the same (or nothing new), how could RSPH introduce AV in a more adaptive manner as shown by these tests.

RSPH samples solution of local Riemann problem in a very different way from GSPH. This is NOT a small difference.
\\[3pt]

\textit{Fig 4 The two versions of GSPH have very similar symbols/colors and can hardly be distinguished.}

Changed in revised manuscript. 
\\[3pt]

\textit{p.16 What is the difference between the RSPH and GSPH-HLLC schemes? Is it
merely the choice of <epsilon>? I.e. is GSPH-HLLC == RSPH with <epsilon>=0? If not, what else is different? This is important, as one would like to understand what drives the differences between the results obtained by these to schemes (mostly near
the onset of the rarefaction region in Fig 4 where RSPH shows a wave while GSPH over-smoothes the rarefaction, but also the energy wiggle at
the contact discontinuity). As it is, this difference remains mysterious and unexplained.}

Yes, choice of <epsilon> is the only difference between \textbf{first order} GSPH-HLLC (GSPH can be second order). That is to say, \textbf{first order} GSPH-HLLC == RSPH with <epsilon>=0.
But this is NOT a small difference.
By the way, since choice of <epsilon> is the only difference, our tests are ``well controlled" comparison, that is to say, the difference in tests results do reflect the essential effect of different choice of <epsilon>. We hope reviewer can appreciate such manner of comparisons.

Why choice of <epsilon> can make such big difference? This is the heart of RCM.
\\[3pt]

\textit{pp. What causes the waves (in RSPH) and what is their wavelength? Perhaps
these waves are related to the correlations introduced by using the same
<epsilon> for all particle pairs (when their wavelength may be comparable
to / scale with h).}

Good question. We added an appendix to explain the source of these waves.
\\[3pt]

\textit{p.17 While simple 1D shock-tube problems are good tests for proof-of-concept implementations, they are not representative of
multi-dimensional flows and cannot be used to reliably validate any scheme. Thus, most tests in §4.2 are meaningless to that end.
A good test (where SPH performs poorly regardless of AV) is the Gresho-Chan vortex test (2D) run over at least one rotation period.}

We do agree that there are additional challenges for multi-dimensional implementations. But we would argue that 1D tests are must for any new method. These ``well controlled" tests could demonstrate the feature of the new method in a more explicit way. In addition, performing well in 1D tests are prerequirement for be doing well in higher dimensional implementations. We observe that many numerical schemes were throughly discussed in 1D and then implemented in 3D.
\\[3pt]

\textit{p.21 The free jet flow is an interesting problem but hardly suitable as a
test here, since there exists no undisputed correct solution (for a converging scheme, such a solution could be obtained by increasing resolution, but this has not been done).}

In terms of demonstrating basic features of RSPH, 1D tests can do a much better job as all factors are well controlled. 
As for 3D jet flow, yes, increasing resolution could help to get better results. But purely increasing resolution might no be enough. See more discussion based on a similar tests by \citet{cha2010kelvin}. 
In addition, different variant versions of RSPH might perform better in different implementations. However, this is not the major topic of this article.
\\[3pt]

\textit{Figs 11 \& 12 lack information which plot is for which scheme. Something is wrong in Fig.12: there are 2 rows of 2 plots each, yet the caption
talks about 2 rows of 3 plots each.}

Thanks, we modified this section to clean up confusions.
\\[3pt]
\bibliographystyle{plainnat}
\bibliography{Reference}
\end{document}

### 2018-12-01 ebp-JCPManuscript.tex
add graphical abstract and highlights
revised manuscript

@@
 \begin{abstract}
-The classical smoothed particle hydrodynamics (SPH) method employs explicit artificial viscosity to properly capture shock waves in hydrodynamics.
-This artificial viscosity typically produces more dissipation than is needed to smooth shocks, incorrectly smears contact discontinuities, and can overwhelm fluid turbulence.
+The classical smoothed particle hydrodynamics (SPH) method employs explicit artificial viscosity to properly capture shock waves in high speed compressible flow.
+This artificial viscosity typically produces more dissipation than is needed to smooth shocks, smears discontinuities, and can overwhelm fluid turbulence.
 Several studies have proposed highly tuned versions of artificial viscosity, turning on and off near shocks or other troublesome wave features.
@@
 We test this method on standard one dimensional shock tube problems and observe several attractive features.
-First of all, this method introduces adaptive artificial viscosity -- larger around discontinuities and smaller elsewhere.
+First of all, this method introduces adaptive artificial viscosity, assigning larger dissipation around discontinuities and smaller elsewhere.
 Secondly, it is less dissipative than classical SPH and GSPH resulting in less smearing of shock.
 Thirdly, as the new method can be viewed as generalized GSPH method in terms of sampling solutions of local Riemann problems, good features of GSPH are inherited, for example, ameliorating pressure ``wiggle" around contact discontinuity.
-When applied to three dimensional jet flow, this method is demonstrated to introduce less overall dissipation than GSPH.
+When applied to three dimensional jet flow, this method is demonstrated to introduce less overall-dissipation than GSPH.
 %Our ultimate goal is to apply this method to jet flow.
@@
 Section \ref{standard-sph} provides a brief review of standard SPH. Section \ref{sec:GSPH-method} shows how the GSPH method is defined. The RSPH method is defined in Section \ref{sec:RSPH-method}.
-One dimensional tests are shown in Section \ref{numericaltests}, followed by the jet flow example in Section \ref{jet}.
+One dimensional tests are shown in Section \ref{sec:numericaltests}, followed by the jet flow example in Section \ref{jet}.
 Other applications and limitations of RSPH are discussed in Section \ref{discussion}
@@
 \end{align}
-Here $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$, the smoothing length $h$ is taken as $h=\frac{h_a + h_b}{2}$, and $\Pi$ is an artificial viscosity term.
+Here $\textbf{v}_{a b} = \textbf{v}_a - \textbf{v}_b$, the smoothing length $h$ is taken as $h=\frac{h_a + h_b}{2}$ \citep{evrard1988beyond}, and $\Pi$ is an artificial viscosity term.
 One of commonly used models of artificial viscosity \citep{monaghan1983shock} is:
@@
 \begin{equation}
-1=\sum_{b} \frac{m_{b}}{\rho(\textbf{x})}w(\textbf{x} - \textbf{x}_{b}, h)
+1=\sum_{b} \frac{m_{b}}{<\rho(\textbf{x})>}w(\textbf{x} - \textbf{x}_{b}, h)
 \label{eq:GSPH-basic1}
@@
 \begin{equation}
-0=\sum_{b} m_{b} \nabla \frac{w(\textbf{x} - \textbf{x}_{b}, h)}{\rho(\textbf{x})}
+0=\sum_{b} m_{b} \nabla \frac{w(\textbf{x} - \textbf{x}_{b}, h)}{<\rho(\textbf{x})>}
 \label{eq:GSPH-basic2}
@@
 In GSPH, the starred state is the solution to a local Riemann problem at a location determined by a weighted average of the specific volumes associated with the two participating particles. 
-Instead of calculating a full solution to the Riemann problem, approximate solvers such as the Roe method or HLLC, might be used. 
-We propose sampling the (approximate) Riemann solution as in the Random choice method, where the approximate solution is given by the HLLC construction (see \cite{toro1994restoration}).
+Instead of calculating a full solution to the Riemann problem, approximate solvers such as the Roe method \citep{roe1981approximate} or HLLC (Harten-Lax-van Leer-Contact) \citep{toro1994restoration}, might be used.
+We propose sampling the (approximate) Riemann solution as in the Random choice method, where the approximate solution is given by the HLLC construction.
 
@@
     \caption{Evaluating of the starred state for  RSPH and GSPH implementations.
-Particles are located at $\textbf{x}_{a} $ and $ \textbf{x}_{ b}$, and the local Riemann problem is defined by the constant states $(u, p)_a$ and $(u,p)_b$.
+$x$ is the local coordinate system for paired two particles, $a$ and $b$.
+The origin is at the middle of the paired two particles.
+The the local Riemann problem is defined by the constant states $(\rho, u, p)_a$ and $(\rho, u,p)_b$, namely $\textbf{W}_L = \textbf{W}_b$, $\textbf{W}_R = \textbf{W}_a$ with $\textbf{W} = (\rho, u,p)^T $, a vector representation of these three variables.
 The horizontal bold solid line at time $\Delta t$ indicates the interval on which to evaluate the solution of the Riemann problem.
 The dark ellipse is an example sample point of RSPH with the random number.
-The white ellipse indicates the stationary state, which is the starred state in GSPH.}
+The red ellipse indicates the stationary state, which is the starred state in GSPH.
+$S_L$, $S_M$ and $S_R$ are singal speeds which are linerized locally in HLLC Riemann solvers \citep{puri2014approximate}.
+Starred region is divided into two sub-regions by the middle contact wave.
+Only $\rho$ changes across the contact wave.
+}
     \label{fig:pick-up-state-GSPH-RSPH}
@@
 
-We mention that, instead of selecting a uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte}.
+We mentioned that, instead of selecting an uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte}.
 
@@
 
-We mention that, in the numerical tests in Section \ref{numericaltests}, Both the HLLC solver and Roe solver are used for GSPH calculations.
+We mention that, in the numerical tests in Section \ref{sec:numericaltests}, Both the HLLC solver and Roe solver are used for GSPH calculations.
 To summarize, our RSPH algorithm proceeds as follows:
@@
 
-\section{Numerical tests} \label{numericaltests}
+\section{Numerical tests} \label{sec:numericaltests}
 We describe results from several numerical tests using SPH, RSPH and GSPH in this section.
-A 1D shock tube tests is used to compare standard SPH, GSPH and RSPH.
-More shock tube simulations are also conducted to check the capacity of RSPH for different situations.
-In addition, order of accuracy is investigated for the 1D shock tube problem.
-In the last subsection we describe a 3D free jet flow simulation with SPH, GSPH and RSPH to check equivalent overall dissipation introduced by each method.
+A 1D shock tube test is investigated in different aspects to compare standard SPH, first order GSPH and RSPH revealling several features of RSPH.
+More shock tube simulations are also conducted to check the capacity of RSPH for different wave patterns.
+In addition, order of accuracy is investigated using the 1D shock tube problem.
+In the last subsection we describe a 3D free jet flow simulation.
+The effect of equivalent overall dissipation is first demonstrated by SPH simulation with different artificial viscosity coefficients.
+Then the equivalent overall dissipations introduced by first order GSPH and RSPH are compared demonstrating that RSPH introduces less dissipation than first order GSPH.
 
@@
 \item Test 3 includes double expansion waves. The initial density is different at right and left hand side. 
-\item Test 4 is a double shock tests with different initial density on the right side and left side.
+\item Test 4 is a double shocks test with different initial densities on the right side and left side.
 \item Test 5 and Test 6 are two extreme cases. Test 5 is a cavity flow while test 6 is a strong blast flow.
@@
 	    	Test 2 & $1.0$ & $1.0$ &$0$ & $0.5$ & $0.2$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.2$\\
-	    	Test 3 & $2.0$ & $1.95$ &$1.0$ & $1.0$ & $1.95$ &$-1.0$  & $0.006$  & $[-0.4, 0.4]$ & $0.13$\\
+	    	Test 3 & $2.0$ & $1.95$ &$-1.0$ & $1.0$ & $1.95$ &$1.0$  & $0.006$  & $[-0.4, 0.4]$ & $0.13$\\
 	    Test 4 & $1.0$ & $2.4$ &$8.0$ & $0.5$ & $0.4$ &$-0.25$ & $0.003$  & $[-0.4, 0.4]$ & $0.05$\\
-	    	Test 5 & $1.0$ & $-2.0$ &$0.4$ & $1.0$ & $0.4$ &$2.0$ & $0.003$  & $[-0.4, 0.4]$ & $0.18$\\
-	    	Test 6 & $1.0$ & $0$ &$1000$ & $1.0$ & $0$ &$0.01$ & $0.003$  & $[-0.5, 0.5]$  & $0.01$\\
+	    	Test 5 & $1.0$ & $0.4$ &$-2.0$ & $1.0$ & $0.4$ &$2.0$ & $0.003$  & $[-0.4, 0.4]$ & $0.18$\\
+	    	Test 6 & $1.0$ & $1000$ &$0$ & $1.0$ & $0.01$ &$0$ & $0.003$  & $[-0.5, 0.5]$  & $0.01$\\
 	    \hline
@@
 $t_f$ is the time to terminate simulation and plotting the results.
-Equal particle mass is assigned to all particles.
 The $x$ axis in all plots is normalized by time, that is $x/t_f$, in plots for shock tube tests results.
+
+In first four tests, density on right and left sides are different.
+Considering that all particles have the same particle mass, assigning smoothing length according to $h \propto \frac{m}{\rho}$ leads to discontinuity of smoothing length at the middle.
+Such discontinuity of smoothing length is the source of numerical oscillations, which usually decay fast and are not observed when there is sufficient dissipation.
+Such  numerical oscillation becomes obvious when dissipation is less.
+For example, when SPH taking $\alpha=0.2$ (see Fig.
+\ref{fig:RCM-Sod-SPH-alf} and Fig.
+\ref{fig:RCM-Sod-SPH-alf-zoom}).
+That is to say, how much the numerical oscillation is suppressed can indicate the amount of numerical dissipation introduced in each SPH scheme providing we are solving invisid fluids (no physical dissipation).
+Refer Appendix B for more information regarding the numerical oscillation due to nonuniform smoothing length.
+Another indicator of numerical dissipation is how much the shock is smeared.
+Both indicators reflect consistent information regarding numerical dissipation throughout our tests, see, for example, plot c) in Fig.
+\ref{fig:RCM-Sod-SPH-alf-zoom} or plot g) in Fig.
+\ref{fig:RCM-GSPH-Sod}.
+We take these two as indicators of numerical dissipation in many discussions regarding 1D tests.
+As for 3D jet flow, we take the distance between jet head and inject vent at the same physical time as the indicator of overall equivalent numerical dissipation.
+As shown in Fig.
+\ref{fig:free-jet-SPH-comparison}, the distance between jet head and inject vent decrease when artificial viscosity coefficients increase.
+This confirms that such distance do reflect overall equivalent dissipation.
+
 \subsection{Comparison of RSPH with standard SPH and GSPH}
+
 \begin{figure}[H]
     \centering
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.45\textwidth}
         \centering a)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-rho}
     \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
+    \begin{minipage}{.545 \textwidth}
         \centering b)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
+        \includegraphics[width=0.99 \textwidth,height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-v}
     \end{minipage}% 
     \\
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.45 \textwidth}
         \centering c)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
+        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-rho-zoom}
     \end{minipage}% 
-    \begin{minipage}{.495 \textwidth}
+    \begin{minipage}{.545\textwidth}
     \centering d)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-v-zoom}    
+        \end{flushleft}
     \end{minipage}%          
-    \caption{a),b) are simulation results of density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
-c), d) are zoomed views, showing that $\alpha=0.2$ provided insufficient viscosity to suppress oscillations around shock.
+    \caption{a),b) are plots for density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients.
+$\alpha,\beta$ satisfies: $\beta=2\alpha$.
+c), d) are corresponding zoomed views, showing that numerical oscillation is obvious, especially around shock, due to insufficient dissipation when $\alpha=0.2$.
 The dissipation introduced by RSPH.
-on the other hand, is adaptive, introducing more damping at the shock (comparable to $\alpha=1.0$) and less damping in the area away from the shock (less than $\alpha=0.2$, as indicated by the magnitude of oscillation).}
+on the other hand, is adaptive, introducing more damping at the shock (comparable to $\alpha=1.0$) and less damping in the area away from the shock (less than $\alpha=0.2$, as indicated by the magnitude of numerical oscillation).}
     \label{fig:RCM-Sod-SPH-alf}
@@
     \centering
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.45\textwidth}
         \centering a)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-e}
     \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
+    \begin{minipage}{.545 \textwidth}
         \centering b)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
+        \includegraphics[width=0.99 \textwidth,height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-p}
     \end{minipage}% 
     \\
-    \begin{minipage}{.495 \textwidth}
+    \begin{minipage}{.45 \textwidth}
         \centering c)
-        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
+        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-e-zoom}
     \end{minipage}% 
-    \begin{minipage}{.495\textwidth}
+    \begin{minipage}{.545\textwidth}
     \centering d)
-        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-p-zoom}    
+        \end{flushleft}
     \end{minipage}%    
     \caption{
-    a),b) are simulation results of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.
-c), d) are zoomed views.
-For $\alpha=1$ and $\alpha=2$, as shown in c), numerical oscillations are completely suppressed though the shock is now smeared.
-$\alpha=0.2$ provided insufficient viscosity to suppress oscillations.
-Comparing RSPH and SPH shows that RSPH is adaptive, more dissipative at the shock (comparable or better than $\alpha=1.0$) and less dissipative away from the shock (less than $\alpha=0.2$).
+    a),b) are plots of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients.
+c), d) are corresponding zoomed views.
+For $\alpha=1$ and $\alpha=2$, as shown in c), numerical oscillations are completely suppressed.
+However there is also more smearing around the shock.
+$\alpha=0.2$ provides insufficient viscosity to suppress oscillations while the smearing around the shock is also less.
+Impressively, RSPH is showing to introduce adaptive dissipation, more dissipative at the shock (comparable or better than $\alpha=1.0$) and less dissipative away from the shock (less than $\alpha=0.2$).
 d) shows pressure around the contact discontinuity.
@@
 
-Test 1 is simulated using standard SPH with different artificial viscosity coefficients, GSPH and RSPH.
-The comparison between RSPH and SPH using different artificial viscosity coefficients is shown in Fig.
+Test 1 is simulated using standard SPH with different artificial viscosity coefficients, GSPH and RSPH. Results are checked from different aspects.  
+The comparison between RSPH and SPH with different artificial viscosity coefficients is shown in Fig.
 \ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}.
-In all simulations, the artificial viscosity coefficient $\beta$ is set to be twice of $\alpha$.
+In all SPH simulations, the artificial viscosity coefficient $\beta$ is set to be twice of $\alpha$.
 For example, for the test ``$SPH-\alpha=2$", $\beta=4$.
-Several interesting observation are made based on the comparison between SPH and RSPH.
-The effect of artificial viscosity is illustrated through comparison.
+
+Several interesting observations are made based on the comparison between SPH and RSPH.
 First of all, dissipation (introduced by artificial viscosity in these tests) decays the numerical fluctuations.
-Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients ($\alpha=1,2$).
-Secondly, the equivalent artificial viscosity introduced by RSPH varies adaptively.
+Numerical fluctuations are suppressed completely when large dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients ($\alpha=1,2$).
+Secondly, the equivalent artificial viscosity introduced by RSPH varies more adaptively.
 As shown in Fig.
 \ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}, RSPH assigns smaller artificial viscosity (equivalent $\alpha$ much less then 0.2) at the area far away from shock and sufficiently large artificial viscosity coefficients (equivalent $\alpha$ is about 1.0) around the shock.
-So RSPH is actually more adaptive than SPH.
+Namely, RSPH adaptively assigns larger equivalent artificial viscosity coefficient around the shock and take smaller equivalent artificial viscosity far away from shock.
 This feature is very desirable not only because it could eliminate parameterization and hence user intervention associated with artificial viscosity coefficients but also because it avoids introducing excess artificial viscosity.
@@
 \ref{fig:RCM-Sod-SPH-alf-zoom}.
+\citet{inutsuka2002reformulation} show that GSPH can almost get rid of pressure wiggle around contact discontinuity while standard SPH has much more obvious pressure wiggle.
+They believe that the pressure wiggle is due to the inconsistency of equation of momentum in the standard SPH discretization.
+However, there are different opinions with respect to the sources of pressure wiggle.
 It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}.
@@
 Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}).
-``Wiggle" in test 1, however, is completely eliminated by both GSPH and RSPH.
+Wiggle in test 1, however, is completely eliminated by both GSPH and RSPH.
 
@@
     \centering
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho}
+    \begin{minipage}{.45\textwidth}
+        \centering a)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-rho}
     \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v}
+    \begin{minipage}{.545\textwidth}
+    \centering b)
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-v}    
+        \end{flushleft}
     \end{minipage}% 
     \\
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e}
+    \begin{minipage}{.45\textwidth}
+        \centering c)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-e}
     \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p}
+    \begin{minipage}{.545 \textwidth}
+        \centering d)
+        \includegraphics[width=0.99 \textwidth,height=0.4954\textwidth]{./Figures/RCM-Sod-GSPH-compare-p}
     \end{minipage}% 
     \\
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho-zoom}
+    \begin{minipage}{.45\textwidth}
+        \centering e)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-rho-zoom}
     \end{minipage}%
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v-zoom}
+    \begin{minipage}{.545\textwidth}
+    \centering f)
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-v-zoom}    
+        \end{flushleft}
     \end{minipage}%  
        \\
-    \begin{minipage}{.495 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e-zoom}
+    \begin{minipage}{.45 \textwidth}
+        \centering g)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-e-zoom}
     \end{minipage}% 
-    \begin{minipage}{.495\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p-zoom}
+    \begin{minipage}{.545\textwidth}
+    \centering h)
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-p-zoom}    
+        \end{flushleft}
     \end{minipage}%     
-    \caption{Comparison of RSPH with GSPH using Roe Riemann solver and HLLC Riemann solver.
+    \caption{Comparison of RSPH with first order GSPH using Roe Riemann solver and HLLC Riemann solver.
 The last four plots are zoomed views.
@@
 Compared with SPH, both GSPH and RSPH avoid pressure ``wiggle" around contact discontinuity.
-Since RSPH shares many commonalities   with Godunov's method, it is not a surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.
+Since RCM shares many commonalities with Godunov's method, it is not a surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.
 
@@
 We observe a rate of convergence of approximately 1 for GSPH and 1.5 for standard SPH and RSPH.
-GSPH with an exact Riemann solver has been shown to be approximately second order of accuracy \citep{puri2014comparison} and comparable in accuracy to the standard SPH schemes when using piece wise linear construction.
-As for GSPH using approximate Riemann solver, \citet{puri2014approximate} reported second order accuracy for HLLC and Roe Riemann solvers adopting piece wise linear Riemann problem construction.
-In addition, they adopted a test problem without discontinuity in the solution.
+Considering Riemann problem is constructed in piece wise constant manner, it is not surprise that GSPH shows first order of accuracy.
+With piece wise linear construction of Riemann problem, GSPH would be higher order of accuracy.
+For example,
+GSPH combined with HLLC and Roe approximate Riemann solvers has been shown to be approximately second order of accuracy \citep{puri2014comparison} and comparable in accuracy to the standard SPH schemes when using piece wise linear construction.
 Presence of discontinuities, such as shock, in the test problem might lower the rate of convergence.
-Since both RSPH and GSPH tests in this paper adopt piece wise constant construction of Riemann problem.
-We conclude that RSPH shows higher order of accuracy than GSPH when using the same Riemann problem construction.
+
+Since both RSPH and GSPH tests in this paper adopt the same manner for Riemann problem construction, the piece wise constant construction.
+We conclude that RSPH shows higher order of accuracy than GSPH providing both use the same Riemann problem construction.
 Compared with SPH, RSPH shows almost the same order of accuracy and level of error.
+
 \begin{figure}[H]
     \centering
-    \begin{minipage}{.332\textwidth}
+    \begin{minipage}{.30\textwidth}
         \centering
@@
     \end{minipage}%
-    \begin{minipage}{.332 \textwidth}
+    \begin{minipage}{.30 \textwidth}
         \centering
@@
     \end{minipage}%
-    \begin{minipage}{.332\textwidth}
+    \begin{minipage}{.39\textwidth}
         \centering
@@
     \end{minipage}%  
-    \caption{ $L_1$ norm errors for 1D shock tube test (test1) for RSPH, standard SPH, GSPH using Roe Riemann solver and GSPH using HLLC Riemann Solver.
+    \caption{ $L_1$ norm of errors for 1D shock tube test (test1) for RSPH, standard SPH, GSPH using Roe Riemann solver and GSPH using HLLC Riemann Solver.
 GSPH with the HLLC approximate Riemann solver exhibits the same convergence rate (around 1) but quantitatively larger errors than that with Roe Riemann solver.
-RSPH and standard SPH shows same rate of convergence and almost same amount of error.}
+RSPH and standard SPH shows same rate of convergence and almost same level of error.}
     \label{fig:Accuracy-test1}
@@
 \subsection{Comprehensive 1D tests} \label{sec:comprehensive-1d-tests}
-Comprehensive tests are presented in this section to check how well does RSPH work for different situations. Input parameters for each tests is given in Table \ref{tab:1D-shock-input_parameters}.
-The results are shown in Fig.
-\ref{fig:RCM-GSPH-Sod} $\sim$ Fig.
-\ref{fig:RCM-strong-blast}.
-$x$ axis in these plots are normalized by the terminal time $t_f$.
+Comprehensive tests are presented in this section to check how well does RSPH work for different wave patterns. Input parameters for each tests is given in Table \ref{tab:1D-shock-input_parameters}.
+The results are shown in Fig. \ref{fig:RCM-GSPH-Sod} $\sim$ Fig. \ref{fig:RCM-strong-blast}. $x$ axis in these plots are normalized by the terminal time $t_f$. 
 We observe that RSPH is able to correctly predict the position and magnitude of all waves for all tests.
@@
 However, such jump is a common issue of SPH schemes and has been reported in many other tests (see, for example, \citep{monaghan1997sph,cha2003implementations,puri2014approximate})
-In addition, a noticeable spike can be observed near the contact discontinuity.
-Similar spike is observed in GSPH simulation \citep{puri2014comparison}.
-%Such spike is evident in the FVM solution as well and is perhaps an artifice of the Lagrangian nature of the two schemes.
+In addition, a noticeable spike can be observed near the contact discontinuity. Similar spike is observed in GSPH simulation \citep{puri2014comparison}.
 \citet{noh1987errors} proposed to adding a small amount of thermal conduction to ameliorate the spike and has been applied in blast-wave test using GSPH \citep{puri2014comparison}.
 We did not adopt such strategy in our simulation.
-Due to less amount of dissipation, numerical fluctuations persist in all simulation results.
-For the strong blast test and double shock test, such fluctuations become more obvious than other tests, even though, the magnitude of fluctuations is within an acceptable range.
+Due to less amount of dissipation, the numerical oscillations, which is due to nonuniform smoothing length as discussed in Appendix B, persist in all simulation results.
+For the strong blast test and double shock test, such oscillation become more obvious than other tests, even though, the magnitude of fluctuations is within an acceptable range.
 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-rho}
+        \includegraphics[width=0.99 \textwidth]{./Figures/GRod-RCM-rho}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-v}
+    \begin{minipage}{.512 \textwidth}
+        \begin{flushleft}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/GRod-RCM-rho}
+        \end{flushleft}
     \end{minipage}%    
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-e}
+        \includegraphics[width=0.99 \textwidth]{./Figures/GRod-RCM-e}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
+    \begin{minipage}{.512 \textwidth}
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-Sod/GRod-RCM-p}
+        \includegraphics[width=0.99 \textwidth]{./Figures/GRod-RCM-p}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-rho}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Dexp-RCM-rho}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-v}
+    \begin{minipage}{.512 \textwidth}
+        \begin{flushleft}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Dexp-RCM-v}
+        \end{flushleft}
     \end{minipage}%     
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-e}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Dexp-RCM-e}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
+    \begin{minipage}{.512 \textwidth}
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_exp/Dexp-RCM-p}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Dexp-RCM-p}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-rho-Rp6}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Dshock-RCM-rho-Rp6}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-v-Rp6}
+    \begin{minipage}{.512 \textwidth}
+        \begin{flushleft}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Dshock-RCM-v-Rp6}
+        \end{flushleft}
     \end{minipage}%     
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-e-Rp6}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Dshock-RCM-e-Rp6}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
+    \begin{minipage}{.512 \textwidth}
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/double_shock/Dshock-RCM-p-Rp6}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Dshock-RCM-p-Rp6}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-rho-Adpt1}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen-RCM-rho-Adpt1}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-v-Adpt1}
+    \begin{minipage}{.512 \textwidth}
+        \begin{flushleft}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Sjogreen-RCM-v-Adpt1}
+        \end{flushleft}
     \end{minipage}%       
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-e-Adpt1}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen-RCM-e-Adpt1}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
+    \begin{minipage}{.512 \textwidth}
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen/Sjogreen-RCM-p-Adpt1}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen-RCM-p-Adpt1}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-rho-Rp3}
+        \includegraphics[width=0.99 \textwidth]{./Figures/StrBlst-RCM-rho-Rp3}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-v-Rp3}
+    \begin{minipage}{.512 \textwidth}
+        \begin{flushleft}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/StrBlst-RCM-v-Rp3}
+        \end{flushleft}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-e-Rp3}
+        \includegraphics[width=0.99 \textwidth]{./Figures/StrBlst-RCM-e-Rp3}
     \end{minipage}%
-    \begin{minipage}{.415 \textwidth}
+    \begin{minipage}{.512 \textwidth}
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/strong-blast/StrBlst-RCM-p-Rp3}
+        \includegraphics[width=0.99 \textwidth]{./Figures/StrBlst-RCM-p-Rp3}
     \end{minipage}% 
@@
 All simulations are using the same set-up and compared at the same physical time.
-In this test, RSPH simulation is carried out based on piece wise constant construction of Riemann problem and a HLLC approximate Riemann solver.
-To do a well-controlled comparison, GSPH adopts the same way for Riemann problem construction and the same Riemann solver as RSPH.
+Considering the fact that RSPH is based on piece wise constant construction of Riemann problem and a HLLC approximate Riemann solver, to do well-controlled comparisons, GSPH also adopts piece wise constant construction of Riemann problem and a HLLC Riemann solver.
 
-The computational domain in this test is a box.
-The boundaries can be categorized into the velocity inlet (a circular area at the center of the bottom of the box), non-slip wall boundary (box bottom) and pressure outlet (other faces of the box).
-The boundaries are set away from vent to avoid boundary effects on simulation.
+Setup of the 3D test is summaried briefly below.
+The computational domain is a box and boundaries are categorized into three types: the velocity inlet (a circular area at the center of the bottom of the box), the non-slip wall boundary (box bottom) and the pressure outlet (other faces of the box) boundary.
 At the vent, exit velocity $\textbf{v}$ is set to $500 m / s$ and radius of the nozzle $r$ is set to $8m $.
@@
 The temperature of both ejected fluids and ambient fluids are set to $273 K$.
-Velocity is zero for non-slip wall boundary.
-The heat flux across wall boundary is zero assuming an adiabatic wall.
-The flux of mass should also be zero on the wall.
-As a result, internal energy flux, which consists of heat flux and energy flux carried by mass flux, vanishes on the wall boundary.
+Velocity is set to zero on the non-slip wall.
+The heat flux across wall boundary is also zero assuming an adiabatic wall.
+The flux of mass should be zero on the wall as well.
+As a result, internal energy flux, which consists of heat flux and energy flux carried by mass flux, vanishes on the non-slip wall boundary.
 The pressure of the surrounding ambient is given. As we ignore the physical viscosity, the shear stress is ignored and normal stress (whose magnitude equals to pressure) balances the ambient pressure.
@@
 
-\begin{figure}[!ht]
+\begin{figure}[H]
     \centering
-%    \begin{minipage}[t]{.325\textwidth}
-%        \centering
-%        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t1p5-cutView}
-%    \end{minipage}%
     \begin{minipage}[t]{.325 \textwidth}
@@
     \centering
-%    \begin{minipage}[t]{.325\textwidth}
-%        \centering
-%        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t3-cutView}
-%    \end{minipage}%
     \begin{minipage}[t]{.325 \textwidth}
@@
     \end{minipage}%
-    \caption{Simulation results of free jet flow by SPH with $\alpha=1.0, \beta=2.0$, GSPH and RSPH.
+    \caption{Simulation results of free jet flow by GSPH and RSPH.
 These pictures are front view of a slice of the domain cut by two planes parallel to $x-z$ plane at $y=-9$ and $y=9$.
-From left to right, the picture is corresponding to SPH, GSPH and RSPH respectively.
+Pictures to the left is for GSPH while those on the right side are for RSPH.
 Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.
@@
 Figure \ref{fig:free-jet-SPH-comparison} shows simulation results of the free jet flow by SPH with different artificial viscosity coefficients.
-The overall damping effect due to artificial dissipation is clearly shown in this figure.
-We observe that the lengths to which these jets reach at $t=3.0 s$ are different when using different artificial viscosity coefficient.
-It is obvious that the larger artificial viscosity, the shorter length the jet can reach.
-The length that free jet reaches can be used as an indicator of overall dissipation.
+The positive correlation between overall damping effect (due to artificial dissipation) and the distance from nozzle to the front of jet flow is clearly shown in this figure.
+At $t=3.0 s$ after jet flow starting, we observe that the distance between front of jet flow and nozzle are different when using different artificial viscosity coefficients.
+Standard SPH adds artificial dissipation explicitly through the artificial viscosity term.
+The amount of artificial dissipation is positively related to artificial viscosity coefficients.
+The artificial dissipation is the total dissipation as there is no physical dissipation in the governing equations.
+It is obvious that the larger the artificial viscosity coefficients, the smaller the distance between the nozzel and the front of free jet flow.
+So the distance between nozzel and front of free jet flow can be used as an indicator of equivalent overall dissipation.
 While introducing undesirable damping effects, artificial viscosity is necessary for numerical stability and simulating of shocks.
-So, in real applications, the artificial viscosity coefficients are usually tuned (see, for example, \citep{gmd-2017-119}) to minimize artificial damping effects.
+So, in real applications, the artificial viscosity coefficients are usually tuned (see, for example, \citep{cao2018plume}) to minimize artificial damping effects.
+Our comparison between GSPH and RSPH in next paragraph is based on the positive correlation between equivalent overall dissipation and the distance from nozzle to the front of jet flow.
 
@@
 Different from SPH, both GSPH and RSPH introduce artificial viscosity in an implicit way by solving local Riemann problems.
-As has been shown in 1D tests, RSPH can introduce less artificial viscosity than GSPH.
+Based on the positive correlation between overall damping effect and the distance between the nozzle and the front of jet flow, we can still infer the amount equivalent overall dissipation introduced by RSPH and GSPH.
+It has been shown in 1D tests that RSPH can introduce less artificial viscosity than GSPH.
 Fig.
@@
 
+\appendix
+\section{Glimm\rq{}s Scheme}
+In \citep{glimm1965solutions}, Glimm proved the existence  of solutions to a  $2\times2$ 
+system of hyperbolic conservation laws within the space of total variation bounded functions. 
+This proof constructed solutions in one space dimension (plus time) by solving local Riemann problems at `grid points\rq{}, sampling these local solutions randomly, and stitching them together to create the full solution.
+Later \citet{liu1977deterministic} proved that a deterministic, uniform sampling
+method was sufficient to establish existence. \citet{chorin1976random} used
+the random Glimm scheme as the basis of a numerical method to solve conservation laws, and
+\citet{concus1979numerical} extended these ideas.
+In his thesis, \citet{colella1978analysis} examined the van der Corput sequence as a sampling procedure (see also \cite{colella1982glimm}).
+
+A signature feature of using Glimm\rq{}s method (or the random choice method) as a computational methodology is that
+it introduces no artificial viscosity into the solution -- shocks and contact discontinuities are
+resolved as sharp interfaces.  Let us explain by example. Consider a centered difference
+method to solve the linear scalar equation 
+\begin{equation}
+\label{linear}
+\frac{\partial u}{\partial t }+ a \frac{\partial )}{\partial x} = 0
+\end{equation}
+at cell index $j$ and time $n+1$:
+\begin{equation}
+u_j^{n+1} = u_j^n - a \frac{\Delta t}{\Delta x} \frac{(u_{j+1}^n - u_{j-1}^n)}{2}
+\end{equation}
+Of course this scheme is unconditionally unstable. Classical approaches to stabilizing the scheme add a small dose of artificial viscosity
+\begin{equation}
+u_j^{n+1} = u_j^n - a \frac{\Delta t}{\Delta x} \frac{(u_{j+1}^n - u_{j-1}^n)}{2} + a \frac{\Delta t}{2 \Delta x} (u_{j+1}^n -2 u_j^n + u_{j-1}^n)
+\end{equation}
+A stable first-order scheme such as upwind differencing (assuming $a>0$)
+\begin{equation}
+u_j^{n+1} = u_j^n - a \frac{\Delta t}{\Delta x} {(u_{j+1}^n - u_{j}^n)}
+\end{equation}
+can be seen as being second order accurate in space with a viscosity term added
+\begin{equation}
+u_j^{n+1} = u_j^n - a \frac{\Delta t}{\Delta x} \frac{(u_{j+1}^n - u_{j-1}^n)}{2} + a \frac{\Delta t}{2 \Delta x} (u_{j+1}^n -2 u_j^n + u_{j-1}^n))
+\end{equation}
+Examining dissipation effects for wide classes of finite difference/finite volume methods 
+shows a similar phenomena (see, for example, \cite{warming1974modified}).
+
+In contrast, Glimm\rq{}s approach solves a local Riemann problem exactly within each cell,
+and samples (randomly or uniformly) the solution states. Consider again the linear advection equation \ref{linear}, with a discontinuity in cell $j$:
+\begin{equation}
+u^n = \left\{ \begin{array}{11}
+			u_L ~~~ x< (j+\xi)\Delta x \\
+ 			u_R ~~~ x> (j+\xi)\Delta x
+ 			\end{array}
+	  \right. 			
+\end{equation}
+where $0<\xi<1$ locates the discontinuity within cell $j$.
+
+At time $n+1$, the discontinuity is either propagated or not, depending on the sampling
+point:
+\begin{equation}
+u^{n+1} = \left\{\begin{array}{11}
+		  u_L ~~~ x< (j+\tilde \xi)\Delta x + a \Delta t \\
+		  u_R ~~~ x> (j+\tilde \xi)\Delta x + a \Delta t
+		  \end{array}
+		  \right.
+\end{equation}
+where $\tilde \xi$ denotes the sample point.
+In either case, the solution remains discontinuous at time $n+1$ and the 
+discontinuity propagates at speed $a$ on average.
+
+The random choice method requires an exact solution of every local Riemann problem, at every time step.
+However this local solution is sampled, and much of the information present in the solution discarded.
+Harten and Lax \citet{harten1981random} suggested solving the local Riemann problem approximately 
+and sampling this approximate solution. The approximate solver reduces the computational
+effort required in a numerical scheme, and the sampling recovers the zero viscosity
+feature of the random choice method. \citet{hartenlax} suggest a finite difference
+method as the approximate solver.
+In our implementation, we propose the HLLC approximate solution as the foundation for
+uniform sampling via the van der Corput sequence.
+\citep{glimm1965solutions}
+\citep{colella1982glimm}
+\citep{chorin1976random}
+\citep{concus1979numerical}
+\citep{warming1974modified}
+\citep{liu1977deterministic}
+
+\section{Numerical oscillation due to non-uniform smoothing length in space}
+Our discussion in this appendix is divided into two parts.
+The first part explains the mechanism how the numerical oscillations are induced by non-uniform smoothing length in space.
+The second parts  shows a ``manmade" numerical oscillation, which backs up our analysis in first part.
+
+There are several options \citep[][e.g.]{evrard1988beyond, hernquist1989treesph} for smoothing length $h$ in Eq.
+(\ref{eq:ns-sph-d} - \ref{eq:ns-sph-v}).
+Major discussions regarding the smoothing length are during 1980s to first several years of 1990s.
+In now days, taking $h=\frac{h_a + h_b}{2}$ is a commonly accepted practice.
+It is also adopted in this article.
+One big advantage is that such treatment can guarantee momentum and energy conservation given any paired particles are within compact support of each other's weighting function.
+However, it could also lead to numerical oscillation when applying the averaged smoothing length formulation in these scenarios with nonuniformly distributed smoothing length in space.
+Such numerical oscillation are usually either too small to observe or decays quickly due to sufficient numerical dissipation.
+Such numerical oscillation is not fully aware of yet by the community.
+In this section we explain how the numerical oscillations are formed.
+
+Recall that the kernel function of particle $a$ is required to be symmetric with repect to particle $a$.
+As a result, the gradient of kernel function at particle $a$ is anti-symmetric.
+All the commonly used kernel functions can satisfy the symmetry requirement as well as the anti-symmetry requirement of its gradient.
+The anti-symmetric properties of gradient of kernel function can guarantee the pressure gradient term, $\left(\dfrac{p_b}{\rho_b^2} + \dfrac{p_a}{\rho_a^2}\right) \nabla_a w_{a b}\left(h\right)$,  in momentum and energy equation (see Eq.
+(\ref{eq:ns-sph-v}) and (\ref{eq:ns-sph-e})) vanshes when pressure is uniform in space.
+For example, if pressure is uniform in space, pressure at particle $a$ and particle $b$ would be equal, the pressure gradient term then equals zero.
+That is, numerical approximation is consistent with real physics.
+However the actual kernel function is not symmetric any more if smoothing length is not uniform in space providing we adopt the averaged smoothing length formulation.
+The gradient of kernel function is also not anti-symmetric any more.
+That is to say, the pressure gradient term becomes non-zero even when pressure is uniform in space.
+This unphysical representation of pressure gradient term by numerical approximation is illustrated in Fig.
+\ref{fig:dw-ha}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.90 \textwidth ]{App-Figure/dw-ha}
+\caption{In this example, we consider two pairs of particles $(a, b_1)$ and $(a b_2)$.
+For simplicity, we assume uniform distance between particles.
+When take $h=\frac{h_a + h_b}{2}$, the actual shape of gradient of kernel function is the combination of two dash curves.
+It is not anti-symmetric.
+We also assume pressure, density and particle mass of all particles are equal.
+However, the pressure gradient term at particle $a$ in discretized formulation do not cancel out ( $-\dfrac{p_{b_1}}{\rho_{b_1}^2} \nabla_a w_{a b_1}\left(\frac{h_a+h_{b_1}}{2}\right) < -\dfrac{p_{b_2}}{\rho_{b_2}^2} \nabla_a w_{a b2}\left(\frac{h_a+h_{b_1}}{2}\right)$) when smoothing lengths are not equal ($h_{b1} \neq h_{b2}$).
+This leads to unphysical non-zero pressure gradient, which is the source of numerical oscillation.
+When smoothing length is uniform in space or take $h = h_a$, the actual shape of gradient of kernel function is the solid curve, which is anti-symmetric.
+As a consequence, $-\dfrac{p_{b_1}}{\rho_{b_1}^2} \nabla_a w_{a b_1}\left(h\right) = \dfrac{p_{b_2}}{\rho_{b_2}^2} \nabla_a w_{a b2}\left(h\right)$, the unphysical non-zero pressure gradient vanishes.}
+\label{fig:dw-ha}
+\end{figure}
+
+To summarize, two necessary conditions for generating unphysical numerical representation of pressure gradient terms are:
+\begin{itemize}
+\item Calculate smoothing length by averaging, for example, $h = \frac{h_a + h_b}{2}$.
+\item Smoothing length is nonuniform in space.
+\end{itemize} 
+This unphysical numerical representation of pressure gradient term could lead to numerical oscillation in numerical solution.
+Sharp changes in smoothing length can induce significant oscillation which usually propagates into the computational domain and corrupts numerical solution.
+
+To illustrate the formation and influence of such numerical oscillation, we intentionally create a situation of non-uniform smoothing length merely by assigning larger smoothing length to boundary ghost particles on left side in the 1D shock tube test (test2).
+As shown in the first plot of Fig.
+\ref{fig:Perturbation-ME2}, the smoothing length is discontinuous at the left boundary.
+\textbf{Just like discontinuity of physical quantities (for example, the discontinuity at the middle of shock tube test), discontinuity in numerical resolution, in terms of smoothing length, also induces a wave.} A oscillation is observed clearly in the simulation result, starting near the left boundary and propagating into simulation domain.
+Recall that larger smoothing length for left boundary ghost particles is the only difference between normal test (as shown in Fig.
+\ref{fig:RCM-GSPH-Sod}) and the new test (see Fig.
+\ref{fig:Perturbation-ME2}), we can conclude that nonuniform smoothing length in space do induce numerical oscillations.
+Another important observation is that the magnitudes of oscillation decays as the time goes.
+We would suppose that it is due to numerical dissipation.
+In section \ref{sec:numericaltests}, we use magnitude of oscillation as an indirect indicator of numerical dissipation.
+
+In another test, based on the previous test with larger smoothing length for ghost particle on left boundary, we adopt $h = h_a$, instead of $h = \frac{h_a + h_b}{2}$.
+The result is shown by Fig.
+\ref{fig:Perturbation-ME0-tp1}.
+The oscillation is get rid of, which confirms that the averaged smoothing length is one of necessary conditions for the unphysical numerical representation of pressure gradient term.
+%Such perturbation would be created unintentionally in real implementation.
+The oscillation can actually be observed in 1D shock tube tests in many other papers, even though they are not as obvious as the one in Fig.
+\ref{fig:Perturbation-ME2}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.90 \textwidth]{App-Figure/Perturbation-ME2}
+\caption{Plots of density for 1D shock tube test 2 at different time.
+The test is simulated using classical SPH with $\alpha = 1$.
+In these plots, $x$ axis is location along shock tube, $y$ axis is density.
+Smoothing length $h = \frac{h_a + h_b}{2}$.
+The first plot is corresponding to $t=0.001s$, color map is for smoothing length.
+The second plot to last plot are corresponding to $t=0.05s$, $t=0.1s$, $t=0.2s$, $t=0.3s$ respectively.
+We observe that a numerical perturbation incepts near the left boundary and propogates into the domain.
+Actually, the smoothing length is also discontinuous at the middle.
+It also induces another numerical perturbation which has smaller magnitude but still observable.
+It has the same propagating speed as the front of rarefaction.
+Both oscillations decays in time due to dissipation.}
+\label{fig:Perturbation-ME2}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.90 \textwidth]{App-Figure/Perturbation-ME0-tp1}
+\caption{Plots of density for 1D shock tube test 2 at $t=0.1s$.
+The test is simulated using classical SPH with $\alpha = 1$.
+In this test, we still intentionally create non-uniform smoothing length distribution in space by assigning larger smoothing length to boundary ghost particles at the left side.
+But we take $h=h_a$.
+No numerical perturbation generated near the left boundary.}
+\label{fig:Perturbation-ME0-tp1}
+\end{figure}
+
+Adaptive smoothing length is now an essential component of SPH method.
+It naturely results to nonuniform smoothing length in space.
+Variation range of smoothing length would be especially larger for compressible flow.
+Fortunately, there are several factors counteracting against the numerical oscillation:
+\begin{itemize}
+\item Numerical dissipation decays such numerical oscillation preventing accumulation of oscilation magnitude.
+\item For incompressible flow or weakly compressible flow, smoothing length only varies in a small range.
+\item Well developed adaptive smoothing length algorithm usually guarantees more ``smoothing" change of smoothing length in space avoiding sharp change of smoothing length in space.
+\end{itemize}
+So we do not think that the numerical oscillation is a challenging issue for SPH. The major motivation of the appendix is to show that 
+\begin{itemize}
+\item The numerical oscillation does exist
+\item Dissipation decays the oscillation, so the the numerical oscillation can serve as an indicator of dissipation.
+\end{itemize}
 \section*{References}

### 2018-12-21 Response to Reviewers.tex
Response

@@
 The comments by the reviewers are recited in italics, followed by our reply in upright font.
-Revisions are highlighted with blue.
+Detailed revisions are described separately in "a summary-of-revisions.pdf".
 Equation, section, figure and reference numbers in our response are corresponding to these in the original
@@
 
-We would like to thank the reviewer for carefully reading our manuscript and giving positive review and critical remarks.
+We would like to thank the reviewer for carefully reading our manuscript and giving a positive review and critical remarks.
 We have revised the manuscript as described in the separate documentation and we hope that we have dealt with all suggestions in an adequate manner. The revised manuscript is also attached.
@@
 
-To response reviewer's recommendation for comparing 1D tests in present article with these 1D tests by \citet{puri2014approximate}:
+To respond to the reviewer's recommendation for comparing 1D tests in present article with these 1D tests by \citet{puri2014approximate}:
 
-The present method adopts HLLC and Roe approximate Riemann solvers presented in \citep{puri2014approximate}.
+The present method merely adopts HLLC and Roe approximate Riemann solvers presented in \citep{puri2014approximate}.
 We did not make any improvement in term of approximate Riemann solvers.
 In that sense, these GSPH results in our paper are similar to these tests in \citep{puri2014approximate}, which combines GSPH with Riemann solvers proposed in that paper.
-Or in other words, we have already done such comparison in current paper.
+Or in other words, we have already done (at least similar) comparison in current paper.
 But we need to mention two sources of differences.
-First of all, we adopted first order GSPH while tests in \citep{puri2014approximate} using second order GSPH.
-The reason why we use first order GSPH instead of second order GSPH is that we want to do ``well controlled" comparison.
-So that we can show the pure effect of ``random choice".
+First of all, we adopted a first order GSPH while most tests in \citep{puri2014approximate} use second order GSPH.
+The reason why we use first order GSPH instead of second order GSPH is that Riemann problem construction (RPC) in RSPH is the same as RPC in first order GSPH.
+We want to do ``well controlled" comparison to show the pure effect of ``random choice".
 Secondly, the shock tube tests adopted in our manuscript are very similar to these presented in \citep{puri2014approximate}, however, they are not exactly the same.
-We intentionally assign different densities to particles at left side and right side.
-This can lead to nonuniform smoothing length distribution in space and induce numerical oscillation.
+We intentionally assign different densities to particles at left side and right side in some of our 1D tests.
+This can lead to nonuniform smoothing length in space and induce more obvious numerical oscillation.
 More details are explained in appendix B of the revised manuscript.
@@
 The motivation and innovative point of the present method is to introduce numerical dissipation in a more adaptive manner, hence introduce less smearing around discontinuities.
-In that sense, the present work can be considered as ``higher numerical accurate", even though it is NOT ``higher order of accuracy".
-Another feature that made present method to be ``higher accurate" is its capability to better suppressing pressure wiggle at contact discontinuity.
+In that sense, the present work can be considered as `` more numerically accurate", even though it is NOT ``higher order of accuracy".
+Another feature that makes the present method  ``more accurate" is its capability to better suppress pressure wiggle at contact discontinuity.
 Both features have been demonstrated in 1D tests.
@@
 Thanks for helping us find another merit of RSPH.
-Compared with second order GSPH, the present method would be, at least slightly, faster (due to less computation for RP construction) on expense of lower order of accuracy.
+Compared with second order GSPH, the present method would be, at least slightly, faster (due to less computation for RP construction) at the expense of lower order of accuracy.
 \\[3pt]
@@
 
-We agree with reviewer. We added an appendix to introduce RCM with a little bit more details. More references are also provided there.\\[3pt]
+We agree with reviewer. We added an appendix to introduce RCM with more details. More references are also provided there.\\[3pt]
 
@@
 The large oscillations in these 1D shock tube tests actually are very critical in demonstrating the merit of present method.
-Such oscillations are caused by nonuniform smoothing length distribution in space.
+Such oscillations are caused by nonuniform smoothing length distribution in space (As explained in Appendix B in the revised manuscript).
 For 1D shock tube tests, smoothing lengths are usually not uniform in space.
-However, due to existence of sufficient numerical dissipation, such osciallations decay fast so are not obviously observed in previous tests.
+However, due to existence of sufficient numerical dissipation, such oscillations decay fast so are not obviously observed in most tests.
 In Fig 3, for example, we can not observe oscillation when $\alpha =1$ and $\alpha = 2$.
 When numerical dissipation is small ($\alpha = 0.2$), such oscillations are not completely suppressed and can be seen.
-Based on such observation, we use ``how much the oscillation get suppressed" as an indirect indicator for numerical dissipation.
+Based on such observation, we use ``how much of the oscillation gets suppressed" as an indirect indicator for numerical dissipation.
 Our following discussions are based on such correlation between observable oscillation and numerical dissipation.
@@
 Such discontinuity in term of resolution is the source of numerical oscillation.
-In revised manuscript, we addressed these points.
+In the revised manuscript, we addressed these points.
 We also added an appendix explaining the mechanism for generating numerical oscillations.
@@
 
-Figure for SPH results were removed while we forgot to update the caption, which makes Figure 12 to be confusing. We revised the caption in our revised manuscript.
+Figure for SPH results were moved to a separate figure while we forgot to update the caption, which makes Figure 12 to be confusing. We revised the caption in our revised manuscript.
 
@@
 The reviewer actually asked two questions here.
+
 With respect to the first question, yes, in our manuscript, we only compared RSPH with first order GSPH while GSPH could be second order as mentioned by the reviewer.
@@
 Namely, RCM (which were proposed in mesh based methods) adopts a ``piece wise constant" way when constructing Riemann problems.
-This should be a disadvantage of RSPH compared with second order GSPH.
-It is not surprise to us that we observe first order of accuracy in our tests as we were testing first order GSPH.
+This should be a disadvantage of RSPH compared with (second order) GSPH.
+It is not a surprise to us that we observe first order of accuracy in our tests as we were testing first order GSPH.
 
-With respect to the second question, yes, that statement would indeed cause confusions to readers. We added more explicit explanation in revised manuscript.
+With respect to the second question, yes, that statement would indeed cause confusion to readers. We added more explicit explanation in revised manuscript.
 \\[3pt]
@@
 
-[13] indeed shown that GSPH can almost get rid of pressure wiggle around contact discontinuity while standard SPH shows much more obvious pressure wiggle.
+[13] indeed show that GSPH can almost get rid of pressure wiggle around contact discontinuity while standard SPH shows much more obvious pressure wiggle.
 They believe that the pressure wiggle is due to the inconsistency of EoM (equation of momentum) of the standard SPH.
 Or in other words, just as what the reviewer mentioned: "The wiggle in the pressure at the contact discontinuity is due to the inconsistency of the standard SPH in evaluating pressure gradient force with a non-smooth distribution of particles." However, there are different opinions with respect to the sources of pressure wiggle.
-For example, other researchers believe that the pressure wiggle has something to do with thermal conduction at the contact discontinuity.
+For example, some other researchers believe that the pressure wiggle has something to do with thermal conduction at the contact discontinuity.
 It has been shown that thermal conduction is essential to mitigate the spurious pressure wiggle at contact discontinuity in SPH [e.g.
@@
 Explanation in [16] seems to be more reasonable.
-Our observation in our 1D shock tube tests shows that even though both RSPH and GSPH adopt EoM proposed in [15], the pressure wiggle still get suppressed.
+Our observation in our 1D shock tube tests shows that even though both RSPH and GSPH adopt EoM proposed in [15], the pressure wiggle is still  suppressed.
 So obviously, EoM might not be the real cause of pressure wiggle.
 
-The present method has many common things with GSPH.
+The present method has many things in common with GSPH.
 Particularly, both are based on solving local Riemann problems.
-Based on our observation that both GSPH and RSPH could suppress pressure wiggle in contact discontinuity.
-We tend to believe that the mechanism for present method to suppress pressure wiggle lies on the basis of present method: solving local Riemann problems.
-The capability of suppression pressure wiggle in contact discontinuity is indeed one attractive feature of present method.
+Based on our observation both GSPH and RSPH  can suppress the pressure wiggle in contact discontinuity.
+We tend to believe that the mechanism for present method to suppress pressure wiggle lies in the basis of the  present method: solving local Riemann problems.
+The capability to suppress pressure wiggle in contact discontinuity is indeed one attractive feature of present method.
 
@@
 It remains unclear why RSPH performs better than GSPH, i.e.
-why the random choice of <epsilon> makes such a difference.
+why the random choice of $\epsilon$ makes such a difference.
 It also remains unclear how well RSPH performs in critical multi-dimensional flows.
@@
 
-We appreciate the reviewer for reviewing our manuscript and giving constructive remarks. 
+We appreciate the reviewer for carefully reviewing our manuscript and giving constructive remarks. 
+%Some questions/confusion are general question for grid-based CFD.
+We will try to give detailed response.
+But we will not include these details in our revised manuscript to avoid being too disruptive to readers.
+We have made a careful revision and hope that we have dealt with all concerns/suggestions in an adequate manner. 
+The revised manuscript is also attached.
 %We understand that the reviewer has solid background in SPH but relatively less background in mesh based CFD (computational fluid dynamics) methods.
-Some questions/confusion are general question for mesh based CFD.
-We will try to give detailed response.
-But we might not include these details in our revised manuscript to avoid being too disruptive.
 
-Our response to reviewer's general critique is following.
+Our response to reviewer's general critique follows:.
 
@@
 Such advantage is well known in the context of \textbf{mesh based method}.
-The essential idea of GSPH, whose full name is Godunov SPH, is to implement Godunov's idea in the context of mesh free methods.
+The essential idea of GSPH, whose full name is Godunov SPH, is to migrate Godunov's idea to the context of mesh free methods.
 The essential idea of RSPH, is to implement the idea of ``random choice" in the context of mesh free methods.
-Why random choice method would introduce much less smear has been well studied and demonstrated by many applications.
-It is not possible to cover such topics in detail this article.
-Considering the fact that some readers might not be familiar with random choice method. We added an appendix introduce RCM method with more references.
+Why random choice method would introduce much less smear has been well studied and demonstrated by many applications in mesh based CFD.
+It is not possible to cover such topics in detail in the limited space available in this article.
+Considering the fact that some readers might not be familiar with random choice method. We added an appendix introducing RCM method with more references.
 
-The attractive features of RSPH actually have been demonstrated in 1D tests. However, some points are not clearly delivered. We will address these points in the revised manuscript.
+The attractive features of RSPH actually have been well demonstrated in 1D tests. However, some points are not clearly delivered. We address these points in the revised manuscript.
 
 As for 3D test case, the effective overall-dissipation is measured indirectly by the length that the 3D jet flow reaches in given time.
-We can still conclude that the effective overall-dissipation introduced by RSPH is smaller than that of GSPH.
-More work would be necessary to explore its implementation in 3D.
-Adopting different test cases might reveal more features of RSPH in different scenarios.
-But implementing RSPH in different scenarios are not major consideration of this article.
+We can still come to the conclusion that the effective overall-dissipation introduced by RSPH is smaller than that of GSPH.
+More work is necessary to explore its implementation in 3D.
+This is not the first priority of the very first paper on RSPH communicating the core idea.
+Adopting different test cases might reveal more features and some shortcomings of RSPH in different scenarios.
+But implementing RSPH in different scenarios are not the major goals of this article.
 \\[12pt]
@@
 Thanks for pointing this out.
-Our research focus more on high speed compressible flow and we were not able aware of the purpose of AV in a more general sense.
-For implementations of SPH in high speed compressible flow, the oscillation around discontinuities, especially aroud shocks can be too large or even corrupt whole simulation.
+Our research focus  on high speed compressible flow and we were not specific about the purpose of  AV in a more general sense.
+For implementations of SPH in high speed compressible flow, the oscillation around discontinuities, especially around shocks can be too large to even corrupt the whole simulation.
+For an extreme example, using SPH to do shock tube test with very small artificial viscosity (e.g.
+$\alpha = 0.01$),  ends up with huge oscillations or a failure of the solver.
 In that sense, AV helps to reduce oscillation at discontinuities.
-So our statement is not as general as it should be, but still make sense in certain application area.
+So our statement is not as general as it should be, but still make sense in the context of the application.
 \\[3pt]
@@
 
-We miss the reviewer's opinion here.
+We are confused by the reviewer's opinion here.
 Do you mean: 
@@
 
-2) AV is related to failure to resolve discontinuities (note, include but not limited to contact discontinuities)?
+2) AV is related to failure to resolve discontinuities (include but not limited to contact discontinuities)?
 
-If what you mean is 1). our response is:
+If opinion is 1). our response is:
 
+We also believe AV is not the source of pressure wiggle around contact discontinuity.
 We never say ``pressure wiggle" is due to AV.
-Instead, we prefer to agreeing with Price's view with respect to the source of ``pressure wiggle".
+Instead, we agree with Price's view with respect to the source of ``pressure wiggle".
 As we mentioned in our response to another reviewer, thermal conduction can help mitigate ``pressure wiggle".
@@
 
-We do believe AV causes some issues when resolve discontinuities (not only contact discontinuities).
-That is, AV usually smears (or smooth out) discontinuities.
+We do believe AV causes some issues in resolving discontinuities (not only contact discontinuities).
+That is, AV usually smears (or smooths out) discontinuities.
 Mathematically, discontinuity should be zero width, however, numerically, discontinuity would have width.
@@
 For example, in subplot c) of Fig.
-3.
-larger AV (with $\alpha = 2$, the red dash line) lead to a wider approximation of the shock (which is discontinuity in theory) than smaller AV (with $\alpha = 1$, the purple line).
+3 in this article, larger AV (with $\alpha = 2$, the red dash line) lead to a wider approximation of the shock (which is discontinuity in theory) than smaller AV (with $\alpha = 1$, the purple line).
 Such wider approximation of discontinuity should not be considered as \textbf{failure} to resolve discontinuities.
@@
 It is more than necessary to borrow well developed ideas from mesh based method to SPH.
-More importantly, both RCM and Godnuov's idea take the hyperbolicity of the system into account.
-The advantages of such treatment are not only introduce implicit (and adaptive) AV.
-Both GSPH and RSPH could also better suppress ``pressure wiggle" around contact discontinuity.
-The under underneath mechanism also relies on properly considering of system's hyperbolicity.
+More importantly, both RCM and Godnuov's idea take the hyperbolicity of the system into account and the advantages of such treatment are not only to introduce implicit (and adaptive) AV but both GSPH and RSPH also suppress the ``pressure wiggle" around contact discontinuity.
+The underlying mechanism for suppressing the wiggles  relies on properly considering of system's hyperbolicity.
 
-Response to reviewer's requests that we need to provide evidence for their bold claim that (the most advanced of) these methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist"
-
-These "highly tuned versions of artificial viscosity", as far as our understanding, none of them take the hyperbolicity of the system into account.
-How could these methods properly accommodate every kind waves without considering the property of system?
-Our claim is not bold at all.
+We would like to respond to reviewer's requests that we need to provide evidence for our claim that (the most advanced of) that these highly tuned SPH methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist" by stating that
+these "highly tuned versions of artificial viscosity", as far as we know, do not take the hyperbolicity of the system into account.
+It is unlikely that these methods properly accommodate every kind of wave without considering the property of system.
+Our claim is not really bold at all.
 
 The reviewer mentioned ``These methods are by now widely used in SPH models of compressive flows".
-With respect to these implementations, we are wondering what is the fluid speed?
-How accurate are they?
-Which physical quantities are of interest in these implementations (smearing of discontinuities might be acceptable for some implementations as there is not demands for resolving discontinuities as true discontinuities)?
+With respect to these implementations, we  would like to understand for What is the fluid speeds?
+How accurate are they?c and Which physical quantities are of interest in these implementations (smearing of discontinuities might be acceptable for some implementations as there is no requirement for resolving discontinuities as true discontinuities)?.
 We did not check all of these "highly tuned versions of artificial viscosity" in depth.
@@
 Some other researchers also reported the same thing, for example [12].
+You can image that how could we manually adjust parameters for real implementations in higher dimension?
 \\[3pt]
 
-\textit{p1/2 The motivation of the new scheme via partially unjustified critique of artificial viscosity) is unnecessary and divisive. A much
+\textit{p1/2 The motivation of the new scheme via partially unjustified critique of artificial viscosity is unnecessary and divisive. A much
 better/correct motivation of RSPH would be as an improvement over standard GSPH.}
 
-One of our original motivation indeed is to develop a method that can apply AV in a more ``smart" way. Even though the method turned out to have other attractive features.
-The current way to add artificial viscosity does have some limitation and can be improved even though they work well in some implementations.
-Compared with GSPH, RSPH do have some advantages while it also has some disadvantages. The major disadvantage is that RSPH can only be 1st order of accuracy.
+Our original motivations indeed was to develop a method that can apply AV in a more ``smart" way even though the method turned out to have other attractive features.
+The current way to add artificial viscosity in standard SPH does have some limitations and can be improved even though they work well in some implementations.
+Compared with GSPH, RSPH does have some advantages while it also has some disadvantages. The major disadvantage is that RSPH can only be 1st order of accuracy.
 We do not view RSPH as an improved version of GSPH, instead they should be two parallel methods.
-Because historically, RCM and Godunov's methods were developed (within the area of mesh based methods) parallely even though they share many common places.
+Because historically, RCM and Godunov's methods were developed (within the area of mesh based methods) parallely even though they share many common features.
 \\[3pt]
@@
 
-We prefer to viewing RSPH as counterpart of RCM in SPH while viewing GSPH as counterpart of Godunov's method in SPH. 
-RSPH can only be first order even with regular particle distribution because the local Riemann problem is defined in a piece-wise constant manner.
-Not because the irregular distribution of particles.
-GSPH, would also be first order accuracy if its local Riemann problems are also defined in a piece-wise constant manner.
-However, GSPH could be second order of accuracy with regular particle distribution \textbf{and} ``piece-wise linear" construction of its local Riemann problem.
-However, GSPH would be between first order of accuracy its local Riemann problem is defined in a piece-wise linear manner \textbf{but} the particle distribution is irregular.
-We added these discussions in revised paper.
+Yes, the irregular distribution of particles is one  major thing that prevents SPH schemes (standard SPH, GSPH and RSPH) to be second order.
+Besides that, for both GSPH and RSPH, how to construct the local Riemann problem would also affect order of accuracy.
+Standard SPH, can be maximum second order of accuracy.
+As for grid methods, things are different.
+Order of accuracy could be as high as needed.
+For example, for finite difference, we can easily achieve that by inlcuding more nodes in approximation.
+This is one disadvantage of SPH compared with standard SPH.
+As for Riemann-solver-based grid methods, the bottle neck is the order of accuracy when constructing local Riemann problems.
+Local Riemann problems can be constructed in piece-wise constant manner (zeroth order), piece-wise linear manner (first order) and so on ...
+
+We added discussions regarding irregular particle distributions in revised manuscript.
 \\[3pt]
@@
 
-Surely higher dimensional problem are more challenging and make more sense in real applications. 
+Surely higher dimensional problems are more challenging and make important sense in real applications. 
 But 1D tests do have several great merits.
@@
 2) 1D tests provide a solid basis for exploring basic property of a new method.
+3)Computationally fast and easy to implement, so are handy tools for learning/initial investigating/comparing numerical methods.
 
 What's more, even though trivial, there is still space for improvement for 1D tests.
-Many variants of SPH scheme can capture the position of different waves while most of them suffer from some common issues such as smearing of discontinuities, pressure wiggles around contact discontinuity, over shoot near other discontinuities.
+Many variants of SPH scheme can capture the position of different waves while most of them suffer from some common issues such as smearing of discontinuities, pressure wiggles around contact discontinuity and over shoot near other discontinuities.
 There is no variants of SPH method can perfectly handle all these issue.
@@
 Thanks for pointing this out. We tried these two, For 1D tests case, it does not make visible difference. But for 3D, it did make some visible difference but did not change our conclusion.
+
+By the way, the truncated Gaussian, if truncated at 3 times of smoothing length, which is adopted in our implementation, would add up to 0.9974. The difference is less than 0.3 percent. 
+In terms of deficiency near boundary, we did adopt a "re-normalization" strategy in the 3D tests.
+We did not mention such details as we feel such technical detail is not related to the major point we try to deliver in this article and would be distractive for readers.
+When implementing RSPH, one can choose to use whichever kernel  is appropriate for the application of interest.
 \\[3pt]
@@
 For this paper, first order scheme should be acceptable.
-Please be notified that all of our test cases adopting the same time integration scheme, in that sense, our comparison are still ``well controlled".
+Please note that all of our test cases adopt the same time integration scheme, in that sense, our comparisons are still ``well controlled".
 RSPH can be combined with higher order time integration scheme.
@@
 
-\textit{p.7 In eqs (21,22) <rho>(x) is not the true fluid density, but only the SPH density estimate.
+\textit{p.7 In eqs (21,22) $\rho(x)$ is not the true fluid density, but only the SPH density estimate.
 These two are different fields and must be carefully distinguished to avoid confusion and incorrect conclusions.}
@@
 Iterative Riemann solvers and non-iterative Riemann solvers have been well studied.
-There are many papers \citep[][e.g.]{roe1981approximate} and books \citep[][e.g.]{toro2013riemann} on this topic, really not necessary to cover any detail in this article.
+There are many papers and books \citep[][e.g.]{toro2013riemann} on this topic, really not necessary to cover any detail in this article.
 \\[3pt]
@@
 
-\textit{p.9 The choice of a random final midpoint <epsilon> appears absurd.
+\textit{p.9 The choice of a random final midpoint  $\epsilon$ appears absurd.
 This must be better motivated/explained.
-I think this point sits at the very heart of the paper: why should using a random <epsilon> (instead of <epsilon>=0) improve the method?
+I think this point sits at the very heart of the paper: why should using a random $\epsilon$(instead of $\epsilon>=0$ improve the method?
 Also, what is the motivation for the exact midpoint as the initial discontinuity of the Riemann problem?
@@
 Is this random?
-What motivates using the same value of <epsilon> for all particle pairs?
+What motivates using the same value of $\epsilon$ for all particle pairs?
 Doesn't this defy the purpose of randomization?
@@
 
-The choice of a random final midpoint <epsilon> does sit at the very heart of the paper.
+The choice of a random final midpoint $\epsilon$ does sit at the very heart of the paper.
 We added an appendix to cover more details with respect to RCM method.
-Reviewer's questions, such as why using a random <epsilon>, why such random <epsilon> help introduce much less smearing of the discontinuities, what motivates using the same value of <epsilon> for all particle pairs, Doesn't this defy the purpose of randomization and introduce artificial correlations?
+Reviewer's questions, such as why are we using a random $\epsilon$, why asuch random $\epsilon$ help introduce much less smearing of the discontinuities, what motivates using the same value of $\epsilon$ for all particle pairs, Doesn't this defy the purpose of randomization and introduce artificial correlations?
 had been asked and answered in the context of mesh based method.
@@
 We do not have to use the exact middle point.
-Different way of determining the initial discontinuity would results to different variants of RSPH.
-Maybe determining initial discontinuity based on particle mass.
-The property of these variants of RSPH is yet to explore.
+Different way of determining the initial discontinuity would result in different variants of RSPH.
+Once could for e.g.
+determine initial discontinuity based on particle mass.
+The property of these variants of RSPH are yet to be explored.
 
@@
 But traditionally, it was called pseudo-random \citep[][e.g.]{toro2013riemann}.
-Should we follow the tradition of RCM or using more correct phrase?
+We have chosen to follow the tradition of RCM rather than using the more correct phrase.
 
-The idea of using a different <epsilon> for every interacting particle pair was actually another variants of RCM. These two different manners turned out to have similar properties. 
+The idea of using a different $\epsilon$ for every interacting particle pair was actually another variant of RCM. These two different manners turned out to have similar properties. 
 \\[3pt]
@@
 \textit{p.11/12 The summary of the 1D test cases is somewhat confusing.
-The initial conditions are not best explained in Table 1: where is the boundary?
+The initial conditions are not best explained in Table 1: Where is the boundary?
 What is the physical meaning of negative-pressure ideal gas?
 (Standard SPH is unstable to clumping in the presence of negative pressure.)
-These tests do not provide a good testsuite. Most operate at similar Mach numbers, albeit with different arrangements/initial conditions. It would
+These tests do not provide a good test suite. Most operate at similar Mach numbers, albeit with different arrangements/initial conditions. It would
 be desirable to test discontinuous initial conditions with a wider range of Mach numbers, from 0.1 to 100. The Mach number should be given in Table 1.}
@@
 
-The tests case adopted here are actually very representive to test \textbf{different wave patterns}.
+The tests case adopted here are actually very representative to test \textbf{different wave patterns}.
 These 1D tests are all well known 1D tests used by both mesh based method \citep[][e.g.]{toro2013riemann, leveque2002finite} and SPH tests \citep[][e.g.]{monaghan1983shock, cha2003implementations, puri2014approximate}.
-Mach number can be easily calculated according to physical quantities. We added Mach number in Table 1 in revised manuscript. 
+Mach number can be easily calculated according to physical quantities and is a function of time and space.
+We are confused about which Mach number the reviewer is asking for, at which time, at which location?
+We claim that our 1D tests are comprehensive because they can cover all possible wave patterns that could arise in 1D and two extreme cases.
 \\[3pt]
 
-\textit{Figs 2,3 Are these really "oscillations around shock" for <alpha>=0.2 SPH? I suspect that instead we have inter-particle penetration, i.e.
+\textit{Figs 2,3 Are these really "oscillations around shock" for $\alpha = 0.2 SPH$? I suspect that instead we have inter-particle penetration, i.e.
 particles swapping positions in 1D SPH.
@@
 
+Reviewer's questions are answered separately in following:
+
+\textit{Figs 2,3 Are these really "oscillations around shock" for $\alpha =0.2 SPH$? I suspect that instead we have inter-particle penetration, i.e.
+particles swapping positions in 1D SPH. Also, in this figure, isn't the interpretation of oscillation==less viscosity rather simplistic? }
+
 They are really oscillations.
-Such oscillations are caused by non-uniform smoothing length (due to uniform particle mass and nonuniform density in space).
+Such oscillations are caused by nonuniform smoothing length in space (due to uniform particle mass and nonuniform density in space).
 We added an appendix to explain the source of such oscillation in the revised manuscript.
+Besides oscillation, we also use another indirect indicator for viscosity for 1D tests, that is, how much the shock is smeared.
+Both indicators of numerical dissipation (viscosity) reveal consistent information.
+
+More importantly, in SPH tests, where we can control the amount of viscosity explicitly by using different artificial viscosity coefficients, these two indicators reflect consistent information.
+For example, in plot c) of Fig.
+3, smaller artificial viscosity coefficients lead to less smearing of shock (narrower width) and larger oscillation.
+This just proves that, the oscillation and the degree the shock is smeared are effective and valid indicator of viscosity.
 
@@
 
-Using internal energy?
 We are a bit confused on how to measure the dissipative heating.
-The correlation between oscillation can be demonstrated by these tests with different artificial viscosity coefficients.
+Using increases of internal energy?
+Internal energy is plotted for all of the 1D tests.
+We can barely see any increase in terms of internal energy.
+But the correlation between oscillation and viscosity is demonstrated by these SPH tests with different artificial viscosity coefficients.
+So practically, oscillation is an effective way to measure viscosity.
 
-We tried to combine 2\&3 and 4\&5. But it would be too large to fit into one page. Inlet plots make it harder to see these details we want to show.
+\textit{I think it'd be better to combine Figs 2\& 3 into one, similar to Fig 4.}
+
+We tried to combine 2\&3 and 4\&5. But it would be too large to fit into one page. Inlet plots make it harder to see the details we want to show.
+
+\textit{Only one legend is required, not 8. Moreover, the details may be shown as inlet plots.}
 
@@
 
-\textit{p.13-15 I think comparing against <alpha>=2 or 0.2 SPH has little merit.
-A comparison to <alpha>=1 SPH makes sense as does a comparison (lacking)
+\textit{p.13-15 I think comparing against $\alpha = 2 or 0.2 $SPH has little merit.
+A comparison to $\alpha=1$ SPH makes sense as does a comparison (lacking)
 against an AV-switch version of SPH.}
 
-Both <alpha>=2 and 0.2 are necessary.
-Comparison of three different values confirms the effect AV, which is the basis of for our further discussion.
+Both $\alpha = 2 or 0.2 $ and 0.2 are necessary.
+Comparison of three different artificial viscosity coefficients in SPH confirms how could AV affects the oscillation, how could VA smear the shock and how could AV affect the distance between nozzle and the front of jet flow.
+Those are the basis of for our further discussion.
 If we only have two different artificial viscosity coefficients sets, some other readers might argue that our comparison is not generic enough.
@@
 This can easily lead to ``unfair" comparison.
-In addition, the major difference between RSPH and AV-switch version of SPH is so obvious -- RSPH does not require explicit AV.
+In addition, the major difference between RSPH and AV-switch version of SPH is  obvious -- RSPH does not require explicit AV.
 \\[3pt]
@@
 But Godunov's method is different from RCM.
-They do share some common places but surely are different. If they are the same (or nothing new), how could RSPH introduce AV in a more adaptive manner as shown by these tests.
+They do share some common places but surely are different. If they are the same (or nothing new), how could RSPH introduce AV in a more adaptive manner as shown by many tests.
 
@@
 \textit{p.16 What is the difference between the RSPH and GSPH-HLLC schemes? Is it
-merely the choice of <epsilon>?
+merely the choice of $\epsilon$?
 I.e.
-is GSPH-HLLC == RSPH with <epsilon>=0?
+is GSPH-HLLC == RSPH with $epsilon$=0?
 If not, what else is different?
@@
 
-Yes, choice of <epsilon> is the only difference between \textbf{first order} GSPH-HLLC (GSPH can be second order). That is to say, \textbf{first order} GSPH-HLLC == RSPH with <epsilon>=0.
+Yes, choice of $\epsilon$ is the only difference between \textbf{first order} GSPH-HLLC (GSPH can be second order). That is to say, \textbf{first order} GSPH-HLLC == RSPH with $\epsilon$=0.
 But this is NOT a small difference.
-By the way, since choice of <epsilon> is the only difference, our tests are ``well controlled" comparison, that is to say, the difference in tests results do reflect the essential effect of different choice of <epsilon>.
+By the way, since choice of $\epsilon$ is the only difference, our tests are ``well controlled" comparison, that is to say, the difference in tests results do reflect the essential effect of different choice of $epsilon$.
 We hope reviewer can appreciate such manner of comparisons.
 
-Why choice of <epsilon> can make such big difference? This is the heart of RCM.
+Why choice of $epsilon$ can make such big difference? This is the heart of RCM. We explained it a little bit in Appendix A in the revised paper. 
 \\[3pt]
@@
 these waves are related to the correlations introduced by using the same
-<epsilon> for all particle pairs (when their wavelength may be comparable
+$epsilon$ for all particle pairs (when their wavelength may be comparable
 to / scale with h).}
 
-Good question. We added an appendix to explain the source of these waves.
+Good question. We added an appendix to explain the source of these waves (oscillations).
 \\[3pt]
@@
 \textit{p.17 While simple 1D shock-tube problems are good tests for proof-of-concept implementations, they are not representative of
-multi-dimensional flows and cannot be used to reliably validate any scheme. Thus, most tests in §4.2 are meaningless to that end.
+multi-dimensional flows and cannot be used to reliably validate any scheme. Thus, most tests in 4.2 are meaningless to that end.
 A good test (where SPH performs poorly regardless of AV) is the Gresho-Chan vortex test (2D) run over at least one rotation period.}
@@
 
-Thanks, we modified this section to clean up confusions.
+Thanks, we modified this section to clear up any confusion.
 \\[3pt]

### 2018-12-22 Response to Reviewers.tex
for final submit

@@
 The comments by the reviewers are recited in italics, followed by our reply in upright font.
-Detailed revisions are described separately in "a summary-of-revisions.pdf".
+Detailed revisions are shown separately in "a-summary-of-revisions.pdf".
 Equation, section, figure and reference numbers in our response are corresponding to these in the original
-version of JCP manuscript if not specified. \\[12pt]
+version of JCP manuscript if not specified.
+We highlighted revsions in revised manuscript.
+Revisions made for first reviewer are highlighted in red.
+Revisions made for the second reviewer are highlighted in green.
+Revisions made for both are highlighted in yellow.
+Many of revisions are actually made for both reviewers and across sections.
+So we recommend to check the file "a-summary-of-revisions.pdf" for more subtle changes.
+\\[12pt]
 
@@
 
-We would like to thank the reviewer for carefully reading our manuscript and giving a positive review and critical remarks.
-We have revised the manuscript as described in the separate documentation and we hope that we have dealt with all suggestions in an adequate manner. The revised manuscript is also attached.
+We would like to thank the reviewer for carefully reading our manuscript and giving positive review and critical remarks.
+We have revised the manuscript as described in the separate documentation and we hope that we have dealt with all concerns in an adequate manner. The revised manuscript is also attached.
 
@@
 
-To respond to the reviewer's recommendation for comparing 1D tests in present article with these 1D tests by \citet{puri2014approximate}:
+To response to the reviewer's recommendation for comparing 1D tests in present article with these 1D tests by \citet{puri2014approximate}:
 
@@
 But we need to mention two sources of differences.
-First of all, we adopted a first order GSPH while most tests in \citep{puri2014approximate} use second order GSPH.
+First of all, we adopted piece wise constant RP construction in both GSPH and RSPH while tests in \citep{puri2014approximate} using piece wise linear RP construction.
 The reason why we use first order GSPH instead of second order GSPH is that Riemann problem construction (RPC) in RSPH is the same as RPC in first order GSPH.
@@
 More details are explained in appendix B of the revised manuscript.
+Considering it is a common practice for GSPH to use piece wise linear RP construction.
+We added comparison between RSPH and GSPH using  piece wise linear RP construction. 
+[See Fig. 5 p. on 19 and 1st paragraph on p. 20]
 
@@
 The motivation and innovative point of the present method is to introduce numerical dissipation in a more adaptive manner, hence introduce less smearing around discontinuities.
-In that sense, the present work can be considered as `` more numerically accurate", even though it is NOT ``higher order of accuracy".
-Another feature that makes the present method  ``more accurate" is its capability to better suppress pressure wiggle at contact discontinuity.
+In that sense, the present work can be considered as ``more numerically accurate", even though it is NOT ``higher order of accuracy".
+Another feature that makes present method ``more accurate" is its capability to better suppress pressure wiggle at contact discontinuity.
 Both features have been demonstrated in 1D tests.
@@
 
-Thanks for helping us find another merit of RSPH.
-Compared with second order GSPH, the present method would be, at least slightly, faster (due to less computation for RP construction) at the expense of lower order of accuracy.
-\\[3pt]
-%Compared with first order GSPH, it will not be faster. So the computational  speed would be a normal feature of present method instead of an attractive feature. 
-%By adopting approximate Riemann solver, the present work would be computationally faster than RCM methods using iterative Riemann solver.
-If all previous RCM method is using iterative Riemann solver, then we may claim that it is the first time to combine RCM with non-iterative Riemann solver.
-And this would be another innovative point of our paper.
+Thanks for helping us find another merit of RSPH. Compared with second order GSPH, the present method would be, at least slightly, faster (due to less computation associated with RP construction).
+[See last two sentence in 1st paragraph on p. 20 in revised manuscript] \\[3pt]
 
@@
 
-We agree with reviewer. We added an appendix to introduce RCM with more details. More references are also provided there.\\[3pt]
+We agree with reviewer. We added an appendix to introduce RCM with more details. More references are also provided there.
+[See Appendix A on p. 30 to p. 32 in revised manuscript]\\[3pt]
 
@@
 Such discontinuity in term of resolution is the source of numerical oscillation.
-In the revised manuscript, we addressed these points.
+In revised manuscript, we addressed these points.
 We also added an appendix explaining the mechanism for generating numerical oscillations.
+[See Appendix B on p. 32 to p. 38 in revised manuscript]
 \\[3pt]
-%need to show that equal density can help reduce oscillation.
-%For compressible flow, smoothing lengths.
-Unfortunately the original manuscript did not delivery this point clearly.
-The shock tube tests were intentionally designed to make such oscillation more obvious by assigning different particles masses.
-In all shock tube tests presented in previous work, uniform particle mass is adopted while in our manuscript, different particle mass are assigned for particles on right side and left side.
-Different particle mass will amplify the oscillation and help to demonstrate the merit of present method in a more obvious manner.
 
@@
 Figure for SPH results were moved to a separate figure while we forgot to update the caption, which makes Figure 12 to be confusing. We revised the caption in our revised manuscript.
-
-We want to mention here that in both GSPH and the present method, the way to handle velocity that perpendicular to local coordinate system need to be improved.
-There are (at least) two different ways to handle the perpendicular velocity component.
-See [13] and [15].
-We are adopting [13]'s method in section 4.4.
+[See Fig. 13 p. 28 in revised manuscript]
 \\[3pt]
@@
 This should be a disadvantage of RSPH compared with (second order) GSPH.
-It is not a surprise to us that we observe first order of accuracy in our tests as we were testing first order GSPH.
+It is not surprise to us that we observe first order of accuracy in our tests as we were testing first order GSPH.
 
-With respect to the second question, yes, that statement would indeed cause confusion to readers. We added more explicit explanation in revised manuscript.
+With respect to the second question, yes, that statement would indeed cause confusions to readers. We added more explicit explanation in revised manuscript.
+[See last paragraph on p. 20 and first two paragraphs in revised manuscript] 
 \\[3pt]
@@
 Particularly, both are based on solving local Riemann problems.
-Based on our observation both GSPH and RSPH  can suppress the pressure wiggle in contact discontinuity.
+Based on our observation that both GSPH and RSPH can suppress the pressure wiggle in contact discontinuity.
 We tend to believe that the mechanism for present method to suppress pressure wiggle lies in the basis of the present method: solving local Riemann problems.
@@
 It remains unclear why RSPH performs better than GSPH, i.e.
-why the random choice of $\epsilon$ makes such a difference.
+why the random choice of <epsilon> makes such a difference.
 It also remains unclear how well RSPH performs in critical multi-dimensional flows.
@@
 We appreciate the reviewer for carefully reviewing our manuscript and giving constructive remarks.
-%Some questions/confusion are general question for grid-based CFD.
-We will try to give detailed response.
-But we will not include these details in our revised manuscript to avoid being too disruptive to readers.
-We have made a careful revision and hope that we have dealt with all concerns/suggestions in an adequate manner. 
-The revised manuscript is also attached.
-%We understand that the reviewer has solid background in SPH but relatively less background in mesh based CFD (computational fluid dynamics) methods.
+We have made careful revision and hope that we have dealt with all concerns/suggestions in an adequate manner.
 
-Our response to reviewer's general critique follows:.
+Our response to reviewer's general critique follows.
 
@@
 The attractive features of RSPH actually have been well demonstrated in 1D tests. However, some points are not clearly delivered. We address these points in the revised manuscript.
+[See last paragraph on p. 12 and p. 13 in revised manuscript.]
 
@@
 More work is necessary to explore its implementation in 3D.
-This is not the first priority of the very first paper on RSPH communicating the core idea.
+This is not the first priority of the very first paper on RSPH comunicating the core idea.
 Adopting different test cases might reveal more features and some shortcomings of RSPH in different scenarios.
-But implementing RSPH in different scenarios are not the major goals of this article.
+But implementing RSPH in different scenarios are not major goal of this article.
+[See line 179 to the end of p. 13 in revised manuscript.]
 \\[12pt]
-%We also want to mention that, for higher dimensional implementation of RSPH and GSPH, how to approximate the velocity component that perpendicular to the local coordinate system is still not well understood.
-For example, there are two different approaches adopted by GSPH (see [13], [16], [17]).
-However, neither of them seems to be sufficient.
-This is a common topic for both GSPH and RSPH, not only for RSPH.
-In our implementation, we adopt the method used by [13] and [16].
 
@@
 Our research focus on high speed compressible flow and we were not specific about the purpose of AV in a more general sense.
-For implementations of SPH in high speed compressible flow, the oscillation around discontinuities, especially around shocks can be too large to even corrupt the whole simulation.
+For implementations of SPH in high speed compressible flow, the oscillation around discontinuities, especially around shocks can be too large to even corrupt whole simulation.
 For an extreme example, using SPH to do shock tube test with very small artificial viscosity (e.g.
-$\alpha = 0.01$),  ends up with huge oscillations or a failure of the solver.
+$\alpha = 0.01$), ends up huge osciallation or a failure of the solver.
 In that sense, AV helps to reduce oscillation at discontinuities.
-So our statement is not as general as it should be, but still make sense in the context of the application.
+So our statement is not as general as it should be, but still make sense in the context of application.
+[See first sentence in Abstract in revised manuscript.]
 \\[3pt]
@@
 
-We are confused by the reviewer's opinion here.
+We are confused about the reviewer's opinion here.
 Do you mean: 
@@
 
-We do believe AV causes some issues in resolving discontinuities (not only contact discontinuities).
+We do believe AV causes some issues is solving discontinuities (not only contact discontinuities).
 That is, AV usually smears (or smooths out) discontinuities.
@@
 More importantly, both RCM and Godnuov's idea take the hyperbolicity of the system into account and the advantages of such treatment are not only to introduce implicit (and adaptive) AV but both GSPH and RSPH also suppress the ``pressure wiggle" around contact discontinuity.
-The underlying mechanism for suppressing the wiggles  relies on properly considering of system's hyperbolicity.
+The underlying mechanism for supressing the wiggles relies on properly considering of system's hyperbolicity.
 
-We would like to respond to reviewer's requests that we need to provide evidence for our claim that (the most advanced of) that these highly tuned SPH methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist" by stating that
-these "highly tuned versions of artificial viscosity", as far as we know, do not take the hyperbolicity of the system into account.
-It is unlikely that these methods properly accommodate every kind of wave without considering the property of system.
+We would like to response to reviewer's requests that we need to provide evidence for our claim that (the most advanced of) that these highly tuned SPH methods "cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist" by stating that these "highly tuned versions of artificial viscosity", as far as we know, do not take the hyperbolicity of the system into account.
+It is unlikely that these methods properly accommodate every kind of waves without considering the property of system.
 Our claim is not really bold at all.
@@
 The reviewer mentioned ``These methods are by now widely used in SPH models of compressive flows".
-With respect to these implementations, we  would like to understand for What is the fluid speeds?
-How accurate are they?c and Which physical quantities are of interest in these implementations (smearing of discontinuities might be acceptable for some implementations as there is no requirement for resolving discontinuities as true discontinuities)?.
+With respect to these implementations, we would liket to understand for what is the fluid speeds?
+How accurate are they?
+and which physical quantities are of interest in these implementations (smearing of discontinuities might be acceptable for some implementations as there is not requirements for resolving discontinuities as true discontinuities if detailed flow field structure are not of interest)?
 We did not check all of these "highly tuned versions of artificial viscosity" in depth.
@@
 
-\textit{p1/2 The motivation of the new scheme via partially unjustified critique of artificial viscosity is unnecessary and divisive. A much
+\textit{p1/2 The motivation of the new scheme via partially unjustified critique of artificial viscosity) is unnecessary and divisive. A much
 better/correct motivation of RSPH would be as an improvement over standard GSPH.}
 
-Our original motivations indeed was to develop a method that can apply AV in a more ``smart" way even though the method turned out to have other attractive features.
+Our original motivation indeed was to develop a method that can apply AV in a more ``smart" way even though the method turned out to have other attractive features.
 The current way to add artificial viscosity in standard SPH does have some limitations and can be improved even though they work well in some implementations.
-Compared with GSPH, RSPH does have some advantages while it also has some disadvantages. The major disadvantage is that RSPH can only be 1st order of accuracy.
+Compared with GSPH, RSPH does have some advantages while it also has some disadvantages. The major disadvantage is that RSPH can only adopt piece wise constant Riemann problem construction.
 We do not view RSPH as an improved version of GSPH, instead they should be two parallel methods.
@@
 For example, for finite difference, we can easily achieve that by inlcuding more nodes in approximation.
-This is one disadvantage of SPH compared with standard SPH.
+This is one disadvantage of SPH compared with mesh based method.
 As for Riemann-solver-based grid methods, the bottle neck is the order of accuracy when constructing local Riemann problems.
@@
 
-We added discussions regarding irregular particle distributions in revised manuscript.
+We added discussions regarding irregular particle distributions in revised manuscript. [See line 262 to 272 on p. 30 and p. 31 in revised manuscript.]
 \\[3pt]
@@
 2) 1D tests provide a solid basis for exploring basic property of a new method.
-3)Computationally fast and easy to implement, so are handy tools for learning/initial investigating/comparing numerical methods.
+3)Computationally fast and easy to implement, so are handy tools for learning, initial investigating or comparing different numerical methods.
 
@@
 There is no variants of SPH method can perfectly handle all these issue.
+In that sense, it is not that trival.
 
@@
 By the way, the truncated Gaussian, if truncated at 3 times of smoothing length, which is adopted in our implementation, would add up to 0.9974. The difference is less than 0.3 percent. 
-In terms of deficiency near boundary, we did adopt a "re-normalization" strategy in the 3D tests.
-We did not mention such details as we feel such technical detail is not related to the major point we try to deliver in this article and would be distractive for readers.
-When implementing RSPH, one can choose to use whichever kernel  is appropriate for the application of interest.
+In terms of deficiency near boundray, we did adopt a "re-normalization" strategy in the 3D tests.
+We did not mention such details as we feel such technical detail is not related to the major point we are try to delivery in this article and would be distractive for readers.
+When implementing RSPH, one can choose to use whichever kernel if approproate for the application of interest.
 \\[3pt]
@@
 Please note that all of our test cases adopt the same time integration scheme, in that sense, our comparisons are still ``well controlled".
-RSPH can be combined with higher order time integration scheme.
+RSPH can be combined with higher order time integration schemes.
 \\[3pt]
@@
 
-We modified the symbol in revised version.
+We modified the symbol in revised version. [See Eq. 21 to 22 on p. 7 in revised manuscript.]
 \\[3pt]
@@
 
-Iterative Riemann solvers and non-iterative Riemann solvers have been well studied.
-There are many papers and books \citep[][e.g.]{toro2013riemann} on this topic, really not necessary to cover any detail in this article.
+Iterative Riemann solvers and non-iterative Riemann solvers have been well studied for many years.
+There are many papers \citep[][e.g.]{roe1981approximate} and books \citep[][e.g.]{toro2013riemann} on this topic, really not necessary to cover any details.
 \\[3pt]
@@
 Thanks, we have added the full phrase of HLLC in revised manuscripts.
+[See line 94 on p. 8 in revised manuscript.]
 \\[3pt]
@@
 This must be better motivated/explained.
-I think this point sits at the very heart of the paper: why should using a random $\epsilon$(instead of $\epsilon>=0$ improve the method?
+I think this point sits at the very heart of the paper: why should using a random $\epsilon$ (instead of $\epsilon$=0) improve the method?
 Also, what is the motivation for the exact midpoint as the initial discontinuity of the Riemann problem?
@@
 We added an appendix to cover more details with respect to RCM method.
-Reviewer's questions, such as why are we using a random $\epsilon$, why asuch random $\epsilon$ help introduce much less smearing of the discontinuities, what motivates using the same value of $\epsilon$ for all particle pairs, Doesn't this defy the purpose of randomization and introduce artificial correlations?
+Reviewer's questions, such as why are we using a random $\epsilon$, why a such random $\epsilon$ help introduce much less smearing of the discontinuities, what motivates using the same value of $\epsilon$ for all particle pairs, Doesn't this defy the purpose of randomization and introduce artificial correlations?
 had been asked and answered in the context of mesh based method.
 RSPH is the counterpart of RCM (which was previously proposed in mesh based method) in SPH.
-Discussions on these topics can be found in these papers.
 
@@
 We do not have to use the exact middle point.
-Different way of determining the initial discontinuity would result in different variants of RSPH.
-Once could for e.g.
-determine initial discontinuity based on particle mass.
-The property of these variants of RSPH are yet to be explored.
+Different way of determining the initial discontinuity would results to different variants of RSPH.
+One could, for example, determineinitial discontinuity based on particle mass.
+The property of these variants of RSPH are yet to explore.
+[Add comments at line 377 to line 379 on p.
+30 in revised manuscript.]
 
@@
 Whether positive direction of local coordinate system is from a to b or from b to a will NOT change the results as long as all the steps (projection from global to local, constructing of local Riemann problem and projection back from local to global) are using consistent local coordinate system (positive direction).
+More details can be found in the first GSPH paper[13].
 \\[3pt]
@@
 Thanks, we cleaned up these confusing points in revised manuscript. 
+[See Fig. 13 on p. 8 in revised manuscript.]
 \\[3pt]
@@
 So why should this work?
-What happens if instead pseudo-random numbers are used and/or if a different <epsilon> is drawn for every interacting particle pair?}
+What happens if instead pseudo-random numbers are used and/or if a different $\epsilon$ is drawn for every interacting particle pair?}
 
@@
 But traditionally, it was called pseudo-random \citep[][e.g.]{toro2013riemann}.
-We have chosen to follow the tradition of RCM rather than using the more correct phrase.
+We have choosen to follow the tradition of RCM rather than using more correct phrase.
 
 The idea of using a different $\epsilon$ for every interacting particle pair was actually another variant of RCM. These two different manners turned out to have similar properties. 
+[See line 396 to 397 on p. 31 in revised manuscript.]
 \\[3pt]
@@
 \textit{p.11/12 The summary of the 1D test cases is somewhat confusing.
-The initial conditions are not best explained in Table 1: Where is the boundary?
+The initial conditions are not best explained in Table 1: where is the boundary?
 What is the physical meaning of negative-pressure ideal gas?
 (Standard SPH is unstable to clumping in the presence of negative pressure.)
-These tests do not provide a good test suite. Most operate at similar Mach numbers, albeit with different arrangements/initial conditions. It would
+These tests do not provide a good testsuite. Most operate at similar Mach numbers, albeit with different arrangements/initial conditions. It would
 be desirable to test discontinuous initial conditions with a wider range of Mach numbers, from 0.1 to 100. The Mach number should be given in Table 1.}
@@
 These 1D tests are all well known 1D tests used by both mesh based method \citep[][e.g.]{toro2013riemann, leveque2002finite} and SPH tests \citep[][e.g.]{monaghan1983shock, cha2003implementations, puri2014approximate}.
-Mach number can be easily calculated according to physical quantities and is a function of time and space.
+
+Mach number can be easily calculated according to physical quantities and \textbf{is a function of time and space}.
 We are confused about which Mach number the reviewer is asking for, at which time, at which location?
@@
 
-\textit{Figs 2,3 Are these really "oscillations around shock" for $\alpha = 0.2 SPH$? I suspect that instead we have inter-particle penetration, i.e.
+\textit{Figs 2,3 Are these really "oscillations around shock" for $\alpha$=0.2 SPH? I suspect that instead we have inter-particle penetration, i.e.
 particles swapping positions in 1D SPH.
@@
 
-\textit{Figs 2,3 Are these really "oscillations around shock" for $\alpha =0.2 SPH$? I suspect that instead we have inter-particle penetration, i.e.
+\textit{Figs 2,3 Are these really "oscillations around shock" for $\alpha$=0.2 SPH? I suspect that instead we have inter-particle penetration, i.e.
 particles swapping positions in 1D SPH. Also, in this figure, isn't the interpretation of oscillation==less viscosity rather simplistic? }
@@
 This just proves that, the oscillation and the degree the shock is smeared are effective and valid indicator of viscosity.
+[Modifications to address these concerns are accross section 4, appendix A and appendix B in revised manuscript.]
 
@@
 So practically, oscillation is an effective way to measure viscosity.
+[Explanations to address these concerns are accross section 4, appendix A and appendix B in revised manuscript.]
 
@@
 We made modification as suggested by reviewer regarding legend. 
-\\[3pt]
+[See Fig. 2 to 11 in section 4 in revised manuscript.]\\[3pt]
 
-\textit{p.13-15 I think comparing against $\alpha = 2 or 0.2 $SPH has little merit.
-A comparison to $\alpha=1$ SPH makes sense as does a comparison (lacking)
+\textit{p.13-15 I think comparing against $\alpha$=2 or 0.2 SPH has little merit.
+A comparison to $\alpha$=1 SPH makes sense as does a comparison (lacking)
 against an AV-switch version of SPH.}
 
-Both $\alpha = 2 or 0.2 $ and 0.2 are necessary.
-Comparison of three different artificial viscosity coefficients in SPH confirms how could AV affects the oscillation, how could VA smear the shock and how could AV affect the distance between nozzle and the front of jet flow.
+Both $\alpha$=2 and 0.2 are necessary.
+Comparison of three different artificial viscosity coefficients in SPH confirms how could AV affect the oscillation, how could AV smear the shock and how could AV affect the distance between nozzle and the front of jet flow.
 Those are the basis of for our further discussion.
-If we only have two different artificial viscosity coefficients sets, some other readers might argue that our comparison is not generic enough.
+If we only have two different artificial viscosity coefficients sets, some other readers might argue that our comparison is not general enough.
 
@@
 This can easily lead to ``unfair" comparison.
-In addition, the major difference between RSPH and AV-switch version of SPH is  obvious -- RSPH does not require explicit AV.
+In addition, the major difference between RSPH and AV-switch version of SPH is so obvious -- RSPH does not require explicit AV.
 \\[3pt]
@@
 
-RSPH samples solution of local Riemann problem in a very different way from GSPH. This is NOT a small difference.
+RSPH samples solution of local Riemann problem in a very different way from GSPH.
+This is NOT a small difference.
+Just like RCM and Godunov's method are considered as two different method in mesh based CFD methods.
 \\[3pt]
@@
 
-Changed in revised manuscript. 
+Colours are changed in revised manuscript, we also use thicker lines. 
+[See Fig. 4 in section 4 in revised manuscript.]
 \\[3pt]
@@
 I.e.
-is GSPH-HLLC == RSPH with $epsilon$=0?
+is GSPH-HLLC == RSPH with $\epsilon$=0?
 If not, what else is different?
@@
 But this is NOT a small difference.
-By the way, since choice of $\epsilon$ is the only difference, our tests are ``well controlled" comparison, that is to say, the difference in tests results do reflect the essential effect of different choice of $epsilon$.
+By the way, since choice of $\epsilon$ is the only difference, our tests are ``well controlled" comparison, that is to say, the difference in tests results do reflect the essential effect of different choice of $\epsilon$.
 We hope reviewer can appreciate such manner of comparisons.
 
-Why choice of $epsilon$ can make such big difference? This is the heart of RCM. We explained it a little bit in Appendix A in the revised paper. 
+Why choice of $\epsilon$ can make such big difference?
+This is the heart of RCM.
+We explained it a little bit in Appendix A in the revised paper.
+[See Fig.
+2 to 11 in section 4 in revised manuscript.]
 \\[3pt]
@@
 these waves are related to the correlations introduced by using the same
-$epsilon$ for all particle pairs (when their wavelength may be comparable
+$\epsilon$ for all particle pairs (when their wavelength may be comparable
 to / scale with h).}
@@
 Good question. We added an appendix to explain the source of these waves (oscillations).
+[See appendix B in revised manuscript.]
 \\[3pt]
@@
 \textit{p.17 While simple 1D shock-tube problems are good tests for proof-of-concept implementations, they are not representative of
-multi-dimensional flows and cannot be used to reliably validate any scheme. Thus, most tests in 4.2 are meaningless to that end.
+multi-dimensional flows and cannot be used to reliably validate any scheme. Thus, most tests in §4.2 are meaningless to that end.
 A good test (where SPH performs poorly regardless of AV) is the Gresho-Chan vortex test (2D) run over at least one rotation period.}
@@
 
-Thanks, we modified this section to clear up any confusion.
+Thanks, we modified this section to clean up any confusions.
+[See Fig. 13 on p. 28 in revised manuscript.]
 \\[3pt]

### 2018-12-22 ebp-JCPManuscript.tex
for final submit

@@
 \begin{abstract}
-The classical smoothed particle hydrodynamics (SPH) method employs explicit artificial viscosity to properly capture shock waves in high speed compressible flow.
+Implementation of the classical smoothed particle hydrodynamics (SPH) method in high-speed compressible flow employs explicit artificial viscosity to properly capture shock waves.
 This artificial viscosity typically produces more dissipation than is needed to smooth shocks, smears discontinuities, and can overwhelm fluid turbulence.
 Several studies have proposed highly tuned versions of artificial viscosity, turning on and off near shocks or other troublesome wave features.
-A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems as building blocks for a numerical SPH solver without explicit numerical dissipation term.
-Unfortunately, a first order Godunov solver still introduces an effective numerical diffusion that can infect the entire numerical solution.
+A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems as building blocks for a numerical SPH solver without explicit numerical dissipation term (GSPH).
+Unfortunately, a Godunov solver based on piece wise constant Riemann problem construction still introduces an effective numerical diffusion that can infect the entire numerical solution.
 We propose a novel SPH scheme that combines an approximate version of Glimm\rq{}s Random Choice method (RCM) with SPH.
@@
 This sub-section describes this GSPH method.
-Our discussion  anticipates that of Section \ref{sec:RSPH-method}, and sub-section \ref{sec:Picking-up-single-state} in particular, which contain details that are only briefly
-introduced here.
+Our discussion anticipates that of Section \ref{sec:RSPH-method}, and sub-section \ref{sec:Picking-up-single-state} in particular, which contain details that are only briefly introduced here.
 
@@
 The origin is at the middle of the paired two particles.
-The the local Riemann problem is defined by the constant states $(\rho, u, p)_a$ and $(\rho, u,p)_b$, namely $\textbf{W}_L = \textbf{W}_b$, $\textbf{W}_R = \textbf{W}_a$ with $\textbf{W} = (\rho, u,p)^T $, a vector representation of these three variables.
+The local Riemann problem is defined by the constant states $(\rho, u, p)_a$ and $(\rho, u,p)_b$, namely $\textbf{W}_L = \textbf{W}_b$, $\textbf{W}_R = \textbf{W}_a$ with $\textbf{W} = (\rho, u,p)^T $, a vector representation of these three variables.
 The horizontal bold solid line at time $\Delta t$ indicates the interval on which to evaluate the solution of the Riemann problem.
@@
 The red ellipse indicates the stationary state, which is the starred state in GSPH.
-$S_L$, $S_M$ and $S_R$ are singal speeds which are linerized locally in HLLC Riemann solvers \citep{puri2014approximate}.
+$S_L$, $S_M$ and $S_R$ are signal speeds which are linearized locally in HLLC Riemann solvers \citep{puri2014approximate}.
 Starred region is divided into two sub-regions by the middle contact wave.
-Only $\rho$ changes across the contact wave.
-}
+Only $\rho$ changes across the contact wave.}
     \label{fig:pick-up-state-GSPH-RSPH}
@@
 
-We mentioned that, instead of selecting an uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte}.
+We mentioned that, instead of selecting a uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte} (classified by some as a quairandom sequence).
 
@@
 We describe results from several numerical tests using SPH, RSPH and GSPH in this section.
-A 1D shock tube test is investigated in different aspects to compare standard SPH, first order GSPH and RSPH revealling several features of RSPH.
+A 1D shock tube test is investigated in different aspects to compare standard SPH, GSPH and RSPH revealing several features of RSPH.
 More shock tube simulations are also conducted to check the capacity of RSPH for different wave patterns.
@@
 In the last subsection we describe a 3D free jet flow simulation.
-The effect of equivalent overall dissipation is first demonstrated by SPH simulation with different artificial viscosity coefficients.
-Then the equivalent overall dissipations introduced by first order GSPH and RSPH are compared demonstrating that RSPH introduces less dissipation than first order GSPH.
+The effect of equivalent numerical dissipation is first demonstrated by SPH simulation with different artificial viscosity coefficients.
+Then the equivalent numerical dissipations introduced by GSPH and RSPH are compared demonstrating that RSPH introduces less dissipation than GSPH.
+In 3D fee jet flow simulation, local Riemann problems are constructed in a piece wise constant manner for both GSPH and RSPH.
 
@@
 \ref{fig:RCM-Sod-SPH-alf-zoom}).
-That is to say, how much the numerical oscillation is suppressed can indicate the amount of numerical dissipation introduced in each SPH scheme providing we are solving invisid fluids (no physical dissipation).
+That is to say, how much the numerical oscillation is suppressed can indicate the amount of numerical dissipation introduced in each SPH scheme providing we are solving inviscid fluids (no physical dissipation).
 Refer Appendix B for more information regarding the numerical oscillation due to nonuniform smoothing length.
@@
 We take these two as indicators of numerical dissipation in many discussions regarding 1D tests.
-As for 3D jet flow, we take the distance between jet head and inject vent at the same physical time as the indicator of overall equivalent numerical dissipation.
+As for 3D jet flow, we take the distance between jet head and inject vent at given physical time as the indicator of overall equivalent numerical dissipation.
 As shown in Fig.
@@
 $\alpha,\beta$ satisfies: $\beta=2\alpha$.
-c), d) are corresponding zoomed views, showing that numerical oscillation is obvious, especially around shock, due to insufficient dissipation when $\alpha=0.2$.
-The dissipation introduced by RSPH.
-on the other hand, is adaptive, introducing more damping at the shock (comparable to $\alpha=1.0$) and less damping in the area away from the shock (less than $\alpha=0.2$, as indicated by the magnitude of numerical oscillation).}
+c), d) are corresponding zoomed views.
+SPH simulations with different artificial viscosity coefficients show that numerical oscillation is obvious, especially around shock, if there is insufficient dissipation ($\alpha=0.2$).
+The dissipation introduced by RSPH, is shown to be more adaptive, introducing more damping at the shock (comparable to $\alpha=1.0$) and less damping in the area away from the shock (less than $\alpha=0.2$, as indicated by the magnitude of numerical oscillation).}
     \label{fig:RCM-Sod-SPH-alf}
@@
 Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}).
-Wiggle in test 1, however, is completely eliminated by both GSPH and RSPH.
+Pressure wiggle in test 1, however, is completely eliminated by both GSPH and RSPH.
 
@@
 
-Zoomed views in Fig.
-\ref{fig:RCM-Sod-GSPH} compare GSPH and RSPH and demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH.
+RSPH is proposed to construct local Riemann problem in a piece wise constant manner while GSPH can adopt different ways for local Riemann problem construction.
+Besides piece wise constant construction of local Riemann problem, GSPH can also use piece wise linear construction or even higher order.
+In purpose of ``well-controlled" comparison, we first compare RSPH with GSPH using piece wise constant Riemann problem construction.
+The only difference between RSPH and piece wise constant GSPH is how to sample the solution of local Riemann problems.
+By such ``well-controlled" comparison, we can reveal the pure effect of random choice, the very heart of RSPH.
+Considering it is more popular for GSPH to construct local Riemann problem in a piece wise linear manner, we also compared RSPH with piece wise linear GSPH.
+
+Fig.
+\ref{fig:RCM-Sod-GSPH} compares piece wise constant GSPH and RSPH demonstrating that RSPH introduces less but sufficient dissipation compared with piece wise constant GSPH.
 The attractive feature of RCM method in preserving true discontinuity is inherited by RSPH in this 1D shock tube test.
@@
 
+\begin{figure}[H]
+    \centering
+    \begin{minipage}{.45\textwidth}
+        \centering a)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-rho}
+    \end{minipage}%
+    \begin{minipage}{.545\textwidth}
+    \centering b)
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-v}    
+        \end{flushleft}
+    \end{minipage}% 
+    \\
+    \begin{minipage}{.45\textwidth}
+        \centering c)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-e}
+    \end{minipage}%
+    \begin{minipage}{.545 \textwidth}
+        \centering d)
+        \includegraphics[width=0.99 \textwidth,height=0.4954\textwidth]{./Figures/RCM-Sod-GSPH2-compare-p}
+    \end{minipage}% 
+    \\
+    \begin{minipage}{.45\textwidth}
+        \centering e)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-rho-zoom}
+    \end{minipage}%
+    \begin{minipage}{.545\textwidth}
+    \centering f)
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-v-zoom}    
+        \end{flushleft}
+    \end{minipage}%  
+       \\
+    \begin{minipage}{.45 \textwidth}
+        \centering g)
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-e-zoom}
+    \end{minipage}% 
+    \begin{minipage}{.545\textwidth}
+    \centering h)
+        \begin{flushleft}
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-p-zoom}    
+        \end{flushleft}
+    \end{minipage}%     
+    \caption{Comparison of RSPH against GSPH with different local Riemann problem construction.
+Riemann problem for RSPH is constructed in a piece wise constant manner while those for GSPH are constructed in either piece wise constant manner (``1st-GSPH") or piece wise linear manner (``2nd-GSPH").
+All methods adopt HLLC Riemann solver.
+The last four plots are corresponding zoomed views.
+``2nd-GSPH" shows better solution than ``1st-GSPH", which is just as expected.
+Compared with RSPH, ``2nd-GSPH" obtains almost as good results as RSPH.
+But it is still visible that more smearing at the shock is introduce by ``2nd-GSPH" than RSPH.
+Surprisely, pressure wiggle become more obvious when GSPH constructing local Riemann problem in a piece wise linear manner.}
+    \label{fig:RCM-Sod-GSPH2}
+\end{figure}
+
+It is more common for GSPH to construct local Riemann problems in a piece wise linear manner.
+Fig.
+\ref{fig:RCM-Sod-GSPH2} RSPH and piece wise linear GSPH.
+As expected, when using higer order local Riemann problem construction, better solutions are obtained.
+Adopting piece wise linear Riemann problem construction reduces the amount of dissipation and hence smearing of the shocks.
+RSPH, even though is based on piece wise constant Riemann problem construction, still introduces less numerical dissipation than GSPH using piece wise linear Riemann problem construction.
+The piece wise linear Riemann problem construction requires calculation of first order derivatives while the piece wise constant manner does not.
+That is to say, the piece wise constant manner is computationally less expensive than the piece wise linear manner.
+As a consequence, RSPH would be, at least a little bit, faster than piece wise linear GSPH.
+
 \subsection{Accuracy tests}
@@
 \ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the density, velocity and pressure profiles for different SPH schemes.
+
+Due to symmetry of kernel function, estimation of density (Eq.
+(\ref{eq:ns-sph-d})) in SPH can reach second order of accuracy if all particles distribute in space with uniform interval.
+However, such ideal situation is very rare.
+Due to irregular particle distribution, we usually observe order of accuracy between 1 and 2.
+Besides the particle distribution in space, which has major affect on order of accuracy of SPH, some other aspects would also influence order of accuracy.
+For SPH schemes that depend on solving Riemann problems, how the local Riemann problem is constructed also influence order of accuracy.
+For GSPH, the Riemann problem can be constructed in piece wise constant manner, piece wise linear manner or even higher order \citep{inutsuka2002reformulation}.
+For RSPH, we can only consider to construct local Riemann problems in the piece wise constant manner.
+When using other higher order construction of local Riemann problem, how to determine the range for ``random choice" is not clear.
+This is a limitation of current RSPH compared with GSPH.
+With simper Riemann problem construction, RSPH is expected to be faster than GSPH adopting higher order Riemann problem construction.
+To compare RSPH and GSPH in a well-controlled manner, all GSPH tests presented in this paper are based on piece wise constant construction of local Riemann problems.
+
 We observe a rate of convergence of approximately 1 for GSPH and 1.5 for standard SPH and RSPH.
@@
 For example,
-GSPH combined with HLLC and Roe approximate Riemann solvers has been shown to be approximately second order of accuracy \citep{puri2014comparison} and comparable in accuracy to the standard SPH schemes when using piece wise linear construction.
-Presence of discontinuities, such as shock, in the test problem might lower the rate of convergence.
-
-Since both RSPH and GSPH tests in this paper adopt the same manner for Riemann problem construction, the piece wise constant construction.
+GSPH combined with HLLC and Roe approximate Riemann solvers has been shown to be approximately second order of accuracy \citep{puri2014comparison} and comparable in accuracy to the standard SPH schemes when construct local Riemann problem in a piece wise linear manners.
+Presence of discontinuities, such as shock, in the test problem might lead to more irregular distribution of particles and lower the rate of convergence.
+
+Since both RSPH and GSPH tests in this paper adopt the same manner for Riemann problem construction.
 We conclude that RSPH shows higher order of accuracy than GSPH providing both use the same Riemann problem construction.
@@
 Due to less amount of dissipation, the numerical oscillations, which is due to nonuniform smoothing length as discussed in Appendix B, persist in all simulation results.
-For the strong blast test and double shock test, such oscillation become more obvious than other tests, even though, the magnitude of fluctuations is within an acceptable range.
+For the strong blast test and double shock test, such oscillation becomes more obvious than other tests, even though, the magnitude of fluctuations is within an acceptable range.
 
@@
 
-Setup of the 3D test is summaried briefly below.
+Setup of the 3D test is summarized briefly below.
 The computational domain is a box and boundaries are categorized into three types: the velocity inlet (a circular area at the center of the bottom of the box), the non-slip wall boundary (box bottom) and the pressure outlet (other faces of the box) boundary.
@@
    \centering
-    \begin{minipage}[t]{.325\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf2-t3-cutView}
-    \end{minipage}%
-    \begin{minipage}[t]{.325 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alf1-t3-cutView}
-    \end{minipage}%
-    \begin{minipage}[t]{.325\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/SPH-alfp3-t3-cutView}
-    \end{minipage}%
+   \includegraphics[width=0.95 \textwidth]{./Figures/SPH-3D-jet}
    \caption{Free jet flow simulation results at $t=3.0 s$ by SPH using different artificial viscosity coefficients.
@@
 Another artificial viscosity coefficient $\beta$ is set to be double of $\alpha$ for all tests.
-Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.}
+Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.
+A positive correlation between overall damping effect and the distance from nozzle to the front of jet flow is shown.}
     \label{fig:free-jet-SPH-comparison}
@@
 These pictures are front view of a slice of the domain cut by two planes parallel to $x-z$ plane at $y=-9$ and $y=9$.
-Pictures to the left is for GSPH while those on the right side are for RSPH.
+Pictures on the left side are for GSPH while those on the right side are for RSPH.
 Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.
@@
 Figure \ref{fig:free-jet-SPH-comparison} shows simulation results of the free jet flow by SPH with different artificial viscosity coefficients.
-The positive correlation between overall damping effect (due to artificial dissipation) and the distance from nozzle to the front of jet flow is clearly shown in this figure.
-At $t=3.0 s$ after jet flow starting, we observe that the distance between front of jet flow and nozzle are different when using different artificial viscosity coefficients.
-Standard SPH adds artificial dissipation explicitly through the artificial viscosity term.
-The amount of artificial dissipation is positively related to artificial viscosity coefficients.
-The artificial dissipation is the total dissipation as there is no physical dissipation in the governing equations.
-It is obvious that the larger the artificial viscosity coefficients, the smaller the distance between the nozzel and the front of free jet flow.
-So the distance between nozzel and front of free jet flow can be used as an indicator of equivalent overall dissipation.
-While introducing undesirable damping effects, artificial viscosity is necessary for numerical stability and simulating of shocks.
-So, in real applications, the artificial viscosity coefficients are usually tuned (see, for example, \citep{cao2018plume}) to minimize artificial damping effects.
-Our comparison between GSPH and RSPH in next paragraph is based on the positive correlation between equivalent overall dissipation and the distance from nozzle to the front of jet flow.
-
-We compare RSPH with GSPH in terms of equivalent overall artificial damping effects in Fig.
+A positive correlation between overall damping effect (due to artificial dissipation) and the distance from nozzle to the front of jet flow is clearly shown in this figure.
+At $t=3.0 s$ after jet flow starting, we observe that the distances between the front of the jet flow and the nozzle increase when artificial viscosity coefficients decrease.
+The standard SPH adds artificial dissipation explicitly through the artificial viscosity term.
+The amount of artificial dissipation positively depends on artificial viscosity coefficients.
+In addition, there is no physical dissipation in the governing equations.
+So the numerical dissipation is the total dissipation.
+As shown in Fig.
+\ref{fig:free-jet-SPH-comparison}, the larger the artificial viscosity coefficients, the smaller the distance between the nozzle and the front of free jet flow.
+So the distance between nozzle and the front of free jet flow can be used as an indicator of equivalent numerical dissipation.
+Our comparison between GSPH and RSPH in the next paragraph is based on the positive correlation between equivalent numerical dissipation and the distance from nozzle to the front of jet flow.
+
+We compare RSPH with GSPH in terms of overall damping effects in Fig.
 \ref{fig:free-jet-comparison}.
 Different from SPH, both GSPH and RSPH introduce artificial viscosity in an implicit way by solving local Riemann problems.
-Based on the positive correlation between overall damping effect and the distance between the nozzle and the front of jet flow, we can still infer the amount equivalent overall dissipation introduced by RSPH and GSPH.
+Based on the positive correlation between overall damping effect and the distance between the nozzle and the front of jet flow, we can infer the amount of equivalent numerical dissipation introduced by RSPH and GSPH.
 It has been shown in 1D tests that RSPH can introduce less artificial viscosity than GSPH.
@@
 Instead, any viscosity that is used in a hydrodynamics simulation is just what the user implicitly adds.
-This control is important in applications with very strong shocks. 
+This control is important in applications with strong shocks. 
 Unlike classical SPH which uses the same artificial viscosity coefficients everywhere, RSPH introduces larger dissipation around the shock to guarantee numerical stability while introduces much smaller dissipation elsewhere.
@@
 This may be particularly important when applying RSPH to other systems, where the explicit construction on which the HLLC solver rests is not readily available.
+In current implementation, the ``interface" between two particles are set at the middle.
+Alternative ways to determine the interface is also worthwhile to explore.
 
@@
 NSF ACI/1131074 from the National Science Foundation.
+We want to give thanks to anonymous reviewers for their constructive comments.
 
@@
 The first part explains the mechanism how the numerical oscillations are induced by non-uniform smoothing length in space.
-The second parts  shows a ``manmade" numerical oscillation, which backs up our analysis in first part.
+The second parts  shows a ``manmade" numerical oscillation, which backs up our analysis in the first part.
 
@@
 However, it could also lead to numerical oscillation when applying the averaged smoothing length formulation in these scenarios with nonuniformly distributed smoothing length in space.
-Such numerical oscillation are usually either too small to observe or decays quickly due to sufficient numerical dissipation.
+Such numerical oscillation are usually either too small to observe or decays quickly due to sufficient (or too large) numerical dissipation.
 Such numerical oscillation is not fully aware of yet by the community.
@@
 
-Recall that the kernel function of particle $a$ is required to be symmetric with repect to particle $a$.
+Recall that the kernel function of particle $a$ is required to be symmetric with respect to particle $a$.
 As a result, the gradient of kernel function at particle $a$ is anti-symmetric.
@@
 The anti-symmetric properties of gradient of kernel function can guarantee the pressure gradient term, $\left(\dfrac{p_b}{\rho_b^2} + \dfrac{p_a}{\rho_a^2}\right) \nabla_a w_{a b}\left(h\right)$,  in momentum and energy equation (see Eq.
-(\ref{eq:ns-sph-v}) and (\ref{eq:ns-sph-e})) vanshes when pressure is uniform in space.
+(\ref{eq:ns-sph-v}) and (\ref{eq:ns-sph-e})), vanishes when pressure is uniform in space.
 For example, if pressure is uniform in space, pressure at particle $a$ and particle $b$ would be equal, the pressure gradient term then equals zero.
 That is, numerical approximation is consistent with real physics.
-However the actual kernel function is not symmetric any more if smoothing length is not uniform in space providing we adopt the averaged smoothing length formulation.
+However the actual kernel function is not symmetric any more if smoothing length is not uniform in space if we adopt the averaged smoothing length formulation.
 The gradient of kernel function is also not anti-symmetric any more.
@@
 This unphysical numerical representation of pressure gradient term could lead to numerical oscillation in numerical solution.
-Sharp changes in smoothing length can induce significant oscillation which usually propagates into the computational domain and corrupts numerical solution.
+Sharp changes in smoothing length can induce significant oscillation, which usually propagates into the computational domain and corrupts numerical solution.
 
@@
 \ref{fig:Perturbation-ME2}, the smoothing length is discontinuous at the left boundary.
-\textbf{Just like discontinuity of physical quantities (for example, the discontinuity at the middle of shock tube test), discontinuity in numerical resolution, in terms of smoothing length, also induces a wave.} A oscillation is observed clearly in the simulation result, starting near the left boundary and propagating into simulation domain.
+\textbf{Just like discontinuity of physical quantities (for example, the discontinuity at the middle of shock tube test), discontinuity in numerical resolution, in terms of smoothing length, also induces a wave.} An oscillation is observed clearly in the simulation result, starting near the left boundary and propagating into simulation domain.
 Recall that larger smoothing length for left boundary ghost particles is the only difference between normal test (as shown in Fig.
@@
 \ref{fig:Perturbation-ME0-tp1}.
-The oscillation is get rid of, which confirms that the averaged smoothing length is one of necessary conditions for the unphysical numerical representation of pressure gradient term.
+The oscillation is gotten rid of, which confirms that the averaged smoothing length is one of necessary conditions for the unphysical numerical representation of pressure gradient term.
 %Such perturbation would be created unintentionally in real implementation.
@@
 The second plot to last plot are corresponding to $t=0.05s$, $t=0.1s$, $t=0.2s$, $t=0.3s$ respectively.
-We observe that a numerical perturbation incepts near the left boundary and propogates into the domain.
+We observe that a numerical perturbation incepts near the left boundary and propagates into the domain.
 Actually, the smoothing length is also discontinuous at the middle.
@@
 \begin{itemize}
-\item Numerical dissipation decays such numerical oscillation preventing accumulation of oscilation magnitude.
+\item Numerical dissipation decays such numerical oscillation preventing accumulation of oscillation magnitude.
 \item For incompressible flow or weakly compressible flow, smoothing length only varies in a small range.
@@
 \begin{itemize}
-\item The numerical oscillation does exist
-\item Dissipation decays the oscillation, so the the numerical oscillation can serve as an indicator of dissipation.
+\item The numerical oscillation does exist commonly in SPH schemes. It is not something only for RSPH.
+\item Dissipation decays the oscillation, so numerical oscillation can serve as an indicator of dissipation.
 \end{itemize}

### 2019-10-28 ebp-JCPManuscript.tex
update tex file to use the new style file

@@
-\documentclass[review]{elsarticle}
-\usepackage{lineno,hyperref}
-% package added by zhixuan, not sure whether allowed by JCP or not!
+%% 
+%% Copyright 2007-2019 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%% 
+%% Template article for Elsevier's document class `elsarticle'
+%% with harvard style bibliographic references
+
+\documentclass[preprint,12pt,authoryear]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times,authoryear]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
+%% \documentclass[final,3p,times,authoryear]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
+%% \documentclass[final,5p,times,authoryear]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+%% The amsthm package provides extended theorem environments
+\usepackage{amsthm}
+% package added by zhixuan
 \usepackage{amsmath}
@@
 
-\modulolinenumbers[5]
-\journal{Journal of Computational Physics}
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Numbered
-\bibliographystyle{model1-num-names}
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-%% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
+
+\journal{Computer Methods in Applied Mechanics and Engineering}
 \begin{document}
@@
 \author{Zhixuan Cao}
+\ead{zhixuan.cao@ansys.com}
+\address{Fluids Business Unit, Ansys Inc., Lebanon, NH, 03766, USA}
 \author{Abani Patra \fnref{mycorrespondingauthor}}
-\address{Department of Mechanical and Aerospace Engineering, The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
+\ead{abani.patra@tufts.edu}
+\address{Department of Computer Science and Department of Mathematics, Tufts University, Medford, MA, 02153, USA}
 \author{E. Bruce Pitman}
-\address{Department of Materials Design and Innovation, The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
+\ead{pitman@buffalo.edu}
+\address{Department of Materials Design and Innovation, The State University of New York at Buffalo, Amherst, NY, 14260, USA}
 %\fntext[myfootnote]{Since 1880.}
@@
 %\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
-\fntext[mycorrespondingauthor]{abani@buffalo.edu}
+\cortext[mycorrespondingauthor]{Corresponding author}
 %\cortext[mycorrespondingauthor]{abani@buffalo.edu}
@@
 
-\linenumbers
 \section{Introduction}
@@
 \begin{equation}
-u^n = \left\{ \begin{array}{11}
+u^n = \begin{cases}
 	u_L ~~~ x< (j+\xi)\Delta x \\
  	u_R ~~~ x> (j+\xi)\Delta x
- 			\end{array}
-	  \right. 			
+	\end{cases}			
 \end{equation}
@@
 \begin{equation}
-u^{n+1} = \left\{\begin{array}{11}
+u^{n+1} = \begin{cases}
 		  u_L ~~~ x< (j+\tilde \xi)\Delta x + a \Delta t \\
 		  u_R ~~~ x> (j+\tilde \xi)\Delta x + a \Delta t
-		  \end{array}
-		  \right.
+	        \end{cases}
 \end{equation}
@@
 \section*{References}
-
+ \bibliographystyle{elsarticle-num} 
 \bibliography{Reference}

### 2020-12-30 ebp-JCPManuscript.tex
change the abstract plus some clean up

@@
 Implementation of the classical smoothed particle hydrodynamics (SPH) method in high-speed compressible flow employs explicit artificial viscosity to properly capture shock waves.
-This artificial viscosity typically produces more dissipation than is needed to smooth shocks, smears discontinuities, and can overwhelm fluid turbulence.
-Several studies have proposed highly tuned versions of artificial viscosity, turning on and off near shocks or other troublesome wave features.
-A different kind of solver adapts Godunov\rq{}s idea of solving local Riemann problems as building blocks for a numerical SPH solver without explicit numerical dissipation term (GSPH).
-Unfortunately, a Godunov solver based on piece wise constant Riemann problem construction still introduces an effective numerical diffusion that can infect the entire numerical solution.
+The amount of artificial viscosity introduced in this explicit way depends on coefficients of the artificial viscosity term.
 We propose a novel SPH scheme that combines an approximate version of Glimm\rq{}s Random Choice method (RCM) with SPH.
@@
 Our version approximately resolves hydrodynamic waves, and samples the approximate solution.
-No explicit artificial viscosity will be needed.
+The new scheme does not require explicit artificial viscosity term.
 We test this method on standard one dimensional shock tube problems and observe several attractive features.
-First of all, this method introduces adaptive artificial viscosity, assigning larger dissipation around discontinuities and smaller elsewhere.
-Secondly, it is less dissipative than classical SPH and GSPH resulting in less smearing of shock.
-Thirdly, as the new method can be viewed as generalized GSPH method in terms of sampling solutions of local Riemann problems, good features of GSPH are inherited, for example, ameliorating pressure ``wiggle" around contact discontinuity.
-When applied to three dimensional jet flow, this method is demonstrated to introduce less overall-dissipation than GSPH.
+This method introduces adaptive artificial viscosity, assigning larger dissipation around discontinuities and smaller elsewhere.
+Less smearing of discontinuity is introduced by this method in one dimensional shock tube tests.
+In addition, it also helps ameliorate pressure ``wiggle" around contact discontinuity.
+When applied to three dimensional jet flow, this method is demonstrated to introduce less overall-dissipation.
 %Our ultimate goal is to apply this method to jet flow.
@@
 \citep{monaghan1983shock, monaghan1997sph,klapp2012strong}. 
-This kind of viscosity, however, usually provides more dissipation than is truly needed at a discontinuity, and the excess dissipation ultimately corrupts the entire computation.
 Various methods have been introduced to tune the artificial viscosity, turning it on and off for particular wave features.
@@
 
-Later, Harten and Lax \cite{hartenlax} proposed approximately solving a Riemann problem based on a finite difference scheme, and sampling this approximate solution.
+Later, \citet{hartenlax} proposed approximately solving a Riemann problem based on a finite difference scheme, and sampling this approximate solution.
 Our approach here is based on the Harten-Lax proposal.
@@
 
-We mentioned that, instead of selecting a uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte} (classified by some as a quairandom sequence).
+We mentioned that, instead of selecting a uniformly distributed random number $\epsilon$, we follow \citet{colella1982glimm} and adopt the Van Der Corput pseudo-random number sequence \citep{hammersley2013monte}.
 
@@
     \end{minipage}%          
-    \caption{a),b) are plots for density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients.
+    \caption{a) and b) are plots for density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients.
 $\alpha,\beta$ satisfies: $\beta=2\alpha$.
@@
     \caption{
-    a),b) are plots of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients.
+    a), b) are plots of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients.
 c), d) are corresponding zoomed views.
@@
 \citet{inutsuka2002reformulation} show that GSPH can almost get rid of pressure wiggle around contact discontinuity while standard SPH has much more obvious pressure wiggle.
-They believe that the pressure wiggle is due to the inconsistency of equation of momentum in the standard SPH discretization.
+%They believe that the pressure wiggle is due to the inconsistency of equation of momentum in the standard SPH discretization.
 However, there are different opinions with respect to the sources of pressure wiggle.
 It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}.
-As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and helps suppress the anomaly \citep{puri2014approximate}.
+%As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and helps suppress the anomaly \citep{puri2014approximate}.
  Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}).
@@
         \centering e)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-rho-zoom}
+        \includegraphics[width= 0.99 \textwidth, height=0.625 \textwidth]{./Figures/RCM-Sod-GSPH-compare-p-zoom}    
     \end{minipage}%
@@
     \end{minipage}%  
-       \\
-    \begin{minipage}{.45 \textwidth}
-        \centering g)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-e-zoom}
-    \end{minipage}% 
-    \begin{minipage}{.545\textwidth}
-    \centering h)
-        \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-p-zoom}    
-        \end{flushleft}
-    \end{minipage}%     
+%    \begin{minipage}{.45\textwidth}
+%        \centering e)
+%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-rho-zoom}
+%    \end{minipage}%
+%    \begin{minipage}{.545\textwidth}
+%    \centering f)
+%        \begin{flushleft}
+%        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-v-zoom}    
+%        \end{flushleft}
+%    \end{minipage}%  
+%       \\
+%    \begin{minipage}{.45 \textwidth}
+%        \centering g)
+%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-e-zoom}
+%    \end{minipage}% 
+%    \begin{minipage}{.545\textwidth}
+%    \centering h)
+%        \begin{flushleft}
+%        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-p-zoom}    
+%        \end{flushleft}
+%    \end{minipage}%     
     \caption{Comparison of RSPH with first order GSPH using Roe Riemann solver and HLLC Riemann solver.
-The last four plots are zoomed views.
-Zoomed view of density and specific internal energy show that GSPH smears the discontinuity at shock much more than RSPH.
+The last two plots are zoomed views of pressure and velocity.
 Zoomed view of velocity shows that fluctuation in GSPH is completely suppressed, which implies that numerical dissipation introduced in GSPH is at least around the same amount as SPH with $\alpha=1.0$.
 This is consistent with information implied by zoomed view of density and specific internal energy.
-The last zoomed view shows that both RSPH and GSPH can get rid of pressure ``wiggle" around the contact discontinuity.}
+Zoomed view of pressure shows that both RSPH and GSPH can get rid of pressure ``wiggle" around the contact discontinuity.}
     \label{fig:RCM-Sod-GSPH}
@@
     \end{minipage}%  
-       \\
-    \begin{minipage}{.45 \textwidth}
-        \centering g)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-e-zoom}
-    \end{minipage}% 
-    \begin{minipage}{.545\textwidth}
-    \centering h)
-        \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-p-zoom}    
-        \end{flushleft}
-    \end{minipage}%     
+%       \\
+%    \begin{minipage}{.45 \textwidth}
+%        \centering g)
+%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-e-zoom}
+%    \end{minipage}% 
+%    \begin{minipage}{.545\textwidth}
+%    \centering h)
+%        \begin{flushleft}
+%        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-p-zoom}    
+%        \end{flushleft}
+%    \end{minipage}%     
     \caption{Comparison of RSPH against GSPH with different local Riemann problem construction.
@@
 All methods adopt HLLC Riemann solver.
-The last four plots are corresponding zoomed views.
+The last two plots are zoomed views of a) and b).
 ``2nd-GSPH" shows better solution than ``1st-GSPH", which is just as expected.
 Compared with RSPH, ``2nd-GSPH" obtains almost as good results as RSPH.
-But it is still visible that more smearing at the shock is introduce by ``2nd-GSPH" than RSPH.
-Surprisely, pressure wiggle become more obvious when GSPH constructing local Riemann problem in a piece wise linear manner.}
+But there is still visible that more smearing at the shock is introduce by ``2nd-GSPH" than RSPH.}
     \label{fig:RCM-Sod-GSPH2}
@@
 That is to say, the piece wise constant manner is computationally less expensive than the piece wise linear manner.
-As a consequence, RSPH would be, at least a little bit, faster than piece wise linear GSPH.
+As a consequence, RSPH would be, at least a little bit, computationally less expensive than piece wise linear GSPH.
 
@@
 \label{linear}
-\frac{\partial u}{\partial t }+ a \frac{\partial )}{\partial x} = 0
+\frac{\partial u}{\partial t }+ a \frac{\partial u}{\partial x} = 0
 \end{equation}
@@
 \includegraphics[width=0.90 \textwidth ]{App-Figure/dw-ha}
-\caption{In this example, we consider two pairs of particles $(a, b_1)$ and $(a b_2)$.
+\caption{In this example, we consider two pairs of particles $(a, b_1)$ and $(a, b_2)$.
 For simplicity, we assume uniform distance between particles.

### 2021-01-01 ebp-JCPManuscript.tex
change the abstract plus some clean up

@@
 The new scheme does not require explicit artificial viscosity term.
-We test this method on standard one dimensional shock tube problems and observe several attractive features.
-This method introduces adaptive artificial viscosity, assigning larger dissipation around discontinuities and smaller elsewhere.
-Less smearing of discontinuity is introduced by this method in one dimensional shock tube tests.
+We test this method on standard one dimensional shock tube problems.
+Beyond good capability of capturing shocks and other discontinuities, this method also introduces adaptive artificial viscosity, assigning larger dissipation around discontinuities and smaller elsewhere.
 In addition, it also helps ameliorate pressure ``wiggle" around contact discontinuity.
-When applied to three dimensional jet flow, this method is demonstrated to introduce less overall-dissipation.
+When applied to three dimensional free jet flow, this method is demonstrated to introduce less overall-dissipation.
 %Our ultimate goal is to apply this method to jet flow.
@@
 where, $p_{a b}^{\ast}$ and $\textbf{v}_{a b}^{\ast}$ are intermediate states derived from the interaction of particles $a$ and $b$.
-Inutsuka proposed this intermediate $\ast$ state be defined as the stationary state of the solution to a local 1-dimensional Riemann for particles $a$ and $b$.
+Inutsuka proposed this intermediate $\ast$ state be defined as the stationary state of the solution to a local one dimensional Riemann Problem for particles $a$ and $b$.
 That is, one rotates coordinates, reducing the particle interaction to one space dimension along the line connecting particle $a$ and particle $b$.
@@
 \subsection{The local 1D Riemann problem} \label{sec:RP-construction}
-The starred state is the solution to a local 1-dimensional Riemann problem.
+The starred state is the solution to a local one dimensional Riemann Problem.
 Given particles $a$ and $b$, rotate coordinates to establish a single spatial dimension along the line connecting the two particles, with direction
@@
 \end{eqnarray}
-[Aside: Cha \cite{cha2003implementations} proposed a second order accurate GSPH method by using
+[Aside:  \citet{inutsuka2002reformulation} proposed a second order accurate GSPH method by using
 a piecewise linear interpolation of the states. We do not pursue higher accuracy here, although the idea is straightforward to consider.]
@@
 The effect of equivalent numerical dissipation is first demonstrated by SPH simulation with different artificial viscosity coefficients.
-Then the equivalent numerical dissipations introduced by GSPH and RSPH are compared demonstrating that RSPH introduces less dissipation than GSPH.
-In 3D fee jet flow simulation, local Riemann problems are constructed in a piece wise constant manner for both GSPH and RSPH.
+Then the equivalent numerical dissipations introduced by GSPH and RSPH are compared demonstrating that RSPH introduces less dissipation than GSPH in 3D free jet flow simulation.
 
@@
 The second parts  shows a ``manmade" numerical oscillation, which backs up our analysis in the first part.
-
+The discussion below is valid for the SPH discretization adopted in this paper.
+Considering there are many variants of SPH method, the same conclusion does not apply to all variants of SPH method.
+The main purpose here is to explain where does the numerical oscillations come from in our tests.
+
+\subsection{Oscillation formation mechanism}
 There are several options \citep[][e.g.]{evrard1988beyond, hernquist1989treesph} for smoothing length $h$ in Eq.
@@
 Major discussions regarding the smoothing length are during 1980s to first several years of 1990s.
-In now days, taking $h=\frac{h_a + h_b}{2}$ is a commonly accepted practice.
-It is also adopted in this article.
-One big advantage is that such treatment can guarantee momentum and energy conservation given any paired particles are within compact support of each other's weighting function.
-However, it could also lead to numerical oscillation when applying the averaged smoothing length formulation in these scenarios with nonuniformly distributed smoothing length in space.
-Such numerical oscillation are usually either too small to observe or decays quickly due to sufficient (or too large) numerical dissipation.
-Such numerical oscillation is not fully aware of yet by the community.
+Taking $h=\frac{h_a + h_b}{2}$ has the advantage of guaranteeing momentum and energy conservation given any paired particles are within compact support of each other's weighting function.
+The averaged smoothing length is also adopted in this article.
+However, it could lead to numerical oscillation when applying the averaged smoothing length formulation in these scenarios with nonuniformly distributed smoothing length in space.
+Such numerical oscillation are usually either too small to observe or decays quickly due to sufficiently large numerical dissipation.
 In this section we explain how the numerical oscillations are formed.
@@
 \end{itemize} 
-This unphysical numerical representation of pressure gradient term could lead to numerical oscillation in numerical solution.
-Sharp changes in smoothing length can induce significant oscillation, which usually propagates into the computational domain and corrupts numerical solution.
-
+%This unphysical numerical representation of pressure gradient term could lead to numerical oscillation.
+% Sharp changes in smoothing length can induce significant oscillation, which usually propagates into the computational domain and corrupts numerical solution.
+
+\subsection{``Manmade"  Oscillation}
 To illustrate the formation and influence of such numerical oscillation, we intentionally create a situation of non-uniform smoothing length merely by assigning larger smoothing length to boundary ghost particles on left side in the 1D shock tube test (test2).
@@
 
-Adaptive smoothing length is now an essential component of SPH method.
-It naturely results to nonuniform smoothing length in space.
-Variation range of smoothing length would be especially larger for compressible flow.
+%May worthwhile to do one more test to demonstrate that if the smoothing length is constant cross the boundary, there will be no oscillation
+
+%May worthwhile to do more tests together with other variants of SPH method.
+
+Nonuniform smoothing length in space is not rare in SPH simulation, several things can contribute to nonuniform smoothing length, such as nonuniform density distribution, adaptive smoothing length and adaptive particle mass size.
 Fortunately, there are several factors counteracting against the numerical oscillation:
@@
 \item Well developed adaptive smoothing length algorithm usually guarantees more ``smoothing" change of smoothing length in space avoiding sharp change of smoothing length in space.
+\item Other variants of SPH formulation might not suffer from it at all.
 \end{itemize}
-So we do not think that the numerical oscillation is a challenging issue for SPH. The major motivation of the appendix is to show that 
+So we do not think that the numerical oscillation is a real challenging issue for SPH. The major motivation of the appendix is to show that 
 \begin{itemize}
 \item The numerical oscillation does exist commonly in SPH schemes. It is not something only for RSPH.
-\item Dissipation decays the oscillation, so numerical oscillation can serve as an indicator of dissipation.
+\item The SPH formulation adopted in this paper do introduce numerical oscillation and we can make use of the oscillation as an indicator for numerical dissipation.
 \end{itemize}
-\section*{References}
+\section*{}
  \bibliographystyle{elsarticle-num} 

### 2021-01-01 ebp-JCPManuscript.tex
reduce discussion regarding the order of accuracy and remove two pictures

@@
 Fig.
-\ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the density, velocity and pressure profiles for different SPH schemes.
-
-Due to symmetry of kernel function, estimation of density (Eq.
+\ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the density profiles for different SPH schemes.
+
+%Due to symmetry of kernel function, estimation of density (Eq.
 (\ref{eq:ns-sph-d})) in SPH can reach second order of accuracy if all particles distribute in space with uniform interval.
@@
 For SPH schemes that depend on solving Riemann problems, how the local Riemann problem is constructed also influence order of accuracy.
-For GSPH, the Riemann problem can be constructed in piece wise constant manner, piece wise linear manner or even higher order \citep{inutsuka2002reformulation}.
+%For GSPH, the Riemann problem can be constructed in piece wise constant manner, piece wise linear manner or even higher order \citep{inutsuka2002reformulation}.
 For RSPH, we can only consider to construct local Riemann problems in the piece wise constant manner.
@@
 This is a limitation of current RSPH compared with GSPH.
-With simper Riemann problem construction, RSPH is expected to be faster than GSPH adopting higher order Riemann problem construction.
+With simpler Riemann problem construction, RSPH is expected to be faster than GSPH adopting higher order Riemann problem construction.
 To compare RSPH and GSPH in a well-controlled manner, all GSPH tests presented in this paper are based on piece wise constant construction of local Riemann problems.
@@
 
-Since both RSPH and GSPH tests in this paper adopt the same manner for Riemann problem construction.
+%Since both RSPH and GSPH tests in this paper adopt the same manner for Riemann problem construction.
 We conclude that RSPH shows higher order of accuracy than GSPH providing both use the same Riemann problem construction.
 Compared with SPH, RSPH shows almost the same order of accuracy and level of error.
-
-\begin{figure}[H]
-    \centering
-    \begin{minipage}{.30\textwidth}
+ Compared with SPH and GSPH, RSPH shows almost the same order of accuracy and level of error as SPH and slightly higher order of accuracy than GSPH which adopts the same Riemann problem construction.
+
+\begin{figure}[H]
+    \centering
+    \begin{minipage}{.5\textwidth}
         \centering
@@
     \end{minipage}%
-    \begin{minipage}{.30 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-vel}
-    \end{minipage}%
-    \begin{minipage}{.39\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
-    \end{minipage}%  
+%    \begin{minipage}{.30 \textwidth}
+%        \centering
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-vel}
+%    \end{minipage}%
+%    \begin{minipage}{.39\textwidth}
+%        \centering
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
+%    \end{minipage}%  
     \caption{ $L_1$ norm of errors for 1D shock tube test (test1) for RSPH, standard SPH, GSPH using Roe Riemann solver and GSPH using HLLC Riemann Solver.

### 2021-01-01 ebp-JCPManuscript.tex
remove appendix B

@@
 Considering that all particles have the same particle mass, assigning smoothing length according to $h \propto \frac{m}{\rho}$ leads to discontinuity of smoothing length at the middle.
-Such discontinuity of smoothing length is the source of numerical oscillations, which usually decay fast and are not observed when there is sufficient dissipation.
+Such discontinuity of smoothing length can cause numerical oscillations, which usually decay fast and are not observed when there is sufficient dissipation.
 Such numerical oscillation becomes obvious when dissipation is less.
@@
 That is to say, how much the numerical oscillation is suppressed can indicate the amount of numerical dissipation introduced in each SPH scheme providing we are solving inviscid fluids (no physical dissipation).
-Refer Appendix B for more information regarding the numerical oscillation due to nonuniform smoothing length.
+% Refer Appendix B for more information regarding the numerical oscillation due to nonuniform smoothing length.
 Another indicator of numerical dissipation is how much the shock is smeared.
@@
 We did not adopt such strategy in our simulation.
-Due to less amount of dissipation, the numerical oscillations, which is due to nonuniform smoothing length as discussed in Appendix B, persist in all simulation results.
+Due to less amount of dissipation, the numerical oscillations
+%, which is due to nonuniform smoothing length as discussed in Appendix B,
+ persist in all simulation results.
 For the strong blast test and double shock test, such oscillation becomes more obvious than other tests, even though, the magnitude of fluctuations is within an acceptable range.
@@
 
-\section{Numerical oscillation due to non-uniform smoothing length in space}
-Our discussion in this appendix is divided into two parts.
+%\section{Numerical oscillation due to non-uniform smoothing length in space}
+%Our discussion in this appendix is divided into two parts.
 The first part explains the mechanism how the numerical oscillations are induced by non-uniform smoothing length in space.
@@
 
-\subsection{Oscillation formation mechanism}
-There are several options \citep[][e.g.]{evrard1988beyond, hernquist1989treesph} for smoothing length $h$ in Eq.
+%\subsection{Oscillation formation mechanism}
+%There are several options \citep[][e.g.]{evrard1988beyond, hernquist1989treesph} for smoothing length $h$ in Eq.
 (\ref{eq:ns-sph-d} - \ref{eq:ns-sph-v}).
@@
 In this section we explain how the numerical oscillations are formed.
-
-Recall that the kernel function of particle $a$ is required to be symmetric with respect to particle $a$.
+%
+%Recall that the kernel function of particle $a$ is required to be symmetric with respect to particle $a$.
 As a result, the gradient of kernel function at particle $a$ is anti-symmetric.
@@
 \ref{fig:dw-ha}.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.90 \textwidth ]{App-Figure/dw-ha}
-\caption{In this example, we consider two pairs of particles $(a, b_1)$ and $(a, b_2)$.
+%
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.90 \textwidth ]{App-Figure/dw-ha}
+%\caption{In this example, we consider two pairs of particles $(a, b_1)$ and $(a, b_2)$.
 For simplicity, we assume uniform distance between particles.
@@
 It is not anti-symmetric.
-We also assume pressure, density and particle mass of all particles are equal.
+%We also assume pressure, density and particle mass of all particles are equal.
 However, the pressure gradient term at particle $a$ in discretized formulation do not cancel out ( $-\dfrac{p_{b_1}}{\rho_{b_1}^2} \nabla_a w_{a b_1}\left(\frac{h_a+h_{b_1}}{2}\right) < -\dfrac{p_{b_2}}{\rho_{b_2}^2} \nabla_a w_{a b2}\left(\frac{h_a+h_{b_1}}{2}\right)$) when smoothing lengths are not equal ($h_{b1} \neq h_{b2}$).
@@
 As a consequence, $-\dfrac{p_{b_1}}{\rho_{b_1}^2} \nabla_a w_{a b_1}\left(h\right) = \dfrac{p_{b_2}}{\rho_{b_2}^2} \nabla_a w_{a b2}\left(h\right)$, the unphysical non-zero pressure gradient vanishes.}
-\label{fig:dw-ha}
-\end{figure}
-
-To summarize, two necessary conditions for generating unphysical numerical representation of pressure gradient terms are:
-\begin{itemize}
-\item Calculate smoothing length by averaging, for example, $h = \frac{h_a + h_b}{2}$.
-\item Smoothing length is nonuniform in space.
-\end{itemize} 
-%This unphysical numerical representation of pressure gradient term could lead to numerical oscillation.
-% Sharp changes in smoothing length can induce significant oscillation, which usually propagates into the computational domain and corrupts numerical solution.
-
-\subsection{``Manmade"  Oscillation}
-To illustrate the formation and influence of such numerical oscillation, we intentionally create a situation of non-uniform smoothing length merely by assigning larger smoothing length to boundary ghost particles on left side in the 1D shock tube test (test2).
+%\label{fig:dw-ha}
+%\end{figure}
+%
+%To summarize, two necessary conditions for generating unphysical numerical representation of pressure gradient terms are:
+%\begin{itemize}
+%\item Calculate smoothing length by averaging, for example, $h = \frac{h_a + h_b}{2}$.
+%\item Smoothing length is nonuniform in space.
+%\end{itemize} 
+%%This unphysical numerical representation of pressure gradient term could lead to numerical oscillation.
+%% Sharp changes in smoothing length can induce significant oscillation, which usually propagates into the computational domain and corrupts numerical solution.
+%
+%\subsection{``Manmade"  Oscillation}
+%To illustrate the formation and influence of such numerical oscillation, we intentionally create a situation of non-uniform smoothing length merely by assigning larger smoothing length to boundary ghost particles on left side in the 1D shock tube test (test2).
 As shown in the first plot of Fig.
@@
 In section \ref{sec:numericaltests}, we use magnitude of oscillation as an indirect indicator of numerical dissipation.
-
-In another test, based on the previous test with larger smoothing length for ghost particle on left boundary, we adopt $h = h_a$, instead of $h = \frac{h_a + h_b}{2}$.
+%
+%In another test, based on the previous test with larger smoothing length for ghost particle on left boundary, we adopt $h = h_a$, instead of $h = \frac{h_a + h_b}{2}$.
 The result is shown by Fig.
@@
 The oscillation is gotten rid of, which confirms that the averaged smoothing length is one of necessary conditions for the unphysical numerical representation of pressure gradient term.
-%Such perturbation would be created unintentionally in real implementation.
+%%Such perturbation would be created unintentionally in real implementation.
 The oscillation can actually be observed in 1D shock tube tests in many other papers, even though they are not as obvious as the one in Fig.
 \ref{fig:Perturbation-ME2}.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.90 \textwidth]{App-Figure/Perturbation-ME2}
-\caption{Plots of density for 1D shock tube test 2 at different time.
+%
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.90 \textwidth]{App-Figure/Perturbation-ME2}
+%\caption{Plots of density for 1D shock tube test 2 at different time.
 The test is simulated using classical SPH with $\alpha = 1$.
@@
 Both oscillations decays in time due to dissipation.}
-\label{fig:Perturbation-ME2}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.90 \textwidth]{App-Figure/Perturbation-ME0-tp1}
-\caption{Plots of density for 1D shock tube test 2 at $t=0.1s$.
+%\label{fig:Perturbation-ME2}
+%\end{figure}
+%
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.90 \textwidth]{App-Figure/Perturbation-ME0-tp1}
+%\caption{Plots of density for 1D shock tube test 2 at $t=0.1s$.
 The test is simulated using classical SPH with $\alpha = 1$.
@@
 No numerical perturbation generated near the left boundary.}
-\label{fig:Perturbation-ME0-tp1}
-\end{figure}
-
-%May worthwhile to do one more test to demonstrate that if the smoothing length is constant cross the boundary, there will be no oscillation
-
-%May worthwhile to do more tests together with other variants of SPH method.
-
-Nonuniform smoothing length in space is not rare in SPH simulation, several things can contribute to nonuniform smoothing length, such as nonuniform density distribution, adaptive smoothing length and adaptive particle mass size.
+%\label{fig:Perturbation-ME0-tp1}
+%\end{figure}
+%
+%%May worthwhile to do one more test to demonstrate that if the smoothing length is constant cross the boundary, there will be no oscillation --> Easy to prove
+%%And another test using constant smoothing length all across the domain, but that means I would need to use different particle mass to make sure approximation of density equals to the physical density.
+%
+%%May worthwhile to do more tests together with other variants of SPH method. 
+%
+%Nonuniform smoothing length in space is not rare in SPH simulation, several things can contribute to nonuniform smoothing length, such as nonuniform density distribution, adaptive smoothing length and adaptive particle mass size.
 Fortunately, there are several factors counteracting against the numerical oscillation:
-\begin{itemize}
-\item Numerical dissipation decays such numerical oscillation preventing accumulation of oscillation magnitude.
-\item For incompressible flow or weakly compressible flow, smoothing length only varies in a small range.
-\item Well developed adaptive smoothing length algorithm usually guarantees more ``smoothing" change of smoothing length in space avoiding sharp change of smoothing length in space.
-\item Other variants of SPH formulation might not suffer from it at all.
-\end{itemize}
-So we do not think that the numerical oscillation is a real challenging issue for SPH. The major motivation of the appendix is to show that 
-\begin{itemize}
-\item The numerical oscillation does exist commonly in SPH schemes. It is not something only for RSPH.
-\item The SPH formulation adopted in this paper do introduce numerical oscillation and we can make use of the oscillation as an indicator for numerical dissipation.
-\end{itemize}
+%\begin{itemize}
+%\item Numerical dissipation decays such numerical oscillation preventing accumulation of oscillation magnitude.
+%\item For incompressible flow or weakly compressible flow, smoothing length only varies in a small range.
+%\item Well developed adaptive smoothing length algorithm usually guarantees more ``smoothing" change of smoothing length in space avoiding sharp change of smoothing length in space.
+%\item Other variants of SPH formulation might not suffer from it at all.
+%\end{itemize}
+%So we do not think that the numerical oscillation is a real challenging issue for SPH. The major motivation of the appendix is to show that 
+%\begin{itemize}
+%\item The numerical oscillation does exist commonly in SPH schemes. It is not something only for RSPH.
+%\item The SPH formulation adopted in this paper do introduce numerical oscillation and we can make use of the oscillation as an indicator for numerical dissipation.
+%\end{itemize}
 \section*{}

### 2021-01-12 CPMManuscript.tex
adopt cpm template

--- 2021-01-01 ebp-JCPManuscript.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+%\begin{filecontents*}{example.eps}
+%%!PS-Adobe-3.0 EPSF-3.0
+%%%BoundingBox: 19 19 221 221
+%%%CreationDate: Mon Sep 29 1997
+%%%Creator: programmed by hand (JK)
+%%%EndComments
+%gsave
+%newpath
+%  20 20 moveto
+%  20 220 lineto
+%  220 220 lineto
+%  220 20 lineto
+%closepath
+%2 setlinewidth
+%gsave
+%  .4 setgray fill
+%grestore
+%stroke
+%grestore
+%\end{filecontents*}
 %%
-%% Copyright 2007-2019 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-
-\documentclass[preprint,12pt,authoryear]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times,authoryear]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
-%% \documentclass[final,3p,times,authoryear]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
-%% \documentclass[final,5p,times,authoryear]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-% package added by zhixuan
+\RequirePackage{fix-cm}
+%
+\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{graphicx}
+%
+\usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
 \usepackage{amsmath}
 \usepackage{float}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-\journal{Computer Methods in Applied Mechanics and Engineering}
+%\usepackage{natbib}
+\usepackage[square,sort,comma,numbers]{natbib}
+\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+ \journalname{Computational Particle Mechanicsl}
+%
 \begin{document}
-\begin{frontmatter}
-\title{A Random Choice SPH Scheme with Adaptive Viscosity}
-%\tnotetext[mytitlenote]{Can add  title note here}
-%% Group authors per affiliation:
-\author{Zhixuan Cao}
-\ead{zhixuan.cao@ansys.com}
-\address{Fluids Business Unit, Ansys Inc., Lebanon, NH, 03766, USA}
-\author{Abani Patra \fnref{mycorrespondingauthor}}
-\ead{abani.patra@tufts.edu}
-\address{Department of Computer Science and Department of Mathematics, Tufts University, Medford, MA, 02153, USA}
-\author{E. Bruce Pitman}
-\ead{pitman@buffalo.edu}
-\address{Department of Materials Design and Innovation, The State University of New York at Buffalo, Amherst, NY, 14260, USA}
-%\fntext[myfootnote]{Since 1880.}
-%% or include affiliations in footnotes:
-%\author[mymainaddress,mysecondaryaddress]%{Elsevier Inc}
-%\ead[url]{www.elsevier.com}
-%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-%\cortext[mycorrespondingauthor]{abani@buffalo.edu}
-%\ead{abani@buffalo.edu}
-%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
-%\address[mysecondaryaddress]{360 Park Avenue South, New York}
+
+\title{A Random Choice SPH Scheme with Adaptive Viscosity%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. General acknowledgments should be placed at the end of the article.}
+}
+%\subtitle{Do you have a subtitle?\\ If so, write it here}
+
+%\titlerunning{Short form of title}        % if too long for running head
+
+\author{First Author         \and
+        Second Author %etc.
+}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{F. Author \at
+              first address \\
+              Tel.: +123-45-678910\\
+              Fax: +123-45-678910\\
+              \email{fauthor@example.com}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           S. Author \at
+              second address
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
 
@@
 The combination of the SPH and RCM together with a shear viscosity produces nicely resolved jet profiles.
-
+\keywords{Smoothed Particle Hydrodynamics (SPH) \and  Random Choice Method (RCM) \and Riemann Solver\and Artificial viscosity \and Hyperbolic PDEs}
+% \PACS{PACS code1 \and PACS code2 \and more}
+% \subclass{MSC code1 \and MSC code2 \and more}
 \end{abstract}
-\begin{keyword}
-Smoothed Particle Hydrodynamics (SPH), Random Choice Method (RCM), Riemann Solver, Artificial viscosity, Hyperbolic PDEs
-\end{keyword}
-\end{frontmatter}
 
 \section{Introduction}
+\label{intro}
 Smoothed particle hydrodynamics (SPH) \citep{gingold1977smoothed,lucy1977numerical} is a mesh-free particle method based on a Lagrangian formulation of the governing equations of motion.
@@
 Various methods have been introduced to tune the artificial viscosity, turning it on and off for particular wave features.
-However, tuning switches cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist (see, for example, \cite{borgani2012hydrodynamic,flebbe1994smoothed,morris1997switch, dolag2005turbulent,cullen2010inviscid,sigalotti2008adaptive,puri2014comparison}).
+However, tuning switches cannot properly accommodate every kind of wave that might arise, and spurious effects and unphysical damping persist (see, for example, \citep{borgani2012hydrodynamic,flebbe1994smoothed,morris1997switch, dolag2005turbulent,cullen2010inviscid,sigalotti2008adaptive,puri2014comparison}).
 
@@
 \citet{chorin1976random} developed the RCM into a practical computational method for solutions of the Euler equations in one space dimension.
-This approach was later extended to two dimensions \cite{chorinporousmedium}.
+This approach was later extended to two dimensions \citep{chorinporousmedium}.
 Others further refined the random choice method \citep{sod1977numerical,concus1979numerical,colella1982glimm, freistuhler1992numerical,toro2013riemann}.
@@
 There are many approximate Riemann solvers available \citep{rider1994review, luo2004computation, puri2014approximate}.
-For purposes here we adopt the HLLC solver, which decomposes the Riemann solution into 3 waves, including a (possible) contact discontinuity \cite{toro1994restoration}.
+For purposes here we adopt the HLLC solver, which decomposes the Riemann solution into 3 waves, including a (possible) contact discontinuity \citep{toro1994restoration}.
 More specifically, we adopt the HLLC formulation proposed by \citet{luo2004computation}.
@@
 Fig.
-\ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the density profiles for different SPH schemes.
+\ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the pressure profiles for different SPH schemes.
 
@@
     \centering
-    \begin{minipage}{.5\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-des}
-    \end{minipage}%
+%    \begin{minipage}{.5\textwidth}
+%        \centering
+%        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-des}
+%    \end{minipage}%
 %    \begin{minipage}{.30 \textwidth}
@@
 %    \end{minipage}%
-%    \begin{minipage}{.39\textwidth}
-%        \centering
-%        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
-%    \end{minipage}%  
+    \begin{minipage}{.70\textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
+    \end{minipage}%  
     \caption{ $L_1$ norm of errors for 1D shock tube test (test1) for RSPH, standard SPH, GSPH using Roe Riemann solver and GSPH using HLLC Riemann Solver.
@@
 
-\section*{Acknowledgements}
+\section{Acknowledgements}
 3D simulations reported here were performed at the Center for Computational Research (CCR) at the University at Buffalo.
@@
 \citet{concus1979numerical} extended these ideas.
-In his thesis, \citet{colella1978analysis} examined the van der Corput sequence as a sampling procedure (see also \cite{colella1982glimm}).
+In his thesis, \citet{colella1978analysis} examined the van der Corput sequence as a sampling procedure (see also \citep{colella1982glimm}).
 
@@
 Examining dissipation effects for wide classes of finite difference/finite volume methods 
-shows a similar phenomena (see, for example, \cite{warming1974modified}).
+shows a similar phenomena (see, for example, \citep{warming1974modified}).
 
@@
 \section*{}
- \bibliographystyle{elsarticle-num} 
-\bibliography{Reference}
+
+%\begin{acknowledgements}
+%If you'd like to thank anyone, place your comments here
+%and remove the percent signs.
+%\end{acknowledgements}
+
+% Authors must disclose all relationships or interests that 
+% could have direct or potential influence or impart bias on 
+% the work: 
+%
+% \section*{Conflict of interest}
+%
+% The authors declare that they have no conflict of interest.
+
+% BibTeX users please use one of
+\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+\bibliography {Reference}   % name your BibTeX data base
+
+%% Non-BibTeX users please use
+%\begin{thebibliography}{}
+%%
+%% and use \bibitem to create references. Consult the Instructions
+%% for authors for reference list style.
+%%
+%\bibitem{RefJ}
+%% Format for Journal Reference
+%Author, Article title, Journal, Volume, page numbers (year)
+%% Format for books
+%\bibitem{RefB}
+%Author, Book title, page numbers. Publisher, place (year)
+%% etc
+%\end{thebibliography}
 
 \end{document}
+% end of file template.tex

### 2021-01-13 CPMManuscript.tex
add author

@@
 
-\author{First Author         \and
-        Second Author %etc.
+\author{Zhixuan Cao \and Abani Patra \and  E. Bruce Pitman %etc.
 }
@@
 
-\institute{F. Author \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{fauthor@example.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
+\institute{Zhixuan Cao \at
+             MAE department, SUNY Buffalo, Buffalo, NY, USA
              \and
-           S. Author \at
-              second address
+             Abani Patra \at
+	  MAE department, SUNY Buffalo, Buffalo, NY, USA \\
+	  \emph{Present address: Robinson Hall, Room 258, 200 College Avenue, Medford, MA, UAS } \\
+	 \email{abani.patra@tufts.edu} 
+	 \and
+	  E. Bruce Pitman \at
+            Department of Materials Design and Innovation, SUNY Buffalo, Buffalo, NY, USA
 }

### 2021-01-14 CPMManuscript.tex
make reference not sorted by author name
tidy up

@@
 %\usepackage{natbib}
-\usepackage[square,sort,comma,numbers]{natbib}
+\usepackage[square, comma, numbers, sort&compress]{natbib} 
 \usepackage{latexsym}
@@
 
-Section \ref{standard-sph} provides a brief review of standard SPH. Section \ref{sec:GSPH-method} shows how the GSPH method is defined. The RSPH method is defined in Section \ref{sec:RSPH-method}.
+This paper is organized as the following.
+Section \ref{standard-sph} provides a brief review of standard SPH.
+Section \ref{sec:GSPH-method} shows how the GSPH method is defined.
+The RSPH method is defined in Section \ref{sec:RSPH-method}.
 One dimensional tests are shown in Section \ref{sec:numericaltests}, followed by the jet flow example in Section \ref{jet}.
@@
 
+It is more common for GSPH to construct local Riemann problems in a piece wise linear manner.
+Fig.
+\ref{fig:RCM-Sod-GSPH2} RSPH and piece wise linear GSPH.
+As expected, when using higer order local Riemann problem construction, better solutions are obtained.
+Adopting piece wise linear Riemann problem construction reduces the amount of dissipation and hence smearing of the shocks.
+RSPH, even though is based on piece wise constant Riemann problem construction, still introduces less numerical dissipation than GSPH using piece wise linear Riemann problem construction.
+The piece wise linear Riemann problem construction requires calculation of first order derivatives while the piece wise constant manner does not.
+That is to say, the piece wise constant manner is computationally less expensive than the piece wise linear manner.
+As a consequence, RSPH would be, at least a little bit, computationally less expensive than piece wise linear GSPH.
+
 \begin{figure}[H]
@@
 
-It is more common for GSPH to construct local Riemann problems in a piece wise linear manner.
-Fig.
-\ref{fig:RCM-Sod-GSPH2} RSPH and piece wise linear GSPH.
-As expected, when using higer order local Riemann problem construction, better solutions are obtained.
-Adopting piece wise linear Riemann problem construction reduces the amount of dissipation and hence smearing of the shocks.
-RSPH, even though is based on piece wise constant Riemann problem construction, still introduces less numerical dissipation than GSPH using piece wise linear Riemann problem construction.
-The piece wise linear Riemann problem construction requires calculation of first order derivatives while the piece wise constant manner does not.
-That is to say, the piece wise constant manner is computationally less expensive than the piece wise linear manner.
-As a consequence, RSPH would be, at least a little bit, computationally less expensive than piece wise linear GSPH.
-
 \subsection{Accuracy tests}
@@
 
-\begin{figure}[H]
-    \centering
-    \begin{minipage}[t]{.325 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t1p5-cutView}
-    \end{minipage}%
-    \begin{minipage}[t]{.325\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t1p5-cutView}
-    \end{minipage}%
-    \\
-    \centering
-    \begin{minipage}[t]{.325 \textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t3-cutView}
-    \end{minipage}%
-    \begin{minipage}[t]{.325\textwidth}
-        \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t3-cutView}
-    \end{minipage}%
-    \caption{Simulation results of free jet flow by GSPH and RSPH.
-These pictures are front view of a slice of the domain cut by two planes parallel to $x-z$ plane at $y=-9$ and $y=9$.
-Pictures on the left side are for GSPH while those on the right side are for RSPH.
-Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.
-Pictures on the first row are corresponding to $t=1.5s$ while pictures on the second row are for $t=3.0 s$}
-    \label{fig:free-jet-comparison}
-\end{figure}
-
 Figure \ref{fig:free-jet-SPH-comparison} shows simulation results of the free jet flow by SPH with different artificial viscosity coefficients.
@@
 
+\begin{figure}[H]
+    \centering
+    \begin{minipage}[t]{.325 \textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t1p5-cutView}
+    \end{minipage}%
+    \begin{minipage}[t]{.325\textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t1p5-cutView}
+    \end{minipage}%
+    \\
+    \centering
+    \begin{minipage}[t]{.325 \textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t3-cutView}
+    \end{minipage}%
+    \begin{minipage}[t]{.325\textwidth}
+        \centering
+        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t3-cutView}
+    \end{minipage}%
+    \caption{Simulation results of free jet flow by GSPH and RSPH.
+These pictures are front view of a slice of the domain cut by two planes parallel to $x-z$ plane at $y=-9$ and $y=9$.
+Pictures on the left side are for GSPH while those on the right side are for RSPH.
+Red particles in pictures are particles erupted from the nozzle while blues are ambient fluids particles.
+Pictures on the first row are corresponding to $t=1.5s$ while pictures on the second row are for $t=3.0 s$}
+    \label{fig:free-jet-comparison}
+\end{figure}
+
 We compare RSPH with GSPH in terms of overall damping effects in Fig.
@@
 
-\appendix
-\section{Glimm\rq{}s Scheme}
+%\appendix
+\section{Appendix -- Glimm\rq{}s Scheme}
 In \citep{glimm1965solutions}, Glimm proved the existence  of solutions to a  $2\times2$ 
@@
 % BibTeX users please use one of
-\bibliographystyle{spbasic}      % basic style, author-year citations
+\bibliographystyle{spbasic_unsrt}      % basic style, author-year citations
 %\bibliographystyle{spmpsci}      % mathematics and physical sciences

### 2021-01-14 CPMManuscript.tex
rename fig files

@@
     \center
-	\includegraphics[width=0.5 \textwidth]{./Figures/RSPH-GSPH}
+	\includegraphics[width=0.5 \textwidth]{./Figures/Fig1}
     \caption{Evaluating of the starred state for RSPH and GSPH implementations.
@@
         \centering a)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-rho}
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Fig2-a}
     \end{minipage}%
@@
         \centering b)
-        \includegraphics[width=0.99 \textwidth,height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-v}
+        \includegraphics[width=0.99 \textwidth,height=0.5780 \textwidth]{./Figures/Fig2-b}
     \end{minipage}% 
@@
         \centering c)
-        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-rho-zoom}
+        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Fig2-c}
     \end{minipage}% 
@@
         \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-v-zoom}    
+        \includegraphics[width= 0.8174 \textwidth, height=0.5780 \textwidth]{./Figures/Fig2-d}    
         \end{flushleft}
@@
         \centering a)
-        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-e}
+        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Fig3-a}
     \end{minipage}%
@@
         \centering b)
-        \includegraphics[width=0.99 \textwidth,height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-p}
+        \includegraphics[width=0.99 \textwidth,height=0.5780 \textwidth]{./Figures/Fig3-b}
     \end{minipage}% 
@@
         \centering c)
-        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/RCM-Sod-SPH-alf-e-zoom}
+        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Fig3-c}
     \end{minipage}% 
@@
         \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.5780 \textwidth]{./Figures/RCM-Sod-SPH-alf-p-zoom}    
+        \includegraphics[width= 0.8174 \textwidth, height=0.5780 \textwidth]{./Figures/Fig3-d}    
         \end{flushleft}
@@
         \centering a)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-rho}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Fig4-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-v}    
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/Fig4-b}    
         \end{flushleft}
@@
         \centering c)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH-compare-e}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Fig4-c}
     \end{minipage}%
@@
         \centering d)
-        \includegraphics[width=0.99 \textwidth,height=0.4954\textwidth]{./Figures/RCM-Sod-GSPH-compare-p}
+        \includegraphics[width=0.99 \textwidth,height=0.4954\textwidth]{./Figures/Fig4-d}
     \end{minipage}% 
@@
         \centering e)
-        \includegraphics[width= 0.99 \textwidth, height=0.625 \textwidth]{./Figures/RCM-Sod-GSPH-compare-p-zoom}    
+        \includegraphics[width= 0.99 \textwidth, height=0.625 \textwidth]{./Figures/Fig4-e}    
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH-compare-v-zoom}    
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/Fig4-f}    
         \end{flushleft}
@@
         \centering a)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-rho}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Fig5-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-v}    
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/Fig5-b}    
         \end{flushleft}
@@
         \centering c)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-e}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Fig5-c}
     \end{minipage}%
@@
         \centering d)
-        \includegraphics[width=0.99 \textwidth,height=0.4954\textwidth]{./Figures/RCM-Sod-GSPH2-compare-p}
+        \includegraphics[width=0.99 \textwidth,height=0.4954\textwidth]{./Figures/Fig5-d}
     \end{minipage}% 
@@
         \centering e)
-        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/RCM-Sod-GSPH2-compare-rho-zoom}
+        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Fig5-e}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/RCM-Sod-GSPH2-compare-v-zoom}    
+        \includegraphics[width= 0.8174 \textwidth, height=0.4954 \textwidth]{./Figures/Fig5-f}    
         \end{flushleft}
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig6}
     \end{minipage}%  
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GRod-RCM-rho}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig7-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width=0.8024 \textwidth]{./Figures/GRod-RCM-rho}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Fig7-b}
         \end{flushleft}
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GRod-RCM-e}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig7-c}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GRod-RCM-p}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig7-d}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Dexp-RCM-rho}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig8-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width=0.8024 \textwidth]{./Figures/Dexp-RCM-v}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Fig8-b}
         \end{flushleft}
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Dexp-RCM-e}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig8-c}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Dexp-RCM-p}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig8-d}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Dshock-RCM-rho-Rp6}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig9-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width=0.8024 \textwidth]{./Figures/Dshock-RCM-v-Rp6}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Fig9-b}
         \end{flushleft}
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Dshock-RCM-e-Rp6}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig9-c}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Dshock-RCM-p-Rp6}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig9-d}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen-RCM-rho-Adpt1}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig10-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width=0.8024 \textwidth]{./Figures/Sjogreen-RCM-v-Adpt1}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Fig10-b}
         \end{flushleft}
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen-RCM-e-Adpt1}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig10-c}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/Sjogreen-RCM-p-Adpt1}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig10-d}
     \end{minipage}% 
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/StrBlst-RCM-rho-Rp3}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig11-a}
     \end{minipage}%
@@
         \begin{flushleft}
-        \includegraphics[width=0.8024 \textwidth]{./Figures/StrBlst-RCM-v-Rp3}
+        \includegraphics[width=0.8024 \textwidth]{./Figures/Fig11-b}
         \end{flushleft}
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/StrBlst-RCM-e-Rp3}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig11-c}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/StrBlst-RCM-p-Rp3}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig11-d}
     \end{minipage}% 
@@
    \centering
-   \includegraphics[width=0.95 \textwidth]{./Figures/SPH-3D-jet}
+   \includegraphics[width=0.95 \textwidth]{./Figures/Fig12}
    \caption{Free jet flow simulation results at $t=3.0 s$ by SPH using different artificial viscosity coefficients.
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t1p5-cutView}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig13-a}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t1p5-cutView}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig13-b}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/GSPH-HLLC-t3-cutView}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig13-c}
     \end{minipage}%
@@
         \centering
-        \includegraphics[width=0.99 \textwidth]{./Figures/RSPH-t3-cutView}
+        \includegraphics[width=0.99 \textwidth]{./Figures/Fig13-d}
     \end{minipage}%
